### 2015-01-16 preamble.tex
initial commit: skeletal draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  PREAMBLE: sets up compiler modes, loads packages, defines macros, etc
%  Steve Rodney, 2012
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
% COMPILER MODES
%%%%%%%%%%%%%%%%%%%%

%% Set default compiler modes 
%% (these will be overridden by the -options.tex  file below, if it exists)

% Manuscript mode : 
%  True  : single-column, double-spaced, markup-ready style (with comments)
%  False : print in two-col single-space publication-ready style (no comments)
\newif\ifms
\msfalse

% Grayscale  mode : use grayscale figures when available
\newif{\ifgrayscale}
\grayscalefalse

% Changetext mode : highlight modified text in bold blue font
\newif{\ifchangetext}
\changetextfalse

%% Read in the -options.tex file (generated by the Makefile)
%%  to set the compile-mode options
\InputIfFileExists{\jobname-options}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% manuscript mode settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifms
  \documentclass[manuscript]{aastex}
  \usepackage{natbib,amsmath,verbatim}
  \received{}
  \revised{}
  \accepted{}
  \citestyle{aa}
  \newcommand{\cmt}[1]{\textcolor{red}{#1}}   % Red text  for printing comments 
\else
  %\documentclass[12pt,ms,iop]{emulateapj}
  \documentclass[revtex4,iop]{emulateapj}
  \font\sevenrm=cmr7 
  \citestyle{aa} 
  \newcommand{\cmt}[1]{}
  %\slugcomment{submitted to ApJ} 
  %\journalinfo{astro-ph/xxxxxx}  % top left corner of first page.
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% changetext  mode settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifchangetext
  % Changed text is highlighted in bold, blue font 
  \newcommand{\change}[1]{{\bf \textcolor{blue}{#1}}}
\else
  % Changed text is indistinguishable
  \newcommand{\change}[1]{#1}
\fi

%%%%%%%%%%%%%%%%%%%%
% PACKAGES INCLUDED
%%%%%%%%%%%%%%%%%%%%
\usepackage{natbib}   % reference citations and bibliography
\usepackage{amsmath}  % extended math symbols
\usepackage{verbatim} % verbatim text formatting
\usepackage{enumerate}% enumerated lists
\usepackage{amssymb}  % extended symbols lib
%\usepackage{url}      % url text formatting
\usepackage{hyperref}      % url text formatting
\usepackage[usenames]{color}  % colored text
%\usepackage{multirow}  % muti-row table cells
%\usepackage{amsmath}  % extended equations lib (split)
%\usepackage{mathrsfs} % extended math fonts (mathscr)
%\usepackage{paralist} % inline enumeration (for Table ref lists)
%\usepackage{authblk}
\usepackage{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PDF mode settings : Auto-select eps or pdf figures 
% based  on the compiler used (i.e. latex vs pdflatex)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifx\pdfoutput\undefined
  \pdffalse
  \DeclareGraphicsExtensions{.eps,.ps}
\else
  \ifnum\pdfoutput=1
    % \pdftrue
    \DeclareGraphicsExtensions{.pdf,.png,.jpg}
  \else
    % \pdffalse
    \DeclareGraphicsExtensions{.eps,.ps}
  \fi
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AUTHOR-DEFINED MACROS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Paper aliases 
\defcitealias{Patel:2014}{P14}
\def\P14{\citetalias{Patel:2014}}

\def\tomas{HFF14Tom}

% General purpose usefulness:
\newcommand{\etal}{{et al.~}}                                             
\def\eg{{e.g.}}
\def\ie{{i.e.}}
\def\etc{{etc.}}
\newcommand{\lta}{\lesssim}                                               
\newcommand{\gta}{\gtrsim}                                                
\newcommand{\gt}{\gtsim}
\newcommand{\kms}{\,\rm km\,s^{-1}}

%\def\pmstat{ \ensuremath{ \substack{ \resizebox{0.7em}{0.5em}{$\pm$} \\ \resizebox{0.7em}{0.2em}{stat}} } }
\def\pmstat{\ensuremath{\substack{\pm \\ \mbox{\scalebox{0.45}{stat}} } } }
\def\pmsyst{\ensuremath{\substack{\pm \\ \mbox{\scalebox{0.45}{syst}} } } }

% Cosmology:
\def\Om{\ensuremath{\Omega_{\rm m}}}
\def\Ot{\ensuremath{\Omega_{\rm tot}}}
\def\Ob{\ensuremath{\Omega_{\rm b}}}
\def\OL{\ensuremath{\Omega_{\Lambda}}}
\def\Ok{\ensuremath{\Omega_{\rm k}}}
\def\om{\ensuremath{\omega_{\rm m}}}
\def\ob{\ensuremath{\omega_{\rm b}}}
\def\wo{\ensuremath{w_0}}
\def\wa{\ensuremath{w_{\rm a}}}
\def\lcdm{$\Lambda$CDM}
\def\LCDM{$\Lambda$CDM}
\def\wcdm{$w$CDM}
\def\Ho{\ensuremath{H_0}}
\def\DA{\ensuremath{D_A}}
\def\DL{\ensuremath{D_L}}

% Astronomy:
\def\arcsec{\ensuremath{^{\prime\prime}}} 
\def\kms{\ensuremath{{\rm km s}^{-1}}}
\def\hgpcq{\mbox{$h^{-3}$Gpc$^3$}}
\def\hmpcq{\mbox{$h^{-3}$Mpc$^3$}}
\def\perhmpcq{\mbox{$h^{3}$Mpc$^{-3}$}}
\def\hmpc{\mbox{$h^{-1}$Mpc}}
\def\hmpci{\mbox{$h$\,Mpc$^{-1}$}}
\def\mpc{\mbox{Mpc}}
\def\mpci{\mbox{Mpc$^{-1}$}}
\def\mpcq{\mbox{Mpc$^{-3}$}}
\def\Msun{\mbox{M$_{\odot}$}}
\def\Av{\mbox{$A_V$}}
\def\Rv{\mbox{$R_V$}}

% Supernovae : 
\newcommand{\CCSN}{CC\,SN}
\newcommand{\CCSNe}{CC\,SNe}
\newcommand{\TNSN}{TN\,SN}
\newcommand{\TNSNe}{TN\,SNe}
\newcommand{\SNIa}{SN\,Ia}
\newcommand{\SNeIa}{SNe\,Ia}
\newcommand{\SNRz}{SNR($z$)}
\def\Mch{\mbox{M$_{\rm Ch}$}}
\def\Ni{\ensuremath{^{56}\mbox{Ni}}}
\newcommand{\dmfifteen}{\ensuremath{\Delta\mbox{m}_{15}}}
\newcommand{\deltamfifteen}{\ensuremath{\Delta\mbox{m}_{15}}}

% Missions:
\def\Hubble{{\it Hubble}}
\def\Hubbles{{\it Hubble's}}
\def\Spitzer{{\it Spitzer}}
\def\Chandra{{\it Chandra}}
\def\Herschel{{\it Herschel}}
\def\XMM{{\it XMM}}

% Institutions
\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, Baltimore, MD 21218.}
\newcommand{\elsewhere}{St. Elsewhere University.}
\newcommand{\STScI}{Space Telescope Science Institute, Baltimore, MD 21218.}
\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411.}
\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521.}
\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101.}
\newcommand{\Copenhagen}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark.}
\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721.}
\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064.}
\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556.}
\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel.}
\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854.}
\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138.}
\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Page Setup 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifms
\else
  \renewcommand{\topfraction}{0.9}
  \renewcommand{\bottomfraction}{0.9}
  \renewcommand{\textfraction}{0.1}
  \renewcommand{\floatpagefraction}{0.9}
  \renewcommand{\dbltopfraction}{0.9}
  \renewcommand{\dblfloatpagefraction}{0.9}
\fi

### 2015-01-16 snTomas.tex
initial commit: skeletal draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  PREAMBLE: sets up compiler modes, loads packages, defines macros, etc
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{preamble}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN DOCUMENT TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\shorttitle{A \SNIa Behind Abell 2744}
\shortauthors{Rodney et al.}

\begin{document}

\title{Illuminating a Dark Lens : A Type Ia Supernova Magnified by Galaxy Cluster Abell 2744}

\ifms
    \author{Steven A.~Rodney\altaffilmark{1}}
    \author{\etal\altaffilmark{2}}

    \altaffiltext{1}{\JHU}
    \altaffiltext{1}{\elsewhere}
\else 
    \author{
      Steven~A.~Rodney\altaffilmark{1},
      \etal\altaffilmark{2}
    }
    \altaffiltext{1}{\JHU}
    \altaffiltext{2}{\elsewhere}
\fi

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.33$
behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
projected separation from the cluster core of $\sim$40\arcsec, closer
than any other cluster-lensed \SNIa.  As such, it provides the first
opportunity to confront gravitational lens models of galaxy clusters
with the direct measurement of an absolute magnification at the edge
of the strong-lensing region.  We derive a tightly constrained measure
of the peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is $0.71\pm0.12$ magnitudes brighter than unlensed \SNeIa\ at similar
redshift, implying a lensing magnification of $\mu_{\rm
obs}=1.9\pm0.2$.  Predicted magnifications from 7 independent groups
are systematically biased to higher values, with a mean of $\mu_{\rm
mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  The most
significant discrepancies arise from models with a strict ``light
traces mass'' assumption.  We evaluate possible causes for this bias,
including variation of the mass-to-light ratio in the nearest cluster
member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
any single cluster could provide a robust evaluation of systematic
biases in lens models.  Until such a sample exists, it is advisable to
increase the estimated uncertainty of any predicted magnification
by an amount comparable to the dispersion from all available lens
models.

\end{abstract}

\keywords{ supernovae: general }

\section{Introduction}
\label{sec:Introduction}

Massive galaxy clusters can be used as cosmic telescopes to magnify
distant background objects through gravitational lensing.  This can
substantially increase the reach of deep imaging surveys, and has
recently been used to discover candidate proto-galaxies formed in the
first Gyr after the Big
Bang \citep{Zheng:2012,Coe:2013,} 
\textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}

Lensed SNe have been discovered
\textcolor{red}{\citep{Goobar:2009,Riehm:2011,Patel:2014,Nordin:2014,}}

\section{Discovery and Follow-up}
\label{sec:DiscoveryAndFollowUp}

\section{Spectrum}
\label{sec:Spectrum}

\section{Light Curve}
\label{sec:LightCurve}

\textcolor{red}{Light curve fitting with MLCS2k2}

\begin{figure*}
\begin{center}
\includegraphics[width=0.49\textwidth]{FIG/lcfit_mlcs2k2_ABmag}
\includegraphics[width=0.49\textwidth]{FIG/specfit_11fe_t-3_z131}
\caption{ {\it (Left)} Light curve fit using MLCS2k2. 
{\it (Right)} Spectral template match to the HST ACS G800L SN
spectrum.  Assuming minimal reddening, the best-fit template is from
SN 2011fe at $z=1.31$ and $t=-3$ rest-frame days before peak
brightness.  Allowing a correction for the broad SED shape using
3rd-order polynomials, the best match is from SN 2012cg at $z=1.31$
and $t=+3 days$.
\label{fig:mlcsfit} }
\end{center}
\end{figure*}

\section{Lensing Magnification}
\label{sec:LensingMagnification}

\subsection{Direct Magnification Measurement}
\label{sec:DirectMagnificationMeasurement}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/magnification_measurement}
\caption{ Deriving the magnification from comparison to field SN
\label{fig:magmeasure} }
\end{center}
\end{figure}

\subsection{Comparison to Model Predictions}
\label{sec:ComparisonToModelPredictions}

1) All of the lens models predict a higher magnification than we observe, some with discrepancies >5 sigma.  This suggests a systematic bias inherent to all the models -- at least for this particular line of sight.

2) the addition of new lensing constraints from the HFF data does not reduce the tension.  From both of the most recent models (Jauzac+ 2014 and Lam+ 2014) the predicted magnification is still significantly higher than the observed.

3) The pre-HFF models that come closest to matching the observed magnification are the Zitrin-NFW and Merten models (also the Williams model, though it has very large uncertainties).  Those happen to be two models that relax or remove the assumption of light-traces-mass.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/lensing_test}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models.
\label{fig:lensingtest} }
\end{center}
\end{figure}

\section{Discussion}

Possible sources for the bias.

Implications for the systematic error budget of high-z lenses.

Proposal for a survey to build a bigger sample : HST GO, Snapshot, ground-based.

\bigskip

{\bf Acknowledgments:}

We are very pleased to thank the Hubble Frontier Fields team at STScI
for their substantial efforts to make the HFF program successful.  In
particular, thanks are due to Matt Mountain for the allocation of
discretionary orbits for the HFF program; to Jennifer Lotz, Norman
Grogin and Patricia Royle for accommodations in strategy and
implementation to make the FrontierSN program possible; and to Dan Coe
for curating the excellent and accessible lens model comparison tools.
We also must thank the CLASH team, led by Marc Postman, for
observations, catalogs, and high level science products that were of
significant value for this analysis.

Financial support for this work was provided by NASA through grants
HST-HF-51312 and HST-GO-13386 from the Space Telescope
Science Institute, which is operated by Associated Universities for
Research in Astronomy, Inc., under NASA contract NAS 5-26555.  Support
for this research at Rutgers University was provided in part by NSF
CAREER award AST-0847157 to SWJ.  The Dark Cosmology Centre is
supported by the Danish National Research Foundation.

{\it Facilities:} \facility{HST (WFC3)}
\smallskip

\bibliographystyle{apj}
\bibliography{bibdesk}

\end{document}

### 2015-01-16 snTomas.tex
discovery and follow-up

@@
 
-\ifms
-    \author{Steven A.~Rodney\altaffilmark{1}}
-    \author{\etal\altaffilmark{2}}
-
-    \altaffiltext{1}{\JHU}
-    \altaffiltext{1}{\elsewhere}
-\else 
 \author{
  Steven~A.~Rodney\altaffilmark{1},
-      \etal\altaffilmark{2}
+  \etal
 }
 \altaffiltext{1}{\JHU}
-    \altaffiltext{2}{\elsewhere}
-\fi
+\altaffiltext{2}{Hubble fellow}
 
@@
 Lensed SNe have been discovered
-\textcolor{red}{\citep{Goobar:2009,Riehm:2011,Patel:2014,Nordin:2014,}}
+\citep{Goobar:2009,Riehm:2011,Patel:2014,Nordin:2014}
+
+In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
+follow-up observations of SN \tomas at $z=1.31$, discovered behind the
+galaxy cluster Abell 2744.  Sections~\ref{sec:Spectrum} and \ref{sec:LightCurve}
+describe the spectroscopy and photometry of this SN, leading to a
+classification of the object as a normal Type Ia SN.  In
+Section~\ref{sec:LensingMagnification} we make a direct measurement of
+the magnification of this source due to gravitational lensing, and
+compare to predicitions from lens models.  Finally,
+Section~\ref{sec:Discussion} discusses the tension between our
+magnification measurement and the lens models, with implications for
+the systematic error budget in magnification estimates for other
+high-$z$ lensed sources.
 
 \section{Discovery and Follow-up}
-\label{sec:DiscoveryAndFollowUp}
+\label{sec:DiscoveryAndFollowup}
+
+SN \tomas\ was discovered in \HST\ observations with the Advanced
+Camera for Surveys (ACS) in the F606W and F814W bands (V and i),
+collected on UT 2014 May 15 as part of the Hubble Frontier Fields
+(HFF) survey (PI:J.Lotz,
+HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
+The HFF program is a 3-year director's discretionary initiative that
+is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
+massive galaxy clusters, plus 6 accompanying ``parallel fields.''
+Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
+and 4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
+although the optical and IR imaging campaigns are separated by $\sim$6
+months. Abell 2744 was the first cluster observed, with IR imaging
+spanning October-November 2013, and the optical imaging from May-July
+2014.
+
+The SN detection was made in difference images using template imaging
+of Abell 2744 from HST+ACS observations taken in 2009 (PI:Dupke,
+HST-PID:11689).  Upon discovery, HST target-of-opportunity
+observations were triggered from the FrontierSN program (PI:Rodney,
+HST-PID:13386), which aims to discover and follow transient sources in
+the HFF cluster and parallel fields. The FrontierSN observations
+provided WFC3-IR imaging as well as spectroscopy using the ACS G800L
+grism, supplementing the rapid-cadence optical imaging from HST+ACS
+already being provided by the HFF program. Difference images for the
+IR follow-up data were generated using templates constructed from the
+HFF WFC3-IR imaging campaign, which concluded in November, 2013.
+
+All of the imaging data were processed using the {\tt sndrizpipe}
+pipeline,\footnote{\url{https://github.com/srodney/sndrizpipe}
+v1.2 DOI:10.5281/zenodo.10731} a custom data reduction package in
+Python that is employs the {\tt DrizzlePac} tools from the Space
+Telescope Science Institute (STScI) \citep{Fruchter:2010}.  Photometry
+was collected using the {\tt PyPhot} software
+package,\footnote{\url{https://github.com/djones1040/PyPhot}} a pure-Python
+implementation of the photometry algorithms from the IDL AstroLib
+package \citep{Landsman:1993}, which in turn are based on the DAOPHOT
+program \citep{Stetson:1987}.  For the IR bands we used point spread
+function (PSF) fitting on the difference images, and for the ACS
+images we used 0\farcs3-aperture photometry.
 

### 2015-01-19 snTomas.tex
Some work on the spectra section

@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{FIG/discovery_image}
+\caption{  
+\textcolor{red}{PLACEHOLDER IMAGE}
+SN \tomas\ in the Abell 2744 field.  The main panel shows a
+UV-optical-IR 3-color composite image constructed from all available
+HST imaging of the Abell 2744 cluster field.  The inset panel shows
+the immediate vicinity of SN \tomas, approximately 40\arcsec\ from
+the center of the cluster.  This inset image is 
+a combination of all ACS optical imaging from the HFF program, collected
+when the SN was detectable.}
+\end{center}
+\end{figure*}
+
 SN \tomas\ was discovered in \HST\ observations with the Advanced
@@
 months. Abell 2744 was the first cluster observed, with IR imaging
-spanning October-November 2013, and the optical imaging from May-July
-2014.
+spanning 2013 October-November, and optical imaging from 2014
+May-July.  A composite image of the HFF data showing the SN is
+presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
+made in difference images, constructed using template imaging of Abell
+2744 from HST+ACS observations taken in 2009 (PI:Dupke,
+HST-PID:11689).
 
-The SN detection was made in difference images using template imaging
-of Abell 2744 from HST+ACS observations taken in 2009 (PI:Dupke,
-HST-PID:11689).  Upon discovery, HST target-of-opportunity
+\input{TABLE/photometry}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/host_sed_fit}
+\caption{  \label{fig:HostSED}
+Best-fit SED template match for the most probable \tomas\ host
+galaxy. Using the {\it BPZ} code to match the observed SED, we find
+the nearest galaxy to the SN position is a late type galaxy with a
+photometric redshift of $z=1.5\pm0.2$.}
+\end{center}
+\end{figure}
+
+The most probable host galaxy for SN \tomas\ is a faint and diffuse
+galaxy immediately to the south-east of the SN location.  With
+photometry of the host galaxy collected from the template images, we
+fit the spectral energy distribution (SED) using the {\it BPZ} code --
+a Bayesian photometric redshift estimator \citep{Benitez:2000}. The best-fit
+SED template match is shown in Figure~\ref{fig:HostSED}.  From the
+{\it BPZ} analysis, we found the host to be most likely a late-type
+galaxy at a redshift of $z=1.5\pm0.2$.
+
+Upon discovery, HST target-of-opportunity
 observations were triggered from the FrontierSN program (PI:Rodney,
@@
 All of the imaging data were processed using the {\tt sndrizpipe}
-pipeline,\footnote{\url{https://github.com/srodney/sndrizpipe}
-v1.2 DOI:10.5281/zenodo.10731} a custom data reduction package in
-Python that is employs the {\tt DrizzlePac} tools from the Space
-Telescope Science Institute (STScI) \citep{Fruchter:2010}.  Photometry
-was collected using the {\tt PyPhot} software
-package,\footnote{\url{https://github.com/djones1040/PyPhot}} a pure-Python
-implementation of the photometry algorithms from the IDL AstroLib
-package \citep{Landsman:1993}, which in turn are based on the DAOPHOT
-program \citep{Stetson:1987}.  For the IR bands we used point spread
-function (PSF) fitting on the difference images, and for the ACS
-images we used 0\farcs3-aperture photometry.
+pipeline,\footnote{\url{https://github.com/srodney/sndrizpipe} v1.2
+DOI:10.5281/zenodo.10731} a custom data reduction package in Python
+that is employs the {\tt DrizzlePac} tools from the Space Telescope
+Science Institute (STScI) \citep{Fruchter:2010}.  Photometry was
+collected using the {\tt PyPhot} software
+package,\footnote{\url{https://github.com/djones1040/PyPhot}} a
+pure-Python implementation of the photometry algorithms from the IDL
+AstroLib package \citep{Landsman:1993}, which in turn are based on the
+DAOPHOT program \citep{Stetson:1987}.  For the IR bands we used point
+spread function (PSF) fitting on the difference images, and in the ACS
+optical bands we collected photometry with a
+0\farcs3 aperture. Table~\ref{tab:Photometry} presents the list of
+observations, along with measured photometry from all available
+imaging data.
 
@@
 \label{sec:Spectrum}
+
+A spectrum of SN \tomas\ was collected with the ACS G800L grism on
+2014 June 4 and 7, using 5 HST orbits from the FrontierSN program for
+a total spectroscopic exposure time of $\sim$10 ksec.  Details of the
+observations are given at the bottom of
+Table~\ref{tab:Photometry}. The grism data were processed and the
+target spectrum was extracted using the custom pipeline employed by
+the Grism Lens Amplified Survey from Space program (GLASS; PI:Treu,
+PID:13459). \textcolor{red}{Is there a citation for this? or more to
+say here?}  Figure~\ref{fig:spectrum} shows the composite 1-D ACS
+grism spectrum, combining all available G800L exposures.  The spectrum
+is largely free of contamination, because as the SN is well separated
+from nearby foreground sources and is hosted by a diffuse and
+optically faint galaxy.  Thus, the SN spectral features can be
+unambiguously identified, most notably the red slope of the continuum
+and a prominent absorption feature at $\sim$8700\AA.  However, the
+signal to noise ratio (S/N) for the host galaxy spectrum was too weak
+to yield any additional constraints on the host type or redshift.
+
+We fit the SN \tomas\ spectrum in two steps.  First we determine a
+spectral classification -- and get a preliminary estimate of the
+redshift and phase -- using the SuperNova IDentification
+software \citep{Blondin:2010}.  Second, we refine the redshift and
+phase using a custom Type Ia spectral template matching
+program.  Details of the fitting are given below and results are
+summarized in Table~\ref{tab:SpectralFits}.
+
+\subsection{SNID Fitting}
+\label{sec:SNID}
+
+The SNID program is designed to estimate the type, redshift, and phase
+of a SN spectrum through cross-correlation matching with a library of
+template spectra.  To account for possible distortions in the broad
+shape of the SN pseudo-continuum due to dust or instrumental
+calibration effects, SNID divides each SED by a smooth cubic spline
+fit. This effectively removes the shape of the SN pseudo-continuum to
+leave behind a flat SED superimposed with spectral absorption and
+emission features.  It is these features which drive the
+cross-correlation fit, so the SNID approach is insensitive to the
+overall color of the SED.  We used v2.0 of the SNID template library,
+which includes template SEDs covering all Type Ia and Core Collapse
+sub-classes, and has recently been updated with corrections and
+improvements to the Type Ib/c templates \citep{Liu:2014}.
+
+Using SNID to fit the \tomas\ spectrum, we find strong evidence that
+the spectral type is a normal Type Ia, with $>$97\% of the matching
+SEDs coming from Type Ia spectra.  The best-fit SEDs are also
+consistent in redshift at $z=1.32\pm0.01$, and in phase at $0.4\pm1.7$
+rest-frame days from peak (meaning MJD$_{\rm pk}$=56813$\pm$4).  At
+this redshift, the absorption at $\sim$8700\AA\ corresponds to the
+blended \ion{Ca}{2} H\&K features.  This \ion{Ca}{2} absorption is
+commonly seen in Type Ia SN spectra near maximum light, although it is
+also prominent in the spectra of Type Ib and Ic core collapse SNe
+(\CCSNe).  The red color of the \tomas\ SED is qualitatively
+consistent with a redshift of $z>1$ -- although this information was
+not used by SNID for the template matching.  As we will see in
+Section~\ref{sec:LightCurve}, this spectral classification of
+SN \tomas\ is supported by the photometric information, which is also
+most consistent with a Type Ia SN at $z=1.3$.
+
+\subsection{Fitting with Additional Type Ia Templates}
+\label{sec:FittingWithAdditionalTypeIaTemplates}
+
+To refine the redshift and phase constraints on \tomas, we next fit
+the spectrum with a custom spectral matching program that employs a
+library of Type Ia SN SEDs.  This library is similar to the Type Ia
+spectral set used by SNID, but also includes more recent SNe with
+well-observed spectral time series that extend to rest-frame UV
+wavelengths (e.g. SN 2011fe and 2014J).  We first use an approach
+similar to the SNID algorithm: warping the pseudo-continuum of each
+template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to match the
+observed SED of SN \tomas.  From this analysis we find results that
+are consistent with the SNID fits: a redshift of $z=1.31\pm0.01$ and a
+phase of $0\pm3$ rest-frame days.
+
+Finally, we repeat the fitting, but without any warping of the
+templates to account for differences in the continuum shape.  In this
+iteration we only allow each template SED to be scaled in flux
+coherently at all wavelengths.  Here we again find that the \tomas\
+SED is well matched by a normal Type Ia SN (SN 2011fe) at redshift
+$z=1.31\pm0.01$.  Without the continuum warping, an alternative fit
+also arises: the normal Type Ia SN 2011iv at
+$z=0.98\pm0.01$. Formally, this match provides a better fit to the
+unwarped \tomas\ spectrum, although this redshift is at odds with the
+host galaxy photo-z ($1.5\pm0.2$), and we will see in the following
+section that the photometric data is incompatible with a normal Type
+Ia SN at $z\sim1.0$.
 
@@
 \textcolor{red}{Light curve fitting with MLCS2k2}
+
+determine a photometric classification
+
+derive a constraint on the time of peak
 

### 2015-01-21 snTomas.tex
Updated detection figure (fig 1), fixed phot table

@@
 
-\section{Discovery and Follow-up}
+\section{Discovery, Follow-up, and Data Processing}
 \label{sec:DiscoveryAndFollowup}
@@
 \caption{  
-\textcolor{red}{PLACEHOLDER IMAGE}
-SN \tomas\ in the Abell 2744 field.  The main panel shows a
-UV-optical-IR 3-color composite image constructed from all available
-HST imaging of the Abell 2744 cluster field.  The inset panel shows
-the immediate vicinity of SN \tomas, approximately 40\arcsec\ from
-the center of the cluster.  This inset image is 
-a combination of all ACS optical imaging from the HFF program, collected
-when the SN was detectable.}
+SN \tomas\ in the Abell 2744 field.  The left panel shows a
+UV/Optical/IR color composite image constructed from all available HST
+imaging of the Abell 2744 cluster field.\footnote{Image Credit: NASA,
+ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team
+(STScI)}  The inset panels at right show F814W imaging of the
+immediate vicinity of SN \tomas, approximately 40\arcsec\ from the
+center of the cluster.  The top panel shows the template image,
+combining all data prior to the SN appearance.
+Labeled ellipses mark the nearest galaxies and their redshift constraints: a photometric redshift for the most likely host galaxy is marked in blue, and the spectroscopic redshift for a likely background galaxy is given in yellow.
+The bottom panel is
+constructed from all HFF F814W imaging taken while the SN was detectable, and marks the SN location with an arrow.}
 \end{center}
@@
 
-We fit the SN \tomas\ spectrum in two steps.  First we determine a
-spectral classification -- and get a preliminary estimate of the
-redshift and phase -- using the SuperNova IDentification
-software \citep{Blondin:2010}.  Second, we refine the redshift and
-phase using a custom Type Ia spectral template matching
-program.  Details of the fitting are given below and results are
-summarized in Table~\ref{tab:SpectralFits}.
+As described below, we fit the SN \tomas\ spectrum in two steps.
+First we determine a spectral classification -- and get a preliminary
+estimate of the redshift and age -- using the SuperNova IDentification
+(SNID) software \citep{Blondin:2007}.  Second, we refine the redshift
+and age measurement using a custom Type Ia spectral template matching
+program.
 
@@
 
-The SNID program is designed to estimate the type, redshift, and phase
+The SNID program is designed to estimate the type, redshift, and age
 of a SN spectrum through cross-correlation matching with a library of
@@
 the spectral type is a normal Type Ia, with $>$97\% of the matching
-SEDs coming from Type Ia spectra.  The best-fit SEDs are also
+SEDs coming from Type Ia spectra.  
+In SNID the goodness of fit is evaluated primarily through the {\it rlap} parameter, which measures the degree of wavelength overlap and the strength of the cross-correlation peak.
+For SN \tomas\ the best matching Type Ia template is the normal Type Ia SN 2004fu at z=1.321 and age=2.4 days past peak, which delivers {\it rlap}=20.8.
+Despite the relatively small rest-frame wavelength window of this spectrum, the SNID classification is quite definitive: \textcolor{red}{no \CCSN\ template achieves an {\it rlap} value better than 5.0 at any redshift.}
+
+The best-fit Type Ia SEDs are also
 consistent in redshift at $z=1.32\pm0.01$, and in phase at $0.4\pm1.7$
@@
 
-\subsection{Fitting with Additional Type Ia Templates}
+\subsection{Extended Type Ia Template Matching}
 \label{sec:FittingWithAdditionalTypeIaTemplates}
@@
 \label{sec:LightCurve}
+
+Relative to other SNe at $z>1$, the SN \tomas\ light curve was
+unusually well sampled at rest-frame ultraviolet wavelengths, due to
+the rapid cadence of the HFF imaging campaign. These ACS observations
+therefore provide a tight constraint on the time of peak brightness
+and the evolution of the SN color.  Supplemental observations with the
+WFC3-IR camera provided critical rest-frame optical photometry,
+enabling a measurement of the apparent luminosity distance through
+light curve fitting.
+
+\subsection{Photometric Classification}
+\label{sec:PhotometricClassification}
+
+As a check on the spectral classification of SN \tomas\
+(Section~\ref{sec:SNID}), we independently classified the SN using a
+Bayesian photometric classifier.  This classification code uses the
+{\tt sncosmo} software
+package\footnote{\url{http://sncosmo.github.io/}} to simulate SN light
+curves at a range of redshifts and evaluate the classification
+probability using traditional Bayesian model selection \citep[as
+in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015}.  In this
+analysis we represent normal Type Ia SNe with the SALT2
+model \citep{Guy:2010}, and \CCSNe\ with 42 discrete templates (26
+Type II and 16 Type Ib/c) drawn from the template library of the
+SuperNova Analysis software \citep[SNANA,][]{Kessler:2009a}.  Due to
+the expected impact of gravitational lensing magnification, we do not
+include any prior on the intrinsic luminosity for any SN sub-class.
+
+From this photometric analysis we derive a Type Ia classification
+probability of $p(\rm Ia|{\bf \rm D})=XX\%$.  Marginalizing over the
+light curve shape and color parameters of the SALT2 model, we extract
+a posterior probability distribution in redshift that is well
+described by a single Gaussian centered at $z=1.32\pm0.03$.
 

### 2015-01-22 snTomas.tex
added initial spec fit fig

@@
 \includegraphics[width=\textwidth]{FIG/discovery_image}
-\caption{  
+\caption{  \label{fig:DiscoveryImage}
 SN \tomas\ in the Abell 2744 field.  The left panel shows a
@@
 presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
-made in difference images, constructed using template imaging of Abell
+made in difference images constructed using template imaging of Abell
 2744 from HST+ACS observations taken in 2009 (PI:Dupke,
@@
 \label{sec:Spectrum}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/specfit}
+\caption{  \label{fig:SpecFit}
+Best-fit Type Ia spectral template matches to the SN \tomas\ spectrum.
+When the templates are not warped, an acceptable fit can be found with
+a normal Type Ia at $z\sim1$ (top), or at $z=1.31$ (middle).  Introducing a smooth 3rd-order polynomial to warp the shape of the template pseudo-continuum makes the $z=1.31$ solution far superior.}
+\end{center}
+\end{figure}
 

### 2015-01-22 snTomas.tex
updated spectroscopy, phot classification sections

@@
 
-\shorttitle{A \SNIa Behind Abell 2744}
+\shorttitle{A Type Ia SN Behind Abell 2744}
 \shortauthors{Rodney et al.}
@@
 are systematically biased to higher values, with a mean of $\mu_{\rm
-mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  The most
-significant discrepancies arise from models with a strict ``light
-traces mass'' assumption.  We evaluate possible causes for this bias,
-including variation of the mass-to-light ratio in the nearest cluster
-member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
-any single cluster could provide a robust evaluation of systematic
-biases in lens models.  Until such a sample exists, it is advisable to
-increase the estimated uncertainty of any predicted magnification
-by an amount comparable to the dispersion from all available lens
-models.
+mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  
+\textcolor{red}{TODO: summarize lensing discussion.}
+%The most
+%significant discrepancies arise from models with a strict ``light
+%traces mass'' assumption.  We evaluate possible causes for this bias,
+%including variation of the mass-to-light ratio in the nearest cluster
+%member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
+%any single cluster could provide a robust evaluation of systematic
+%biases in lens models.  Until such a sample exists, it is advisable to
+%increase the estimated uncertainty of any predicted magnification
+%by an amount comparable to the dispersion from all available lens
+%models.
 
@@
 first Gyr after the Big
-Bang \citep{Zheng:2012,Coe:2013,} 
+Bang \citep{Zheng:2012,Coe:2013} 
 \textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}
@@
 follow-up observations of SN \tomas at $z=1.31$, discovered behind the
-galaxy cluster Abell 2744.  Sections~\ref{sec:Spectrum} and \ref{sec:LightCurve}
+galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy} and \ref{sec:PhotometricClassification}
 describe the spectroscopy and photometry of this SN, leading to a
@@
 \begin{center}
-\includegraphics[width=\textwidth]{FIG/discovery_image}
+%\includegraphics[width=\textwidth]{FIG/discovery_image}
+\includegraphics[width=\textwidth]{FIG/discovery_image_lowres}
 \caption{  \label{fig:DiscoveryImage} 
@@
 UV/Optical/IR color composite image constructed from all available HST
-imaging of the Abell 2744 cluster field.\footnote{Image Credit: NASA,
-ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team
-(STScI)}  The inset panels at right show F814W imaging of the
-immediate vicinity of SN \tomas, approximately 40\arcsec\ from the
-center of the cluster.  The top panel shows the template image,
-combining all data prior to the SN appearance.
-Labeled ellipses mark the nearest galaxies and their redshift constraints: a photometric redshift for the most likely host galaxy is marked in blue, and the spectroscopic redshift for a likely background galaxy is given in yellow.
-The bottom panel is
-constructed from all HFF F814W imaging taken while the SN was detectable, and marks the SN location with an arrow.}
+imaging of the Abell 2744 cluster field.  The inset panels at right
+show F814W imaging of the immediate vicinity of SN \tomas,
+approximately 40\arcsec\ from the center of the cluster. The top panel
+shows the template image, combining all data prior to the SN
+appearance.  Labeled ellipses mark the nearest galaxies and their
+redshift constraints: a photometric redshift for the most likely host
+galaxy is marked in blue, and the spectroscopic redshift for a likely
+background galaxy is given in yellow. The bottom panel is constructed
+from all HFF F814W imaging taken while the SN was detectable, and
+marks the SN location with an arrow.  (Left panel image credit: NASA,
+ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team (STScI))
+}
 \end{center}
@@
 
-\section{Spectrum}
-\label{sec:Spectrum}
+\section{Spectroscopy}
+\label{sec:Spectroscopy}
 
@@
 \caption{  \label{fig:SpecFit}
-Best-fit Type Ia spectral template matches to the SN \tomas\ spectrum.
-When the templates are not warped, an acceptable fit can be found with
-a normal Type Ia at $z\sim1$ (top), or at $z=1.31$ (middle).  Introducing a smooth 3rd-order polynomial to warp the shape of the template pseudo-continuum makes the $z=1.31$ solution far superior.}
+Redshift and age determination from spectral template matching to the
+the SN \tomas\ maximum light spectrum.  The y axis plots flux in
+arbitrary units, and the x axis marks wavelength in \AA\ with the
+observer-frame on the bottom and rest-frame on the top.
+The \tomas\ spectrum observed with the
+HST ACS G800L grism is shown in black, overlaid with model fits
+derived from a library of Type Ia templates that have extended
+rest-frame UV coverage.  {\it Top}: The best match is at $z=1.31$ with
+age=$+3$ days, from the normal Type Ia SN 2012cg template when using a
+smooth 3rd-order polynomial to warp the shape of the template
+pseudo-continuum.  When the templates are not warped, an acceptable
+fit can be found with a normal Type Ia at $z=1.31$ (middle) or at
+$z\sim1$ (bottom), although the latter is inconsistent with the host
+galaxy redshift prior and the light curve. No \CCSN\ templates can
+provide a statistically acceptable fit at any redshift, within the age
+constraints imposed by the light curve.}
 \end{center}
@@
 A spectrum of SN \tomas\ was collected with the ACS G800L grism on
-2014 June 4 and 7, using 5 HST orbits from the FrontierSN program for
-a total spectroscopic exposure time of $\sim$10 ksec.  Details of the
-observations are given at the bottom of
-Table~\ref{tab:Photometry}. The grism data were processed and the
-target spectrum was extracted using the custom pipeline employed by
-the Grism Lens Amplified Survey from Space program (GLASS; PI:Treu,
-PID:13459). \textcolor{red}{Is there a citation for this? or more to
-say here?}  Figure~\ref{fig:spectrum} shows the composite 1-D ACS
-grism spectrum, combining all available G800L exposures.  The spectrum
-is largely free of contamination, because as the SN is well separated
-from nearby foreground sources and is hosted by a diffuse and
-optically faint galaxy.  Thus, the SN spectral features can be
-unambiguously identified, most notably the red slope of the continuum
-and a prominent absorption feature at $\sim$8700\AA.  However, the
-signal to noise ratio (S/N) for the host galaxy spectrum was too weak
-to yield any additional constraints on the host type or redshift.
+2014 June 4 and 7, when the SN was very near to its peak brightness.
+The observations -- listed at the bottom of Table~\ref{tab:Photometry}
+-- used 5 HST orbits from the FrontierSN program for a total
+spectroscopic exposure time of $\sim$10 ksec.  The grism data were
+processed and the target spectrum was extracted using the custom
+pipeline employed by the Grism Lens Amplified Survey from Space
+program (GLASS; PI:Treu, PID:13459). \textcolor{red}{Is there a
+citation for this? or more to say here?}
+
+Figure~\ref{fig:SpecFit} shows the composite 1-D ACS grism spectrum,
+combining all available G800L exposures, overlaid with SN model fits
+that will be described below.  The spectrum is largely free of
+contamination, because the orientation was chosen to avoid nearby
+bright sources and the host galaxy is diffuse and optically faint.
+Thus, the SN spectral features can be unambiguously identified, most
+notably the red slope of the continuum and a prominent absorption
+feature at $\sim$8700\AA.  However, the signal to noise ratio (S/N)
+for the host galaxy spectrum was too weak to yield any additional
+constraints on the host type or redshift.
 
@@
 
-\subsection{SNID Fitting}
+\subsection{Classification with SNID}
 \label{sec:SNID}
@@
 
-Using SNID to fit the \tomas\ spectrum, we find strong evidence that
-the spectral type is a normal Type Ia, with $>$97\% of the matching
-SEDs coming from Type Ia spectra.  
-In SNID the goodness of fit is evaluated primarily through the {\it rlap} parameter, which measures the degree of wavelength overlap and the strength of the cross-correlation peak.
-For SN \tomas\ the best matching Type Ia template is the normal Type Ia SN 2004fu at z=1.321 and age=2.4 days past peak, which delivers {\it rlap}=20.8.
-Despite the relatively small rest-frame wavelength window of this spectrum, the SNID classification is quite definitive: \textcolor{red}{no \CCSN\ template achieves an {\it rlap} value better than 5.0 at any redshift.}
+In SNID the goodness of fit is evaluated primarily through the {\it
+rlap} parameter, which measures the degree of wavelength overlap and
+the strength of the cross-correlation peak.  Typically, an {\it rlap}
+value $>5$ is required to be considered an acceptable match.
 
-The best-fit Type Ia SEDs are also
-consistent in redshift at $z=1.32\pm0.01$, and in phase at $0.4\pm1.7$
-rest-frame days from peak (meaning MJD$_{\rm pk}$=56813$\pm$4).  At
-this redshift, the absorption at $\sim$8700\AA\ corresponds to the
-blended \ion{Ca}{2} H\&K features.  This \ion{Ca}{2} absorption is
-commonly seen in Type Ia SN spectra near maximum light, although it is
-also prominent in the spectra of Type Ib and Ic core collapse SNe
-(\CCSNe).  The red color of the \tomas\ SED is qualitatively
-consistent with a redshift of $z>1$ -- although this information was
-not used by SNID for the template matching.  As we will see in
-Section~\ref{sec:LightCurve}, this spectral classification of
-SN \tomas\ is supported by the photometric information, which is also
-most consistent with a Type Ia SN at $z=1.3$.
+To match the SN \tomas\ spectrum we use conservative constraints on
+age and redshift: limiting the age to $\pm$5 rest-frame days of peak
+brightness and $0.8<z<1.8$, consistent with the SN light curve and
+host galaxy photo-$z$.  With these constraints we find that the only
+acceptable match is a normal Type Ia SN near $z=1.3$. The best match
+has {\it rlap}$=8.7$, using the normal Type Ia SN 2005cf at $z=1.35$
+and age=-2.2 rest-frame days before peak.  Within these constraints,
+the best non-Ia matches all have {\it rlap}$<2.5$.
 
-\subsection{Extended Type Ia Template Matching}
-\label{sec:FittingWithAdditionalTypeIaTemplates}
+The {\tt SNID} library can generate an acceptable \CCSN\ match only
+when we remove all age and redshift constraints, In this case the best
+non-Ia match is the Type Ic SN 1997ef, which delivers {\it rlap}$=6.8$
+at $z=0.51$ and age=47.3 rest-frame days past peak.  This is not as
+good a fit as the best Type Ia models, is at odds with the host galaxy
+redshift prior, and is strongly disfavored by the shape and colors of
+the SN light curve (see Section~\ref{sec:PhotometricClassification}).
+
+From the preceding analysis, we conclude that \tomas\ is a Type Ia SN
+at $z\approx1.3$.  At this redshift, the absorption at $\sim$8700\AA\
+corresponds to the blended \ion{Ca}{2} H\&K features.
+This \ion{Ca}{2} absorption is commonly seen in Type Ia SN spectra
+near maximum light, although it is also prominent in the spectra of
+Type Ib and Ic core collapse SNe (\CCSNe).  The red color of
+the \tomas\ SED is qualitatively consistent with a redshift of $z>1$
+-- although this information was not used by {\tt SNID} for the
+template matching.  As we will see in Section~\ref{sec:PhotometricClassification},
+this spectral classification of SN \tomas\ is reinforced by the
+photometric information, which also supports classification as a Type
+Ia SN at $z=1.3$.
+
+\subsection{Spectroscopic Redshift}
+\label{sec:SpecRedshift}
 
@@
 similar to the SNID algorithm: warping the pseudo-continuum of each
-template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to match the
-observed SED of SN \tomas.  From this analysis we find results that
-are consistent with the SNID fits: a redshift of $z=1.31\pm0.01$ and a
-phase of $0\pm3$ rest-frame days.
+template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
+match the observed SED of SN \tomas.  From this analysis we find
+results that are consistent with the SNID fits: a redshift of
+$z=1.31\pm0.01$ and a phase of $0\pm3$ rest-frame days. The
+best-fitting spectral template is the normal Type Ia SN 2012cg, shown
+in the bottom panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
+per degree of freedom $\nu$ equal to 42.1/87.
 
@@
 iteration we only allow each template SED to be scaled in flux
-coherently at all wavelengths.  Here we again find that the \tomas\
-SED is well matched by a normal Type Ia SN (SN 2011fe) at redshift
-$z=1.31\pm0.01$.  Without the continuum warping, an alternative fit
-also arises: the normal Type Ia SN 2011iv at
-$z=0.98\pm0.01$. Formally, this match provides a better fit to the
-unwarped \tomas\ spectrum, although this redshift is at odds with the
-host galaxy photo-z ($1.5\pm0.2$), and we will see in the following
-section that the photometric data is incompatible with a normal Type
-Ia SN at $z\sim1.0$.
+coherently at all wavelengths.  As shown in Figure~\ref{fig:SpecFit},
+we again find that the \tomas\ SED can be matched by a normal Type Ia
+SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
+warping, an alternative fit also arises: the normal Type Ia SN 2011iv
+at $z=0.98\pm0.01$. Formally, this match provides a slightly better
+fit to the unwarped \tomas\ spectrum, although the fit is notably poor
+at $\sim8700$\AA\ where the most significant absorption feature is
+found. Furthermore, a redshift $z\sim1$ is at odds with the host
+galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
+that the photometric data is incompatible with a normal Type Ia SN at
+$z\sim1.0$.
 
-\section{Light Curve}
-\label{sec:LightCurve}
+Setting aside the $z\sim1$ solution, all other template matches
+provide a consistent redshift constraint of $z=1.31\pm0.01$,
+regardless of whether the templates are warped to match the SN \tomas\
+continuum shape.  The inferred age from these fits is $0\pm3$
+rest-frame days from peak brightness, which is also consistent with
+the observed light curve.
+
+\section{Photometric Classification}
+\label{sec:PhotometricClassification}
 
@@
 light curve fitting.
-
-\subsection{Photometric Classification}
-\label{sec:PhotometricClassification}
 
@@
 Type II and 16 Type Ib/c) drawn from the template library of the
-SuperNova Analysis software \citep[SNANA,][]{Kessler:2009a}.  Due to
-the expected impact of gravitational lensing magnification, we do not
-include any prior on the intrinsic luminosity for any SN sub-class.
+SuperNova Analysis software package \citep[SNANA,][]{Kessler:2009a}.
+Likelihoods are defined by comparing the observed fluxes to model
+predictions in all passbands where the model is defined.  In practice,
+this means we exclude the F435W and F606W bands, which are too blue
+for our models at $z>1$.
 
-From this photometric analysis we derive a Type Ia classification
-probability of $p(\rm Ia|{\bf \rm D})=XX\%$.  Marginalizing over the
-light curve shape and color parameters of the SALT2 model, we extract
-a posterior probability distribution in redshift that is well
-described by a single Gaussian centered at $z=1.32\pm0.03$.
+The \CCSN\ models have free parameters for date of peak brightness
+($t_{\rm pk}$), amplitude, and redshift ($z$). Due to the expected
+impact of gravitational lensing magnification, we do not include any
+prior on the intrinsic luminosity for any SN sub-class.  We also do
+not assign a prior for the SN redshift. This allows our photometric
+analysis to provide an independent check on the host galaxy photo-$z$
+and spectroscopic redshift (Sections~\ref{sec:HostGalaxy}
+and \ref{sec:SpecFit}).
 
-\textcolor{red}{Light curve fitting with MLCS2k2}
+For Type Ia SNe, the SALT2 model has two additional parameters that
+control the shape ($x_1$) and color ($c$) of the light curve.  We use
+conservative priors here, defined to encompass a range of Type Ia SN
+shapes and colors that is broader than typically allowed in
+cosmological analyses \citep[see
+e.g.][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
+a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
+$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
+color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
+$\sigma_c^+=0.54$.  The $c$ parameter in SALT2 combines intrinsic SN
+color and extinction due to dust, so the large red tail of this
+distribution allows for the possibility of several magnitudes
+of dust extinction along the \tomas\ line of sight.
 
-determine a photometric classification
+We also assign a class prior for each of the three primary SN
+sub-classes (Type Ia, Ib/c, and II), using a fixed relative fraction for
+each sub-class as determined at $z=0$ by \citet{Smartt:2009}
+and \citet{Li:2011a}.  A more rigorous classification would extrapolate
+these local SN class fractions to higher redshift using models or
+measurements of the volumetric SN rate.  For simplicity, we do not
+vary the class priors with redshift, and in practice these priors do
+not have any significant impact on the resulting classification.
 
-derive a constraint on the time of peak
+The final photometric classification probability for SN \tomas\ is
+$p({\rm Ia}|{\bf \rm D})=1.0$, with the classification
+probability from all \CCSN\ sub-classes totaling less than $10^{-100}$.  The
+marginal posterior distribution in redshift for the Type Ia model is
+sharply peaked at $z=1.36\pm0.02$, which is $<2.5\sigma$ from
+the spectroscopic redshift of $z=1.31\pm0.01$ derived in
+Section~\ref{sec:SpecRedshift}.  The time of peak brightness is also
+tightly constrained at $t_{\rm pk}=56816.0\pm0.2$, which means the
+spectroscopic observations were collected within 2 rest-frame days of
+the epoch of peak brightness, consistent with our spectroscopic
+analysis.
 
-\begin{figure*}
+\section{Light Curve Fitting}
+\label{sec:LightCurveFitting}
+
+With the spectroscopic type and redshift securely defined as a normal
+Type Ia SN at $z=1.3$, we now turn to fitting the light curve with
+Type Ia templates to measure the distance modulus.  Here we use two
+independent light curve fitters: first the SALT2 model described
+above, and then the MLCS2k2 model from \citep{Jha:2007}.
+
+\subsection{SALT2 Fit}
+\label{sec:SALT2Fit}
+
+in \citep{Patel:2014}:   $\alpha=1.367\pm0.086$,
+$\beta=3.179\pm0.101$, $M=-19.12\pm0.03$.
+
+For the SALT2 Type Ia model one can define a shape- and color-corrected apparent
+B-band magnitude using 
+$m_{\rm B}^\prime = m_{\rm B} + \alpha x_1 - \beta c$.
+
+For the SALT2 model we fix the model parameters to the values
+derived in the \citet{Rest:2014} analysis of the Pan-STARRS1 SN sample:
+$\alpha=0.147$, $\beta=3.13$, $M_B=-19.34$.
+
+Comparing salt2 color to Av \citep{Kessler:2009b}:
+$c = (0.464 ± 0.021)AV − (0.121 ± 0.014)$
+
+from \citet{Patel:2014}:
+``Finally, to ensure a consistent zeropoint between the SALT2 and
+MLCS2k2 distance moduli, we applied both methods to a sample of SDSS
+Supernova Survey SNe Ia from Holtzman et al. (2008) and Kessler et
+al. (2009a). We added a zeropoint correction of 0.20 mag to the
+distance moduli reported by SNANA in the MLCS2k2 fit (dmMLCS2k2), to
+put them on the same scale as the SALT2 distances (dmSALT2).''
+
+\subsection{MLCS2k2 Fit}
+\label{sec:MLCS2k2Fit}
+
+As in \citep{Patel:2014}.
+
+$R_v$ fixed to 1.9.
+
+for Rv = 1.9, the calibrated distance is: $\mu = \mu_{\rm mlcs}-0.2006$.
+
+\begin{figure}
 \begin{center}
 \includegraphics[width=0.49\textwidth]{FIG/lcfit_mlcs2k2_ABmag}
-\includegraphics[width=0.49\textwidth]{FIG/specfit_11fe_t-3_z131}
-\caption{ {\it (Left)} Light curve fit using MLCS2k2. 
-{\it (Right)} Spectral template match to the HST ACS G800L SN
-spectrum.  Assuming minimal reddening, the best-fit template is from
-SN 2011fe at $z=1.31$ and $t=-3$ rest-frame days before peak
-brightness.  Allowing a correction for the broad SED shape using
-3rd-order polynomials, the best match is from SN 2012cg at $z=1.31$
-and $t=+3 days$.
+\caption{  Light curve fit using MLCS2k2. 
 \label{fig:mlcsfit} }
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 
-Proposal for a survey to build a bigger sample : HST GO, Snapshot, ground-based.
+Design elements for a survey to build a bigger sample : HST GO, Snapshot, ground-based.
 

### 2015-02-18 snTomas.tex
added light curve fitting figure and table  showing the mlcs2k2 and salt2 fits

@@
 \author{
- Steven~A.~Rodney\altaffilmark{1},
+ Steven~A.~Rodney\altaffilmark{1,2},
   \etal
@@
 Lensed SNe have been discovered
-\citep{Goobar:2009,Riehm:2011,Patel:2014,Nordin:2014}
+\citep{Goobar:2009,Riehm:2011}
+
+\citet[][hereafter P14]{Patel:2014} and \citet{Nordin:2014} presented
+independent analyses of three lensed SNe, of which at least 2 are securely
+classified as Type Ia SNe.  All of these three objects were found in
+the Cluster Lensing and Supernova survey with Hubble (CLASH,
+PI:Postman, HST Program ID 12068).
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/snTomas_lightcurve_classification}
+\caption{ 
+Maximum likelihood model for each SN sub-class, derived from Bayesian
+model selection using the photometric data alone. Grey points show the
+observed SN \tomas\ photometry with error bars, though these are typically
+smaller than the size of the marker.  The Type Ia model
+(orange solid line) is drawn from the SALT2 template at $z=1.35$. The
+best match from all Type Ib/Ic models is based on the Type Ic SN
+SDSS-14475 at $z=0.695$ (green dashed line). For the Type II class, the
+best match is from the Type II-L SN 2007pg at $z=1.8$ (blue dash-dot line). The Type
+Ia model is by far the best match, and the only one that is consistent
+with both the photo-$z$ of the probable host galaxy and the
+spectroscopic redshift from the SN spectrum.
+\label{fig:photoclass} }
+\end{center}
+\end{figure}
+
 As a check on the spectral classification of SN \tomas\
 (Section~\ref{sec:SNID}), we independently classified the SN using a
-Bayesian photometric classifier.  This classification code uses the
+Bayesian photometric classifier.  We use the
 {\tt sncosmo} software
 package\footnote{\url{http://sncosmo.github.io/}} to simulate SN light
-curves at a range of redshifts and evaluate the classification
+curves from $z=0.3$ to 2.3 and evaluate the classification
 probability using traditional Bayesian model selection \citep[as
@@
 Type II and 16 Type Ib/c) drawn from the template library of the
-SuperNova Analysis software package \citep[SNANA,][]{Kessler:2009a}.
+SuperNova Analysis software
+package \citep[SNANA,][]{Kessler:2009a}.\footnote{Throughout this work
+we use SNANA v10\_35g.}
 Likelihoods are defined by comparing the observed fluxes to model
@@
 this means we exclude the F435W and F606W bands, which are too blue
-for our models at $z>1$.
+for our models at $z>0.85$.
 
@@
 analysis to provide an independent check on the host galaxy photo-$z$
-and spectroscopic redshift (Sections~\ref{sec:HostGalaxy}
-and \ref{sec:SpecFit}).
+and spectroscopic redshift (Sections~\ref{sec:DiscoveryAndFollowup}
+and \ref{sec:SpecRedshift}).
 
@@
 The final photometric classification probability for SN \tomas\ is
-$p({\rm Ia}|{\bf \rm D})=1.0$, with the classification
-probability from all \CCSN\ sub-classes totaling less than $10^{-100}$.  The
-marginal posterior distribution in redshift for the Type Ia model is
-sharply peaked at $z=1.36\pm0.02$, which is $<2.5\sigma$ from
-the spectroscopic redshift of $z=1.31\pm0.01$ derived in
-Section~\ref{sec:SpecRedshift}.  The time of peak brightness is also
-tightly constrained at $t_{\rm pk}=56816.0\pm0.2$, which means the
-spectroscopic observations were collected within 2 rest-frame days of
-the epoch of peak brightness, consistent with our spectroscopic
+$p({\rm Ia}|{\rm {\bf D}})=1.0$, with the classification probability
+from all \CCSN\ sub-classes totaling less than $10^{-32}$.  The
+best-fit models for each sub-class are shown in
+Figure~\ref{fig:photoclass}, which demonstrates that the \CCSN\ models
+cannot adequately match the observed photometry. In particular, only
+the Type Ia model can simultaneously provide an acceptable fit to the
+well-sampled rising light curve in F814W and the F814W-F160W
+color near peak.
+
+The marginal posterior distribution in redshift for the Type Ia model
+is sharply peaked at $z=1.35\pm0.02$, which is fully consistent with
+the photo-$z$ of the presumed host galaxy ($z=1.5\pm0.2$), and
+$<2\sigma$ from the spectroscopic redshift of $z=1.31\pm0.01$ derived
+in Section~\ref{sec:SpecRedshift}.  The time of peak brightness is
+also tightly constrained at $t_{\rm pk}=56816.3\pm0.3$, which means
+the spectroscopic observations were collected within 2 rest-frame days
+of the epoch of peak brightness, consistent with our spectroscopic
 analysis.
@@
 Type Ia templates to measure the distance modulus.  Here we use two
-independent light curve fitters: first the SALT2 model described
-above, and then the MLCS2k2 model from \citep{Jha:2007}.
+independent light curve fitters: the SALT2 model described
+above and the MLCS2k2 model \citep{Jha:2007}.
 
-\subsection{SALT2 Fit}
-\label{sec:SALT2Fit}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{FIG/snTomas_lightcurve_fit_fluxAB25}
+\caption{ Type Ia light curve fits to SN \tomas\ using the MLCS2k2
+(top row) and SALT2 (bottom row) fitters. The model redshifts are set to
+$z=1.33\pm0.02$, encompassing both redshift values as determined from
+spectroscopic and photometric constraints.  Solid lines denote the
+best-fit model and shaded lines show the range allowed by 1-$\sigma$
+uncertainties on the model parameters. 
+Observed fluxes are shown as diamonds, scaled to an AB magnitude
+zero point of 25. Error bars are plotted, but most are commensurate
+with the size of the points. The left-most panel includes observations
+in the F435W and F606W filters, although these were not used for the
+fit, as they are bluer than the minimum wavelength for the model. The
+lower axis marks time in observer frame days, while the top axis shows
+the time in the rest frame relative to the epoch of peak brightness.
+\label{fig:LightCurveFits} }
+\end{center}
+\end{figure*}
 
-in \citep{Patel:2014}:   $\alpha=1.367\pm0.086$,
-$\beta=3.179\pm0.101$, $M=-19.12\pm0.03$.
+With both fitters we find light curve shape and color parameters that
+are fully consistent with a normal Type Ia SN, regardless of whether
+we adopt the spectroscopic redshift $z=1.31$ from
+Section~\ref{sec:SpecRedshift} or the photometric redshift $z=1.35$
+from Section~\ref{sec:PhotometricClassification}.  For SALT2, with the
+redshift range set to $1.33\pm0.02$, we find a light curve shape
+parameter of $x_1=0.164\pm0.199$ and a color parameter of
+$c=-0.115\pm0.025$, yielding a $\chi^2$ value of 48.4 for 36 degrees
+of freedom, $\nu$.  With the MLCS2k2 fitter the best-fit shape
+parameter is $\Delta=-0.033\pm0.083$ and the color term is
+$A_{\rm V}=0.014\pm0.037$, giving $\chi^2/\nu=23.9/36$.
 
-For the SALT2 Type Ia model one can define a shape- and color-corrected apparent
-B-band magnitude using 
-$m_{\rm B}^\prime = m_{\rm B} + \alpha x_1 - \beta c$.
+\subsection{Distance Modulus}
+\label{sec:DistanceModulus}
 
-For the SALT2 model we fix the model parameters to the values
-derived in the \citet{Rest:2014} analysis of the Pan-STARRS1 SN sample:
-$\alpha=0.147$, $\beta=3.13$, $M_B=-19.34$.
+As in \citet{Patel:2014}, we derive a distance modulus 
+from the SALT2 fit using\footnote{This avoids confusion by reserving the symbol $\mu$
+to refer to the lensing magnification. The 'dm' is a standard distance
+modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$ is the
+luminosity distance in Mpc.}
 
-Comparing salt2 color to Av \citep{Kessler:2009b}:
-$c = (0.464 ± 0.021)AV − (0.121 ± 0.014)$
+\begin{equation} \label{eqn:dmSALT2}
+ {\rm dm}_{\rm SALT2} = m_B^* - M + \alpha(s-1) - \beta C.
+\end{equation}
 
-from \citet{Patel:2014}:
-``Finally, to ensure a consistent zeropoint between the SALT2 and
-MLCS2k2 distance moduli, we applied both methods to a sample of SDSS
-Supernova Survey SNe Ia from Holtzman et al. (2008) and Kessler et
-al. (2009a). We added a zeropoint correction of 0.20 mag to the
-distance moduli reported by SNANA in the MLCS2k2 fit (dmMLCS2k2), to
-put them on the same scale as the SALT2 distances (dmSALT2).''
+\noindent  Here the parameters for light curve shape $s$ and color $C$ 
+correspond to the SiFTO light curve fitter \citep{Conley:2008}, so we
+first use the formulae from \citet{Guy:2010} to convert from SALT2
+($x_1$ and $c$) into the equivalent SiFTO parameters.  We also add an
+offset of 0.27 mag to the value of $m_B^*$ returned by SNANA, in order
+to match the arbitrary normalization of the SALT2 fitter used
+by \citet{Guy:2010} and \citet{Sullivan:2011}.  This conversion allows
+us to adopt values for the constants $M$, $\alpha$, and $\beta$
+from \citet{Sullivan:2011}, which have been calibrated using 472 SNe
+from the SNLS3 sample \citep{Conley:2011}: $M=-19.12\pm0.03$,
+$\alpha=1.367\pm0.086$, and $\beta=3.179\pm0.101$.
 
-\subsection{MLCS2k2 Fit}
-\label{sec:MLCS2k2Fit}
+\input{TABLE/lcfits}
 
-As in \citep{Patel:2014}.
+The SNANA version of the MLCS2k2 fitter returns a value for the
+distance modulus (dm$_{\rm MLCS2k2}$) that has an arbitrary zero point
+offset relative to the SALT2 distances (dm$_{\rm SALT2}$).  To put the
+two distances onto the same reference frame we add a zeropoint
+correction of 0.20 mag to the MLCS2k2 distances as
+in \citet{Patel:2014}.  This correction was derived by applying both
+fitters to a sample of Type Ia SNe from the SDSS
+survey \citep{Holtzman:2008,Kessler:2009b}, with the extinction law
+$R_V$ fixed at 1.9.
 
-$R_v$ fixed to 1.9.
+Final values for the SN distance modulus are shown in
+Table~\ref{tab:DistanceAndMagnification}, both for the spectroscopic
+redshift ($z=1.31$) and the photometric redshift ($z=1.35$).  The two
+light curve fitters are consistent within the uncertainties.
 
-for Rv = 1.9, the calibrated distance is: $\mu = \mu_{\rm mlcs}-0.2006$.
+\subsection{Magnification}
+\label{sec:Magnification}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.49\textwidth]{FIG/lcfit_mlcs2k2_ABmag}
-\caption{  Light curve fit using MLCS2k2. 
-\label{fig:mlcsfit} }
-\end{center}
-\end{figure}
+To measure the lensing magnification, we would like to avoid
+introducing systematic uncertainties inherent to any assumed
+cosmological model \citep[e.g.][]{Nordin:2014}.  To that end, we
+follow \citet{Patel:2014} and define the magnification by comparing
+the measured distance modulus of SN \tomas\ against an average
+distance modulus derived from a ``control sample'' of unlensed Type Ia
+SN at similar redshift.  This allows us to make only the minimal
+assumption that the redshift-distance relationship for Type Ia SN is
+smooth and approximately linear over a small redshift span, which
+should be true for any plausible cosmological model.
 
-\section{Lensing Magnification}
-\label{sec:LensingMagnification}
+The unlensed sample comprises 18 spectroscopically confirmed Type Ia
+SNe in the range $1.14\leq z \leq1.42$ from the GOODS and SCP
+surveys,\footnote{GOODS: Great Observatories Origins Deep Survey,
+PI:Giavalisco, HST-PID:; SCP: Supernova Cosmology Project,
+PI:Perlmutter} which used the HST Advanced Camera for
+Surveys \citep{Riess:2006,Suzuki:2012}.  Using the SALT2 and MLCS2k2
+fitters as described above, we get distance modulus measures for every
+object in this control sample.  We then fit a linear relationship for
+distance modulus vs. redshift, and derive a prediction for the
+distance modulus of a normal Type Ia SN at the redshift of SN \tomas
+(Figure~\ref{fig:MagnificationMeasurement}).
+This predicted value is given in
+Table~\ref{tab:DistanceAndMagnification} under the ``Control'' column.
+The difference between the observed distance of SN \tomas\ and this
+control sample value is attributed to the magnification from
+gravitational lensing:
 
-\subsection{Direct Magnification Measurement}
-\label{sec:DirectMagnificationMeasurement}
+\begin{equation} \label{eqn:mu}
+{\rm dm}_{\rm control} - {\rm dm}_{\rm \tomas} = 2.5 \log_{10}\mu.
+\end{equation}
+
+\noindent This inferred magnification is reported in the final column of
+Table~\ref{tab:DistanceAndMagnification}.
 
@@
 \includegraphics[width=\columnwidth]{FIG/magnification_measurement}
-\caption{ Deriving the magnification from comparison to field SN
-\label{fig:magmeasure} }
+\caption{ Measurement of the lensing magnification from comparison of
+the \tomas\ distance modulus to a sample of unlensed field SN.
+The distance modulus for each SN is derived from light curve fits
+using the SALT2 fitter (top panel) and the MLCS2k2 fitter (right).
+\label{fig:MagnificationMeasurement} }
 \end{center}

### 2015-03-13 TABLE/magnifications.tex
Finished writing discussion, summary and conclusions.

\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
\tablecolumns{5}
\tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
\startdata
%Sharon         & 2.57$^{+0.19}_{-0.16}$ &   \citealt{Jullo:2007} \\[2mm]
Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong lensing based model.\\
CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong+weak lensing based model.\\
Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac       & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & Free-form, strong+weak-lensing based model\\
Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{f} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{g} : Free-form strong+weak lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.
\enddata
\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : }
\tablenotetext{f}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies}
\end{deluxetable*}

### 2015-03-13 snTomas.tex
Finished writing discussion, summary and conclusions.

@@
 
-\title{Illuminating a Dark Lens : A Type Ia Supernova Magnified by Galaxy Cluster Abell 2744}
+\title{Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744}
 
@@
 \begin{abstract}
-SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.33$
+SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.31$
 behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
@@
 exinction.  In a cosmology-independent analysis, we find that \tomas\
-is $0.71\pm0.12$ magnitudes brighter than unlensed \SNeIa\ at similar
+is $0.75\pm0.10$ magnitudes brighter than unlensed \SNeIa\ at similar
 redshift, implying a lensing magnification of $\mu_{\rm
-obs}=1.9\pm0.2$.  Predicted magnifications from 7 independent groups
-are systematically biased to higher values, with a mean of $\mu_{\rm
-mod}=2.4\pm0.3$ and some models disagreeing by $>6\sigma$.  
-\textcolor{red}{TODO: summarize lensing discussion.}
-%The most
-%significant discrepancies arise from models with a strict ``light
-%traces mass'' assumption.  We evaluate possible causes for this bias,
-%including variation of the mass-to-light ratio in the nearest cluster
-%member galaxy.  A sample of \textcolor{red}{$\sim$10??} \SNeIa\ behind
-%any single cluster could provide a robust evaluation of systematic
-%biases in lens models.  Until such a sample exists, it is advisable to
-%increase the estimated uncertainty of any predicted magnification
-%by an amount comparable to the dispersion from all available lens
-%models.
-
+obs}=2.00\pm0.19$.  We compare this direct measurement of the
+magnification against predicted magnifications from 11 lens models,
+representing a broad range of methodologies and incorporating a
+variety of strong- and weak-lensing constraints.  The models are
+collectively fairly accurate, with a naive unweighted mean of
+$\mu_{\rm mod}=2.6$.  However, they are systematically biased to
+higher values: none of the tested models predict a magnification equal
+to or lower than the observed $\mu$, and some models are more than
+$5\sigma$ above the measured magnification.  We evaluate possible
+causes for this bias, and find that intercomparison of the lens models
+rules out several simple possibilities.  A larger sample of
+$\sim$10 \SNeIa\ behind any single cluster could provide a robust
+evaluation of systematic biases in lens models.  Until such a sample
+exists, it is advisable to increase the estimated uncertainty of any
+predicted magnification by an amount comparable to the dispersion from
+all available lens models.
 \end{abstract}
@@
 
+\textcolor{red}{TODO: write and polish introduction}.
 Massive galaxy clusters can be used as cosmic telescopes to magnify
@@
 
-Lensed SNe have been discovered
-\citep{Goobar:2009,Riehm:2011}
+\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Quimby:2014}.}
 
@@
 classification of the object as a normal Type Ia SN.  In
-Section~\ref{sec:LensingMagnification} we make a direct measurement of
+Section~\ref{sec:Magnification} we make a direct measurement of
 the magnification of this source due to gravitational lensing, and
-compare to predicitions from lens models.  Finally,
+compare to predictions from lens models.  Finally,
 Section~\ref{sec:Discussion} discusses the tension between our
@@
 redshift constraints: a photometric redshift for the most likely host
-galaxy is marked in blue, and the spectroscopic redshift for a likely
+galaxy is marked in blue, and the spectroscopic redshift for a
 background galaxy is given in yellow. The bottom panel is constructed
@@
 
-SN \tomas\ was discovered in \HST\ observations with the Advanced
-Camera for Surveys (ACS) in the F606W and F814W bands (V and i),
-collected on UT 2014 May 15 as part of the Hubble Frontier Fields
-(HFF) survey (PI:J.Lotz,
+SN \tomas\ was discovered in Hubble Space Telescop (\HST) observations
+with the Advanced Camera for Surveys (ACS) in the F606W and F814W
+bands (V and i), collected on UT 2014 May 15 as part of the Hubble
+Frontier Fields (HFF) survey (PI:J.Lotz,
 HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
@@
 fit the spectral energy distribution (SED) using the {\it BPZ} code --
-a Bayesian photometric redshift estimator \citep{Benitez:2000}. The best-fit
-SED template match is shown in Figure~\ref{fig:HostSED}.  From the
-{\it BPZ} analysis, we found the host to be most likely a late-type
-galaxy at a redshift of $z=1.5\pm0.2$.
+a Bayesian photometric redshift estimator \citep{Benitez:2000}. The
+best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
+From the {\it BPZ} analysis, we found the host to be most likely an
+actively star-forming galaxy at a redshift of $z=1.5\pm0.2$.  Another
+nearby bright galaxy to the East of the SN has a spectroscopic
+redshift of $z=1.742$, making it most likely a background object.
+This redshift was determined from a spectrum taken with the G141 grism
+of the HST WFC3-IR camera, collected as part of the Grism Lens
+Amplified Survey from Space (GLASS, PI:Treu, PID:13459).
 
-Upon discovery, HST target-of-opportunity
-observations were triggered from the FrontierSN program (PI:Rodney,
-HST-PID:13386), which aims to discover and follow transient sources in
-the HFF cluster and parallel fields. The FrontierSN observations
-provided WFC3-IR imaging as well as spectroscopy using the ACS G800L
-grism, supplementing the rapid-cadence optical imaging from HST+ACS
-already being provided by the HFF program. Difference images for the
-IR follow-up data were generated using templates constructed from the
-HFF WFC3-IR imaging campaign, which concluded in November, 2013.
+Upon discovery, HST target-of-opportunity observations were triggered
+from the FrontierSN program (PI:Rodney, HST-PID:13386), which aims to
+discover and follow transient sources in the HFF cluster and parallel
+fields. The FrontierSN observations provided WFC3-IR imaging as well
+as spectroscopy using the ACS G800L grism, supplementing the
+rapid-cadence optical imaging from HST+ACS already being provided by
+the HFF program. Difference images for the IR follow-up data were
+generated using templates constructed from the HFF WFC3-IR imaging
+campaign, which concluded in November, 2013.
 
@@
 
-As in \citet{Patel:2014}, we derive a distance modulus 
-from the SALT2 fit using\footnote{This avoids confusion by reserving the symbol $\mu$
-to refer to the lensing magnification. The 'dm' is a standard distance
-modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$ is the
-luminosity distance in Mpc.}
+As in \P14, we derive a distance modulus\footnote{We use 'dm' to
+indicate the distance modulus to avoid confusion, reserving the symbol
+$\mu$ to refer to the lensing magnification. This 'dm' is a standard
+distance modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$
+is the luminosity distance in Mpc.}  from the SALT2 fit using
 
@@
 
-\input{TABLE/lcfits}
+\input{TABLE/dist_mag}
 
@@
 correction of 0.20 mag to the MLCS2k2 distances as
-in \citet{Patel:2014}.  This correction was derived by applying both
+in \P14.  This correction was derived by applying both
 fitters to a sample of Type Ia SNe from the SDSS
@@
 Final values for the SN distance modulus are shown in
-Table~\ref{tab:DistanceAndMagnification}, both for the spectroscopic
+Table~\ref{tab:MeasuredMagnification}, both for the spectroscopic
 redshift ($z=1.31$) and the photometric redshift ($z=1.35$).  The two
@@
 cosmological model \citep[e.g.][]{Nordin:2014}.  To that end, we
-follow \citet{Patel:2014} and define the magnification by comparing
+follow \P14\ and define the magnification by comparing
 the measured distance modulus of SN \tomas\ against an average
@@
 This predicted value is given in
-Table~\ref{tab:DistanceAndMagnification} under the ``Control'' column.
+Table~\ref{tab:MeasuredMagnification} under the ``Control'' column.
 The difference between the observed distance of SN \tomas\ and this
@@
 \noindent This inferred magnification is reported in the final column of
-Table~\ref{tab:DistanceAndMagnification}.
+Table~\ref{tab:MeasuredMagnification}.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/magnification_measurement}
+\includegraphics[width=\columnwidth]{FIG/snTomas_hubble_diagram}
 \caption{ Measurement of the lensing magnification from comparison of
@@
 The distance modulus for each SN is derived from light curve fits
-using the SALT2 fitter (top panel) and the MLCS2k2 fitter (right).
+using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom panel).
 \label{fig:MagnificationMeasurement} }
@@
 
+\section{Discussion}
+\label{sec:Discussion}
+
 \subsection{Comparison to Model Predictions}
@@
 
-1) All of the lens models predict a higher magnification than we observe, some with discrepancies >5 sigma.
-This suggests a systematic bias inherent to all the models -- at least for this particular line of sight.
+Before the Frontier Fields observations began, the Space Telescope
+Science Institute (STScI) issued a call for lens modeling teams to
+generate mass models of all 6 Frontier Field clusters, using a shared
+collection of all imaging and spectroscopic data available at the
+time.  In response to this opportunity, five teams generated eight
+models for Abell 2744.  These models were necessarily quite
+preliminary, and they were principally intended to be used for quick
+estimation of magnifications for lensed background sources. An
+interactive web tool was created by D. Coe and hosted at STScI, to
+extract magnification estimates and uncertainties from each model for
+any given redshift and position.  In this work we also consider three
+additional models that were created later, taking advantage of new
+multiply-imaged galaxies discovered in the HFF imaging as well as new
+redshifts for lensed background galaxies.
 
-2) the addition of new lensing constraints from the HFF data does not reduce the tension.
-From both of the most recent models (Jauzac+ 2014 and Lam+ 2014) the predicted magnification is still significantly higher than the observed.
-
-3) The pre-HFF models that come closest to matching the observed magnification are the Zitrin-NFW and Merten models (also the Williams model, though it has very large uncertainties).
-Those happen to be two models that relax or remove the assumption of light-traces-mass.
+\input{TABLE/magnifications}
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/lensing_test}
+\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
 \caption{ 
 Comparison of the observed lensing magnification to predictions from
-lens models.
+lens models. Solid vertical lines show the constraints from SN \tomas\
+derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
+MLCS2k2 (blue) fitters, with shaded regions marking the total
+uncertainty for each. Markers with horizontal error bars show the
+median magnification and 68\%\ confidence region from each of the 10
+lensing models.  Circles indicate models that use only strong-lensing
+constraints, while diamonds denote those that also incorporate
+weak-lensing measurements.  Models shown with open markers were
+constructed using only data available before the start of the Frontier
+Fields observations.  Filled markers indicate models that use
+additional input constraints, including new multiply imaged systems
+and redshifts.  The seven models shown in black at the top are from
+the ``parametric'' family, and the four in green at the bottom are
+``free-form.''  The dashed grey line marks the unweighted mean of all
+model magnifications, with grey shading indicating the standard error
+of the mean from naively assuming all are independent predictions.
 \label{fig:lensingtest} }
@@
 
-\section{Discussion}
+Table~\ref{tab:PredictedMagnifications} lists the 11 models, giving
+for each one the predicted magnification and uncertainty for a source
+at $z=1.31\pm0.01$ and at the position of \tomas.  These
+models represent a broad sampling of the techniques and assumptions
+that can be applied to the modeling of mass distributions in galaxy
+clusters. A rigorous comparison of these disparate lens modeling
+techniques is beyond the scope of this work. Table 10 includes a brief
+description of each model, but for a complete discussion of the
+methodology the reader is referred to the listed references.
 
-Possible sources for the bias.
+In Figure~\ref{fig:lensingtest} the model predictions are plotted
+alongside the observed magnification of SN \tomas, derived in
+Section~\ref{sec:Magnification}.  This comparison shows that these 11
+models are largely consistent with each other. Naively treating each
+model as an independent prediction for the magnification (and ignoring
+their quoted uncertainties), one would get a mean for the full sample
+of $\mu=2.62\pm0.34$ (shown as a grey band in
+Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
+magnification by $\delta\mu/\mu=30\%$, which is a 1.7$\sigma$
+difference.
 
-Implications for the systematic error budget of high-z lenses.
+The models shown in Figure~\ref{fig:lensingtest} are separated along
+the $y$ direction into two broad classes, with the six {\it
+parametric} models on top and the four {\it free-form} models on the
+bottom.  Broadly speaking, parametric models use parameterized density
+distributions to describe the arrangement of mass within the cluster,
+typically associating massive dark matter halos with the positions of
+bright cluster member galaxies. Therefore, parametric models rely (to
+varying degrees) on the assumption that the observed light from
+cluster galaxies is a good tracer of the cluster's dark matter.
+Free-form models divide the cluster into a grid, generally using an
+adaptive mesh to get better sampling in denser regions. Each grid cell
+is assigned a mass, and then the grid spacing and the mass values are
+iteratively refined to match the observed lensing constraints.
 
-Design elements for a survey to build a bigger sample : HST GO, Snapshot, ground-based.
+Figure~\ref{fig:lensingtest} also separates the models based on the
+scope of input data constraints used.  Seven of the models rely only
+on strong-lensing constraints (plotted as circles), while the other
+four also use weak-lensing measurements (diamonds).  Eight of the
+models were constructed using only pre-HFF data (open symbols), and
+three others added new multiply-imaged systems and redshifts.
+
+In spite of the great variety in input data and methodology, these
+lens models overall are delivering consistent and fairly accurate
+estimates of the magnification.  Furthermore, the scatter amongst
+models provides a reasonable estimate of the magnification
+uncertainty.  This is largely in agreement with the results
+of \citetalias{Patel:2014} and \citet{Nordin:2014}.  The fact that the
+model predictions are collectively within $2\sigma$ of the observed
+magnification is especially encouraging for these Abell 2744
+models. This is a merging cluster with a complex mass distribution,
+and most of the models we are evaluating are preliminary products,
+generated quickly and without access to the rich data from the
+Frontier Fields program.
+
+However, beyond this first-order agreement, there is a systematic bias
+apparent. All of the lens models predict a magnification that is {\it
+higher} than the observed value, and no model has a median value that
+falls within the $1\sigma$ range of the observed magnifications.  It
+is important to emphasize that SN \tomas\ only samples a single
+sight-line through the cluster, so any conclusions to be drawn from
+this analysis are necesssarily limited.  Nevertheless, a systematic shift
+common to all models is surprising, given the wide range of modeling
+strategies, input data, and physical assumptions represented by this
+set of models.  In the following subsections we examine possible
+explanations for this apparently universal bias.
+
+\subsection{Nearby Cluster Member Galaxy}
+\label{sec:NearbyClusterMemberGalaxy}
+
+The line of sight to SN \tomas\ is 5\farcs8 from a bright cluster
+member galaxy, due North of the SN position (see
+Figure~\ref{fig:DiscoveryImage}).  If the mass-to-light ratio (M/L)
+for this galaxy were significantly different from the M/L for other
+cluster member galaxies, then its proximity to the SN sight-line could
+introduce a bias in the magnification.  This bias might be
+particularly acute for models that make a strict ``light traces mass''
+assumption, such as the Sharon, CATS, Jauzac, GLAFIC and Zitrin-LTM
+models.
+
+We tested this hypothesis using the Jauzac model by allowing the mass
+of the nearby cluster member galaxy to vary as a free parameter in the
+model. We found that the change in the SN \tomas\ magnification
+prediction was less than $\Delta\mu=0.1$.  This additional dispersion
+is already included in the uncertainties quoted for that model in
+Table~\ref{tab:PredictedMagnifications} and
+Figure~\ref{fig:lensingtest}.  Furthermore, an erroneous M/L
+value for the nearby cluster member galaxy could not explain the
+systematic shift of all lens models, because some do not incorporate
+cluster member galaxies into their constraints at all (the free-form
+Bradac, Williams and Merten models).
+
+\subsection{Sparse Strong Lensing Constraints}
+\label{sec:SparseStrongLensingConstraints}
+
+At the outset of the HFF survey, only 33 multiply-imaged galaxies
+behind Abell 2744 were known.  One might expect that the addition of
+new lensing constraints from the HFF data would improve the model
+constraints and reduce the tension between the predicted and observed
+magnification.  However, for both of the most recent
+models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
+constraints, the predicted magnification is still significantly higher
+than the observed value.  Again the CATS model family provides a
+useful case study.  The Jauzac model shares the same lens modeling
+software (LensTool), and the same primary methodology as the earlier
+CATS models.  A key difference is that the Jauzac model incorporates
+many new multiply imaged galaxies and corrects a mis-identified
+multiply-imaged system near the SN \tomas\ position.  These
+improvements should in principle make the Jauzac model magnification
+estimates more accurate, though we in fact see the opposite result:
+the Jauzac model predicts a $\mu$ that is higher than the measured
+value by $5.6\sigma$.
+
+This shift to higher magnifications is not, however, unique to the
+SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
+mass model of Abell 2744 results in a systematic increase in the
+magnification values across the cluster field. Examining a sample of
+$\sim$30 multiple images, \citeauthor{Jauzac} found that the
+magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
+models.  Although this single sight-line can only provide a very
+limited test of the model, the $5.6\sigma$ discrepancy is at least a
+strong suggestion that improving the number and quality of
+strong-lensing constraints can still lead to magnification maps that
+are susceptible to systematic biases.
+
+\subsection{Mass Profile Truncation}
+\label{sec:MassProfileTruncation}
+
+Seven of the mass models evaluated here are constrained only using
+strong-lensing features such as multiply-imaged background galaxies
+and highly magnified arcs.  There are now $\sim$150 known lensed
+images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
+located several arcseconds outside the core region of the cluster
+where these multiply-imaged galaxies are found.  Therefore these seven
+``strong-lensing only'' models must necessarily rely on extrapolations
+to provide a prediction for the SN \tomas\ magnification.  If the true
+cluster density profile for Abell 2744 happens to be truncated -- with
+a sharp drop right at the edge of this core strong-lensing region --
+then these seven models might well overestimate the mass interior to
+the \tomas\ position, and thus systematically overestimate the
+magnification.
+
+The other four models in our comparison set also use the strong
+lensing constraints from the core region, but also utilize weak
+lensing measurements to provide additional constraints on the mass
+distribution farther from the cluster core.  The signal from weak
+lensing relies on a large sample of background galaxies, so this
+constraint operates principally at separations more than 1\arcmin from
+the cluster core.  At a projected separation of $\sim40\arcsec$,
+SN \tomas\ falls in between the strong- and weak-lensing regimes, and
+one would expect that models incorporating both of those constraints
+would be less susceptible to the systematic bias of a truncated mass
+profile.  The lowest magnification estimate in our sample (from the
+Merten model) is among this sub-sample.  However, we find that
+collectively these four strong+weak models (shown as diamonds in
+Figure~\ref{fig:lensingtest}) exhibit the same propensity to
+overestimate the magnification along this line of sight.  Thus, a
+sudden change in the mass profile outside the strong lensing region is
+not a likely explanation for this small systematic bias.
+
+With two versions of the CATS model, we also have a more direct test
+of the effect of introducing weak lensing constraints.  The initial
+CATS model uses only strong-lensing constraints, and gives
+$\mu=2.27^{+0.05}_{-0.04}$, slightly higher than the measured value.
+A second iteration of this model, labeled here as CATS-SL+WL, used the
+same strong-lensing features, but added in weak lensing constraints.
+The revised magnification of $\mu=2.62\pm0.18$ is further from the
+measured value, which serves to reinforce the conclusion that adding
+weak lensing constraints cannot resolve this bias.
+
+\section{Summary and Conclusions}
+\label{sec:SummaryAndConclusions}
+
+The appearance of a Type Ia SN behind a massive galaxy cluster
+provides a rare opportunity to use a standard candle for a direct
+measurement of the absolute magnification due to gravitational
+lensing.  The discovery of SN \tomas\ in the HFF imaging of Abell 2744
+offers the first chance to apply this test on a cluster with multiple
+publicly-available lens models.  We have found that the spectrum and
+light curve of SN \tomas\ are well matched by templates of a normal
+Type Ia SN at $z=1.31\pm0.01$.  Using the two most prevalent \SNIa\
+light curve fitters, SALT2 and MLCS2k2, we get a consistent
+measurement of the distance modulus
+(Table~\ref{tab:MeasuredMagnification}).  Using a
+cosmology-independent comparison against a sample of unlensed \SNeIa\
+at similar redshifts, we find that SN \tomas\ is $\sim0.7$ magnitudes
+brighter than the field sample would predict.  Attributing this
+difference to the gravitational lensing magnification (and accounting
+for the intrinsic scatter in luminosity of the \SNIa\ population), we
+have derived a consistent measured magnification of $\mu_{\rm
+SALT2}=1.89\pm0.29$.  $\mu_{\rm MLCS2k2}=2.00\pm0.19$, from the two
+light curve fitters.
+
+Taking advantage of the availability of eleven well-constrained lens
+models for the Abell 2744 cluster, we have used SN \tomas\ to ask
+how accurately these lens models can predict the magnification along
+this line of sight.   We find that these models are consistent, and
+fairly accurate, collectively predicting $\mu=2.60\pm0.34$.  This is
+encouraging, and reinforces the quality and value of these public lens
+models for studying magnified background objects.   However, the fact
+that all models predict a larger magnification value than we observe
+is an indication that there is a small systematic bias inherent to
+this cluster or sight-line.
+
+We have speculated on the possible origin of this systematic bias,
+evaluating three possible causes:
+
+\begin{enumerate}
+\item The close proximity of a cluster member galaxy is leading to a
+biased magnification, because that galaxy's M/L is atypical.
+\item The models are limited by a scarcity of strong lensing constraints
+\item The cluster mass profile exhibits a sudden change outside of the core
+strong-lensing region, where we lack multiply-imaged background
+sources to constrain it. 
+\end{enumerate}
+
+\noindent None of these three explanations is completely
+satisfactory.  For each of these scenarios, we would expect that
+certain subsets of the available lens models would be less sensitive
+to the proposed systematic bias.  However, the small discrepancy
+between the predicted and observed lensing magnification is persistent
+when we bifurcate the sample of lens models according to methodology
+(parametric vs. free-form), number of strong-lensing constraints (pre-
+vs post-HFF), and scope of lensing constraints (strong-lensing only
+vs. strong+weak).  We do not have any definitive explanation for this
+magnification discrepancy.
+
+This single object behind a single cluster is not in and of itself a
+cause for alarm.  Previous analyses of lensed \SNIa\ found no
+significant discrepancy beween the observed \SNIa\ magnifications and
+the predictions from lens models
+(\citetalias{Patel:2014}; \citealt{Nordin:2014}), albeit with a much
+smaller set of lens models being tested.  The observed systematic bias
+for \tomas\ is small, and many of the lens models being evaluated are
+preliminary models that have not been updated to include all of the
+HFF data.  Future revisions of the lens models for Abell 2744 should
+either incorporate the observed magnification of \tomas\ as a new
+model constraint, or can revisit this test to evaluate whether the
+bias persists.
+
+Increasing the sample of SNe behind well studied strong lensing
+clusters would allow this test to be repeated and refined.  With 10 or
+100 such objects, it would be possible to see whether the SN \tomas\
+$\mu$ discrepancy is simply an outlier, or an indication of a more
+pernicious systematic error.  Any cluster that has been vetted by
+pencil-beam magnification tests using lensed \SNIa\ will be able to
+provide a more reliable measure of the magnifications for very high
+redshift objects.  Similarly, a broad sample of SNe like \tomas\ would
+help to define the preferred lens modeling methodology by highlighting
+any models that consistently perform well in \SNIa\ lensing tests.
+The ongoing FrontierSN program will discover and follow any more
+highly magnified SNe that appear behind the Frontier Field
+clusters. Unfortunately, the HFF survey is not designed with high-z
+transient discovery as a primary science goal, so the FrontierSN
+effort will likely add no more than 1-3 new lensed \SNIa. Further
+imaging of strong-lensing clusters with \HST\ or the James Webb Space
+Telescope (JWST) could enable a larger sample to be collected,
+especially if the filters and cadence are optimized for detection
+of \SNIa\ at $z>1$.  Massive clusters such as Abell 2744 will continue
+to be attractive as cosmic telescopes, allowing the next generation of
+telescopes to reach the faintest objects in the very early universe.
+The puzzling bias revealed by SN \tomas\ supports a concerted effort
+to improve these lenses with a larger sample of magnified SNe.
 

### 2015-03-23 TABLE/magnifications.tex
incorporating most of Marusa's comments.   * including adding in a section on redshift error

@@
 Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac       & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & Free-form, strong+weak-lensing based model\\
+Bradac       & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
 Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{f} : Free-form strong-lensing model using a genetic algorithm.  \\
 Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
-Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{g} : Free-form strong+weak lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.
+Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{g} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.
 \enddata

### 2015-03-23 snTomas.tex
incorporating most of Marusa's comments.   * including adding in a section on redshift error

@@
 \begin{abstract}
-SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.31$
+SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.31\pm0.01$
 behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
@@
 is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
-massive galaxy clusters, plus 6 accompanying ``parallel fields.''
+massive galaxy clusters, plus 6 accompanying parallel fields.
 Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
@@
 The {\tt SNID} library can generate an acceptable \CCSN\ match only
-when we remove all age and redshift constraints, In this case the best
+when we remove all age and redshift constraints. In this case the best
 non-Ia match is the Type Ic SN 1997ef, which delivers {\it rlap}$=6.8$
@@
 cosmological analyses \citep[see
-e.g.][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
+e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
 a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
@@
 magnification values across the cluster field. Examining a sample of
-$\sim$30 multiple images, \citeauthor{Jauzac} found that the
+$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
 magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
@@
 weak lensing constraints cannot resolve this bias.
+
+\subsection{Redshift Error}
+\label{sec:RedshiftError}
+
+If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
+were incorrect, then one would derive a different value for the
+magnification, both from the SN measurement and the lens model
+predictions.  Conceivably, this could resolve the tension between the
+measurement and the models.  It is often the case in SN surveys that
+redshifts are assigned based on a host galaxy association, typically
+inferred from the projected separation between the SN and nearby
+galaxies.  In this case the redshift evidence comes from the SN
+itself, and we find a consistent redshift from both the SN spectrum
+(Section~\ref{sec:SpecRedshift}) and the light curve
+Section~\ref{sec:PhotometricClassification}, which are both within the
+$1\sigma$ range of the photometric redshift for the nearest detected
+galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
+picture, so the evidence strongly disfavors any redshift that is
+significantly different from $z=1.3$.
+
+We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
+magnification comparison.  Spectroscopic redshifts are generally more
+precise and accurate than those derived from photometric
+observations \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
+this case the spectrum is limited to the rest-frame near-UV
+wavelengths, where the available SN spectral template libraries are
+more limited than at optical wavelengths.  If we use the photometric
+redshift of $z=1.35\pm0.02$ instead, then the measured magnification
+is reduced. \footnote{By increasing the redshift, the SN is presumed
+to be at a greater distance, so to first order one would be expect it
+to appear slightly fainter (larger distance modulus). If the distance
+modulus inferred from the light curve fit remained constant, this
+would drive the inferred magnification to a higher value.  However,
+the intrinsic peak brightness as derived from light curve fitting is
+more strongly affected by the covariance between redshift, color, and
+light curve width.  In this case, these effects drive the distance
+modulus to a larger value at $z=1.35$ that is closer to the unlensed
+population than we get at $z=1.31$.}  From the SALT2 fitter we derive
+$\mu_{\rm SALT2}=1.80\pm0.30$ and from MLCS2k2 we get $\mu_{\rm
+MLCS2k2}=1.83\pm0.17$.  The lens models are also shifted, and they
+uniformly move in the opposite direction, to magnification values that
+are {\it larger}, by $\sim1$\%.  Thus, shifting the SN to the
+photometric redshift of $z=1.35$ only serves to (slightly) exacerbate
+the tension between the observations and models.
 

### 2015-03-24 TABLE/magnifications.tex
implemented most of Chema's comments  and added updated magnification estimates from Bradac/Hoag and Chema to Table 3  and highlighting changes in blue  Note the new sections in the discussion on Redshift Error and System 3.3.

--- 2015-03-13 TABLE/magnifications.tex
@@
 Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac       & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & Free-form, strong+weak-lensing based model\\
-Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{f} : Free-form strong-lensing model using a genetic algorithm.  \\
+Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
+Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
+Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
 Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
-Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{g} : Free-form strong+weak lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.
+Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Diego\tablenotemark{i}			 & \nodata & 2.10$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
 \enddata
@@
 \tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
-\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
 \tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
@@
 \tablenotetext{g}{{\tt GRALE} : }
-\tablenotetext{f}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies}
+\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
+\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the Lam model.}}
 \end{deluxetable*}

### 2015-03-24 snTomas.tex
implemented most of Chema's comments  and added updated magnification estimates from Bradac/Hoag and Chema to Table 3  and highlighting changes in blue  Note the new sections in the discussion on Redshift Error and System 3.3.

@@
 spectroscopic exposure time of $\sim$10 ksec.  The grism data were
-processed and the target spectrum was extracted using the custom
-pipeline employed by the Grism Lens Amplified Survey from Space
-program (GLASS; PI:Treu, PID:13459). \textcolor{red}{Is there a
-citation for this? or more to say here?}
+processed and the target spectrum was extracted using a custom
+pipeline \citep{Brammer:2012}, which was developed for the 3D-HST
+program (PI:Van Dokkum; PID:12177, 12328) and also used by the Grism
+Lens Amplified Survey from Space (GLASS; PI:Treu; PID:13459).
 
@@
 for each one the predicted magnification and uncertainty for a source
-at $z=1.31\pm0.01$ and at the position of \tomas.  These
-models represent a broad sampling of the techniques and assumptions
-that can be applied to the modeling of mass distributions in galaxy
-clusters. A rigorous comparison of these disparate lens modeling
-techniques is beyond the scope of this work. Table 10 includes a brief
-description of each model, but for a complete discussion of the
-methodology the reader is referred to the listed references.
+at $z=1.31\pm0.01$ and at the position of \tomas.  These models
+represent a broad sampling of the techniques and assumptions that can
+be applied to the modeling of mass distributions in galaxy clusters. A
+rigorous comparison of these disparate lens modeling techniques is
+beyond the scope of this work. Table~\ref{tab:PredictedMagnifications}
+includes a brief description of each model, but for a complete
+discussion of the methodology the reader is referred to the listed
+references.
 
@@
 
+\change{
+\subsection{Misidentification of System 3}
+\label{sec:MisidentificationOfSystem3}
+}
+\change{
+It is important to note that in regards to the impact on this
+particular sight-line, not all strong-lensing constraints are equal.
+An error in the association of multiple images or 
+in the redshift of a multiply-imaged galaxy would have a
+more significant impact if that system has a projected position
+close to our SN sight-line.  It happens that there is one such system,
+for which the position of a multiple image near SN \tomas\ is presently disputed.  
+}
+
+\change{
+This multiply-imaged galaxy was originally labeled as {\it System 3}
+in \citet{Merten:2011}.  As shown in Figure~\ref{fig:System3}, it is
+stretched into two adjacent arcs northwest of the cluster core (images
+3.1 and 3.2), with a third image on the western edge of the
+strong-lensing region (image 3.3 at 00:14:18.595,
+-30:23:58.42).  \citet{Richard:2014} echoed this initial
+identification in producing the {\tt CATS} models, which we cite in
+Table~\ref{tab:PredictedMagnifications} and
+Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
+models, \citet{Johnson:2014} provided a secure spectroscopic
+constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
+the combined 3.1+3.2 source. The identification of the original image
+3.3 has been called into question by two independent analyses.  Using
+HFF imaging data, \citet{Lam:2014} suggested an alternative third
+image for this system roughly 8\arcsec\ to the south, which we will
+call \33p\ (00:14:18.39, -30:24:06.53).
+However, \citeauthor{Lam:2014} rejected this possibility based on a
+difference in colors between \33p\ and images 3.1 and 3.2.  In
+contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
+is correct, and find that reassigning this multiple image results in a
+tighter model reconstruction for the locations of other
+multiply-imaged systems in the vicinity.
+}
+
+\change{
+Resolving the identification of this single multiply-imaged galaxy
+could be an important component in resolving the magnification
+discrepancy, though it is unlikely to completely remove the tension.
+It is true that the model that reassigns the position to \33p\
+({\tt Jauzac}) is also the one with the largest deviation from our
+observed $\mu$ value.  However, the bias is still present even if we
+remove that model and only consider models using the original position
+3.3.  
+}
+
 \subsection{Mass Profile Truncation}
@@
 
-Seven of the mass models evaluated here are constrained only using
+Eight of the mass models evaluated here are constrained only using
 strong-lensing features such as multiply-imaged background galaxies
@@
 
-The other four models in our comparison set also use the strong
-lensing constraints from the core region, but also utilize weak
+The other three models in our comparison set also use the strong
+lensing constraints from the core region, but additionally utilize weak
 lensing measurements to provide additional constraints on the mass
@@
 Merten model) is among this sub-sample.  However, we find that
-collectively these four strong+weak models (shown as diamonds in
+collectively these three strong+weak models (shown as diamonds in
 Figure~\ref{fig:lensingtest}) exhibit the same propensity to
@@
 
+\change{
 If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
@@
 significantly different from $z=1.3$.
+}
 
+\change{
 We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
@@
 redshift of $z=1.35\pm0.02$ instead, then the measured magnification
-is reduced. \footnote{By increasing the redshift, the SN is presumed
-to be at a greater distance, so to first order one would be expect it
-to appear slightly fainter (larger distance modulus). If the distance
+is reduced.\footnote{By increasing the redshift, the SN is presumed to
+be at a greater distance, so to first order one would be expect it to
+appear slightly fainter (larger distance modulus). If the distance
 modulus inferred from the light curve fit remained constant, this
 would drive the inferred magnification to a higher value.  However,
-the intrinsic peak brightness as derived from light curve fitting is
-more strongly affected by the covariance between redshift, color, and
-light curve width.  In this case, these effects drive the distance
-modulus to a larger value at $z=1.35$ that is closer to the unlensed
-population than we get at $z=1.31$.}  From the SALT2 fitter we derive
-$\mu_{\rm SALT2}=1.80\pm0.30$ and from MLCS2k2 we get $\mu_{\rm
-MLCS2k2}=1.83\pm0.17$.  The lens models are also shifted, and they
-uniformly move in the opposite direction, to magnification values that
-are {\it larger}, by $\sim1$\%.  Thus, shifting the SN to the
-photometric redshift of $z=1.35$ only serves to (slightly) exacerbate
-the tension between the observations and models.
+the light curve fitting is more strongly affected by the covariance
+between redshift, color, and light curve width.  In this case, these
+effects drive the distance modulus to a larger value at $z=1.35$,
+resulting in a smaller value of the observed magnification $\mu$.}
+From the SALT2 fitter we derive $\mu_{\rm SALT2}=1.80\pm0.30$ and from
+MLCS2k2 we get $\mu_{\rm MLCS2k2}=1.83\pm0.17$.  The lens models are
+also shifted, and they uniformly move in the opposite direction, to
+magnification values that are {\it larger} than at $z=1.31$, by
+$\sim1$\%.  Thus, shifting the SN to the photometric redshift of
+$z=1.35$ only serves to (slightly) exacerbate the tension between the
+observations and models.
+}
 
@@
 
-We have speculated on the possible origin of this systematic bias,
-evaluating three possible causes:
+We have speculated on the origin of this systematic bias,
+evaluating five possible causes:
 
@@
 sources to constrain it. 
+\item \change{The redshift assigned to SN \tomas\ is in error.}
+\item \change{SN \tomas\ is not a normal Type Ia SN.}
 \end{enumerate}
 
-\noindent None of these three explanations is completely
-satisfactory.  For each of these scenarios, we would expect that
-certain subsets of the available lens models would be less sensitive
-to the proposed systematic bias.  However, the small discrepancy
-between the predicted and observed lensing magnification is persistent
-when we bifurcate the sample of lens models according to methodology
-(parametric vs. free-form), number of strong-lensing constraints (pre-
-vs post-HFF), and scope of lensing constraints (strong-lensing only
-vs. strong+weak).  We do not have any definitive explanation for this
-magnification discrepancy.
+\noindent The first three of these take on the discrepancy from 
+the lens modeling side, but none are completely satisfactory. For each
+of these scenarios, we would expect that certain subsets of the
+available lens models would be less sensitive to the proposed
+systematic bias.  However, the small discrepancy between the predicted
+and observed lensing magnification is persistent when we bifurcate the
+sample of lens models according to methodology (parametric
+vs. free-form), number of strong-lensing constraints (pre- vs
+post-HFF), and scope of lensing constraints (strong-lensing only
+vs. strong+weak). Thus, comparison of the available models does not
+provide any definitive explanation for this magnification tension.
+
+\change{
+The last two possible explanations presume an error in the
+interpretation of the available SN data.  We reject the possibility
+that a redshift error is the primary cause of the discrepancy, as the
+redshift evidence is derived principally from the SN itself and not
+from the host galaxy. A value of $z\sim1.3$ is well supported by both
+the spectroscopic and photometric SN data, and changing the redshift
+within the constraints of these complementary observations only serves
+to increase the tension between the observed and predicted
+magnifications.
+}
+
+\change{
+Finally, we have considered whether the SN could be
+mis-classified. Once again the combination of spectroscopic and
+photometric evidence strongly supports our classification of
+SN \tomas\ as a normal Type Ia SN.  The most plausible
+mis-classification would be that the object is a peculiar Type Ia of
+the SN 2006bt-like sub-class.  We find this possibility to be 
+ \textcolor{red}{TODO: summarize the 06bt misclassification discussion}
+}
 
@@
 
-We are very pleased to thank the Hubble Frontier Fields team at STScI
+We are p
+
+We thank the Hubble Frontier Fields team at STScI
 for their substantial efforts to make the HFF program successful.  In
@@
 
+J.M.D acknowledges support of the consolider project CAD2010-00064 and
+AYA2012-39475-C02-01 funded by the Ministerio de Economia y
+Competitividad.
+
 {\it Facilities:} \facility{HST (WFC3)}

### 2015-04-01 TABLE/magnifications.tex
incorporated comments from Julian and Tommaso}

@@
 Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
-Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  SaWLENS, free-form strong+weak lensing based model.\\
+Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
 Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
@@
 \tablenotetext{g}{{\tt GRALE} : }
+\tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
 \tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}

### 2015-04-01 snTomas.tex
incorporated comments from Julian and Tommaso}

@@
 \begin{abstract}
-SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at $z=1.31\pm0.01$
-behind the galaxy cluster Abell 2744 ($z=0.308$). This SN has a
-projected separation from the cluster core of $\sim$40\arcsec, closer
-than any other cluster-lensed \SNIa.  As such, it provides the first
-opportunity to confront gravitational lens models of galaxy clusters
-with the direct measurement of an absolute magnification at the edge
-of the strong-lensing region.  We derive a tightly constrained measure
-of the peak apparent magnitude, corrected for light curve shape and
+SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
+$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
+SN has a projected separation from the cluster core of
+$\sim$40\arcsec, closer to the critical lensing line than any previous
+cluster-lensed \SNIa.  As such, it provides the first opportunity to
+confront gravitational lens models of galaxy clusters with the direct
+measurement of an absolute magnification at the edge of the
+strong-lensing region.  We derive a tightly constrained measure of the
+peak apparent magnitude, corrected for light curve shape and
 exinction.  In a cosmology-independent analysis, we find that \tomas\
@@
 representing a broad range of methodologies and incorporating a
-variety of strong- and weak-lensing constraints.  The models are
-collectively fairly accurate, with a naive unweighted mean of
-$\mu_{\rm mod}=2.6$.  However, they are systematically biased to
-higher values: none of the tested models predict a magnification equal
-to or lower than the observed $\mu$, and some models are more than
-$5\sigma$ above the measured magnification.  We evaluate possible
-causes for this bias, and find that intercomparison of the lens models
-rules out several simple possibilities.  A larger sample of
-$\sim$10 \SNeIa\ behind any single cluster could provide a robust
-evaluation of systematic biases in lens models.  Until such a sample
-exists, it is advisable to increase the estimated uncertainty of any
-predicted magnification by an amount comparable to the dispersion from
-all available lens models.
+variety of strong- and weak-lensing constraints. 
+The models are collectively fairly accurate, with 3 that are
+consistent within the 1$\sigma$ uncertainties.
+% a naive unweighted mean of  $\mu_{\rm mod}=2.6$.  
+However, the models are systematically biased to higher values: none
+of the tested models predict a magnification equal to or lower than
+the observed $\mu$, and some models are more than $5\sigma$ above the
+measured magnification.  We evaluate possible causes for this bias,
+and find that intercomparison of the lens models rules out several
+simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
+single cluster could provide a robust evaluation of systematic biases
+in lens models.  Until such a sample exists, it is advisable
+to \change{increase the estimated uncertainty of predicted
+magnifications to match the dispersion observed across multiple lens
+models.}
 \end{abstract}
@@
 
+\change{
+One of the key values in observing standard candles behind
+gravitational lenses is that {\it all} lensing reconstructions suffer
+from the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
+degeneracy arises because one can introduce into a lens model an
+unassociated sheet of mass in front of or behind the lens, without
+disturbing the primary observable quantities.  For example, take a
+lens model with a given surface mass density $\kappa$, and then
+transform the surface mass density to
+$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
+$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
+produce exactly the same values for all positional and shear
+constraints from strong and weak lensing.  This is the simplest case
+illustrating a positional constraint degeneracy, but there are more
+complex versions \citep{Schneider:2014}.  Such mass sheet
+degeneracies do not extend to the \citep{absolute} magnification of a
+background source's flux and size.  Therefore, an absolute measurement
+of magnification from a standard candle or a standard ruler
+\citep{Sonnenfeld:2011}  can break this fundamental degeneracy
+\citep{Holz:2001}.
+}
+
 In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
 follow-up observations of SN \tomas at $z=1.31$, discovered behind the
-galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy} and \ref{sec:PhotometricClassification}
-describe the spectroscopy and photometry of this SN, leading to a
-classification of the object as a normal Type Ia SN.  In
-Section~\ref{sec:Magnification} we make a direct measurement of
-the magnification of this source due to gravitational lensing, and
-compare to predictions from lens models.  Finally,
-Section~\ref{sec:Discussion} discusses the tension between our
-magnification measurement and the lens models, with implications for
-the systematic error budget in magnification estimates for other
+galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
+and \ref{sec:PhotometricClassification} describe the spectroscopy and
+photometry of this SN, leading to a classification of the object as a
+normal Type Ia SN.  In Section~\ref{sec:LightCurveFitting} we make a
+direct measurement of the magnification of this source due to
+gravitational lensing, and compare to predictions from lens models.
+Finally, Section~\ref{sec:Discussion} discusses the tension between
+our magnification measurement and the lens models, with implications
+for the systematic error budget in magnification estimates for other
 high-$z$ lensed sources.
@@
 UV/Optical/IR color composite image constructed from all available HST
-imaging of the Abell 2744 cluster field.  The inset panels at right
+imaging of the Abell 2744 cluster field.  The inset panels on the right
 show F814W imaging of the immediate vicinity of SN \tomas,
@@
 From the {\it BPZ} analysis, we found the host to be most likely an
-actively star-forming galaxy at a redshift of $z=1.5\pm0.2$.  Another
-nearby bright galaxy to the East of the SN has a spectroscopic
-redshift of $z=1.742$, making it most likely a background object.
-This redshift was determined from a spectrum taken with the G141 grism
-of the HST WFC3-IR camera, collected as part of the Grism Lens
-Amplified Survey from Space (GLASS, PI:Treu, PID:13459).
+actively star-forming galaxy at a redshift of $z=1.5\pm0.2$.
+
+Another nearby bright galaxy to the East of the SN has a spectroscopic
+redshift of $z=1.742$.  This redshift was determined from a spectrum
+taken with the G141 grism of the HST WFC3-IR camera, collected as part
+of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
+PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
+and \ref{sec:PhotometricClassification}, the SN data are inconsistent
+with that redshift, meaning that this nearby galaxy is a background
+object and therefore has no impact on the SN classification or
+luminosity measurement.}
 
@@
 rapid-cadence optical imaging from HST+ACS already being provided by
-the HFF program. Difference images for the IR follow-up data were
-generated using templates constructed from the HFF WFC3-IR imaging
-campaign, which concluded in November, 2013.
+the HFF program. \change{The last detections in the IR F105W and F140W
+bands came from the direct-imaging component of the GLASS program}.
+Difference images for the IR follow-up data were generated using
+templates constructed from the HFF WFC3-IR imaging campaign, which
+concluded in November, 2013.
 
@@
 of a SN spectrum through cross-correlation matching with a library of
-template spectra.  To account for possible distortions in the broad
-shape of the SN pseudo-continuum due to dust or instrumental
-calibration effects, SNID divides each SED by a smooth cubic spline
-fit. This effectively removes the shape of the SN pseudo-continuum to
-leave behind a flat SED superimposed with spectral absorption and
-emission features.  It is these features which drive the
-cross-correlation fit, so the SNID approach is insensitive to the
-overall color of the SED.  We used v2.0 of the SNID template library,
-which includes template SEDs covering all Type Ia and Core Collapse
-sub-classes, and has recently been updated with corrections and
-improvements to the Type Ib/c templates \citep{Liu:2014}.
+template spectra, \change{using the algorithm of \citet{Tonry:1979}.}
+To account for possible distortions in the broad shape of the SN
+pseudo-continuum due to dust or instrumental calibration effects, SNID
+divides each SED by a smooth cubic spline fit. This effectively
+removes the shape of the SN pseudo-continuum to leave behind a flat
+SED superimposed with spectral absorption and emission features.  It
+is these features which drive the cross-correlation fit, so the SNID
+approach is insensitive to the overall color of the SED.  We used v2.0
+of the SNID template library, which includes template SEDs covering
+all Type Ia and Core Collapse sub-classes, and has recently been
+updated with corrections and improvements to the Type Ib/c
+templates \citep{Liu:2014}.
 
@@
 
-The {\tt SNID} library can generate an acceptable \CCSN\ match only
+Using {\tt SNID} we can find an acceptable \CCSN\ match only
 when we remove all age and redshift constraints. In this case the best
@@
 photometric information, which also supports classification as a Type
-Ia SN at $z=1.3$.
+Ia SN at $z\approx1.3$.
 
@@
 probability using traditional Bayesian model selection \citep[as
-in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015}.  In this
+in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015a}.  In this
 analysis we represent normal Type Ia SNe with the SALT2
@@
 $p({\rm Ia}|{\rm {\bf D}})=1.0$, with the classification probability
-from all \CCSN\ sub-classes totaling less than $10^{-32}$.  The
-best-fit models for each sub-class are shown in
-Figure~\ref{fig:photoclass}, which demonstrates that the \CCSN\ models
-cannot adequately match the observed photometry. In particular, only
-the Type Ia model can simultaneously provide an acceptable fit to the
-well-sampled rising light curve in F814W and the F814W-F160W
-color near peak.
+from all \CCSN\ sub-classes totaling less than
+$10^{-32}$.  \change{Although this Bayesian classification utilizes
+the full posterior probability distribution, for illustration we
+highlight in Figure~\ref{fig:photoclass} a single best-fit model for
+each sub-class.} This demonstrates how the \CCSN\ models fail to
+adequately match the observed photometry. In particular, only the Type
+Ia model can simultaneously provide an acceptable fit to the
+well-sampled rising light curve in F814W and the F814W-F160W color
+near peak.
 
@@
 With the spectroscopic type and redshift securely defined as a normal
-Type Ia SN at $z=1.3$, we now turn to fitting the light curve with
+Type Ia SN at $z=1.31$, we now turn to fitting the light curve with
 Type Ia templates to measure the distance modulus.  Here we use two
@@
 surveys,\footnote{GOODS: Great Observatories Origins Deep Survey,
-PI:Giavalisco, HST-PID:; SCP: Supernova Cosmology Project,
+PI:Giavalisco, HST-PID:9425,9583; SCP: Supernova Cosmology Project,
 PI:Perlmutter} which used the HST Advanced Camera for
@@
 time.  In response to this opportunity, five teams generated eight
-models for Abell 2744.  These models were necessarily quite
-preliminary, and they were principally intended to be used for quick
-estimation of magnifications for lensed background sources. An
-interactive web tool was created by D. Coe and hosted at STScI, to
-extract magnification estimates and uncertainties from each model for
-any given redshift and position.  In this work we also consider three
+models for Abell 2744.  \change{These models necessarily relied on
+pre-HFF data, and were required to be complete before the HFF program
+began, in order to enable the estimation of magnifications for any new
+lensed background sources revealed by the HFF imaging.} An interactive
+web tool was created by D. Coe and hosted at STScI, to extract
+magnification estimates and uncertainties from each model for any
+given redshift and position.  In this work we also consider three
 additional models that were created later, taking advantage of new
@@
 The models shown in Figure~\ref{fig:lensingtest} are separated along
-the $y$ direction into two broad classes, with the six {\it
-parametric} models on top and the four {\it free-form} models on the
-bottom.  Broadly speaking, parametric models use parameterized density
+the $y$ direction into two broad classes, with the
+six \change{so-called} {\it parametrized} models on top and the four
+{\it free-form} models on the bottom.\footnote{\change{Although this
+nomenclature is becoming standard in the literature, it is somewhat
+misleading, as the pixels or grid cells in free-form models are
+effectively parameters as well. Perhaps ``simply-parameterized'' would
+be more accurate, though we adopt the more common usage here.}}
+Broadly speaking, the parametric models use parameterized density
 distributions to describe the arrangement of mass within the cluster,
@@
 adaptive mesh to get better sampling in denser regions. Each grid cell
-is assigned a mass, and then the grid spacing and the mass values are
-iteratively refined to match the observed lensing constraints.
+is assigned a mass or a potential, and then the grid spacing and the
+mass values are iteratively refined to match the observed lensing
+constraints.
 
@@
 lens models overall are delivering consistent and fairly accurate
-estimates of the magnification.  Furthermore, the scatter amongst
+estimates of the magnification.  \change{Four of the tested models
+(CATS, GLAFIC, Zitrin-NFW, Merten) report a median value that falls
+within the 1$\sigma$ uncertainty range of the measured magnification,
+and two of the models (Williams, Merten) report uncertainties that
+overlap the central $\mu$ from at least one of the light curve
+fitters.}  Furthermore, the scatter amongst
 models provides a reasonable estimate of the magnification
-uncertainty.  This is largely in agreement with the results
+uncertainty.
+
+This is largely in agreement with the results
 of \citetalias{Patel:2014} and \citet{Nordin:2014}.  The fact that the
@@
 
+\subsection{Foreground Dust}
+\label{sec:ForegroundDust}
+
+\change{
+All SN sight-lines must intersect some amount of foreground dust from
+the immediate circumstellar environment, the host galaxy, and the
+intergalactic medium (IGM). In the case of SN \tomas\ one might posit
+some dust extinction from the intra-cluster medium (ICM) of Abell
+2744, although measurements of rich clusters suggest that the ICM has
+only a negligible dust
+content \citep{Maoz:1995,Stickel:2002,Bai:2007}.  When fitting
+the \tomas\ light curve we account for dust by including corrections
+that modify the inferred luminosity distance based on the SN color.
+If after applying these dust corrections we are still {\it
+underestimating} the effect of dust along this sight-line, then the SN
+would appear more dim, the inferred distance modulus would be higher,
+and the measured magnification would be reduced -- consistent with the
+discrepancy we observe.  
+}
+
+\change{
+One might suppose that a bias could be introduced if we have adopted
+incorrect values for the color correction parameter $\beta$ or
+extinction law $R_V$ in the SALT2 and MLCS2k2 fits, respectively.  The
+appropriate value to use for this color correction and how it affects
+inferences about the intrinsic scatter in Type Ia SN luminosities is a
+complex question that is beyond the scope of this work \citep[see
+e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
+However, we can already rule this out as a solution for the
+magnification discrepancy.  Our error on the \tomas\ distance modulus
+already includes an uncertainty in the extinction law and a related
+error to account for the intrinsic luminosity scatter. These are well
+vetted paraemeters, based on observations of $\sim500$ SNe extending
+to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, changing the color
+correction applied to SN \tomas\ would requre the same adjustment to
+be applied to the unlensed SNe at similar redshift that make up our
+comparison sample, unless one proposes without evidence that
+SN \tomas\ is uniquely affected by a peculiar type of dust.  
+}
+
+\change{
+The traditional color corrections as formalized in SN light curve
+fitters are designed to account for a dust component that lies in the
+rest frame of the SN.  The inferred luminosity of a SN can also be
+affected by the presence of foreground dust with a different redshift
+and possibly a different reddening law \citep{Menard:2010b}.  However,
+the magnitude of such a bias is insufficient to account for the
+observed discrepancy, \citet{Menard:2010a} estimate the opacity of the
+universe as $\langle A_{V}\rangle\sim0.03$ mag up to $z=0.5$.  While
+this can have a measurable impact on precise cosmological constraints,
+it is far less than the 0.285 mag difference between the observed
+magnification of \tomas\ and the mean of the model predictions.  
+}
+
+\section{Misclassification}
+\label{sec:Misclassification}
+
+\textcolor{red}{TODO : discuss 2006bt-like misclassification}
+
+\change{
+In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
+the blue end of the normal range of Type Ia SN colors.  With the SALT2
+fitter we measured a color parameter $c=-0.115\pm0.025$, and with
+MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
+V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
+as we are fitting to photometry that covers a rest-frame wavelength
+range from $\sim3500-7000$\AA and extends to $\sim$30 days past
+maximum brightness.
+
+\textcolor{red}{TODO : discuss 2006bt-like colors}
+}
+
 \section{Summary and Conclusions}
@@
 \item \change{The redshift assigned to SN \tomas\ is in error.}
+\item \change{The color corrections for SN \tomas\ underestimate the foreground dust.}
 \item \change{SN \tomas\ is not a normal Type Ia SN.}
@@
 bias persists.
+
+\change{
+A promising avenue for exploring the origins of systematic biases in
+cluster lens models is through the use of simulated data.  One can
+start with very deep high-resolution multi-band imaging on an unlensed
+field that has a fairly complete spectroscopic redshift catalog, such
+as the Hubble Ultra Deep Field.  Then a simulated galaxy cluster is
+placed in the field, and the background galaxies are distorted into
+arcs and multiple images using a well-defined lensing prescription.
+The artificially lensed images can then be distributed to lens
+modeling teams who attempt to reconstruct the (known) mass profile of
+the simulated cluster.  This exercise has recently been pursued with a
+set of synthetic clusters similar to those observed in the HFF program
+(Meneghetti et al. in prep).  Preliminary analysis of this simulation
+comparison suggests that systematic biases such as we have seen for
+SN \tomas\ may be common for sources that lie close to the critical
+curve in elongated and highly asymmetric clusters like Abell 2744.
+This SN analysis indicates that such simulation efforts will be an
+important step for moving toward precision science with cluster-lensed
+sources. 
+}
 
@@
 The puzzling bias revealed by SN \tomas\ supports a concerted effort
-to improve these lenses with a larger sample of magnified SNe.
+to improve these lenses with \change{further examination of lensing
+systematics through simulations and collection of} a larger sample of
+magnified SNe.
 
@@
 
-We are p
+This work is dedicated to our colleague and friend Tomas Dahlen
+(-2014), for whom this supernova has been named in memorium. He is
+greatly missed.
 
@@
 
-Financial support for this work was provided by NASA through grants
+Financial support for this work was provided to SAR by NASA through grants
 HST-HF-51312 and HST-GO-13386 from the Space Telescope
 Science Institute, which is operated by Associated Universities for
-Research in Astronomy, Inc., under NASA contract NAS 5-26555.  Support
-for this research at Rutgers University was provided in part by NSF
-CAREER award AST-0847157 to SWJ.  The Dark Cosmology Centre is
+Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+
+Support for this research at Rutgers University was provided in part
+by NSF CAREER award AST-0847157 to SWJ.  The Dark Cosmology Centre is
 supported by the Danish National Research Foundation.
@@
 
+J.M. contributed to this research from the Jet Propulsion Laboratory,
+California Institute of Technology, under a contract with NASA and
+acknowledges support from NASA Grants HST-GO-13343.05-A and
+HST-GO-13386.13-A. The research leading to these results has received
+funding from the People Programme (Marie Curie Actions) of the European
+Union's Seventh Framework Programme (FP7/2007-­2013) under REA grant
+agreement number 627288.
+
 {\it Facilities:} \facility{HST (WFC3)}

### 2015-04-02 TABLE/magnifications.tex
incorporated some comments from TT,RF,MJ: UNCERTAINTY CHANGE   *  This iteration includes a significant change in the measured magnification uncertainty,     correcting an oversight in prior versions (I had dropped the error term accounting for the     intrinsic scatter in SN Ia luminosities... thanks to Ryan and Saurabh for correction)

@@
 \startdata
-%Sharon         & 2.57$^{+0.19}_{-0.16}$ &   \citealt{Jullo:2007} \\[2mm]
+Sharon(v1)   & 2.53 & 2.57$^{+0.18}_{-0.16}$ & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\
 Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
-CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong lensing based model.\\
-CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL hybrid parametric/free-form, strong+weak lensing based model.\\
+CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
+CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
 Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\

### 2015-04-02 snTomas.tex
incorporated some comments from TT,RF,MJ: UNCERTAINTY CHANGE   *  This iteration includes a significant change in the measured magnification uncertainty,     correcting an oversight in prior versions (I had dropped the error term accounting for the     intrinsic scatter in SN Ia luminosities... thanks to Ryan and Saurabh for correction)

@@
 exinction.  In a cosmology-independent analysis, we find that \tomas\
-is $0.75\pm0.10$ magnitudes brighter than unlensed \SNeIa\ at similar
-redshift, implying a lensing magnification of $\mu_{\rm
-obs}=2.00\pm0.19$.  We compare this direct measurement of the
-magnification against predicted magnifications from 11 lens models,
-representing a broad range of methodologies and incorporating a
-variety of strong- and weak-lensing constraints. 
-The models are collectively fairly accurate, with 3 that are
-consistent within the 1$\sigma$ uncertainties.
-% a naive unweighted mean of  $\mu_{\rm mod}=2.6$.  
+is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
+similar redshift, implying a lensing magnification
+of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
+measurement of the magnification against predicted magnifications
+from \change{14 lens models,} representing a broad range of
+methodologies and incorporating a variety of strong- and weak-lensing
+constraints.  The models are collectively fairly accurate. \change{
+Half of the models deliver median magnifications that are consistent
+with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
 However, the models are systematically biased to higher values: none
@@
 
-\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Quimby:2014}.}
+\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Li:2012,Quimby:2014}.}
 
@@
 complex versions \citep{Schneider:2014}.  Such mass sheet
-degeneracies do not extend to the \citep{absolute} magnification of a
+degeneracies do not extend to the {\it absolute} magnification of a
 background source's flux and size.  Therefore, an absolute measurement
@@
 with that redshift, meaning that this nearby galaxy is a background
-object and therefore has no impact on the SN classification or
-luminosity measurement.}
+object and therefore has no impact on the SN magnification.}
 
@@
 
+\change{
+The total uncertainty in the distance modulus is  
+}
+
+\begin{equation} \label{eqn:sigmatot}
+ \sigma_{\rm tot} = \sqrt{ \sigma_{\rm stat}^2 + \sigma_{int}^2}.
+\end{equation}
+
+\change{
+\noindent
+The $\sigma_{\rm stat}$ term is the statistical uncertainty, which
+encapsulates uncertainties from the data and the model, and
+$\sigma_{\rm int}$ accounts for the remaining {\it unmodeled} scatter.
+This latter term is derived by finding the amount of additional
+distance modulus scatter that needs to be added to a Type Ia SN
+population to get $\chi^2$ per degree of freedom equal to 1 for a
+fiducial cosmological model fit to the SN Ia Hubble diagram (distance
+modulus vs redshift).  Thus, $\sigma_{\rm int}$ is designed to
+account for any unknown sources of scatter in the Type Ia SN
+population, including unidentified errors in the data analysis as well
+as the natural scatter in intrinsic Type Ia SN luminosities.  The value of 
+$\sigma_{\rm int}$ may be expected to vary as a function of
+redshift and also from survey to survey.  
+}
+
+\change{
+Recent work has highlighted the inadequacy of this simplistic approach
+for handling intrinsic scatter in the Type Ia SN
+population \citep{Marriner:2011,Kessler:2013,Mosher:2014,Scolnic:2014a,Betoule:2014},
+but a full consideration of those alternative approaches is beyond the
+scope of this work.  We adopt the simple approach of using a single
+empirically defined value for $\sigma_{\rm int}$, reflecting
+principally an intrinsic scatter in Type Ia SN intrinsic luminosity
+that is fixed across time and phase.  Measurements of $\sigma_{\rm
+int}$ range from 0.08 mag \citep{Jha:2007,Conley:2011} to 0.15
+mag \citep{Kessler:2009b,Suzuki:2012}.  We adopt a value of
+$\sigma_{\rm int}=0.08$ mag, as derived by \citet{Jha:2007}
+and \citet{Conley:2011}.  Although this is on the low end of the range
+reported in the literature, this value is the most appropriate to
+apply to our analysis for two reasons.  First and foremost, for the
+SALT2 fitter we are using light curve fit parameters
+($\alpha$,$\beta$) with associated uncertainties that have been
+derived from the joint analysis of \citet{Conley:2011}
+and \citet{Sullivan:2011}. Similarly, the implementation of MLCS2k2
+that we have used is based on the uncertainty model derived from model
+training in \citet{Jha:2007}.  Inflating $\sigma_{int}$ beyond 0.08
+mag would therefore be equivalent to driving the reduced $\chi^2$ of
+the Type Ia SN Hubble diagram to $<1$.  Second, the value of 0.08 mag
+determined in \citet{Conley:2011} is specific to the HST SN sample,
+from \citet{Riess:2007} and \citet{Suzuki:2011}, which is the SN
+subset that is most similar to \tomas\ in terms of redshift and data
+analysis.  Larger values for $\sigma_{\rm int}$ are typically
+associated with SN samples at significantly lower redshifts that have
+less homogeneous data collection and analysis. }
+
+\change{
 Final values for the SN distance modulus are shown in
-Table~\ref{tab:MeasuredMagnification}, both for the spectroscopic
-redshift ($z=1.31$) and the photometric redshift ($z=1.35$).  The two
-light curve fitters are consistent within the uncertainties.
+Table~\ref{tab:MeasuredMagnification}, adopting the spectroscopic
+redshift ($z=1.31$).  In addition to modifying the distance modulus
+uncertainty for SN \tomas, we also add $\sigma_{\rm int}=0.08$ mag in
+quadrature to the uncertainty for every SN in the control sample. Note
+however that the uncertainty on the control sample value at $z=1.31$
+is only 0.05 mag, smaller than the intrinsic dispersion because it
+reflects only our measurement error on the mean distance modulus of
+the population.  The distance moduli derived from the SALT2 and
+MLCS2k2 light curve fitters are fully consistent within the
+uncertainties.  }
 
@@
 uncertainty for each. Markers with horizontal error bars show the
-median magnification and 68\%\ confidence region from each of the 10
+median magnification and 68\%\ confidence region from each of the 14
 lensing models.  Circles indicate models that use only strong-lensing
@@
 ``free-form.''  The dashed grey line marks the unweighted mean of all
-model magnifications, with grey shading indicating the standard error
-of the mean from naively assuming all are independent predictions.
+model magnifications.
 \label{fig:lensingtest} }
@@
 
-Table~\ref{tab:PredictedMagnifications} lists the 11 models, giving
+Table~\ref{tab:PredictedMagnifications} lists the \change{14} models, giving
 for each one the predicted magnification and uncertainty for a source
@@
 their quoted uncertainties), one would get a mean for the full sample
-of $\mu=2.62\pm0.34$ (shown as a grey band in
+of $\mu=2.51\pm0.34$ (shown as a grey dashed line in
 Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
@@
 the $y$ direction into two broad classes, with the
-six \change{so-called} {\it parametrized} models on top and the four
-{\it free-form} models on the bottom.\footnote{\change{Although this
+six \change{so-called} {\it parametric}\footnote{\change{Although this
 nomenclature is becoming standard in the literature, it is somewhat
@@
 be more accurate, though we adopt the more common usage here.}}
+models on top and the four {\it free-form} models on the bottom.
 Broadly speaking, the parametric models use parameterized density
@@
 cluster galaxies is a good tracer of the cluster's dark matter.
-Free-form models divide the cluster into a grid, generally using an
-adaptive mesh to get better sampling in denser regions. Each grid cell
-is assigned a mass or a potential, and then the grid spacing and the
-mass values are iteratively refined to match the observed lensing
-constraints.
+Free-form models divide the cluster into a grid, generally using a
+\change{multi-scale grid} to get better sampling in denser regions. Each grid cell
+is assigned a mass or a potential, and then the mass values are
+iteratively refined to match the observed lensing
+constraints. \change{In some cases an adaptive grid is used so
+that the grid spacing itself can also be modified as the model is
+iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.}
 
@@
 this can have a measurable impact on precise cosmological constraints,
-it is far less than the 0.285 mag difference between the observed
+it is far less than the 0.25 mag difference between the observed
 magnification of \tomas\ and the mean of the model predictions.  
@@
 maximum brightness.  
+}
 
 \textcolor{red}{TODO : discuss 2006bt-like colors}
-}
 

### 2015-04-03 snTomas.tex
added host mass correction section

@@
 
+\subsection{Host Galaxy Mass Correction}
+\label{sec:HostGalaxyMassCorrection}
+
+\change{
+It is now an accepted practice in cosmological analyses using Type Ia
+SN to apply a correction to the luminosity of each SN based on the
+stellar mass of its host galaxy. Typically this is described as a
+simple bifurcation of the SN population: SNe that appear in more
+massive hosts are observed to be $\sim$0.08 mag brighter (after
+corrections for light curve shape and color) than SNe in low-mass
+hosts \citep{Kelly:2010,Sullivan:2010}.  The dividing line for this
+purely empirical ``mass step'' correction is generally set around
+$10^{10}$\Msun, although this is somewhat arbitrary \citep[see
+e.g.][]{Betoule:2014}.  This happens to be very close to the
+SN \tomas\ host galaxy mass, which we have measured to be
+$10^{10.135}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
+{\it BPZ} SED fit to define rest-frame optical magnitudes.
+}
+
+\change{
+The physical mechanism that drives the mass step is not yet
+understood, but may be related to the metallicity or age of the SN
+progenitor systems. In either case, it is reasonable to expect that
+the significance of this effect decreases with redshift, as metal-rich
+passive galaxies become much less common at $z>1$.  Indeed, when the
+size of the mass step correction is allowed to vary with redshift,
+there is no significant evidence that a non-zero mass step is required
+at $z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
+absence of a clear physical model and the lack of empirical support
+for a high-$z$ mass step, we do not apply any correction to SN \tomas
+or the control sample.
+}
+
 \subsection{Magnification}

### 2015-04-03 authors.tex
updated authors list

\author{Steven~A.~Rodney\altaffilmark{1,2}}

\author{Brandon Patel}

\author{Daniel Scolnic}

\author{Ryan Foley}

\author{Alberto Molino}

\author{Marusa Bradac}

\author{Gabriel Brammer}

\author{Jose~Maria~Diego}

\author{Jens Hjorth}

\author{Austin Hoag}

\author{Mathilde Jauzac}

\author{Saurabh Jha}

\author{Patrick Kelly}

\author{Daniel Lam}

\author{Julian~Merten}

\author{Johan Richard}

\author{Keren Sharon}

\author{Louis-Gregory Strolger}

\author{Tommaso Treu}

\author{Adi Zitrin}

\altaffiltext{1}{\JHU}
\altaffiltext{1}{\Rutgers}
\altaffiltext{1}{\Chicago}
\altaffiltext{1}{\Illinois}
\altaffiltext{1}{\CSIC}
\altaffiltext{1}{\SaoPaulo}
\altaffiltext{1}{\UCDavis}
\altaffiltext{1}{\STScI}
\altaffiltext{1}{\Copenhagen}
\altaffiltext{1}{\UCDavis}
\altaffiltext{1}{\Rutgers}
\altaffiltext{1}{\Berkeley}
\altaffiltext{1}{\STScI}
\altaffiltext{1}{\WKU}
\altaffiltext{1}{\UCLA}
\altaffiltext{1}{\CalTech}
\altaffiltext{2}{Hubble fellow}

### 2015-04-03 preamble.tex
discovery and follow-up
Finished writing discussion, summary and conclusions.
implemented most of Chema's comments  and added updated magnification estimates from Bradac/Hoag and Chema to Table 3  and highlighting changes in blue  Note the new sections in the discussion on Redshift Error and System 3.3.
updated authors list

@@
 \newif{\ifchangetext}
-\changetextfalse
+\changetexttrue
 
@@
 \usepackage{appendix}
+%\usepackage{array}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% New table column types, allowing left- or right-justified text in 
+% paragraph mode, that also allows manual line-breaks
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 \def\tomas{HFF14Tom}
+\def\33p{\ensuremath{3.3^{\prime}}}
+%\def\tomas{Tomas}
 
@@
 % Missions:
+\def\HST{{\it HST}}
 \def\Hubble{{\it Hubble}}
@@
 % Institutions
-\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, Baltimore, MD 21218.}
+\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 N. Charles St., Baltimore, MD 21218, USA}
 \newcommand{\elsewhere}{St. Elsewhere University.}
-\newcommand{\STScI}{Space Telescope Science Institute, Baltimore, MD 21218.}
-\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411.}
-\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521.}
-\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101.}
-\newcommand{\Copenhagen}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark.}
-\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721.}
-\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064.}
-\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556.}
-\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel.}
-\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854.}
-\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138.}
-\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA.}
+\newcommand{\STScI}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\newcommand{\Chicago}{Department of Physics, The University of Chicago, Chicago, IL 60637, USA}
+\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411, USA}
+\newcommand{\LBNL}{Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA}
+\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521, USA}
+\newcommand{\CSIC}{Instituto de Astrof\'isica de Andaluc\'ia (CSIC), E-18080 Granada, Spain}
+\newcommand{\SaoPaulo}{Instituto de Astronomia, Geof\'isica e Ci\^encias
+Atmosf\'ericas, Universidade de S\~ao Paulo, Cidade Universit\'aria,
+05508-090, S\~ao Paulo, Brazil}
+
+\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101, USA}
+\newcommand{\AMNH}{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th Street, New York, NY 10024, USA}
+\newcommand{\NYU}{Center for Cosmology and Particle Physics, New York University, New York, NY 10003, USA}
+\newcommand{\Copenhagen}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark}
+\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721, USA}
+\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064, USA}
+\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556, USA}
+\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel}
+\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854, USA}
+\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
+\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA}
+\newcommand{\NOAO}{National Optical Astronomical Observatory, Tucson, AZ 85719, USA}
+\newcommand{\UCSB}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\newcommand{\SantaBarbara}{\UCSB}
+\newcommand{\LCOGT}{Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Goleta, California 93117, USA}
+\newcommand{\Colby}{Colby College, 4000 Mayflower Hill Dr, Waterville, ME 04901, USA}
+\newcommand{\Kentucky}{University of Kentucky, Lexington, KY 40506}
+\newcommand{\UCDavis}{University of California Davis, 1 Shields Avenue, Davis, CA 95616}
+\newcommand{\Illinois}{University of Illinois at Urbana-Champagne, 1002 W. Green Street, Urbana, IL 61801}
+\newcommand{\UCLA}{University of California, Los Angeles, CA 90095}
+\newcommand{\CalTech}{California Institute of Technology, 1200 East California Boulevard, Pasadena, CA 91125}
 

### 2015-04-03 snTomas.tex
updated authors list

@@
 
-\author{
- Steven~A.~Rodney\altaffilmark{1,2},
-  \etal
-}
-\altaffiltext{1}{\JHU}
-\altaffiltext{2}{Hubble fellow}
+\input{authors}
 
@@
 have derived a consistent measured magnification of $\mu_{\rm
-SALT2}=1.89\pm0.29$.  $\mu_{\rm MLCS2k2}=2.00\pm0.19$, from the two
+SALT2}=1.88\pm0.35$.  $\mu_{\rm MLCS2k2}=2.00\pm0.28$, from the two
 light curve fitters.

### 2015-04-04 TABLE/magnifications.tex
added sn06bt color curve fig

--- 2015-04-01 TABLE/magnifications.tex
@@
 Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
-Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
+Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.
+\\
 Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\

### 2015-04-04 preamble.tex
added sn06bt color curve fig

@@
 
+\newcommand{\Durham}{Institute for Computational Cosmology, Durham University, South Road, Durham DH1 3LE, UK}
+\newcommand{\KwaZulu}{Astrophysics and Cosmology Research Unit, School of Mathematical Sciences, University of KwaZulu-Natal, Durban 4041, South Africa}
+
+\newcommand{\IFCA}{IFCA, Instituto de F\'isica de Cantabria (UC-CSIC), Av. de Los Castros s/n, 39005 Santander, Spain}
+
+\newcommand{\HongKong}{Department of Physics, The University of Hong Kong, Pokfulam Road, Hong Kong}
+\newcommand{\Oxford}{Department of Physics, University of Oxford, Clarendon Laboratory, Parks Road, Oxford, UK}
+
+\newcommand{\CRAL}{CRAL, Observatoire de Lyon, Universit\'e Lyon 1, 9 Avenue Ch. Andr\'e, F-69561 Saint Genis Laval Cedex, France}
+\newcommand{\Michigan}{Department of Astronomy, University of Michigan, 1085 S. University Avenue, Ann Arbor, MI 48109, USA}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-04-04 snTomas.tex
added sn06bt color curve fig

@@
 In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
-follow-up observations of SN \tomas at $z=1.31$, discovered behind the
+follow-up observations of SN \tomas\ at $z=1.31$, discovered behind the
 galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
@@
 
-\section{Misclassification}
+\subsection{Misclassification}
 \label{sec:Misclassification}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/snTomas_sn06bt_colorcurves}
+\caption{ 
+Comparing \tomas\ observations to the color curves of SN 2006bt and a
+normal Type Ia SN model. Grey points show the observed colors of SN \tomas, k-corrected to rest-frame UBVr bands. Solid orange lines show the observed color
+curves for the peculiar Type Ia SN 2006bt. Dashed blue lines show the
+color curves for a normal Type Ia SN, derived from the SALT2 model with a color parameter $c=-0.12$, set to match the best-fit color for SN \tomas.
+\label{fig:colorcomparison} }
+\end{center}
+\end{figure}
 

### 2015-04-04 snTomas.tex
finished sn06bt comparison section

@@
 \change{
-One might suppose that a bias could be introduced if we have adopted
-incorrect values for the color correction parameter $\beta$ or
-extinction law $R_V$ in the SALT2 and MLCS2k2 fits, respectively.  The
-appropriate value to use for this color correction and how it affects
-inferences about the intrinsic scatter in Type Ia SN luminosities is a
-complex question that is beyond the scope of this work \citep[see
+In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
+the blue end of the normal range of Type Ia SN colors.  With the SALT2
+fitter we measured a color parameter $c=-0.115\pm0.025$, and with
+MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
+V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
+as we are fitting to photometry that covers a rest-frame wavelength
+range from $\sim3500-7000$\AA and extends to $\sim$30 days past
+maximum brightness.  This leaves little room for the luminosity
+measurement to be biased by dust, as the dimming of \tomas\ would also
+necessarily be accompanied by some degree of reddening. 
+}
+
+\change{
+Nevertheless, one might suppose that a bias could be introduced if we
+have adopted incorrect values for the color correction parameter
+$\beta$ or extinction law $R_V$ in the SALT2 and MLCS2k2 fits,
+respectively.  The appropriate value to use for this color correction
+and how it affects inferences about the intrinsic scatter in Type Ia
+SN luminosities is a complex question that is beyond the scope of this
+work \citep[see
 e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
@@
 vetted paraemeters, based on observations of $\sim500$ SNe extending
-to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, changing the color
-correction applied to SN \tomas\ would requre the same adjustment to
-be applied to the unlensed SNe at similar redshift that make up our
-comparison sample, unless one proposes without evidence that
-SN \tomas\ is uniquely affected by a peculiar type of dust.  
-}
+to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason
+to propose that SN \tomas\ is uniquely affected by a peculiar type of
+dust.  Thus, any change in the color correction applied to SN \tomas\
+would require the same adjustment to be applied to the unlensed SNe at
+similar redshift that make up our comparison sample, largely negating
+the effect on the inferred magnification.  }
 
@@
 Comparing \tomas\ observations to the color curves of SN 2006bt and a
-normal Type Ia SN model. Grey points show the observed colors of SN \tomas, k-corrected to rest-frame UBVr bands. Solid orange lines show the observed color
-curves for the peculiar Type Ia SN 2006bt. Dashed blue lines show the
-color curves for a normal Type Ia SN, derived from the SALT2 model with a color parameter $c=-0.12$, set to match the best-fit color for SN \tomas.
+normal Type Ia SN model. Grey points show the observed colors of
+SN \tomas, k-corrected to rest-frame UBVr bands. Solid orange lines
+show the observed color curves for the peculiar Type Ia SN
+2006bt. Dashed blue lines show the color curves for a normal Type Ia
+SN, derived from the SALT2 model with a color parameter $c=-0.12$, set
+to match the best-fit color for SN \tomas.
 \label{fig:colorcomparison} }
@@
 
-\textcolor{red}{TODO : discuss 2006bt-like misclassification}
-
-\change{
-In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
-the blue end of the normal range of Type Ia SN colors.  With the SALT2
-fitter we measured a color parameter $c=-0.115\pm0.025$, and with
-MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
-V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
-as we are fitting to photometry that covers a rest-frame wavelength
-range from $\sim3500-7000$\AA and extends to $\sim$30 days past
-maximum brightness.  
-}
-
-\textcolor{red}{TODO : discuss 2006bt-like colors}
+\change{
+Is it possible that \tomas\ is an example of a peculiar stellar
+explosion that does not follow the relationship between light curve
+shape and luminosity observed in normal Type Ia SNe?  In
+Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
+classified SN Tomas as a normal Type Ia SN based on both the
+spectroscopic and photometric evidence.  This rules out the
+possibility that \tomas\ belongs to a different class of normal SN
+explosions (Type Ib, Ic, or II). In
+Section \ref{sec:LightCurveFitting} we fit the \tomas\ light curve to
+determine a luminosity distance and found that the light curve shape
+and color are consistent with a Type Ia SN of average light curve
+width, with minimal dust extinction.  This excludes the possibility
+that \tomas\ is one of the sub-class of ``fast declining'' Type Ia SNe
+like SN 1991bg.
+}
+
+\change{
+One remaining possibility is that \tomas\ could be part of a rare
+sub-category of peculiar Type Ia SNe that masquerade as their normal
+cousins, epitomized by the prototype SN 2006bt \citep{Foley:2010}.
+These objects appear to have a normal Type Ia light curve shape,
+except for the absence of a secondary maximum or ``shoulder'' in
+near-IR bands.  The reddest filter available for the \tomas\ light
+curve is F160W, which has an effective rest-frame wavelength of
+6623\AA\ at $z=1.31$, making it close to the rest-frame {\it r} band.
+Although the near-IR shoulder is more prominent in the rest-frame {\it
+i} band, we can see in Figures~\ref{fig:LightCurveFits} that the F160W
+light curve may suggest a weak or delayed near-IR shoulder.  The
+second-to-last observation in F160W is $\sim1\sigma$ lower than
+predicted by the best-fit SALT2 and MLCS2k2 models. This is tenuous
+evidence, but it would be consistent with a 2006bt-like light curve.
+}
+
+\change{
+In this case, however, the color of SN \tomas\ can rule out a
+classification as a 2006bt-like object.  All members of this peculiar
+sub-class exhibit very red colors across all optical and near-IR
+bands, consistent with a very cool photosphere \citep{Foley:2010}.
+Figure~\ref{fig:colorcomparison} shows that \tomas\ is bluer than the
+SN 2006bt prototype by at least 0.25 magnitudes in every color. The
+observed \tomas\ colors are fully consistent with the a normal, blue
+Type Ia SN (the SALT2 model is shown).
+}
 
@@
 \item \change{The redshift assigned to SN \tomas\ is in error.}
-\item \change{The color corrections for SN \tomas\ underestimate the foreground dust.}
+\item \change{SN \tomas\ is dimmed by foreground dust.}
 \item \change{SN \tomas\ is not a normal Type Ia SN.}
@@
 \change{
-The last two possible explanations presume an error in the
+The last three possible explanations presume an error in the
 interpretation of the available SN data.  We reject the possibility
@@
 to increase the tension between the observed and predicted
-magnifications.
-}
+magnifications.  We also find it implausible that there is sufficient
+dust in the cluster or elsewhere along the line of sight to account
+for the magnification discrepancy.  A dust-induced bias is also
+disfavored by the very blue color of SN \tomas.  }
 
@@
 mis-classification would be that the object is a peculiar Type Ia of
-the SN 2006bt-like sub-class.  We find this possibility to be 
- \textcolor{red}{TODO: summarize the 06bt misclassification discussion}
+the SN 2006bt-like sub-class.  Although the light curve shape could
+allow this possibility, the blue color of \tomas\ can once again
+reject this alternative. 
 }

### 2015-04-04 TABLE/magnifications.tex
Various changes, incorporating comments from various co-authors

--- 2015-04-01 TABLE/magnifications.tex
@@
-\begin{deluxetable*}{lccp{1.5in}p{2.2in}}
+\begin{deluxetable*}{lccp{1.9in}p{2.2in}}
 \tablecolumns{5}
@@
 Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model\\
-Bradac(v2)   & 2.23 & 2.20$^{+0.03}_{-0.01}$ &   \citealt{Bradac:2005,Bradac:2009} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.}\\
-Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
+Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model.
+Errors from bootstrap resampling only weak-lensing constraints.\\
+Bradac(v2)   & 2.21 & 2.23$^{+0.05}_{-0.03}$ &   \citealt{Wang:2015} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Errors from bootstrap resampling only strong-lensing constraints.}\\
+Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.
+\\
 Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
@@
 \tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
-\tablenotetext{g}{{\tt GRALE} : }
+\tablenotetext{g}{{\tt GRALE} : GRAvitational LEnsing.}
 \tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}

### 2015-04-04 snTomas.tex
Various changes, incorporating comments from various co-authors

@@
 $\sim$40\arcsec, closer to the critical lensing line than any previous
-cluster-lensed \SNIa.  As such, it provides the first opportunity to
+cluster-lensed \SNIa.  As such, it provides a valuable opportunity to
 confront gravitational lens models of galaxy clusters with the direct
@@
 One of the key values in observing standard candles behind
-gravitational lenses is that {\it all} lensing reconstructions suffer
-from the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
+gravitational lenses is that most lensing reconstructions suffer from
+the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
 degeneracy arises because one can introduce into a lens model an
@@
 produce exactly the same values for all positional and shear
-constraints from strong and weak lensing.  This is the simplest case
-illustrating a positional constraint degeneracy, but there are more
-complex versions \citep{Schneider:2014}.  Such mass sheet
+constraints from strong and weak lensing.  When lensed background
+sources are available across a wide range of redshifts (as is the case
+for the Abell 2744 cluster discussed here), it should in principle be
+possible to account for the simplest form of a single mass sheet
+within that redshift range.  However, there are more complex versions
+of positional constraint
+degeneracies \citep{Schneider:2014,Liesenborgs:2012}.  Such
 degeneracies do not extend to the {\it absolute} magnification of a
@@
 of magnification from a standard candle or a standard ruler
-\citep{Sonnenfeld:2011}  can break this fundamental degeneracy
+\citep{Sonnenfeld:2011}  can break these fundamental degeneracies
 \citep{Holz:2001}.
@@
 SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
-warping, an alternative fit also arises: the normal Type Ia SN 2011iv
+warping, an alternative fit also arises: the \change{fast-declining
+(91bg-like)} Type Ia SN 2011iv
 at $z=0.98\pm0.01$. Formally, this match provides a slightly better
@@
 galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
-that the photometric data is incompatible with a normal Type Ia SN at
+that the photometric data is also incompatible with a Type Ia SN at
 $z\sim1.0$.
@@
 determined in \citet{Conley:2011} is specific to the HST SN sample,
-from \citet{Riess:2007} and \citet{Suzuki:2011}, which is the SN
+from \citet{Riess:2007} and \citet{Suzuki:2012}, which is the SN
 subset that is most similar to \tomas\ in terms of redshift and data
@@
 absence of a clear physical model and the lack of empirical support
-for a high-$z$ mass step, we do not apply any correction to SN \tomas
-or the control sample.
-}
+for a high-$z$ mass step, we do not apply any correction to SN \tomas\ 
+or the control sample.  }
 
@@
 distance modulus vs. redshift, and derive a prediction for the
-distance modulus of a normal Type Ia SN at the redshift of SN \tomas
+distance modulus of a normal Type Ia SN at the redshift of SN \tomas\
 (Figure~\ref{fig:MagnificationMeasurement}).
@@
 
+\change{
+In general, free-form methods tend to explore the model parameter
+space more fully than parametric methods. This is reflected in the
+size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
+GRALE, which has the largest, and possibly the most realistic
+uncertainties is able to account for mass sheet degeneracy by
+introducing a free parameter in the reconstruction that represents an
+arbitrarily positioned mass sheet, with normalization to be chosen by
+the genetic algorithm.  More complex degeneracies are also accounted
+for in GRALE through the use of basis
+functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
+}
+
 Figure~\ref{fig:lensingtest} also separates the models based on the
@@
 However, beyond this first-order agreement, there is a systematic bias
-apparent. All of the lens models predict a magnification that is {\it
-higher} than the observed value, and no model has a median value that
-falls within the $1\sigma$ range of the observed magnifications.  It
-is important to emphasize that SN \tomas\ only samples a single
-sight-line through the cluster, so any conclusions to be drawn from
-this analysis are necesssarily limited.  Nevertheless, a systematic shift
-common to all models is surprising, given the wide range of modeling
-strategies, input data, and physical assumptions represented by this
-set of models.  In the following subsections we examine possible
-explanations for this apparently universal bias.
+apparent. All of the lens models \change{return median magnifications
+that are} {\it higher} than the observed value, and \change{half of
+the models are discrepant by more than $1\sigma$.}  It is important to
+emphasize that SN \tomas\ only samples a single sight-line through the
+cluster, so any conclusions to be drawn from this analysis are
+necesssarily limited.  Nevertheless, a systematic shift common to all
+models is surprising, given the wide range of modeling strategies,
+input data, and physical assumptions represented by this set of
+models.  In the following subsections we examine possible explanations
+for this \change{small but} apparently universal bias.
 
@@
 particular sight-line, not all strong-lensing constraints are equal.
-An error in the association of multiple images or 
-in the redshift of a multiply-imaged galaxy would have a
-more significant impact if that system has a projected position
-close to our SN sight-line.  It happens that there is one such system,
-for which the position of a multiple image near SN \tomas\ is presently disputed.  
-}
+An error in the association of multiple images or in the redshift of a
+multiply-imaged galaxy would have a more significant impact if that
+system has a projected position close to our SN sight-line.  It
+happens that there is one such system, for which the position of a
+multiple image near SN \tomas\ is presently disputed.  }
 
@@
 Resolving the identification of this single multiply-imaged galaxy
-could be an important component in resolving the magnification
+could be a component in resolving the magnification
 discrepancy, though it is unlikely to completely remove the tension.
@@
 ({\tt Jauzac}) is also the one with the largest deviation from our
-observed $\mu$ value.  However, the bias is still present even if we
-remove that model and only consider models using the original position
-3.3.  
-}
-
-\subsection{Mass Profile Truncation}
-\label{sec:MassProfileTruncation}
+observed $\mu$ value.  However, \citet{Jauzac:2014c} have already
+evaluated the impact of relocating this single source, and
+they find that it is not responsible for the observed increase in
+magnifications across the field. Rather, the 
+primary cause for the general magnification increase is the addition
+of new multiple images in the Northern region, detected using the new
+HFF data. }
+
+\subsection{Mass Profile Extrapolation}
+\label{sec:MassProfileExtrapolation}
 
@@
 located several arcseconds outside the core region of the cluster
-where these multiply-imaged galaxies are found.  Therefore these seven
+where these multiply-imaged galaxies are found.  Therefore these eight
 ``strong-lensing only'' models must necessarily rely on extrapolations
-to provide a prediction for the SN \tomas\ magnification.  If the true
-cluster density profile for Abell 2744 happens to be truncated -- with
-a sharp drop right at the edge of this core strong-lensing region --
-then these seven models might well overestimate the mass interior to
-the \tomas\ position, and thus systematically overestimate the
-magnification.
+to provide a prediction for the SN \tomas\ magnification.  Let us
+suppose that the true cluster density profile for Abell 2744 happens
+to have a sharp drop right at the edge of this core strong-lensing
+region. In that case these eight models might well overestimate the
+mass interior to the \tomas\ position, and thus systematically
+overestimate the magnification.
 
 The other three models in our comparison set also use the strong
-lensing constraints from the core region, but additionally utilize weak
-lensing measurements to provide additional constraints on the mass
-distribution farther from the cluster core.  The signal from weak
+lensing constraints from the core region, but additionally utilize
+weak lensing measurements to provide additional constraints on the
+mass distribution farther from the cluster core.  The signal from weak
 lensing relies on a large sample of background galaxies, so this
-constraint operates principally at separations more than 1\arcmin from
+constraint operates principally at separations more than 1\arcmin\ from
 the cluster core.  At a projected separation of $\sim40\arcsec$,
@@
 one would expect that models incorporating both of those constraints
-would be less susceptible to the systematic bias of a truncated mass
-profile.  The lowest magnification estimate in our sample (from the
-Merten model) is among this sub-sample.  However, we find that
-collectively these three strong+weak models (shown as diamonds in
-Figure~\ref{fig:lensingtest}) exhibit the same propensity to
-overestimate the magnification along this line of sight.  Thus, a
+would be less susceptible to the systematic bias of a sharply
+steepening mass profile.  The lowest magnification estimate in our
+sample (from the Merten model) is among this sub-sample.  However, we
+find that collectively these three strong+weak models (shown as
+diamonds in Figure~\ref{fig:lensingtest}) exhibit the same propensity
+to overestimate the magnification along this line of sight.  Thus, a
 sudden change in the mass profile outside the strong lensing region is
@@
 measured value, which serves to reinforce the conclusion that adding
-weak lensing constraints cannot resolve this bias.
+weak lensing constraints cannot, by itself, resolve this bias.
 
@@
 We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
-magnification comparison.  Spectroscopic redshifts are generally more
-precise and accurate than those derived from photometric
-observations \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
+magnification comparison.  Spectroscopic SN redshifts are generally more
+precise and accurate than those derived from SN
+photometry \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
 this case the spectrum is limited to the rest-frame near-UV
@@
 $z=1.35$ only serves to (slightly) exacerbate the tension between the
-observations and models.
-}
+observations and models.  }
 
@@
 as we are fitting to photometry that covers a rest-frame wavelength
-range from $\sim3500-7000$\AA and extends to $\sim$30 days past
+range from $\sim3500-7000$\AA\ and extends to $\sim$30 days past
 maximum brightness.  This leaves little room for the luminosity
@@
 
-This work is dedicated to our colleague and friend Tomas Dahlen
-(-2014), for whom this supernova has been named in memorium. He is
-greatly missed.
+This work is dedicated to our colleague and friend Tomas Dahlen, for
+whom this supernova has been named in memorium. He is dearly missed.
 
@@
 
+AM acknowledge the financial support of the Brazilian funding agency
+FAPESP (Post-doc fellowship - process number 2014/11806-9)
+
 Support for this research at Rutgers University was provided in part

### 2015-04-04 snTomas.tex
incorporated most comments from JH,KS, others

@@
 One of the key values in observing standard candles behind
-gravitational lenses is that most lensing reconstructions suffer from
-the mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
+gravitational lenses is \changeG{in addressing the problem of the
+mass-sheet degeneracy} \citep{Falco:1985,Bradac:2004}.  This
 degeneracy arises because one can introduce into a lens model an
-unassociated sheet of mass in front of or behind the lens, without
-disturbing the primary observable quantities.  For example, take a
-lens model with a given surface mass density $\kappa$, and then
-transform the surface mass density to
+unassociated sheet of uniform mass in front of or behind the
+lens, without disturbing the primary observable quantities.  For
+example, take a lens model with a given surface mass density $\kappa$,
+and then transform the surface mass density to
 $\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
@@
 
-As described below, we fit the SN \tomas\ spectrum in two steps.
-First we determine a spectral classification -- and get a preliminary
-estimate of the redshift and age -- using the SuperNova IDentification
-(SNID) software \citep{Blondin:2007}.  Second, we refine the redshift
-and age measurement using a custom Type Ia spectral template matching
-program.
+\changeG{
+Spectra of Type I SNe (including all sub-classes Ia, Ib and Ic) are
+dominated by broad absorption features, which cannot in general be
+used to directly extract a spectroscopic redshift \citep[see
+e.g.][]{Filippenko:1997}.  As described below, we fit template spectra
+to the SN \tomas\ data in two steps.}  First we determine a spectral
+classification -- and get a preliminary estimate of the redshift and
+age -- using the SuperNova IDentification (SNID)
+software \citep{Blondin:2007}.  Second, we refine the redshift and age
+measurement using a custom Type Ia spectral template matching program.
 
@@
 distance modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$
-is the luminosity distance in Mpc.}  from the SALT2 fit using
+is the luminosity distance in Mpc.} \changeG{while ignoring the
+effects of gravitational lensing, so that we can later use it to
+derive a direct measurment of the magnification.}  From the SALT2 fit
+we get
 
@@
 In general, free-form methods tend to explore the model parameter
-space more fully than parametric methods. This is reflected in the
+space more fully than parametric methods. 
+ This is reflected in the
 size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
@@
 lens models overall are delivering consistent and fairly accurate
-estimates of the magnification.  \change{Four of the tested models
-(CATS, GLAFIC, Zitrin-NFW, Merten) report a median value that falls
-within the 1$\sigma$ uncertainty range of the measured magnification,
-and two of the models (Williams, Merten) report uncertainties that
-overlap the central $\mu$ from at least one of the light curve
-fitters.}  Furthermore, the scatter amongst
-models provides a reasonable estimate of the magnification
+estimates of the magnification.  \change{Six of the tested models
+(CATS, GLAFIC, Zitrin-NFW, Bradac(v2), Merten, Diego) report a median
+value that falls within the 1$\sigma$ uncertainty range of the
+measured magnification, and two of the free-form models (Williams,
+Diego) report uncertainties that overlap the central $\mu$ as measured
+from both of the SN light curve fitters.}  Furthermore, the scatter
+amongst models provides a reasonable estimate of the magnification
 uncertainty.
@@
 multiply-imaged galaxy would have a more significant impact if that
-system has a projected position close to our SN sight-line.  It
-happens that there is one such system, for which the position of a
-multiple image near SN \tomas\ is presently disputed.  }
+system has a projected position close to our SN
+sight-line \changeG{\citep[see][for a quantitative assessment of this
+effect]{Johnson:2014}.}  It happens that there is one such system, for
+which the position of a multiple image near SN \tomas\ is presently
+disputed.  }
 
@@
 We have speculated on the origin of this systematic bias,
-evaluating five possible causes:
+evaluating six possible causes:
 
@@
 provide any definitive explanation for this magnification tension.
+
+\changeG{
+At least for this particular sight-line, the free-form models perform
+better in the sense that they deliver more realistic uncertainties.
+This may indicate that the free-form approach in general is more
+successful in capturing the uncertainty from biases inherent to the
+mass modeling exercise, such as the mass sheet degeneracy and more
+complex ``approximate
+invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  }
 
@@
 
-Increasing the sample of SNe behind well studied strong lensing
-clusters would allow this test to be repeated and refined.  With 10 or
-100 such objects, it would be possible to see whether the SN \tomas\
-$\mu$ discrepancy is simply an outlier, or an indication of a more
+Increasing the sample of SNe behind clusters \changeG{like those in
+the HFF program -- with rich lensing constraints and deep imaging -- }
+would allow this test to be repeated and refined.  With 10 or 100 such
+objects, it would be possible to see whether the SN \tomas\ $\mu$
+discrepancy is simply an outlier, or an indication of a more
 pernicious systematic error.  Any cluster that has been vetted by

### 2015-04-05 snTomas.tex
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig

@@
 methodologies and incorporating a variety of strong- and weak-lensing
-constraints.  The models are collectively fairly accurate. \change{
-Half of the models deliver median magnifications that are consistent
+constraints.  The models are collectively fairly accurate: \change{
+half of the models deliver median magnifications that are consistent
 with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
@@
 of the tested models predict a magnification equal to or lower than
-the observed $\mu$, and some models are more than $5\sigma$ above the
+the observed $\mu$, and three models are $2-4\sigma$ above the
 measured magnification.  We evaluate possible causes for this bias,
-and find that intercomparison of the lens models rules out several
-simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
-single cluster could provide a robust evaluation of systematic biases
+\changeG{considering both modeling errors and misinterpretation of the SN
+data. Although we find no single explanation that accounts for the
+entire discrepancy, we do find that the subset of ``free-form'' lens
+models are more accurate and provide more realistic uncertainties than
+``parametric models'' for this sight-line.} A larger sample of 10-100
+lensed \SNeIa\ could provide a robust evaluation of systematic biases
 in lens models.  Until such a sample exists, it is advisable
@@
 
-\textcolor{red}{TODO: write and polish introduction}.
-Massive galaxy clusters can be used as cosmic telescopes to magnify
-distant background objects through gravitational lensing.  This can
-substantially increase the reach of deep imaging surveys, and has
-recently been used to discover candidate proto-galaxies formed in the
-first Gyr after the Big 
-Bang \citep{Zheng:2012,Coe:2013} 
-\textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}
-
-\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Li:2012,Quimby:2014}.}
-
+\changeG{
+Galaxy clusters can be used as cosmic telescopes to magnify distant
+background objects through gravitational lensing, which can
+substantially increase the reach of deep imaging surveys.  The lensing
+magnification enables the study of objects that would otherwise be
+unobservable because they are either intrinsically
+faint \citep[e.g.][]{Schenker:2012,Alavi:2014} or extremely
+distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014}.
+Background galaxies are also {\it spatially} magnified, allowing for
+studies of the internal structure of galaxies in the early universe
+with resolutions of $\sim$100
+pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
+}
+
+\changeG{
+Gravitational lensing can also provide a powerful window onto the {\it
+transient} sky through an appropriately cadenced imaging survey.  The
+flux magnification from strong-lensing clusters is especially valuable
+for the study of $z>1.5$ supernovae
+(SNe) \citep[e.g.]{Kovner:1988,Kolatt:1998,Sullivan:2000,Saini:2000,Gunnarsson:2003,Goobar:2009,Postman:2012},
+which are still extremely difficult to characterize in unlensed
+fields \citep[e.g.]{Riess:2001,Riess:2007,Suzuki:2012,Rodney:2012,Rubin:2013,Jones:2013}.
+}
+
+\changeG{
+In the case of lensed SNe, we can also reverse the experimental setup:
+instead of using strong-lensing clusters to study distant SNe, we can
+use the SNe as tools for examining the lenses \citep{Riehm:2011}.  The
+most valuable transients for testing and improving cluster lens models
+would be {\it strongly lensed} SNe that are resolved into multiple
+images \citep{Holz:2001,Oguri:2003}.  Transients that are lensed into
+multiple images can also become cosmological tools, as the measurement
+of time delays between the images can provide cosmographic information
+to constrain the Hubble parameter \citep{Refsdal:1964} and other
+cosmological parameters \citep{Linder:2011}.  We have recently
+observed the first example of a multiply-imaged
+SN \citep{Kelly:2015}, and expect to detect the reappearance of this
+object (called ``SN Refsdal'') within 5 years, delivering a precise
+test of lens model predictions \citep{Oguri:2015,Sharon:2015}.
+Although detections of such objects are currently very
+unlikely \citep{Li:2012}, they will become much more common in the
+next decade \citep{Coe:2009,Dobke:2009}, and may be developed into an
+important new cosmological tool.
+}
+
+\changeG{
+In addition to time delays from multiply-imaged SNe, we can also
+put cluster mass models to the test with the much more common category
+of lensed Type Ia SNe.  
 \citet[][hereafter P14]{Patel:2014} and \citet{Nordin:2014} presented
-independent analyses of three lensed SNe, of which at least 2 are securely
-classified as Type Ia SNe.  All of these three objects were found in
-the Cluster Lensing and Supernova survey with Hubble (CLASH,
-PI:Postman, HST Program ID 12068).
+independent analyses of three lensed SNe, of which at least 2 are
+securely classified as Type Ia SNe -- all found in the Cluster Lensing
+and Supernova survey with Hubble (CLASH, PI:Postman, HST Program ID
+12068, \citealt{Postman:2012}).  Both groups demonstrated that these
+standard candles can be used to provide accurate and precise
+measurements of the true absolute magnification along a random sight
+line through the cluster.  Although in these cases the SNe were used
+to {\it test} the cluster mass models, one could in principle
+incorporate the measured magnifications of Type Ia SNe into the
+cluster as additional model constraints.  In that role, Type Ia SNe
+have the particular value that they can be found anywhere in the
+cluster field.  Thus, they can deliver model constraints in regions of
+``middle distance'' from the cluster core, where both strong- and
+weak-lensing constraints are unavailable.
+}
 
@@
 additional input constraints, including new multiply imaged systems
-and redshifts.  The seven models shown in black at the top are from
-the ``parametric'' family, and the four in green at the bottom are
-``free-form.''  The dashed grey line marks the unweighted mean of all
-model magnifications.
+and redshifts.  The eight models shown in black at the top are from
+the ``parametric'' family, and the six in green at the bottom are
+``free-form.''  Dashed lines mark the unweighted mean of each model
+family and shaded regions show the standard error of the mean.
 \label{fig:lensingtest} }
@@
 
-Table~\ref{tab:PredictedMagnifications} lists the \change{14} models, giving
-for each one the predicted magnification and uncertainty for a source
-at $z=1.31\pm0.01$ and at the position of \tomas.  These models
+Table~\ref{tab:PredictedMagnifications} lists the \change{14} models,
+giving for each one the predicted magnification and uncertainty for a
+source at $z=1.31\pm0.01$ and at the position of \tomas.  These models
 represent a broad sampling of the techniques and assumptions that can
@@
 alongside the observed magnification of SN \tomas, derived in
-Section~\ref{sec:Magnification}.  This comparison shows that these 11
+Section~\ref{sec:Magnification}.  This comparison shows that these 14
 models are largely consistent with each other. Naively treating each
@@
 their quoted uncertainties), one would get a mean for the full sample
-of $\mu=2.51\pm0.34$ (shown as a grey dashed line in
-Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
-magnification by $\delta\mu/\mu=30\%$, which is a 1.7$\sigma$
+of $\mu=2.51\pm0.34$.  This is separated from the observed SN
+magnification by $\delta\mu/\mu=27\%$, which is only a 1.2$\sigma$
 difference.
@@
 The models shown in Figure~\ref{fig:lensingtest} are separated along
-the $y$ direction into two broad classes, with the
-six \change{so-called} {\it parametric}\footnote{\change{Although this
+the $y$ direction into two broad classes, with 
+eight \change{so-called} {\it parametric}\footnote{\change{Although this
 nomenclature is becoming standard in the literature, it is somewhat
@@
 be more accurate, though we adopt the more common usage here.}}
-models on top and the four {\it free-form} models on the bottom.
+models on top and six {\it free-form} models on the bottom.
 Broadly speaking, the parametric models use parameterized density
@@
 In general, free-form methods tend to explore the model parameter
-space more fully than parametric methods. 
- This is reflected in the
+space more fully than parametric methods.  This is reflected in the
 size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
@@
 for in GRALE through the use of basis
-functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
-}
+functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }
 
 Figure~\ref{fig:lensingtest} also separates the models based on the
-scope of input data constraints used.  Seven of the models rely only
+scope of input data constraints used.  Ten of the models rely only
 on strong-lensing constraints (plotted as circles), while the other
-four also use weak-lensing measurements (diamonds).  Eight of the
+four also use weak-lensing measurements (diamonds).  Ten of the
 models were constructed using only pre-HFF data (open symbols), and
-three others added new multiply-imaged systems and redshifts.
+four others added new multiply-imaged systems and redshifts.
 
@@
 constraints and reduce the tension between the predicted and observed
-magnification.  However, for both of the most recent
+magnification.  However, for \changeG{two} of the most recent
 models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
@@
 the Jauzac model predicts a $\mu$ that is higher than the measured
-value by $5.6\sigma$.
+value by \changeG{$4.3\sigma$.}
 
@@
 models.  Although this single sight-line can only provide a very
-limited test of the model, the $5.6\sigma$ discrepancy is at least a
-strong suggestion that improving the number and quality of
+limited test of the model, the \changeG{$4.3\sigma$} discrepancy is at
+least a strong suggestion that improving the number and quality of
 strong-lensing constraints can still lead to magnification maps that
@@
 }
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/system3.png}
+\caption{ 
+The disputed component of the multiply-imaged galaxy System 3. The
+original position, as given in \citet{Merten:2011} is marked with a
+dashed magenta circle labeled 3.3. The solid magenta circle shows the
+revised location as proposed in \citet{Jauzac:2014c}.  Both positions
+are $\sim$10\arcsec\ from the SN location.  The inset panel shows the
+other two components of this multiply-imaged system, 3.1 and 3.2 (on
+the same scale as the main panel), which are located north-east of the
+cluster center.
+\label{fig:system3} }
+\end{center}
+\end{figure}
+
 \change{
@@
 This multiply-imaged galaxy was originally labeled as {\it System 3}
-in \citet{Merten:2011}.  As shown in Figure~\ref{fig:System3}, it is
-stretched into two adjacent arcs northwest of the cluster core (images
+in \citet{Merten:2011}.  As shown in Figure~\ref{fig:system3}, it is
+stretched into two adjacent arcs northeast of the cluster core (images
 3.1 and 3.2), with a third image on the western edge of the
@@
 width, with minimal dust extinction.  This excludes the possibility
-that \tomas\ is one of the sub-class of ``fast declining'' Type Ia SNe
-like SN 1991bg.
-}
+that \tomas\ is one of the sub-class of faint and fast-declining Type
+Ia SNe like SN 1991bg.  }
 
@@
 At least for this particular sight-line, the free-form models perform
-better in the sense that they deliver more realistic uncertainties.
-This may indicate that the free-form approach in general is more
-successful in capturing the uncertainty from biases inherent to the
-mass modeling exercise, such as the mass sheet degeneracy and more
-complex ``approximate
-invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  }
+better both in the sense that the mean and standard error for this
+subset ($2.34\pm0.27$) is closer to the measured value ($2.00\pm0.28$)
+than is the parametric set ($2.59 +- 0.36$).  These free-form models
+also deliver more realistic uncertainties (with the exception of the
+Bradac(v2) model -- see \citet{Wang:2015} for further discussion of
+the changes made from v1 to v2 of that model).  This may indicate that
+the free-form approach in general is more successful in capturing the
+uncertainty from biases inherent to the mass modeling exercise, such
+as the mass sheet degeneracy and more complex ``approximate
+invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  It may also be
+the case that the greater flexibility of the free-form models makes
+them better suited for predicting magnifications of sources that fall
+outside the strong-lensing region -- such as SN \tomas.  }
 
@@
 (Meneghetti et al. in prep).  Preliminary analysis of this simulation
-comparison suggests that systematic biases such as we have seen for
-SN \tomas\ may be common for sources that lie close to the critical
-curve in elongated and highly asymmetric clusters like Abell 2744.
-This SN analysis indicates that such simulation efforts will be an
+comparison suggests that \changeG{magnifications tend to be
+overestimated} for sources that lie outside the strong-lensing region
+along the minor axis direction of an elongated cluster.  Our analysis
+of SN \tomas\ here indicates that such simulation efforts will be an
 important step for moving toward precision science with cluster-lensed
-sources. 
-}
+sources.  }
 

### 2015-04-05 snTomasCode/__init__.py
added python code and data for generating figures

@@ -1,0 +1,8 @@
+__all__=['lightcurvefig.py']
+
+import lightcurve_fitting_fig
+
+_ALPHA2FILTER = {'H':'F160W','N':'F140W','J':'F125W','Y':'F105W',
+                'B':'F435W','V':'F606W','I':'F814W',
+                }
+

### 2015-04-05 snTomasCode/convert_data.py

@@ -1,0 +1,40 @@
+def snana_to_sncosmo( snanafile='HST_FFSN_tomas_snana_ab.dat') :
+    """ make the SN Tomas light curve fit figure"""
+    import sncosmo
+    import numpy as np
+    from . import _ALPHA2FILTER
+
+    snanadat = sncosmo.read_snana_ascii(snanafile)
+    mjd = snanadat[1]['OBS']['MJD']
+    band = snanadat[1]['OBS']['FLT']
+    fluxcal = snanadat[1]['OBS']['FLUXCAL']
+    fluxcalerr = snanadat[1]['OBS']['FLUXCALERR']
+    mag  = snanadat[1]['OBS']['MAG']
+    magerr = snanadat[1]['OBS']['MAGERR']
+    zptab  = snanadat[1]['OBS']['ZPTAB']
+
+    flux = fluxcal * 10**(-0.4*(27.5-zptab))
+    fluxerr = fluxcalerr * 10**(-0.4*(27.5-zptab))
+
+    magab = -2.5*np.log10( flux ) + zptab
+    magaberr = 1.0857 * fluxerr / flux
+
+
+    filter = [ _ALPHA2FILTER[b] for b in band ]
+
+    fout = open('HST_FFSN_tomas.sncosmo.dat','w')
+    print >> fout, "# mjd     filter    flux     fluxerr    mag     magerr  zpt    magsys"
+
+    for i in range(len(mjd)) :
+        if flux[i]>0 :
+            print >> fout, "%8.2f  %6s  %8.3f %8.3f  %8.2f %6.2f  %7.3f   AB"%(
+                mjd[i], filter[i], flux[i], fluxerr[i], magab[i], magaberr[i], zptab[i]
+            )
+        else :
+            print >> fout, "%8.2f  %6s  %8.3f %8.3f  %8.2f %6.2f  %7.3f   AB"%(
+                mjd[i], filter[i], flux[i], fluxerr[i],
+                -2.5*np.log10(3*fluxerr[i]) + zptab[i], -9.0, zptab[i]
+            )
+
+    fout.close()
+

### 2015-04-05 snTomasCode/hubble_fig.py

@@ -1,0 +1,149 @@
+def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
+    from pytools import plotsetup, colorpalette as cp
+    from astropy.io import ascii
+    import numpy as np
+    from scipy import optimize as scopt
+    from matplotlib import pyplot as pl
+    from matplotlib import ticker
+    import os
+    import sys
+
+    dmint_mlcs=0.08 # intrinsic scatter in SNIa luminosities for MLCS2k2 (Jha:2007)
+    dmint_salt=0.08 # intrinsic scatter in SNIa luminosities for SALT2 (Conley:2011)
+
+    zTomas = 1.31#,1.35]
+    zerrTomas = 0.01#,0.02]
+    dmTomas_mlcs = 44.06#,44.22]
+    dmerrTomas_mlcs = np.sqrt(0.09**2 + dmint_mlcs**2)
+    dmTomas_salt = 44.09#,44.19]
+    dmerrTomas_salt = np.sqrt(0.16**2 + dmint_salt**2)
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.dirname( os.path.abspath(thisfile))
+
+    datfile = os.path.join( thisdir, datfilename )
+    hubbledat = ascii.read( datfile, format='commented_header', header_start=-1, data_start=0)
+    z = hubbledat['z']
+    dm_mlcs = hubbledat['dm_mlcs']
+    dm_mlcs_err = np.sqrt(hubbledat['dm_mlcs_err']**2 + dmint_mlcs**2)
+    dm_salt = hubbledat['dm_salt']
+    dm_salt_err = np.sqrt(hubbledat['dm_salt_err']**2 + dmint_salt**2)
+    iscp = np.where( hubbledat['survey']=='scp')
+    igoods = np.where( hubbledat['survey']=='goods')
+    fig = plotsetup.halfpaperfig( )
+    pl.clf()
+    if fitter.lower()=='both':
+        ax1 = fig.add_subplot(2,1,1)
+        ax2 = fig.add_subplot(2,1,2, sharex=ax1, sharey=ax1)
+    elif fitter.lower().startswith('mlcs') :
+        ax1 = fig.add_subplot(1,1,1)
+        ax2 = ax1
+    elif fitter.lower().startswith('salt') :
+        ax1 = fig.add_subplot(1,1,1)
[…]

### 2015-04-05 snTomasCode/lensing_test_fig.py

@@ -1,0 +1,136 @@
+
+#------------------------------------------------------------
+# The lensing comparison figure
+import numpy as np
+
+def mkLensingTestFig( presfig=False ):
+    from matplotlib import pyplot as pl
+    from matplotlib.patches import FancyArrowPatch
+    from pytools import plotsetup, colorpalette as cp
+    from astropy.io import ascii
+    import os
+    import sys
+
+    if presfig :
+        fig = plotsetup.presfig( figsize=[12,8])
+        labelvalues=True
+        pl.clf()
+        ax1 = pl.axes( [0.01,0.14,0.67,0.83] )
+        ms=15
+    else :
+        labelvalues=False
+        fig = plotsetup.fullpaperfig( figsize=[4,5])
+        ms=8
+        pl.clf()
+        ax1 = pl.axes( [0.01,0.08,0.7,0.86] )
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.dirname( os.path.abspath(thisfile))
+
+    lensdatfile = os.path.join(thisdir,'data/lensing/lensing_medians.dat')
+    lensingdat = ascii.read( lensdatfile, format='commented_header',
+                             header_start=-1, data_start=0 )
+
+    ytop=15.2
+    y = ytop-0.7
+    for row in lensingdat:
+        y-=1
+        color = row['parametric'] and 'k' or 'g'
+        mfc = row['postFF'] and color or 'w'
+        model = row['model']
+        best = row['best']
+        med = row['med']
+        errplus = row['med+']-med
+        errminus = row['med-']-med
+        if row['strong+weak']:
+            marker='D'
+        else:
+            marker='o'
+
+        #ax1.plot( best, y, marker='x', ms=ms, color=color,
+        #          zorder=100, label='_nolegend_' )
+        if med+errplus>3.6 :
+            # make an arrow for the really long williams error
+            errplus = 3.5-med
+            ax1.errorbar( med, y, yerr=None, xerr=[[0],[errplus]],
+                          marker=None, capsize=0.6*ms, color=color,
[…]

### 2015-04-05 snTomasCode/lightcurve_classification_fig.py

@@ -1,0 +1,173 @@
+
+# Results of the classification run using sncosmo.classify()
+# sncosmo.classify.classify( snTomas, zhost = 1.30, zhosterr=0.5,
+#                       t0_range=[56800,56840], zminmax=[0.9,1.8], verbose=3 )
+
+_bestfitIa = {
+    'model':'salt2-extended', 'class':'Ia',
+    'z': 1.35126, 'zerr':0.01608,
+    'c':-0.09321, 'cerr':0.01946,
+    'x1': 0.03530,'x1err':0.18911,
+    'mB':24.66244,'mBerr':0.01881,
+    't0':56816.28,'t0err':0.33732,
+    'x0':2.171e-6,'x0err':0.038e-6,
+}
+
+_bestfitII = {
+    'model':'snana-2007pg', 'class':'II',
+    'z':1.79865, 'zerr':0.00134,
+    't0':56808.6, 't0err':0.25432,
+    'amplitude':2.98840e-18, 'amplitudeerr':9.81812e-20,
+    'hostebv':0.00870956, 'hostebverr':0.00694,
+    'hostr_v':2.94742, 'hostr_verr':0.25432,
+    }
+
+
+_bestfitIbc = {
+    'model':'snana-sdss014475', 'class':'Ib/c',
+    'z':0.695, 'zerr':0.016,
+    't0':56805.4, 't0err':0.34,
+    'amplitude':2.263e-17, 'amplitudeerr':3.289e-18,
+    'hostebv':0.349, 'hostebverr':0.044,
+    'hostr_v':3.72, 'hostr_verr':0.24,
+    }
+
+
+def mk_figure(yunit='flux'):
+    """ make a figure showing the SN Tomas light curve classification
+    best-fit models for each class
+    :return:
+    """
+    import numpy as np
+    from matplotlib import pyplot as pl, ticker, gridspec, rcParams
+    import sys
+    import os
+    from pytools import colorpalette as cp, plotsetup
+    from astropy.io import ascii
+    import sncosmo
+
+    bandlist = ['f814w','f105w','f125w','f140w','f160w']
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.abspath( os.path.dirname(thisfile))
+
+    obsdat = ascii.read(os.path.join(thisdir,'data/HST_FFSN_tomas.dat'),
+                        format='commented_header',
+                        header_start=-1, data_start=0)
+    if yunit=='mag':
[…]

### 2015-04-05 snTomasCode/lightcurve_fitting_fig.py

@@ -1,0 +1,391 @@
+
+
+
+
+def plot_light_curve_fit( fitter='mlcs2k2', plotmags=True,
+                          compare=False ) :
+    """ make the SN Tomas light curve fit figure"""
+    from pytools import plotsetup, colorpalette as cp
+    from astropy.io import ascii
+    import numpy as np
+    from matplotlib import pyplot as pl
+    from matplotlib import ticker, gridspec
+    import os
+    import sys
+    from hstphot import hstzpt
+
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.abspath( os.path.dirname(thisfile))
+
+    sn = ascii.read(os.path.join(thisdir,'data/HST_FFSN_tomas.dat'),
+                    format='commented_header', header_start=-1, data_start=0)
+
+    alpha2filter = { 'H':'F160W','N':'F140W','J':'F125W',
+                     'Y':'F105W','I':'F814W','V':'F606W','B':'F435W' }
+    colordict = { 'H':'k', 'N':cp.darkred,
+                  'J':cp.darkgold, 'Y':cp.cadetblue,
+                  'I':cp.darkgreen, 'V':cp.coral,
+                  'B':cp.purple}
+
+    if fitter=='both' :
+        plotsetup.fullpaperfig([8,4])
+        gs = gridspec.GridSpec( 2,5 )
+        rowdict = {'salt2':1,'mlcs2k2':0}
+        fitterlist=['mlcs2k2','salt2']
+    else :
+        plotsetup.fullpaperfig([8,4])
+        gs = gridspec.GridSpec(1,5)
+        rowdict = {fitter:0}
+        fitterlist = [fitter]
+    fig = pl.gcf()
+    pl.clf()
+
+    for fitter in fitterlist :
+        axdict = {
+            'B':fig.add_subplot(gs[rowdict[fitter],0]),
+            'Y':fig.add_subplot(gs[rowdict[fitter],1]),
+            'J':fig.add_subplot(gs[rowdict[fitter],2]),
+            'N':fig.add_subplot(gs[rowdict[fitter],3]),
+            'H':fig.add_subplot(gs[rowdict[fitter],4]),
+            }
+        axdict['V'] = axdict['B']
+        axdict['I'] = axdict['B']
+
+        for band in ['V','I','Y','J','N','H'] :
+            ax = axdict[band.upper()]
+            filtname = alpha2filter[band]
[…]

### 2015-04-05 snTomasCode/sn06bt_comparison_fig.py

@@ -1,0 +1,226 @@
+__author__ = 'rodney'
+
+def getdata():
+    """ read in the 06bt and tomas rest-frame UBVri light curves
+    :return:
+    """
+    import sys
+    import os
+    from astropy.io import ascii
+    from astropy.table import Table, Column
+    import sncosmo
+    import numpy as np
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.abspath( os.path.dirname(thisfile))
+    datadir = os.path.join( thisdir, "data/sn06bt/lightcurve")
+
+    # read in the 06bt and tomas rest-frame UBVri light curves
+    sn06bt = ascii.read(os.path.join(datadir,'sn06bt_lightcurve.dat'))
+    tomas = ascii.read(os.path.join(datadir,'tomas_UBVri.dat'))
+
+    # simulate a normal SN Ia
+    snIa = sncosmo.Model( 'salt2' )
+    snIa.set(c=-0.15)
+    snIa.set(z=0.001)
+    trest=[]
+    mag = []
+    magerr = []
+    bandlist=[]
+    t = np.arange(-5,25,0.1)
+    zeros = np.zeros(len(t))
+    for band in ['bessellux','bessellb','bessellv','sdssr']:
+        m = snIa.bandmag( band, 'Vega', t )
+        trest = np.append( trest, t )
+        mag = np.append( mag, m )
+        magerr = np.append( magerr, zeros )
+        bandlist = np.append( bandlist, [band for i in range(len(m))])
+    snIaUBVr = Table({'trest':trest,'mag':mag,'magerr':magerr,'filter':bandlist})
+
+    return( sn06bt, tomas, snIaUBVr )
+
+def plotcolorcurve( band1='bessellb', band2='bessellv', **plotargs):
+    """  plot color vs time
+    :return:
+    """
+    from matplotlib import pyplot as pl
+    import numpy as np
+
+    # read in the 06bt and tomas rest-frame UBVri light curves
+    sn06bt, tomas, snIa = getdata()
+
+    ax = pl.gca()
+
+    # for band1,band2 in (['bessellb','bessellv'],['bessellb','sdssr'],['sdssr','sdssi']):
+    for sn, clr, marker, ls in zip([sn06bt,tomas, snIa],
+                                     ['darkorange','0.5','b'],
[…]

### 2015-04-05 snTomasCode/specfig.py

@@ -1,0 +1,111 @@
+
+def getchi2(templatedatfile, obsdatfile='SPECTRUM/snTomas_acs_g800l_1d.dat'):
+    import numpy as np
+    from matplotlib import pyplot as pl, ticker
+
+    wave, flux, err, sens = np.loadtxt(obsdatfile, unpack=True)#, usecols=[0,1])
+    wavemod,fluxmod= np.loadtxt(templatedatfile, unpack=True)
+    chi2 = np.sum( (fluxmod-flux)**2 / err**2 )
+    return( chi2 )
+
+
+
+
+def mkspecfig(plotflam=False, showerr=False):
+    from astropy.io import ascii
+    import numpy as np
+    from matplotlib import pyplot as pl, ticker
+    from pytools import plotsetup
+    import sys
+    import os
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile:
+        thisfile = __file__
+    thisdir = os.path.dirname( thisfile )
+    
+    plotsetup.halfpaperfig( figsize=[4,6])
+    specfile = thisdir+'/data/spectrum/snTomas_acs_g800l_1d.dat'
+    wave, flux, err, sens = np.loadtxt(specfile, unpack=True)#, usecols=[0,1])
+
+    flambda = flux / sens * 1e-17
+    flambdaErr = err / sens * 1e-17
+
+    templist = [thisdir+'/data/spectrum/sm-cont-1.31000-sn2012cg-visit1-hst.flm',
+                thisdir+'/data/spectrum/sm-1.31000-sn2011fe-visit4-hst.flm',
+                thisdir+'/data/spectrum/sm-0.980000-sn2011iv-hst.flm',
+                ]
+    zlist = [1.31, 1.31, 0.98]
+    labellist = ['SN 2012cg (warped)\nz=1.31\nage=+3',
+                 'SN 2011fe\nz=1.31\nage=-3',
+                 'SN 2011iv\nz=0.98\nage=0',
+                 ]
+    chi2list = [ getchi2(tempfile) for tempfile in templist ]
+    ndoflist = [ len(wave)-6, len(wave)-2, len(wave)-2 ]
+
+    fig = pl.gcf()
+
+    fig.subplots_adjust( left=0.03, right=0.97, top=0.9, bottom=0.1, hspace=0.5)
+    pl.clf()
+    nax = len( templist )
+    iax = 0
+    colorlist = ['r','g','b']
[…]

### 2015-04-05 snTomas.tex
test

@@
 best-fitting spectral template is the normal Type Ia SN 2012cg, shown
-in the bottom panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
+in the top panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
 per degree of freedom $\nu$ equal to 42.1/87.

### 2015-04-05 snTomas.tex
Small edit test

@@
 and \ref{sec:PhotometricClassification}, the SN data are inconsistent
-with that redshift, meaning that this nearby galaxy is a background
+with that redshift, meaning that this spatially nearby galaxy is a background
 object and therefore has no impact on the SN magnification.}
@@
 color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
-$\sigma_c^+=0.54$.  The $c$ parameter in SALT2 combines intrinsic SN
+$\sigma_c^+=0.54$ using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
 color and extinction due to dust, so the large red tail of this

### 2015-04-07 authors.tex
authors list updated
added sn06bt color curve fig
Various changes, incorporating comments from various co-authors
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig
Overhauled author list to allow automatic indexing

@@
-\author{Steven~A.~Rodney\altaffilmark{1,2}}
+% --------------------------------------------------
+% Institutions
+%   define a command for each institution's mailing address
+% --------------------------------------------------
+\newcommand{\HubbleFellow}{Hubble Fellow}
+\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 N. Charles St., Baltimore, MD 21218, USA}
+\newcommand{\elsewhere}{St. Elsewhere University.}
+\newcommand{\STScI}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
+\newcommand{\Chicago}{Department of Physics, The University of Chicago, Chicago, IL 60637, USA}
+\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411, USA}
+\newcommand{\LBNL}{Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA}
+\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521, USA}
+\newcommand{\Andalucia}{Instituto de Astrof\'isica de Andaluc\'ia (CSIC), E-18080 Granada, Spain}
+\newcommand{\Cantabria}{IFCA, Instituto de F\'isica de Cantabria (UC-CSIC), Av. de Los Castros s/n, 39005 Santander, Spain}
+\newcommand{\IFCA}{\Cantabria}
+\newcommand{\SaoPaulo}{Instituto de Astronomia, Geof\'isica e Ci\^encias Atmosf\'ericas, Universidade de S\~ao Paulo, Cidade Universit\'aria, 05508-090, S\~ao Paulo, Brazil}
+\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101, USA}
+\newcommand{\AMNH}{Department of Astrophysics, American Museum of Natural History, Central Park West and 79th Street, New York, NY 10024, USA}
+\newcommand{\NYU}{Center for Cosmology and Particle Physics, New York University, New York, NY 10003, USA}
+\newcommand{\DARK}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark}
+\newcommand{\Copenhagen}{\DARK}
+\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721, USA}
+\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064, USA}
+\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556, USA}
+\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel}
+\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854, USA}
+\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
+\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA}
+\newcommand{\NOAO}{National Optical Astronomical Observatory, Tucson, AZ 85719, USA}
+\newcommand{\UCSB}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
+\newcommand{\SantaBarbara}{\UCSB}
+\newcommand{\LCOGT}{Las Cumbres Observatory Global Telescope Network, 6740 Cortona Dr., Suite 102, Goleta, California 93117, USA}
+\newcommand{\Colby}{Colby College, 4000 Mayflower Hill Dr, Waterville, ME 04901, USA}
+\newcommand{\Kentucky}{University of Kentucky, Lexington, KY 40506}
+\newcommand{\UCDavis}{University of California Davis, 1 Shields Avenue, Davis, CA 95616}
+\newcommand{\UCLA}{University of California, Los Angeles, CA 90095}
+\newcommand{\CalTech}{California Institute of Technology, 1200 East California Boulevard, Pasadena, CA 91125}
+\newcommand{\Durham}{Institute for Computational Cosmology, Durham University, South Road, Durham DH1 3LE, UK}
+\newcommand{\KwaZulu}{Astrophysics and Cosmology Research Unit, School of Mathematical Sciences, University of KwaZulu-Natal, Durban 4041, South Africa}
+\newcommand{\HongKong}{Department of Physics, The University of Hong Kong, Pokfulam Road, Hong Kong}
+\newcommand{\Oxford}{Department of Physics, University of Oxford, Clarendon Laboratory, Parks Road, Oxford, UK}
+\newcommand{\CRAL}{CRAL, Observatoire de Lyon, Universit\'e Lyon 1, 9 Avenue Ch. Andr\'e, F-69561 Saint Genis Laval Cedex, France}
+\newcommand{\Michigan}{Department of Astronomy, University of Michigan, 1085 S. University Avenue, Ann Arbor, MI 48109, USA}
+\newcommand{\Hebrew}{The Hebrew University, The Edmond J. Safra Campus - Givat Ram, Jerusalem 9190401, Israel}
+\newcommand{\IllinoisAstro}{ Astronomy Department, University of Illinois at Urbana-Champaign, 1002 W.\ Green Street, Urbana, IL 61801, USA }
+\newcommand{\IllinoisPhysics}{ Department of Physics, University of Illinois at Urbana-Champaign, 1110 W.\ Green Street, Urbana, IL 61801, USA }
 
-\author{Brandon Patel}
+% --------------------------------------------------
+% Author list 
+%   use the \affilref and \affilreftxt commands 
+%   to get an author list and footnoted institutional
+%   addresses that count themselves without duplicating
+% --------------------------------------------------
+\newcounter{affilct}
+\setcounter{affilct}{0}
 
-\author{Daniel Scolnic}
+% --------------------------------------------------
+% \affilref{refcode}
+%   Use this command inside each \altaffilmark{} instance.
+%   It checks if the affiliation has already been used, and generates
+%   a new affiliation reference number only if needed.
+%   The user-defined refcode value will then be used by \affilreftxt
+%   to set the same index number in the author list at the top and 
+%   the footnoted list of institutional addresses. 
+\makeatletter
+\newcommand{\affilref}[1]{%
+    \@ifundefined{c@#1}{%
+    	\newcounter{#1}%
+    	\setcounter{#1}{0}%
+    }{}%
+    \ifthenelse{\value{#1} > 0}{%
+      \ref{#1}%
+    }{%
+      \refstepcounter{affilct}%
+    	\label{#1}%
+      \ref{#1}%
+    	\addtocounter{#1}{1}%
+    }%
+}
+\makeatother
 
-\author{Ryan Foley}
+% --------------------------------------------------
+% \affilreftxt{refcode}{address} : 
+%   Use this command after each author definition 
+%   to generate the footnote text containing one institutional
+%   address for that author. 
+%   It checks if the address has already been used, and generates
+%   a new affiliation footnote with text only if needed.
+\makeatletter
+\newcommand{\affilreftxt}[2]{%
+    \@ifundefined{c@#1txt}{%
+    	\newcounter{#1txt}%
+    	\setcounter{#1txt}{0}%
+    }{}%
+    \ifthenelse{\value{#1txt} > 0}{%
+    }{%
+      \altaffiltext{\ref{#1}}{#2}%
+    	\addtocounter{#1txt}{1}%
+    }%
+}
+\makeatother
+% --------------------------------------------------
 
-\author{Alberto Molino}
+\author{Steven~A.~Rodney\altaffilmark{\affilref{JHU},\affilref{HubbleFellow}}}
+\affilreftxt{JHU}{\JHU}
+\affilreftxt{HubbleFellow}{\HubbleFellow}
 
-\author{Marusa Bradac}
+\author{Brandon~Patel\altaffilmark{\affilref{Rutgers}}}
+\affilreftxt{Rutgers}{\Rutgers}
 
-\author{Gabriel Brammer}
+\author{Daniel~Scolnic\altaffilmark{\affilref{Chicago}}}
+\affilreftxt{Chicago}{\Chicago}
 
-\author{Jose~Maria~Diego}
+\author{Ryan Foley\altaffilmark{\affilref{IllinoisPhysics},\affilref{IllinoisAstro}}}
+\affilreftxt{IllinoisPhysics}{\IllinoisPhysics}
+\affilreftxt{IllinoisAstro}{\IllinoisAstro}
 
-\author{Jens Hjorth}
+\author{Alberto Molino\altaffilmark{\affilref{Andalucia},\affilref{SaoPaulo}}}
+\affilreftxt{Andalucia}{\Andalucia}
+\affilreftxt{SaoPaulo}{\SaoPaulo}
 
-\author{Austin Hoag}
+\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
+\affilreftxt{Durham}{\Durham}
+\affilreftxt{KwaZulu}{\KwaZulu}
 
-\author{Mathilde Jauzac}
+\author{Gabriel Brammer\altaffilmark{\affilref{STScI}}}
+\affilreftxt{STScI}{\STScI}
 
-\author{Saurabh Jha}
+\author{Marusa Bradac\altaffilmark{\affilref{UCDavis}}}
+\affilreftxt{UCDavis}{\UCDavis}
 
-\author{Patrick Kelly}
+\author{Jose~Maria~Diego\altaffilmark{\affilref{Cantabria}}}
+\affilreftxt{Cantabria}{\Cantabria}
 
-\author{Daniel Lam}
+\author{Jens Hjorth\altaffilmark{\affilref{DARK}}}
+\affilreftxt{DARK}{\DARK}
 
-\author{Julian~Merten}
+\author{Or Graur\altaffilmark{\affilref{NYU},\affilref{AMNH}}}
+\affilreftxt{NYU}{\NYU}
+\affilreftxt{AMNH}{\AMNH}
 
-\author{Johan Richard}
+\author{Austin Hoag\altaffilmark{\affilref{UCDavis}}}
+\affilreftxt{UCDavis}{\UCDavis}
 
-\author{Keren Sharon}
+\author{Saurabh Jha\altaffilmark{\affilref{Rutgers}}}
+\affilreftxt{Rutgers}{\Rutgers}
 
-\author{Louis-Gregory Strolger}
+\author{Patrick Kelly\altaffilmark{\affilref{Berkeley}}}
+\affilreftxt{Berkeley}{\Berkeley}
 
-\author{Tommaso Treu}
+\author{Daniel Lam\altaffilmark{\affilref{HongKong}}}
+\affilreftxt{HongKong}{\HongKong}
 
-\author{Adi Zitrin}
+\author{Elinor Medezinski\altaffilmark{\affilref{JHU},\affilref{Hebrew}}}
+\affilreftxt{JHU}{\JHU}
+\affilreftxt{Hebrew}{\Hebrew}
 
-\altaffiltext{1}{\JHU}
-\altaffiltext{1}{\Rutgers}
-\altaffiltext{1}{\Chicago}
-\altaffiltext{1}{\Illinois}
-\altaffiltext{1}{\CSIC}
-\altaffiltext{1}{\SaoPaulo}
-\altaffiltext{1}{\UCDavis}
-\altaffiltext{1}{\STScI}
-\altaffiltext{1}{\Copenhagen}
-\altaffiltext{1}{\UCDavis}
-\altaffiltext{1}{\Rutgers}
-\altaffiltext{1}{\Berkeley}
-\altaffiltext{1}{\STScI}
-\altaffiltext{1}{\WKU}
-\altaffiltext{1}{\UCLA}
-\altaffiltext{1}{\CalTech}
-\altaffiltext{2}{Hubble fellow}
+\author{Julian~Merten\altaffilmark{\affilref{Oxford}}}
+\affilreftxt{Oxford}{\Oxford}
+
+\author{Johan Richard\altaffilmark{\affilref{CRAL}}}
+\affilreftxt{CRAL}{\CRAL}
+
+\author{Keren Sharon\altaffilmark{\affilref{Michigan}}}
+\affilreftxt{Michigan}{\Michigan}
+
+\author{Louis-Gregory Strolger\altaffilmark{\affilref{STScI},\affilref{WKU}}}
+\affilreftxt{STScI}{\STScI}
+\affilreftxt{WKU}{\WKU}
+
+\author{Tommaso Treu\altaffilmark{\affilref{UCLA}}}
+\affilreftxt{UCLA}{\UCLA}
+
+\author{Liliya Williams\altaffilmark{\affilref{Minnesota}}}
+\affilreftxt{Minnesota}{\Minnesota}
+
+\author{Adi Zitrin\altaffilmark{\affilref{CalTech},\affilref{HubbleFellow}}}
+\affilreftxt{CalTech}{\CalTech}

### 2015-04-07 preamble.tex
incorporated most comments from JH,KS, others
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig
Overhauled author list to allow automatic indexing

--- 2015-01-16 preamble.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% changetext  mode settings
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\ifchangetext
-  % Changed text is highlighted in bold, blue font 
-  \newcommand{\change}[1]{{\bf \textcolor{blue}{#1}}}
-\else
-  % Changed text is indistinguishable
-  \newcommand{\change}[1]{#1}
-\fi
-
 %%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%
+\usepackage{ifthen}
 \usepackage{natbib}   % reference citations and bibliography
@@
 \usepackage{hyperref}      % url text formatting
-\usepackage[usenames]{color}  % colored text
+\usepackage[usenames,dvipsnames]{xcolor}  % colored text
 %\usepackage{multirow}  % muti-row table cells
@@
 \usepackage{appendix}
+%\usepackage{array}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% changetext  mode settings
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ifchangetext
+  % Changed text is highlighted in bold, blue font 
+  \newcommand{\change}[1]{{\bf \textcolor{blue}{#1}}}
+  \newcommand{\changeB}[1]{{\bf \textcolor{blue}{#1}}}
+  \newcommand{\changeG}[1]{{\bf \textcolor{ForestGreen}{#1}}}
+  \newcommand{\changeR}[1]{{\bf \textcolor{red}{#1}}}
+\else
+  % Changed text is indistinguishable
+  \newcommand{\change}[1]{#1}
+  \newcommand{\changeB}[1]{#1}
+  \newcommand{\changeG}[1]{#1}
+  \newcommand{\changeR}[1]{#1}
+\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% New table column types, allowing left- or right-justified text in 
+% paragraph mode, that also allows manual line-breaks
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 
@@
 \def\XMM{{\it XMM}}
-
-% Institutions
-\newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, Baltimore, MD 21218.}
-\newcommand{\elsewhere}{St. Elsewhere University.}
-\newcommand{\STScI}{Space Telescope Science Institute, Baltimore, MD 21218.}
-\newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411.}
-\newcommand{\Riverside}{Department of Physics and Astronomy, University of California, Riverside, CA 92521.}
-\newcommand{\WKU}{Department of Physics, Western Kentucky University, Bowling Green, KY 42101.}
-\newcommand{\Copenhagen}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, DK-2100 Copenhagen, Denmark.}
-\newcommand{\Arizona}{Department of Astronomy, University of Arizona, Tucson, AZ 85721.}
-\newcommand{\SantaCruz}{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 92064.}
-\newcommand{\NotreDame}{Department of Physics, University of Notre Dame, Notre Dame, IN 46556.}
-\newcommand{\TelAviv}{Department of Astrophysics, Tel Aviv University, 69978 Tel Aviv, Israel.}
-\newcommand{\Rutgers}{Department of Physics and Astronomy, Rutgers, The State University of New Jersey, Piscataway, NJ 08854.}
-\newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138.}
-\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA.}
 

### 2015-04-07 snTomas.tex

@@
 color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
-$\sigma_c^+=0.54$ using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
+$\sigma_c^+=0.54$, using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
 color and extinction due to dust, so the large red tail of this
@@
 
-\noindent This inferred magnification is reported in the final column of
+\noindent The inferred magnifications for the two different fitters are reported in the final column of
 Table~\ref{tab:MeasuredMagnification}.
@@
 size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
-GRALE, which has the largest, and possibly the most realistic
+GRALE(Williams?), which has the largest, and possibly the most realistic
 uncertainties is able to account for mass sheet degeneracy by
@@
 the genetic algorithm.  More complex degeneracies are also accounted
-for in GRALE through the use of basis
+for in GRALE(Williams?) through the use of basis
 functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }
@@
 error to account for the intrinsic luminosity scatter. These are well
-vetted paraemeters, based on observations of $\sim500$ SNe extending
+vetted parameters, based on observations of $\sim500$ SNe extending
 to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason

### 2015-04-07 snTomas.tex

@@
 and \ref{sec:PhotometricClassification}, the SN data are inconsistent
-with that redshift, meaning that this spatially nearby galaxy is a background
+with that redshift, meaning that this is a background
 object and therefore has no impact on the SN magnification.}
@@
 cosmological analyses \citep[see
-e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior is
-a bifurcated Gaussian distribution with mean $\bar{x}_1=0$, dispersion
-$\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The prior for the
-color parameter $c$ has $\bar{c}=0.0$, $\sigma_c^-=0.08$, and
-$\sigma_c^+=0.54$, using the same distribution as for $x_1$.  The $c$ parameter in SALT2 combines intrinsic SN
-color and extinction due to dust, so the large red tail of this
-distribution allows for the possibility of several magnitudes
-of dust extinction along the \tomas\ line of sight.
+e.g.,][]{Kessler:2009b,Sullivan:2011,Rest:2014}. For $x_1$ the prior
+is a bifurcated Gaussian distribution with mean $\bar{x}_1=0$,
+dispersion $\sigma_{x_1}^+={0.9}$ and $\sigma_{x_1}^-={-1.5}$.  The
+bifurcated Gaussian prior for the color parameter $c$ has
+$\bar{c}=0.0$, $\sigma_c^-=0.08$, and $\sigma_c^+=0.54$.  The $c$
+parameter in SALT2 combines intrinsic SN color and extinction due to
+dust, so the large red tail of this distribution allows for the
+possibility of several magnitudes of dust extinction along the \tomas\
+line of sight.
 
@@
 
-\noindent The inferred magnifications for the two different fitters are reported in the final column of
-Table~\ref{tab:MeasuredMagnification}.
+\noindent The inferred magnifications for the two different fitters are
+reported in the final column of Table~\ref{tab:MeasuredMagnification}.
 
@@
 size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
-GRALE(Williams?), which has the largest, and possibly the most realistic
-uncertainties is able to account for mass sheet degeneracy by
-introducing a free parameter in the reconstruction that represents an
-arbitrarily positioned mass sheet, with normalization to be chosen by
-the genetic algorithm.  More complex degeneracies are also accounted
-for in GRALE(Williams?) through the use of basis
+the Williams model (using GRALE), which has the largest, and possibly the
+most realistic uncertainties is able to account for mass sheet
+degeneracy by introducing a free parameter in the reconstruction that
+represents an arbitrarily positioned mass sheet, with normalization to
+be chosen by the genetic algorithm.  More complex degeneracies are
+also accounted for in this model through the use of basis
 functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }

### 2015-04-07 TABLE/magnifications.tex
incorporated AZ comments

@@
-\begin{deluxetable*}{lccp{1.9in}p{2.2in}}
+\begin{deluxetable*}{lcccp{1.4in}p{2.1in}}
 \tablecolumns{5}
 \tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
-\tablehead{ \colhead{Model} & \colhead{Best}\tablenotemark{a} & \colhead{Median\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
+\tablehead{ \colhead{Model} & \colhead{Best\tablenotemark{a}} & \colhead{Median\tablenotemark{b}} & \colhead{68\% Conf. Range\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
 \startdata
-Sharon(v1)   & 2.53 & 2.57$^{+0.18}_{-0.16}$ & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\
-Sharon(v2)   & 2.73 & 2.69$^{+0.14}_{-0.06}$ &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model\\
-CATS-SL      & 2.25 & 2.27$^{+0.05}_{-0.04}$ &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
-CATS-SL+WL   & \nodata & 2.62$^{+0.18}_{-0.18}$ & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
-Jauzac		 & \nodata & 3.37$^{+0.14}_{-0.15}$ &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
-GLAFIC       & 2.32 & 2.28$^{+0.07}_{-0.11}$ &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
-Zitrin-NFW   & 2.07 & 2.27$^{+0.23}_{-0.22}$ &   \citealt{Zitrin:2009a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
-Zitrin-LTM   & 2.64 & 2.96$^{+0.77}_{-0.38}$ &   \citealt{Zitrin:2013a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac(v1)   & 3.15 & 2.45$^{+0.19}_{-0.16}$ &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model.
+Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\
+Sharon(v2)   & 2.73     & 2.69  &   2.63$-$2.83 &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\
+CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
+CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
+Jauzac		 & \nodata  & 3.37  &   3.22$-$3.51 &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
+GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
+Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
+Zitrin-LTM   & 2.64     & 2.96  &   2.58$-$3.73 &   \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
+Bradac(v1)   & 3.15     & 2.45  &   2.29$-$2.64 &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
-Bradac(v2)   & 2.21 & 2.23$^{+0.05}_{-0.03}$ &   \citealt{Wang:2015} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Bradac(v2)   & 2.21     & 2.23  &   2.20$-$2.28 &   \citealt{Wang:2015} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
 Errors from bootstrap resampling only strong-lensing constraints.}\\
-Williams     & 2.67 & 2.78$^{+2.68}_{-1.14}$ &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.
+Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.
 \\
-Merten       & 2.31 & 2.22$^{+0.67}_{-0.19}$ &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam			 & \nodata & 2.77$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Diego\tablenotemark{i}			 & \nodata & 2.10$^{+0.36}_{-0.36}$ &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
+Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Diego\tablenotemark{i}        & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
 \enddata
 \tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
-\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Uncertainties enclose 68\%\ of the realized values.}  
+\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Confidence ranges enclose 68\%\ of the realized values.}  
 \tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
@@
 \tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
-\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the Lam model.}}
+\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}}
 \end{deluxetable*}

### 2015-04-07 snTomas.tex
incorporated AZ comments

@@
 DOI:10.5281/zenodo.10731} a custom data reduction package in Python
-that is employs the {\tt DrizzlePac} tools from the Space Telescope
+that employs the {\tt DrizzlePac} tools from the Space Telescope
 Science Institute (STScI) \citep{Fruchter:2010}.  Photometry was
@@
 model selection using the photometric data alone. Grey points show the
-observed SN \tomas\ photometry with error bars, though these are typically
-smaller than the size of the marker.  The Type Ia model
+observed SN \tomas\ photometry with error bars, though these are
+typically smaller than the size of the marker.  The Type Ia model
 (orange solid line) is drawn from the SALT2 template at $z=1.35$. The
 best match from all Type Ib/Ic models is based on the Type Ic SN
-SDSS-14475 at $z=0.695$ (green dashed line). For the Type II class, the
-best match is from the Type II-L SN 2007pg at $z=1.8$ (blue dash-dot line). The Type
-Ia model is by far the best match, and the only one that is consistent
-with both the photo-$z$ of the probable host galaxy and the
-spectroscopic redshift from the SN spectrum.
+SDSS-14475 at $z=0.695$ (green dashed line). For the Type II class,
+the best match is from the Type II-L SN 2007pg at $z=1.8$ (blue
+dash-dot line). The Type Ia model is by far the best match, and the
+only one that is consistent with both the photo-$z$ of the probable
+host galaxy and the spectroscopic redshift from the SN spectrum.  The
+date of the HST spectral observations is marked with a thin grey
+vertical line.
 \label{fig:photoclass} }
@@
 (Section~\ref{sec:SNID}), we independently classified the SN using a
-Bayesian photometric classifier.  We use the
-{\tt sncosmo} software
+Bayesian photometric classifier.  We use the {\tt sncosmo} software
 package\footnote{\url{http://sncosmo.github.io/}} to simulate SN light
-curves from $z=0.3$ to 2.3 and evaluate the classification
-probability using traditional Bayesian model selection \citep[as
+curves from $z=0.3$ to 2.3 and evaluate the classification probability
+using traditional Bayesian model selection \citep[as
 in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015a}.  In this
@@
 package \citep[SNANA,][]{Kessler:2009a}.\footnote{Throughout this work
-we use SNANA v10\_35g.}
-Likelihoods are defined by comparing the observed fluxes to model
-predictions in all passbands where the model is defined.  In practice,
-this means we exclude the F435W and F606W bands, which are too blue
-for our models at $z>0.85$.
+we use SNANA v10\_35g.}  Likelihoods are defined by comparing the
+observed fluxes to model predictions in all passbands where the model
+is defined.  In practice, this means we exclude the SN detections in
+the F435W and F606W bands, which are too blue for our models at
+$z>0.85$.
 
@@
 the $y$ direction into two broad classes, with
-eight \change{so-called} {\it parametric}\footnote{\change{Although this
-nomenclature is becoming standard in the literature, it is somewhat
-misleading, as the pixels or grid cells in free-form models are
-effectively parameters as well. Perhaps ``simply-parameterized'' would
-be more accurate, though we adopt the more common usage here.}}
-models on top and six {\it free-form} models on the bottom.
-Broadly speaking, the parametric models use parameterized density
+eight \change{so-called} {\it parametric}\footnote{\change{Although
+this nomenclature is becoming standard in the literature, it is
+somewhat misleading, as the pixels or grid cells in free-form models
+are effectively parameters as well. Perhaps ``simply-parameterized''
+would be more accurate, though we adopt the more common usage here.}}
+models on top and six {\it free-form} models on the bottom.  Broadly
+speaking, the parametric models use parameterized density
 distributions to describe the arrangement of mass within the cluster,
@@
 bright cluster member galaxies. Therefore, parametric models rely (to
-varying degrees) on the assumption that the observed light from
-cluster galaxies is a good tracer of the cluster's dark matter.
+varying degrees) on the assumption that the 
+\changeR{cluster's dark matter can be described
+by analytic forms such as NFW halos \citep{Navarro:1997}, or pseudo isothermal elliptical mass distributions \citep{Kassiola:1993}.}
 Free-form models divide the cluster into a grid, generally using a
@@
 degeneracy by introducing a free parameter in the reconstruction that
-represents an arbitrarily positioned mass sheet, with normalization to
+represents an arbitrarily scaled mass sheet, with normalization to
 be chosen by the genetic algorithm.  More complex degeneracies are
@@
 limited test of the model, the \changeG{$4.3\sigma$} discrepancy is at
-least a strong suggestion that improving the number and quality of
-strong-lensing constraints can still lead to magnification maps that
-are susceptible to systematic biases.
+least a strong suggestion that \changeR{even with a large number of
+high-quality} strong-lensing constraints \changeR{it is still possible
+to generate} magnification maps that are susceptible to systematic
+biases.
 
@@
 lensing relies on a large sample of background galaxies, so this
-constraint operates principally at separations more than 1\arcmin\ from
-the cluster core.  At a projected separation of $\sim40\arcsec$,
+constraint operates principally at separations more than 1\arcmin\
+from the cluster core.  At a projected separation of $\sim40\arcsec$,
 SN \tomas\ falls in between the strong- and weak-lensing regimes, and
 one would expect that models incorporating both of those constraints
-would be less susceptible to the systematic bias of a sharply
-steepening mass profile.  The lowest magnification estimate in our
-sample (from the Merten model) is among this sub-sample.  However, we
-find that collectively these three strong+weak models (shown as
-diamonds in Figure~\ref{fig:lensingtest}) exhibit the same propensity
-to overestimate the magnification along this line of sight.  Thus, a
-sudden change in the mass profile outside the strong lensing region is
-not a likely explanation for this small systematic bias.
+would be less susceptible to the \changeR{possible} systematic bias of
+a sharply steepening mass profile.  The lowest magnification estimate
+in our sample (from the Merten model) is among this sub-sample.
+However, we find that collectively these three strong+weak models
+(shown as diamonds in Figure~\ref{fig:lensingtest}) exhibit the same
+propensity to overestimate the magnification along this line of sight.
+Thus, a sudden change in the mass profile outside the strong lensing
+region is not a likely explanation for this small systematic bias.
 
@@
 preliminary models that have not been updated to include all of the
-HFF data.  Future revisions of the lens models for Abell 2744 should
-either incorporate the observed magnification of \tomas\ as a new
-model constraint, or can revisit this test to evaluate whether the
-bias persists.
+HFF data.  Future revisions of the lens models for Abell
+2744 \changeR{could} either incorporate the observed magnification
+of \tomas\ as a new model constraint, or can revisit this test to
+evaluate whether the bias persists.
 

### 2015-04-07 snTomasCode/lightcurve_classification_fig.py

@@ -128,18 +128,23 @@ def mk_figure(yunit='flux'):
     ax814.set_xlim(56790,56969)
     ax814.xaxis.set_major_locator( ticker.MultipleLocator(50) )
     ax814.xaxis.set_minor_locator( ticker.MultipleLocator(10) )
+    ax814.axvline(56813.5,ls='-',color='0.5',lw=0.75)
+    ax814.legend(loc='right', frameon=False, labelspacing=0.08,
+                 fontsize=11.5, handletextpad=0.08)
 
     ax105 = axdict['F105W']
     ax105.set_xlim(56790,56969)
     ax105.xaxis.set_major_locator( ticker.MultipleLocator(50) )
     ax105.xaxis.set_minor_locator( ticker.MultipleLocator(10) )
-    ax814.legend(loc='right', frameon=False, labelspacing=0.08,
-                 fontsize=11.5, handletextpad=0.08)
+    ax105.axvline(56813.5,ls='-',color='0.5',lw=0.75)
+    ax105.text(56812,0.2,'spectrum',rotation=90,ha='right',va='bottom',
+               color='0.5', fontsize='small')
 
     ax125 = axdict['F125W']
     ax125.set_xlim(56790,56877)
     ax125.xaxis.set_major_locator( ticker.MultipleLocator(50) )
     ax125.xaxis.set_minor_locator( ticker.MultipleLocator(10) )
+    ax125.axvline(56813.5,ls='-',color='0.5',lw=0.75)
 
     ax140 = axdict['F140W']
     pl.setp(ax140.yaxis.get_ticklabels(), visible=False)
@@ -148,12 +153,14 @@ def mk_figure(yunit='flux'):
     ax140.set_xlim(56883,56969)
     ax140.xaxis.set_major_locator( ticker.MultipleLocator(50) )
     ax140.xaxis.set_minor_locator( ticker.MultipleLocator(10) )
+    ax140.axvline(56813.5,ls='-',color='0.5',lw=0.75)
 
     ax160 = axdict['F160W']
     ax160.set_xlim(56790,56969)
     ax160.xaxis.set_major_locator( ticker.MultipleLocator(50) )
     ax160.xaxis.set_minor_locator( ticker.MultipleLocator(10) )
     ax160.set_xlabel('Observer-frame Days (MJD)')
+    ax160.axvline(56813.5,ls='-',color='0.5',lw=0.75)
 
     for ax in axdict.values():
         ax.yaxis.set_major_locator( ticker.MultipleLocator(1) )

### 2015-04-07 TABLE/magnifications.tex
Incorporated comments from KS, MJ, AZ   * added positions   * added a section on cosmological parameter uncertainty   * subsumed the section 3.3 discussion into the preceding subsection

@@
 \startdata
-Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\
+Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL\tablenotemark{c} parametric, strong-lensing based model\\
 Sharon(v2)   & 2.73     & 2.69  &   2.63$-$2.83 &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\
-CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
-CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
-Jauzac		 & \nodata  & 3.37  &   3.22$-$3.51 &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
-GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
-Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\
+CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2007,Richard:2014} &  CATS\tablenotemark{d} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 &   \citealt{Jullo:2007,Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
+CATS-SL(v2)  & 3.37     & 3.35  &   3.18$-$3.53 &   \citealt{Richard:2014,Jauzac:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
+GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{e} \\
+Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{f} profiles for galaxies and NFW\tablenotemark{g} profiles for dark matter halos.\\
 Zitrin-LTM   & 2.64     & 2.96  &   2.58$-$3.73 &   \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
@@
 Errors from bootstrap resampling only strong-lensing constraints.}\\
-Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.
+Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{h} : Free-form strong-lensing model using a genetic algorithm.
 \\
-Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Diego\tablenotemark{i}        & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}
+Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{i} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{j} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Diego\tablenotemark{k}   & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{j} model, using a different set of strong-lensing constraints and redshifts.
 \enddata
@@
 \tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
-\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
-\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
-\tablenotetext{g}{{\tt GRALE} : GRAvitational LEnsing.}
-\tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
-\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}}
+\tablenotetext{d}{{\tt CATS} : Clusters As TelescopeS lens modeling team.}
+\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{f}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
+\tablenotetext{g}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
+\tablenotetext{h}{{\tt GRALE} : GRAvitational LEnsing.}
+\tablenotetext{i}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
+\tablenotetext{j}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
+\tablenotetext{k}{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}
 \end{deluxetable*}

### 2015-04-07 TABLE/positions.tex
Incorporated comments from KS, MJ, AZ   * added positions   * added a section on cosmological parameter uncertainty   * subsumed the section 3.3 discussion into the preceding subsection

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablecaption{Coordinates\tablenotemark{a} of \tomas, host, and cluster. \label{tab:Positions}}
\tablehead{ 
    \colhead{Object}
  & \colhead{R.A.}
  & \colhead{Decl.}
  & \colhead{R.A.}
  & \colhead{Decl.}\\
    \colhead{}
  & \colhead{(h:m:s)}
  & \colhead{(d:m:s)}
  & \colhead{(deg)}
  & \colhead{(deg)}
}
\startdata
\tomas       &  00:14:17.87 &  -30:23:59.7  &  3.574458 &  -30.399917 \\
Host galaxy  &  00:14:17.88 &  -30:24:00.6  &  3.574483 &  -30.400175 \\
Abell 2744   &  00:14:21.20 &  -30:23:50.1  &  3.588333 &  -30.397250
\enddata
\tablenotetext{a}{Coordinates in Right Ascension and Declination, on the J2000 reference system.}
\end{deluxetable}

### 2015-04-07 snTomas.tex
Incorporated comments from KS, MJ, AZ   * added positions   * added a section on cosmological parameter uncertainty   * subsumed the section 3.3 discussion into the preceding subsection

@@
 faint \citep[e.g.][]{Schenker:2012,Alavi:2014} or extremely
-distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014}.
+distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014b}.
 Background galaxies are also {\it spatially} magnified, allowing for
@@
 is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
-massive galaxy clusters, plus 6 accompanying parallel fields.
-Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
-and 4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
+massive galaxy clusters, plus 6 accompanying parallel fields.  Each
+field is observed in 3 optical bands (ACS F435W, F606W and F814W) and
+4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
 although the optical and IR imaging campaigns are separated by $\sim$6
@@
 May-July.  A composite image of the HFF data showing the SN is
-presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
-made in difference images constructed using template imaging of Abell
-2744 from HST+ACS observations taken in 2009 (PI:Dupke,
-HST-PID:11689).
+presented in Figure~\ref{fig:DiscoveryImage}, \changeR{and the
+locations of the cluster center, the SN, and the presumed host galaxy
+are given in Table~\ref{tab:Positions}.}  The SN detection was made in
+difference images constructed using template imaging of Abell 2744
+from HST+ACS observations taken in 2009 (PI:Dupke, HST-PID:11689).
+
+\input{TABLE/positions}
 
@@
 
-\subsection{Comparison to Model Predictions}
-\label{sec:ComparisonToModelPredictions}
+%\subsection{Comparison to Model Predictions}
+%\label{sec:ComparisonToModelPredictions}
 
@@
 introduce a bias in the magnification.  This bias might be
-particularly acute for models that make a strict ``light traces mass''
-assumption, such as the Sharon, CATS, Jauzac, GLAFIC and Zitrin-LTM
-models.
-
-We tested this hypothesis using the Jauzac model by allowing the mass
+particularly acute for models that \changeR{hew more closely to a
+simple} ``light traces mass'' assumption, such as the Sharon, CATS,
+GLAFIC and Zitrin-LTM models.
+
+We tested this hypothesis using the CATS-SL(v2) model by allowing the mass
 of the nearby cluster member galaxy to vary as a free parameter in the
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/system3.png}
+\caption{ 
+The disputed component of the multiply-imaged galaxy System 3. The
+original position, as given in \citet{Merten:2011} is marked with a
+dashed magenta circle labeled 3.3. The solid magenta circle
+labeled \33p\ shows the revised location as proposed
+in \citet{Jauzac:2014c}.  Both positions are $\sim$10\arcsec\ from the
+SN location.  The inset panel shows the other two components of this
+multiply-imaged system, 3.1 and 3.2 (on the same scale as the main
+panel), which are located north-east of the cluster center, and have a
+secure spectroscopic redshift of $z=3.98\pm0.02$ \citep{Johnson:2014}.
+\label{fig:system3} }
+\end{center}
+\end{figure}
+
 At the outset of the HFF survey, only 33 multiply-imaged galaxies
@@
 than the observed value.  Again the CATS model family provides a
-useful case study.  The Jauzac model shares the same lens modeling
-software (LensTool), and the same primary methodology as the earlier
-CATS models.  A key difference is that the Jauzac model incorporates
-many new multiply imaged galaxies and corrects a mis-identified
-multiply-imaged system near the SN \tomas\ position.  These
-improvements should in principle make the Jauzac model magnification
-estimates more accurate, though we in fact see the opposite result:
-the Jauzac model predicts a $\mu$ that is higher than the measured
-value by \changeG{$4.3\sigma$.}
-
-This shift to higher magnifications is not, however, unique to the
+useful case study.  The CATS-SL(v2) model \citep[from][]{Jauzac:2014c}
+shares the same lens modeling software (LensTool), and the same
+primary methodology as the earlier CATS models, \changeR{though with
+two key differences:  (1) the CATS-SL(v2) model changes the location of a
+multiply-imaged system near the SN \tomas\ position; and (2) the model
+incorporates 33 new multiply imaged galaxies.}  These improvements
+should in principle make the CATS-SL(v2) model magnification estimates
+more accurate, though we in fact see the opposite result: the
+CATS-SL(v2) model predicts a $\mu$ that is higher than the measured
+value by \changeR{$4.1\sigma$, and higher than either of the previous
+two versions of the CATS models.}
+
+\changeR{
+The change in location proposed by \citet{Jauzac:2014c} is for image
+3.3, the third component of a triply-imaged
+galaxy \citep{Merten:2011}, shown in Figure~\ref{fig:system3}.  Images
+3.1 and 3.2 of this system have a secure spectroscopic redshift of
+$z=3.98\pm0.02$ \citep{Johnson:2014}. \citet{Jauzac:2014c} found that
+reassigning this multiple image to a source roughly 8\arcsec\ to the
+south results in a tighter model reconstruction for the locations of
+other multiply-imaged systems in the vicinity \citep[though][argue
+against the reassignment based on the colors of the two sources in
+question]{Lam:2014}.  Given the large discrepancy between the
+CATS-SL(v2) model and the SN measurement, one might question whether
+this change in the position of image 3.3 is driving the increase in
+the predicted $\mu$ for SN \tomas. However, \citet{Jauzac:2014c} also
+examined a version of the CATS-SL(v2) model where this single source
+is left in the original position, and find that it does not
+significantly affect the predicted magnification.}
+
+\changeR{Furthermore,} the shift to higher magnifications is not unique to the
 SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
@@
 magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
-models.  Although this single sight-line can only provide a very
-limited test of the model, the \changeG{$4.3\sigma$} discrepancy is at
-least a strong suggestion that \changeR{even with a large number of
-high-quality} strong-lensing constraints \changeR{it is still possible
-to generate} magnification maps that are susceptible to systematic
-biases.
-
-\change{
-\subsection{Misidentification of System 3}
-\label{sec:MisidentificationOfSystem3}
-}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{FIG/system3.png}
-\caption{ 
-The disputed component of the multiply-imaged galaxy System 3. The
-original position, as given in \citet{Merten:2011} is marked with a
-dashed magenta circle labeled 3.3. The solid magenta circle shows the
-revised location as proposed in \citet{Jauzac:2014c}.  Both positions
-are $\sim$10\arcsec\ from the SN location.  The inset panel shows the
-other two components of this multiply-imaged system, 3.1 and 3.2 (on
-the same scale as the main panel), which are located north-east of the
-cluster center.
-\label{fig:system3} }
-\end{center}
-\end{figure}
-
-\change{
-It is important to note that in regards to the impact on this
-particular sight-line, not all strong-lensing constraints are equal.
-An error in the association of multiple images or in the redshift of a
-multiply-imaged galaxy would have a more significant impact if that
-system has a projected position close to our SN
-sight-line \changeG{\citep[see][for a quantitative assessment of this
-effect]{Johnson:2014}.}  It happens that there is one such system, for
-which the position of a multiple image near SN \tomas\ is presently
-disputed.  }
-
-\change{
-This multiply-imaged galaxy was originally labeled as {\it System 3}
-in \citet{Merten:2011}.  As shown in Figure~\ref{fig:system3}, it is
-stretched into two adjacent arcs northeast of the cluster core (images
-3.1 and 3.2), with a third image on the western edge of the
-strong-lensing region (image 3.3 at 00:14:18.595,
--30:23:58.42).  \citet{Richard:2014} echoed this initial
-identification in producing the {\tt CATS} models, which we cite in
-Table~\ref{tab:PredictedMagnifications} and
-Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
-models, \citet{Johnson:2014} provided a secure spectroscopic
-constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
-the combined 3.1+3.2 source. The identification of the original image
-3.3 has been called into question by two independent analyses.  Using
-HFF imaging data, \citet{Lam:2014} suggested an alternative third
-image for this system roughly 8\arcsec\ to the south, which we will
-call \33p\ (00:14:18.39, -30:24:06.53).
-However, \citeauthor{Lam:2014} rejected this possibility based on a
-difference in colors between \33p\ and images 3.1 and 3.2.  In
-contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
-is correct, and find that reassigning this multiple image results in a
-tighter model reconstruction for the locations of other
-multiply-imaged systems in the vicinity.
-}
-
-\change{
-Resolving the identification of this single multiply-imaged galaxy
-could be a component in resolving the magnification
-discrepancy, though it is unlikely to completely remove the tension.
-It is true that the model that reassigns the position to \33p\
-({\tt Jauzac}) is also the one with the largest deviation from our
-observed $\mu$ value.  However, \citet{Jauzac:2014c} have already
-evaluated the impact of relocating this single source, and
-they find that it is not responsible for the observed increase in
-magnifications across the field. Rather, the 
-primary cause for the general magnification increase is the addition
-of new multiple images in the Northern region, detected using the new
-HFF data. }
+models.  Although \changeR{the single sight-line to SN \tomas\ } can
+only provide a very limited test of the model,
+the \changeR{$4.1\sigma$} discrepancy is at least a strong suggestion
+that \changeR{even with a large number of high-quality} strong-lensing
+constraints \changeR{it is still possible to generate} magnification
+maps that are susceptible to systematic biases.
 
@@
 weak lensing constraints cannot, by itself, resolve this bias.
+
+\subsection{Cosmological Uncertainty}
+
+\changeR{
+All of the models presented here use a fixed assumption for the
+parameters of a standard \LCDM\ cosmology (typically: \Om=0.3,\OL=0.7,\Ho=70 km
+s$^{-1}$ Mpc$^{-1}$).  The parameter values selected for this fiducial
+cosmology do have an impact on the inferred magnifications, and
+variation of these parameters must be accounted for when using cluster
+mass models for cosmological tests \citep{Zitrin:2014b}. 
+\citep{Bayliss:2015} demonstrated that
+changing the cosmological parameter within the range of current
+acceptable cosmologies \citep[e.g.][]{Hinshaw:2013,Planck:2015},
+introduces a magnification uncertainty that is comparable in magnitude
+to that of the statistical uncertainties.  This leads to the
+conclusion that the lens modeling uncertainties presented here are
+underestimated, and should be significantly increased. 
+}
+
+\changeR{
+As a quantitative example, we have modified the Sharon(v2) model to
+include this cosmological parameter uncertainty,
+following \citep{Bayliss:2015}. At the position of SN \tomas, the
+68\%\ confidence range for the magnification at $z=1.31$ increases
+from [2.63,2.83] to [2.42,2.85], and the best-fit magnification value
+of $mu=2.73$ remains the same.  This moves the Sharon(v2) model from
+being discrepant at the $2.5\sigma$ level to a $1.75\sigma$ tension.
+Incorporating this cosmological parameter uncertainty in the other
+models would similarly reduce the tension between models and
+observation, but would not resolve the overall systematic shift.  Even
+a factor of 2.5 increase in the uncertainties (the most drastic change
+seen in the analysis of \citep{Bayliss:2015}) would still leave the
+most extreme outlier (CATS-SL(v2)) discrepant by $2.6\sigma$.
+}
 
@@
 
-Taking advantage of the availability of eleven well-constrained lens
+Taking advantage of the availability of \changeR{14} well-constrained lens
 models for the Abell 2744 cluster, we have used SN \tomas\ to ask
@@
 We have speculated on the origin of this systematic bias,
-evaluating six possible causes:
+evaluating \changeR{seven} possible causes:
 
@@
 \item The models are limited by a scarcity of strong lensing constraints
+\item Model uncertainties are underestimated, by not accounting for 
+       uncertainties in cosmological parameters.
 \item The cluster mass profile exhibits a sudden change outside of the core
@@
 
-\noindent The first three of these take on the discrepancy from 
+\noindent The first \changeR{four} of these take on the discrepancy from 
 the lens modeling side, but none are completely satisfactory. For each

### 2015-04-13 snTomasCode/hubble_fig.py
cleaned up author ref macros and preamble, updated code   * adjusting figures to reflect the new redshift from the host galaxy

@@ -11,11 +11,11 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
     dmint_mlcs=0.08 # intrinsic scatter in SNIa luminosities for MLCS2k2 (Jha:2007)
     dmint_salt=0.08 # intrinsic scatter in SNIa luminosities for SALT2 (Conley:2011)
 
-    zTomas = 1.31#,1.35]
-    zerrTomas = 0.01#,0.02]
-    dmTomas_mlcs = 44.06#,44.22]
+    zTomas = 1.3457#1.31#,
+    zerrTomas = 0.001#,0.01]
+    dmTomas_mlcs = 44.22#,44.06#,
     dmerrTomas_mlcs = np.sqrt(0.09**2 + dmint_mlcs**2)
-    dmTomas_salt = 44.09#,44.19]
+    dmTomas_salt = 44.19#44.09
     dmerrTomas_salt = np.sqrt(0.16**2 + dmint_salt**2)
 
     thisfile = sys.argv[0]
@@ -66,7 +66,7 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
 
     # dm_mlcs = slope * z - intercept
     def line( x, slope, intercept ):
-        return slope*(x-1.31) + intercept
+        return slope*(x-1.3457) + intercept
 
     lineparam0 = np.array([1,45])
     fit_mlcs, cov_mlcs = scopt.curve_fit( line, z, dm_mlcs, lineparam0, dm_mlcs_err)
@@ -83,16 +83,16 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
         if fitter.lower().startswith('salt') and fittername!='SALT2' : continue
         slope, intercept  = fit
         slope_err, intercept_err = np.sqrt( np.diagonal(cov) )
-        fit_string = r'dm$_{\rm %s} = (%.2f\pm%.2f)(z-1.31)+(%.2f\pm%.2f)$'%(
+        fit_string = r'dm$_{\rm %s} = (%.2f\pm%.2f)(z-1.3457)+(%.2f\pm%.2f)$'%(
             fittername, round(slope,2),round(slope_err,2),
             round(intercept,2),round(intercept_err,2) )
 
         zfit = np.arange(0.9,1.8,0.01)
-        dmfit =  slope*(zfit-1.31) + intercept
-        a =  (slope+slope_err)*(zfit-1.31) + intercept+intercept_err
[…]

### 2015-04-13 snTomasCode/lensing_test_fig.py

@@ -3,7 +3,7 @@
 # The lensing comparison figure
 import numpy as np
 
-def mkLensingTestFig( presfig=False ):
+def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
     from matplotlib import pyplot as pl
     from matplotlib.patches import FancyArrowPatch
     from pytools import plotsetup, colorpalette as cp
@@ -22,7 +22,11 @@ def mkLensingTestFig( presfig=False ):
         fig = plotsetup.fullpaperfig( figsize=[4,5])
         ms=8
         pl.clf()
-        ax1 = pl.axes( [0.01,0.08,0.7,0.86] )
+        if showlegend:
+            ax1 = pl.axes( [0.01,0.14,0.7,0.84] )
+        else:
+            ax1 = pl.axes( [0.01,0.14,0.7,0.84] )
+
 
     thisfile = sys.argv[0]
     if 'ipython' in thisfile :
@@ -33,8 +37,8 @@ def mkLensingTestFig( presfig=False ):
     lensingdat = ascii.read( lensdatfile, format='commented_header',
                              header_start=-1, data_start=0 )
 
-    ytop=15.2
-    y = ytop-0.7
+    ytop=len(lensingdat['med'])+1
+    y = ytop
     for row in lensingdat:
         y-=1
         color = row['parametric'] and 'k' or 'g'
@@ -51,12 +55,12 @@ def mkLensingTestFig( presfig=False ):
 
         #ax1.plot( best, y, marker='x', ms=ms, color=color,
         #          zorder=100, label='_nolegend_' )
-        if med+errplus>3.6 :
+        if med+errplus>3.65 :
             # make an arrow for the really long williams error
-            errplus = 3.5-med
+            errplus = 3.6-med
             ax1.errorbar( med, y, yerr=None, xerr=[[0],[errplus]],
                           marker=None, capsize=0.6*ms, color=color,
-                          xuplims=[True], zorder=10, label='_nolegend_' )
+                          xlolims=[True], zorder=10, label='_nolegend_' )
         ax1.errorbar( med, y, yerr=None,
[…]

### 2015-04-13 snTomasCode/lightcurve_fitting_fig.py

@@ -3,7 +3,7 @@
 
 
 def plot_light_curve_fit( fitter='mlcs2k2', plotmags=True,
-                          compare=False ) :
+                          showblue=False, compare=False ) :
     """ make the SN Tomas light curve fit figure"""
     from pytools import plotsetup, colorpalette as cp
     from astropy.io import ascii
@@ -43,6 +43,10 @@ def plot_light_curve_fit( fitter='mlcs2k2', plotmags=True,
     fig = pl.gcf()
     pl.clf()
 
+    if showblue:
+        bandlist = ['B','V','I','Y','J','N','H']
+    else:
+        bandlist = ['I','Y','J','N','H']
     for fitter in fitterlist :
         axdict = {
             'B':fig.add_subplot(gs[rowdict[fitter],0]),
@@ -54,7 +58,7 @@ def plot_light_curve_fit( fitter='mlcs2k2', plotmags=True,
         axdict['V'] = axdict['B']
         axdict['I'] = axdict['B']
 
-        for band in ['V','I','Y','J','N','H'] :
+        for band in bandlist:
             ax = axdict[band.upper()]
             filtname = alpha2filter[band]
             color = colordict[band]

### 2015-04-15 TABLE/magnifications.tex
updated some figures, reset the changetext coloring, updated the spectroscopy a bit

@@
 Errors from bootstrap resampling only weak-lensing constraints.\\
-Bradac(v2)   & 2.21     & 2.23  &   2.20$-$2.28 &   \citealt{Wang:2015} & \change{Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
-Errors from bootstrap resampling only strong-lensing constraints.}\\
+Bradac(v2)   & 2.21     & 2.23  &   2.20$-$2.28 &   \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Errors from bootstrap resampling only strong-lensing constraints.\\
 Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{h} : Free-form strong-lensing model using a genetic algorithm.
@@
 \tablenotetext{i}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{j}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
+\tablenotetext{j}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
 \tablenotetext{k}{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}

### 2015-04-15 snTomas.tex
cleaned up author ref macros and preamble, updated code   * adjusting figures to reflect the new redshift from the host galaxy
updated some figures, reset the changetext coloring, updated the spectroscopy a bit

@@
 SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
-$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
+\change{$z=1.3457\pm0.0001$} behind the galaxy cluster Abell 2744 ($z=0.308$). This
 SN has a projected separation from the cluster core of
 $\sim$40\arcsec, closer to the critical lensing line than any previous
-cluster-lensed \SNIa.  As such, it provides a valuable opportunity to
-confront gravitational lens models of galaxy clusters with the direct
-measurement of an absolute magnification at the edge of the
-strong-lensing region.  We derive a tightly constrained measure of the
-peak apparent magnitude, corrected for light curve shape and
+cluster-lensed Type Ia SN.  As such, it provides a valuable
+opportunity to confront gravitational lens models of galaxy clusters
+with the direct measurement of an absolute magnification at the edge
+of the strong-lensing region.  We derive a tightly constrained measure
+of the peak apparent magnitude, corrected for light curve shape and
 exinction.  In a cosmology-independent analysis, we find that \tomas\
-is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
-similar redshift, implying a lensing magnification
-of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
+is \change{$0.77\pm0.15$} magnitudes brighter than unlensed Type Ia
+SNe at similar redshift, implying a lensing magnification
+of \change{$\mu_{\rm obs}=2.03\pm0.29$}.  We compare this direct
 measurement of the magnification against predicted magnifications
-from \change{14 lens models,} representing a broad range of
+from 14 lens models, representing a broad range of
 methodologies and incorporating a variety of strong- and weak-lensing
-constraints.  The models are collectively fairly accurate: \change{
-half of the models deliver median magnifications that are consistent
-with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
-However, the models are systematically biased to higher values: none
-of the tested models predict a magnification equal to or lower than
-the observed $\mu$, and three models are $2-4\sigma$ above the
-measured magnification.  We evaluate possible causes for this bias,
-\changeG{considering both modeling errors and misinterpretation of the SN
-data. Although we find no single explanation that accounts for the
-entire discrepancy, we do find that the subset of ``free-form'' lens
-models are more accurate and provide more realistic uncertainties than
-``parametric models'' for this sight-line.} A larger sample of 10-100
-lensed \SNeIa\ could provide a robust evaluation of systematic biases
-in lens models.  Until such a sample exists, it is advisable
-to \change{increase the estimated uncertainty of predicted
-magnifications to match the dispersion observed across multiple lens
-models.}
+constraints.  The models are collectively fairly accurate: 6 of the
+models deliver median magnifications that are consistent with the
+measured $\mu$ to within the 1$\sigma$ uncertainties.  However, the
+models are systematically biased to higher values: \change{all but
+one} of the tested models yield a median magnification higher than the
+observed $\mu$, and \change{6 of the models are $\geq1.5\sigma$}
+above the measured magnification.  We evaluate possible causes for
+this mild bias, considering both modeling errors and
+misinterpretation of the SN data. Although we find no single
+explanation that can resolve this, we \change{ highlight several ways
+that lens models can deliver more realistic uncertainties, such as
+incorporating errors from assumed cosmological parameters and allowing
+greater flexibility in the form of the cluster mass distribution.  A
+more robust evaluation of systematic biases could be achieved with
+further cooperative lens model comparisons using a larger sample of
+lensed Type Ia SNe and cluster lensing simulations.}
 \end{abstract}
 
-\keywords{ supernovae: general }
+\keywords{ supernovae: general, supernovae: individual: HFF14Tom, galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, gravitational lensing: strong, gravitational lensing: weak  }
 
@@
 
-\changeG{
 Galaxy clusters can be used as cosmic telescopes to magnify distant
@@
 pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
-}
-
-\changeG{
+
 Gravitational lensing can also provide a powerful window onto the {\it
@@
 fields \citep[e.g.]{Riess:2001,Riess:2007,Suzuki:2012,Rodney:2012,Rubin:2013,Jones:2013}.
-}
-
-\changeG{
+
 In the case of lensed SNe, we can also reverse the experimental setup:
@@
 important new cosmological tool.
-}
-
-\changeG{
+
 In addition to time delays from multiply-imaged SNe, we can also
@@
 weak-lensing constraints are unavailable.
-}
-
-\change{
+
 One of the key values in observing standard candles behind
-gravitational lenses is \changeG{in addressing the problem of the
-mass-sheet degeneracy} \citep{Falco:1985,Bradac:2004}.  This
+gravitational lenses is in addressing the problem of the
+mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
 degeneracy arises because one can introduce into a lens model an
@@
 \citep{Holz:2001}.
-}
 
 In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
-follow-up observations of SN \tomas\ at $z=1.31$, discovered behind the
+follow-up observations of SN \tomas\ at $z=1.3457$, discovered behind the
 galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
@@
 May-July.  A composite image of the HFF data showing the SN is
-presented in Figure~\ref{fig:DiscoveryImage}, \changeR{and the
+presented in Figure~\ref{fig:DiscoveryImage}, and the
 locations of the cluster center, the SN, and the presumed host galaxy
-are given in Table~\ref{tab:Positions}.}  The SN detection was made in
+are given in Table~\ref{tab:Positions}.  The SN detection was made in
 difference images constructed using template imaging of Abell 2744
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{FIG/host_sed_fit}
-\caption{  \label{fig:HostSED}
-Best-fit SED template match for the most probable \tomas\ host
-galaxy. Using the {\it BPZ} code to match the observed SED, we find
-the nearest galaxy to the SN position is a late type galaxy with a
-photometric redshift of $z=1.5\pm0.2$.}
-\end{center}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=\columnwidth]{FIG/host_sed_fit}
+%\caption{  \label{fig:HostSED}
+%Best-fit SED template match for the most probable \tomas\ host
+%galaxy. Using the {\it BPZ} code to match the observed SED, we find
+%the nearest galaxy to the SN position is a late type galaxy with a
+%photometric redshift of $z=1.5\pm0.2$.}
+%\end{center}
+%\end{figure}
 
@@
 fit the spectral energy distribution (SED) using the {\it BPZ} code --
-a Bayesian photometric redshift estimator \citep{Benitez:2000}. The
-best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
+a Bayesian photometric redshift estimator \citep{Benitez:2000}. 
+%The best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
 From the {\it BPZ} analysis, we found the host to be most likely an
-actively star-forming galaxy at a redshift of $z=1.5\pm0.2$.
-
-Another nearby bright galaxy to the East of the SN has a spectroscopic
-redshift of $z=1.742$.  This redshift was determined from a spectrum
-taken with the G141 grism of the HST WFC3-IR camera, collected as part
-of the Grism Lens Amplified Survey from Space (GLASS, PI:Treu,
-PID:13459, \citealt{Treu:2015}). \change{As we will see in Sections~\ref{sec:Spectroscopy}
-and \ref{sec:PhotometricClassification}, the SN data are inconsistent
-with that redshift, meaning that this is a background
-object and therefore has no impact on the SN magnification.}
+actively star-forming galaxy at a redshift of
+$z=1.5\pm0.2$.  \change{This photo-z was subsequently supported by a
+spectroscopic redshift of $z=1.3457\pm0.0001$, based on emission lines
+consistent with \textcolor{red}{??? the [OII] $\lambda\lambda$ 3726-3729 \AA\ doublet.
+???}}  Another nearby bright galaxy to the East of the SN has a
+spectroscopic redshift of $z=1.742$.  This redshift was determined
+from a spectrum taken with the G141 grism of the HST WFC3-IR camera,
+collected as part of the Grism Lens Amplified Survey from Space
+(GLASS, PI:Treu, PID:13459, \citealt{Treu:2015}). As we will see in
+Sections~\ref{sec:Spectroscopy}
+and \ref{sec:PhotometricClassification}, the SN data are \change{consistent
+with $z=1.3457$,} meaning that the latter galaxy is a background object and
+therefore has no impact on the SN magnification.
 
@@
 fields. The FrontierSN observations provided WFC3-IR imaging as well
-as spectroscopy using the ACS G800L grism, supplementing the
-rapid-cadence optical imaging from HST+ACS already being provided by
-the HFF program. \change{The last detections in the IR F105W and F140W
-bands came from the direct-imaging component of the GLASS program}.
-Difference images for the IR follow-up data were generated using
-templates constructed from the HFF WFC3-IR imaging campaign, which
-concluded in November, 2013.
+as spectroscopy of the SN itself using the ACS G800L grism,
+supplementing the rapid-cadence optical imaging from HST+ACS already
+being provided by the HFF program. The last detections in the IR F105W
+and F140W bands came from the direct-imaging component of the GLASS
+program.  Difference images for the IR follow-up data were generated
+using templates constructed from the HFF WFC3-IR imaging campaign,
+which concluded in November, 2013.
 
@@
 notably the red slope of the continuum and a prominent absorption
-feature at $\sim$8700\AA.  However, the signal to noise ratio (S/N)
-for the host galaxy spectrum was too weak to yield any additional
-constraints on the host type or redshift.
-
-\changeG{
+feature at $\sim$8700\AA.  
+%However, the signal to noise ratio (S/N)
+%for the host galaxy spectrum was too weak to yield any additional
+%constraints on the host type or redshift.
+
 Spectra of Type I SNe (including all sub-classes Ia, Ib and Ic) are
@@
 e.g.][]{Filippenko:1997}.  As described below, we fit template spectra
-to the SN \tomas\ data in two steps.}  First we determine a spectral
+to the SN \tomas\ data in two steps.  First we determine a spectral
 classification -- and get a preliminary estimate of the redshift and
@@
 of a SN spectrum through cross-correlation matching with a library of
-template spectra, \change{using the algorithm of \citet{Tonry:1979}.}
+template spectra, using the algorithm of \citet{Tonry:1979}.
 To account for possible distortions in the broad shape of the SN
@@
 To match the SN \tomas\ spectrum we use conservative constraints on
-age and redshift: limiting the age to $\pm$5 rest-frame days of peak
+age and redshift: limiting the age to $\pm$5 rest-frame days from peak
 brightness and $0.8<z<1.8$, consistent with the SN light curve and
-host galaxy photo-$z$.  With these constraints we find that the only
+the two plausible host galaxies.  With these constraints we find that the only
 acceptable match is a normal Type Ia SN near $z=1.3$. The best match
 has {\it rlap}$=8.7$, using the normal Type Ia SN 2005cf at $z=1.35$
-and age=-2.2 rest-frame days before peak.  Within these constraints,
+and age=-2.2 rest-frame days before peak.  In contrast, 
 the best non-Ia matches all have {\it rlap}$<2.5$.
@@
 
-\subsection{Spectroscopic Redshift}
+\subsection{Spectral Fitting with UV Type Ia Templates}
 \label{sec:SpecRedshift}
@@
 match the observed SED of SN \tomas.  From this analysis we find
-results that are consistent with the SNID fits: a redshift of
-$z=1.31\pm0.01$ and a phase of $0\pm3$ rest-frame days. The
-best-fitting spectral template is the normal Type Ia SN 2012cg, shown
-in the top panel of Figure~\ref{fig:SpecFit}, which has $\chi^2$
-per degree of freedom $\nu$ equal to 42.1/87.
-
-Finally, we repeat the fitting, but without any warping of the
-templates to account for differences in the continuum shape.  In this
-iteration we only allow each template SED to be scaled in flux
-coherently at all wavelengths.  As shown in Figure~\ref{fig:SpecFit},
-we again find that the \tomas\ SED can be matched by a normal Type Ia
-SN (SN 2011fe) at redshift $z=1.31\pm0.01$.  Without the continuum
-warping, an alternative fit also arises: the \change{fast-declining
-(91bg-like)} Type Ia SN 2011iv
-at $z=0.98\pm0.01$. Formally, this match provides a slightly better
-fit to the unwarped \tomas\ spectrum, although the fit is notably poor
-at $\sim8700$\AA\ where the most significant absorption feature is
+results that are consistent with the SNID fits \change{and the host
+galaxy redshift}: $z=1.31\pm0.03$ and a phase of $0\pm3$ rest-frame
+days. The best-fitting spectral template is the normal Type Ia SN
+2012cg, shown in the top panel of Figure~\ref{fig:SpecFit}, which has
+$\chi^2$ per degree of freedom $\nu$ equal to 42.1/87.  \change{If we
+fix the redshift at $z=1.3457$ then we find the best fit is from the
+normal Type Ia SN 2014J, with $\chi^2/\nu=51.8/87$.}
+
+Next, we repeat the fitting, but without any warping of the templates
+to account for differences in the continuum shape.  In this iteration
+we only allow each template SED to be scaled in flux coherently at all
+wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that
+the \tomas\ SED can be matched by a normal Type Ia SN (SN 2011fe) at
+redshift $z=1.31\pm0.02$.  \change{Fixing the redshift at the host redshift of
+$z=1.3457$, we also find the best match is from SN 2011fe, with
+$\chi^2/\nu=133.7/91$. }
+
+Without the continuum warping, an alternative
+fit also arises: the fast-declining (91bg-like) Type Ia SN 2011iv at
+$z=0.98\pm0.01$. Formally, this match provides a slightly better fit
+to the unwarped \tomas\ spectrum, although the fit is notably poor at
+$\sim8700$\AA\ where the most significant absorption feature is
 found. Furthermore, a redshift $z\sim1$ is at odds with the host
@@
 from all \CCSN\ sub-classes totaling less than
-$10^{-32}$.  \change{Although this Bayesian classification utilizes
+$10^{-32}$.  Although this Bayesian classification utilizes
 the full posterior probability distribution, for illustration we
 highlight in Figure~\ref{fig:photoclass} a single best-fit model for
-each sub-class.} This demonstrates how the \CCSN\ models fail to
+each sub-class. This demonstrates how the \CCSN\ models fail to
 adequately match the observed photometry. In particular, only the Type
@@
 distance modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$
-is the luminosity distance in Mpc.} \changeG{while ignoring the
+is the luminosity distance in Mpc.} while ignoring the
 effects of gravitational lensing, so that we can later use it to
-derive a direct measurment of the magnification.}  From the SALT2 fit
+derive a direct measurment of the magnification.  From the SALT2 fit
 we get
@@
 
-\change{
 The total uncertainty in the distance modulus is
-}
 
@@
 
-\change{
 \noindent
@@
 redshift and also from survey to survey.
-}
-
-\change{
+
 Recent work has highlighted the inadequacy of this simplistic approach
@@
 associated with SN samples at significantly lower redshifts that have
-less homogeneous data collection and analysis. }
-
-\change{
+less homogeneous data collection and analysis.
+
 Final values for the SN distance modulus are shown in
@@
 MLCS2k2 light curve fitters are fully consistent within the
-uncertainties.  }
+uncertainties.
 
@@
 
-\change{
 It is now an accepted practice in cosmological analyses using Type Ia
@@
 {\it BPZ} SED fit to define rest-frame optical magnitudes.
-}
-
-\change{
+
 The physical mechanism that drives the mass step is not yet
@@
 for a high-$z$ mass step, we do not apply any correction to SN \tomas\ 
-or the control sample.  }
+or the control sample.
 
@@
 time.  In response to this opportunity, five teams generated eight
-models for Abell 2744.  \change{These models necessarily relied on
+models for Abell 2744.  These models necessarily relied on
 pre-HFF data, and were required to be complete before the HFF program
 began, in order to enable the estimation of magnifications for any new
-lensed background sources revealed by the HFF imaging.} An interactive
+lensed background sources revealed by the HFF imaging. An interactive
 web tool was created by D. Coe and hosted at STScI, to extract
@@
 
-Table~\ref{tab:PredictedMagnifications} lists the \change{14} models,
+Table~\ref{tab:PredictedMagnifications} lists the \change{11} models,
 giving for each one the predicted magnification and uncertainty for a
-source at $z=1.31\pm0.01$ and at the position of \tomas.  These models
+source at \change{$z=1.3457$} and at the position of \tomas.  These models
 represent a broad sampling of the techniques and assumptions that can
@@
 The models shown in Figure~\ref{fig:lensingtest} are separated along
-the $y$ direction into two broad classes, with
-eight \change{so-called} {\it parametric}\footnote{\change{Although
-this nomenclature is becoming standard in the literature, it is
-somewhat misleading, as the pixels or grid cells in free-form models
-are effectively parameters as well. Perhaps ``simply-parameterized''
-would be more accurate, though we adopt the more common usage here.}}
-models on top and six {\it free-form} models on the bottom.  Broadly
-speaking, the parametric models use parameterized density
-distributions to describe the arrangement of mass within the cluster,
-typically associating massive dark matter halos with the positions of
-bright cluster member galaxies. Therefore, parametric models rely (to
-varying degrees) on the assumption that the 
-\changeR{cluster's dark matter can be described
-by analytic forms such as NFW halos \citep{Navarro:1997}, or pseudo isothermal elliptical mass distributions \citep{Kassiola:1993}.}
-Free-form models divide the cluster into a grid, generally using a
-\change{multi-scale grid} to get better sampling in denser regions. Each grid cell
+the $y$ direction into two broad classes, with eight so-called {\it
+parametric}\footnote{Although this nomenclature is becoming standard
+in the literature, it is somewhat misleading, as the pixels or grid
+cells in free-form models are effectively parameters as well. Perhaps
+``simply-parameterized'' would be more accurate, though we adopt the
+more common usage here.}  models on top and six {\it free-form} models
+on the bottom.  Broadly speaking, the parametric models use
+parameterized density distributions to describe the arrangement of
+mass within the cluster, typically associating massive dark matter
+halos with the positions of bright cluster member galaxies. Therefore,
+parametric models rely (to varying degrees) on the assumption that the
+cluster's dark matter can be described by analytic forms such as NFW
+halos \citep{Navarro:1997}, or pseudo isothermal elliptical mass
+distributions \citep{Kassiola:1993}.  Free-form models divide the
+cluster into a grid, generally using a
+multi-scale grid to get better sampling in denser regions. Each grid cell
 is assigned a mass or a potential, and then the mass values are
 iteratively refined to match the observed lensing
-constraints. \change{In some cases an adaptive grid is used so
+constraints. In some cases an adaptive grid is used so
 that the grid spacing itself can also be modified as the model is
-iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.}
-
-\change{
+iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.
+
 In general, free-form methods tend to explore the model parameter
@@
 also accounted for in this model through the use of basis
-functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} }
+functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
 
@@
 lens models overall are delivering consistent and fairly accurate
-estimates of the magnification.  \change{Six of the tested models
+estimates of the magnification.  Six of the tested models
 (CATS, GLAFIC, Zitrin-NFW, Bradac(v2), Merten, Diego) report a median
@@
 Diego) report uncertainties that overlap the central $\mu$ as measured
-from both of the SN light curve fitters.}  Furthermore, the scatter
+from both of the SN light curve fitters.  Furthermore, the scatter
 amongst models provides a reasonable estimate of the magnification
@@
 However, beyond this first-order agreement, there is a systematic bias
-apparent. All of the lens models \change{return median magnifications
-that are} {\it higher} than the observed value, and \change{half of
-the models are discrepant by more than $1\sigma$.}  It is important to
+apparent. All of the lens models return median magnifications
+that are {\it higher} than the observed value, and half of
+the models are discrepant by more than $1\sigma$.  It is important to
 emphasize that SN \tomas\ only samples a single sight-line through the
@@
 models.  In the following subsections we examine possible explanations
-for this \change{small but} apparently universal bias.
+for this small but apparently universal bias.
 
@@
 introduce a bias in the magnification.  This bias might be
-particularly acute for models that \changeR{hew more closely to a
-simple} ``light traces mass'' assumption, such as the Sharon, CATS,
+particularly acute for models that hew more closely to a
+simple ``light traces mass'' assumption, such as the Sharon, CATS,
 GLAFIC and Zitrin-LTM models.
@@
 constraints and reduce the tension between the predicted and observed
-magnification.  However, for \changeG{two} of the most recent
+magnification.  However, for two of the most recent
 models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
@@
 shares the same lens modeling software (LensTool), and the same
-primary methodology as the earlier CATS models, \changeR{though with
+primary methodology as the earlier CATS models, though with
 two key differences:  (1) the CATS-SL(v2) model changes the location of a
 multiply-imaged system near the SN \tomas\ position; and (2) the model
-incorporates 33 new multiply imaged galaxies.}  These improvements
+incorporates 33 new multiply imaged galaxies.  These improvements
 should in principle make the CATS-SL(v2) model magnification estimates
@@
 CATS-SL(v2) model predicts a $\mu$ that is higher than the measured
-value by \changeR{$4.1\sigma$, and higher than either of the previous
-two versions of the CATS models.}
-
-\changeR{
+value by $4.1\sigma$, and higher than either of the previous
+two versions of the CATS models.
+
 The change in location proposed by \citet{Jauzac:2014c} is for image
@@
 is left in the original position, and find that it does not
-significantly affect the predicted magnification.}
-
-\changeR{Furthermore,} the shift to higher magnifications is not unique to the
+significantly affect the predicted magnification.
+
+Furthermore, the shift to higher magnifications is not unique to the
 SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
@@
 magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
-models.  Although \changeR{the single sight-line to SN \tomas\ } can
+models.  Although the single sight-line to SN \tomas\ can
 only provide a very limited test of the model,
-the \changeR{$4.1\sigma$} discrepancy is at least a strong suggestion
-that \changeR{even with a large number of high-quality} strong-lensing
-constraints \changeR{it is still possible to generate} magnification
+the $4.1\sigma$ discrepancy is at least a strong suggestion
+that even with a large number of high-quality strong-lensing
+constraints it is still possible to generate magnification
 maps that are susceptible to systematic biases.
@@
 one would expect that models incorporating both of those constraints
-would be less susceptible to the \changeR{possible} systematic bias of
+would be less susceptible to the possible systematic bias of
 a sharply steepening mass profile.  The lowest magnification estimate
@@
 
-\changeR{
 All of the models presented here use a fixed assumption for the
@@
 underestimated, and should be significantly increased.
-}
-
-\changeR{
+
 As a quantitative example, we have modified the Sharon(v2) model to
@@
 most extreme outlier (CATS-SL(v2)) discrepant by $2.6\sigma$.
-}
 
@@
 
-\change{
 If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
@@
 significantly different from $z=1.3$.
-}
-
-\change{
+
 We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
@@
 $z=1.35$ only serves to (slightly) exacerbate the tension between the
-observations and models.  }
+observations and models.
 
@@
 
-\change{
 All SN sight-lines must intersect some amount of foreground dust from
@@
 discrepancy we observe.
-}
-
-\change{
+
 In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
@@
 necessarily be accompanied by some degree of reddening.
-}
-
-\change{
+
 Nevertheless, one might suppose that a bias could be introduced if we
@@
 similar redshift that make up our comparison sample, largely negating
-the effect on the inferred magnification.  }
-
-\change{
+the effect on the inferred magnification.
+
 The traditional color corrections as formalized in SN light curve
@@
 magnification of \tomas\ and the mean of the model predictions.
-}
 
@@
 
-\change{
 Is it possible that \tomas\ is an example of a peculiar stellar
@@
 that \tomas\ is one of the sub-class of faint and fast-declining Type
-Ia SNe like SN 1991bg.  }
-
-\change{
+Ia SNe like SN 1991bg.
+
 One remaining possibility is that \tomas\ could be part of a rare
@@
 evidence, but it would be consistent with a 2006bt-like light curve.
-}
-
-\change{
+
 In this case, however, the color of SN \tomas\ can rule out a
@@
 Type Ia SN (the SALT2 model is shown).
-}
 
@@
 
-Taking advantage of the availability of \changeR{14} well-constrained lens
+Taking advantage of the availability of 14 well-constrained lens
 models for the Abell 2744 cluster, we have used SN \tomas\ to ask
@@
 We have speculated on the origin of this systematic bias,
-evaluating \changeR{seven} possible causes:
+evaluating seven possible causes:
 
@@
 sources to constrain it.
-\item \change{The redshift assigned to SN \tomas\ is in error.}
-\item \change{SN \tomas\ is dimmed by foreground dust.}
-\item \change{SN \tomas\ is not a normal Type Ia SN.}
+\item The redshift assigned to SN \tomas\ is in error.
+\item SN \tomas\ is dimmed by foreground dust.
+\item SN \tomas\ is not a normal Type Ia SN.
 \end{enumerate}
 
-\noindent The first \changeR{four} of these take on the discrepancy from 
+\noindent The first four of these take on the discrepancy from 
 the lens modeling side, but none are completely satisfactory. For each
@@
 
-\changeG{
 At least for this particular sight-line, the free-form models perform
@@
 them better suited for predicting magnifications of sources that fall
-outside the strong-lensing region -- such as SN \tomas.  }
-
-\change{
+outside the strong-lensing region -- such as SN \tomas.
+
 The last three possible explanations presume an error in the
@@
 for the magnification discrepancy.  A dust-induced bias is also
-disfavored by the very blue color of SN \tomas.  }
-
-\change{
+disfavored by the very blue color of SN \tomas.
+
 Finally, we have considered whether the SN could be
@@
 reject this alternative.
-}
 
@@
 HFF data.  Future revisions of the lens models for Abell
-2744 \changeR{could} either incorporate the observed magnification
+2744 could either incorporate the observed magnification
 of \tomas\ as a new model constraint, or can revisit this test to
@@
 
-\change{
 A promising avenue for exploring the origins of systematic biases in
@@
 (Meneghetti et al. in prep).  Preliminary analysis of this simulation
-comparison suggests that \changeG{magnifications tend to be
-overestimated} for sources that lie outside the strong-lensing region
+comparison suggests that magnifications tend to be
+overestimated for sources that lie outside the strong-lensing region
 along the minor axis direction of an elongated cluster.  Our analysis
@@
 important step for moving toward precision science with cluster-lensed
-sources.  }
-
-Increasing the sample of SNe behind clusters \changeG{like those in
-the HFF program -- with rich lensing constraints and deep imaging -- }
+sources.
+
+Increasing the sample of SNe behind clusters like those in
+the HFF program -- with rich lensing constraints and deep imaging -- 
 would allow this test to be repeated and refined.  With 10 or 100 such
@@
 The puzzling bias revealed by SN \tomas\ supports a concerted effort
-to improve these lenses with \change{further examination of lensing
-systematics through simulations and collection of} a larger sample of
+to improve these lenses with further examination of lensing
+systematics through simulations and collection of a larger sample of
 magnified SNe.

### 2015-04-15 snTomasCode/hubble_fig.py

@@ -1,4 +1,4 @@
-def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
+def plot_hubble_fig( fitter='both', showlcdm=False, datfilename='data/distances/z135/hubblefig.dat'):
     from pytools import plotsetup, colorpalette as cp
     from astropy.io import ascii
     import numpy as np
@@ -8,15 +8,17 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
     import os
     import sys
 
+    from pytools import cosmo
+
     dmint_mlcs=0.08 # intrinsic scatter in SNIa luminosities for MLCS2k2 (Jha:2007)
     dmint_salt=0.08 # intrinsic scatter in SNIa luminosities for SALT2 (Conley:2011)
 
     zTomas = 1.3457#1.31#,
     zerrTomas = 0.001#,0.01]
-    dmTomas_mlcs = 44.22#,44.06#,
-    dmerrTomas_mlcs = np.sqrt(0.09**2 + dmint_mlcs**2)
-    dmTomas_salt = 44.19#44.09
-    dmerrTomas_salt = np.sqrt(0.16**2 + dmint_salt**2)
+    dmTomas_mlcs = 44.205#,44.06#,
+    dmerrTomas_mlcs = np.sqrt(0.0859**2 + dmint_mlcs**2)
+    dmTomas_salt = 44.177#44.09
+    dmerrTomas_salt = np.sqrt(0.163**2 + dmint_salt**2)
 
     thisfile = sys.argv[0]
     if 'ipython' in thisfile :
@@ -32,6 +34,7 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
     dm_salt_err = np.sqrt(hubbledat['dm_salt_err']**2 + dmint_salt**2)
     iscp = np.where( hubbledat['survey']=='scp')
     igoods = np.where( hubbledat['survey']=='goods')
+    icandels = np.where( hubbledat['survey']=='candels')
     fig = plotsetup.halfpaperfig( )
     pl.clf()
     if fitter.lower()=='both':
@@ -47,12 +50,14 @@ def plot_hubble_fig( fitter='both', datfilename='data/distances/hubblefig.dat'):
     if fitter.lower()[:5] in ['both','mlcs'] :
[…]

### 2015-04-15 snTomasCode/lensing_test_fig.py

@@ -11,6 +11,11 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
     import os
     import sys
 
+    muSNmlcs = 2.03
+    muSNmlcserr = 0.29
+    muSNsalt = 1.99
+    muSNsalterr = 0.38
+
     if presfig :
         fig = plotsetup.presfig( figsize=[12,8])
         labelvalues=True
@@ -23,9 +28,9 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
         ms=8
         pl.clf()
         if showlegend:
-            ax1 = pl.axes( [0.01,0.14,0.7,0.84] )
+            ax1 = pl.axes( [0.01,0.14,0.68,0.84] )
         else:
-            ax1 = pl.axes( [0.01,0.14,0.7,0.84] )
+            ax1 = pl.axes( [0.01,0.14,0.68,0.84] )
 
 
     thisfile = sys.argv[0]
@@ -66,6 +71,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
                              marker=marker, mfc=mfc, mec=color, ms=ms,
                              capsize=1, color=color, zorder=10,
                              label='_nolegend_' )
+        print( "%s discrepancy = %.2f sigma"%(model,(med-muSNmlcs)/np.sqrt(errminus**2+muSNmlcserr**2)))
         if labelvalues:
             label = '%s: $%.2f^{%+.2f}_{%+.2f}$'%( model, med, errplus, errminus )
             xlabel=1.35
@@ -79,7 +85,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
                   color=color, transform=ax1.transAxes)
     fig.text( 0.98, 0.75, 'Parametric', ha='right', va='center', size='large',
               color='k', transform=fig.transFigure, rotation=-90)
-    fig.text( 0.98, 0.42, 'Free-Form', ha='right', va='center',size='large',
+    fig.text( 0.98, 0.34, 'Free-Form', ha='right', va='center',size='large',
               color='g', transform=fig.transFigure, rotation=-90)
 
     ax1.spines['right'].set_visible(False)
@@ -92,8 +98,8 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
     iff = np.where(lensingdat['parametric']==0)[0]
[…]

### 2015-04-16 snTomas.tex
minor text edits and updated light curve fitting fig

@@
 we only allow each template SED to be scaled in flux coherently at all
-wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that
-the \tomas\ SED can be matched by a normal Type Ia SN (SN 2011fe) at
-redshift $z=1.31\pm0.02$.  \change{Fixing the redshift at the host redshift of
-$z=1.3457$, we also find the best match is from SN 2011fe, with
+wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that when the \change{redshift is allowed as a free parameter} 
+the \tomas\ SED is best matched by a normal Type Ia SN (SN 2011fe) at
+redshift $z=1.31\pm0.02$.  \change{Fixing the redshift to 
+$z=1.3457$ of the host, we also find the best match is from SN 2011fe, with
 $\chi^2/\nu=133.7/91$. }
@@
 Setting aside the $z\sim1$ solution, all other template matches
-provide a consistent redshift constraint of $z=1.31\pm0.01$,
+provide a consistent redshift constraint of $z=1.31\pm0.02$,
 regardless of whether the templates are warped to match the SN \tomas\

### 2015-04-16 snTomasCode/lightcurve_fitting_fig.py

@@ -46,7 +46,7 @@ def plot_light_curve_fit( fitter='mlcs2k2', plotmags=True,
     if showblue:
         bandlist = ['B','V','I','Y','J','N','H']
     else:
-        bandlist = ['I','Y','J','N','H']
+        bandlist = ['V','I','Y','J','N','H']
     for fitter in fitterlist :
         axdict = {
             'B':fig.add_subplot(gs[rowdict[fitter],0]),

### 2015-04-17 TABLE/magnifications.tex
Significant clean up of the magnifications table.   * better spacing, fixed references, added new notes

@@
-\begin{deluxetable*}{lcccp{1.4in}p{2.1in}}
-\tablecolumns{5}
+\begin{deluxetable*}{p{0.7in}cccp{1.4in}p{2.5in}}
+\tablecolumns{6}
 \tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
-\tablehead{ \colhead{Model} & \colhead{Best\tablenotemark{a}} & \colhead{Median\tablenotemark{b}} & \colhead{68\% Conf. Range\tablenotemark{b}} & \colhead{References} & \colhead{Description}}
+\tablehead{ \colhead{Model} & \colhead{Best\tablenotemark{a}} & \colhead{Median\tablenotemark{b}} & \colhead{68\% Conf. Range\tablenotemark{c}} & \colhead{References} & \colhead{Description}}
 \startdata
-Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL\tablenotemark{c} parametric, strong-lensing based model\\
-Sharon(v2)   & 2.73     & 2.69  &   2.63$-$2.83 &   \citealt{Jullo:2007};\citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\
-CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2007,Richard:2014} &  CATS\tablenotemark{d} team implementation of LENSTOOL parametric strong-lensing based model.\\
-CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 &   \citealt{Jullo:2007,Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS-SL(v2)  & 3.37     & 3.35  &   3.18$-$3.53 &   \citealt{Richard:2014,Jauzac:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
-GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{e} \\
-Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{f} profiles for galaxies and NFW\tablenotemark{g} profiles for dark matter halos.\\
-Zitrin-LTM   & 2.64     & 2.96  &   2.58$-$3.73 &   \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac(v1)   & 3.15     & 2.45  &   2.29$-$2.64 &   \citealt{Bradac:2005,Bradac:2009} & {\tt SWUnited} : Free-form, strong+weak-lensing based model.
+Sharon(v1)   & 2.56     & 2.60  &   2.44$-$2.78 &   HFF\tablenotemark{d}  & LENSTOOL\tablenotemark{e} parametric, strong-lensing based model\\
+Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\
+CATS(v1)     & 2.28     & 2.29  &   2.25$-$2.34 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS(v1sw)   & \nodata  & 2.62  &   2.44$-$2.80 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team LENSTOOL parametric model with both strong and weak lensing constraints.\\
+CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies.\\
+GLAFIC       & 2.34     & 2.29  &   2.19$-$2.37 &   HFF\tablenotemark{d}; \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{g} \\
+Zitrin-NFW   & 2.09     & 2.29  &   2.07$-$2.52 &   HFF\tablenotemark{d}; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{h} profiles for galaxies and NFW\tablenotemark{i} profiles for dark matter halos.\\
+Zitrin-LTM   & 2.67     & 2.99  &   2.61$-$3.77 &   HFF\tablenotemark{d}; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
+Bradac(v1)   & 3.19     & 2.48  &   2.31$-$2.66 &   HFF\tablenotemark{d}; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{j} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
-Bradac(v2)   & 2.21     & 2.23  &   2.20$-$2.28 &   \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Bradac(v2)   & 2.23     & 2.26  &   2.30$-$2.23 &   \citealt{Wang:2015} & Updated version of the {\tt SWUnited}\tablenotemark{j} model with new strong-lensing constraints from HFF imaging.
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{h} : Free-form strong-lensing model using a genetic algorithm.
-\\
-Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{i} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{j} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Diego\tablenotemark{k}   & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{j} model, using a different set of strong-lensing constraints and redshifts.
+Williams     & 2.70     & 2.81  &   1.65$-$5.54 &   HFF\tablenotemark{d} & {\tt GRALE}\tablenotemark{k} : Free-form strong-lensing model using a genetic algorithm.  \\
+Merten       & 2.33     & 2.24  &   2.04$-$2.92 &   HFF\tablenotemark{d}; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{l} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Diego\tablenotemark{n}  & \nodata  & 1.80  &   1.44$-$2.16 & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{m} model, using a different set of strong-lensing constraints and redshifts.
 \enddata
 \tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
-\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model. Confidence ranges enclose 68\%\ of the realized values.}  
-\tablenotetext{c}{{\tt LENSTOOL} : \url{http://projects.lam.fr/repos/lenstool/wiki}}
-\tablenotetext{d}{{\tt CATS} : Clusters As TelescopeS lens modeling team.}
-\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{f}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
-\tablenotetext{g}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
-\tablenotetext{h}{{\tt GRALE} : GRAvitational LEnsing.}
-\tablenotetext{i}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{j}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
-\tablenotetext{k}{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}
+\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
+\tablenotetext{c}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
+\tablenotetext{d}{Lens models with the reference code ``HFF'' were produced as part of the 
+Hubble Frontier Fields lens modeling
+program, using arcs identified in HST archival imaging from
+\citealt{Merten:2011}, spectroscopic redshifts from
+\citealt{Richard:2014}, and ground-based imaging from
+\citealt{Cypriano:2004,Okabe:2008,Okabe:2010a,Okabe:2010b}. Details on
+the model construction and an interactive model magnification web interface 
+are available at
+\url{http://archive.stsci.edu/prepds/frontier/lensmodels/} 
+}
+\tablenotetext{e}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
+\tablenotetext{f}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
+\tablenotetext{g}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{h}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
+\tablenotetext{i}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
+\tablenotetext{j}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
+\tablenotetext{k}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
+\tablenotetext{l}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
+\tablenotetext{m}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
+\tablenotetext{n}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
+No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.
+}
 \end{deluxetable*}

### 2015-04-17 TABLE/magnifications.tex
finished the update to z=1.3457   * also ran spell-check

@@
 Sharon(v1)   & 2.56     & 2.60  &   2.44$-$2.78 &   HFF\tablenotemark{d}  & LENSTOOL\tablenotemark{e} parametric, strong-lensing based model\\
-Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.\\
+Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.
+Includes cosmological parameter variations in uncertainty estimates.\\
 CATS(v1)     & 2.28     & 2.29  &   2.25$-$2.34 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team implementation of LENSTOOL parametric strong-lensing based model.\\
 CATS(v1sw)   & \nodata  & 2.62  &   2.44$-$2.80 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies.\\
+CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
 GLAFIC       & 2.34     & 2.29  &   2.19$-$2.37 &   HFF\tablenotemark{d}; \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{g} \\
@@
 Merten       & 2.33     & 2.24  &   2.04$-$2.92 &   HFF\tablenotemark{d}; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{l} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
 Diego\tablenotemark{n}  & \nodata  & 1.80  &   1.44$-$2.16 & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{m} model, using a different set of strong-lensing constraints and redshifts.

### 2015-04-17 snTomas.tex
finished the update to z=1.3457   * also ran spell-check

@@
 of the peak apparent magnitude, corrected for light curve shape and
-exinction.  In a cosmology-independent analysis, we find that \tomas\
+extinction.  In a cosmology-independent analysis, we find that \tomas\
 is \change{$0.77\pm0.15$} magnitudes brighter than unlensed Type Ia
@@
 
-SN \tomas\ was discovered in Hubble Space Telescop (\HST) observations
+SN \tomas\ was discovered in Hubble Space Telescope (\HST) observations
 with the Advanced Camera for Surveys (ACS) in the F606W and F814W
@@
 From the preceding analysis, we conclude that \tomas\ is a Type Ia SN
-at $z\approx1.3$.  At this redshift, the absorption at $\sim$8700\AA\
+at $z\approx1.35$.  At this redshift, the absorption at $\sim$8700\AA\
 corresponds to the blended \ion{Ca}{2} H\&K features.
@@
 photometric information, which also supports classification as a Type
-Ia SN at $z\approx1.3$.
+Ia SN at $z\approx1.35$.
 
@@
 template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
-match the observed SED of SN \tomas.  From this analysis we find
-results that are consistent with the SNID fits \change{and the host
-galaxy redshift}: $z=1.31\pm0.03$ and a phase of $0\pm3$ rest-frame
-days. The best-fitting spectral template is the normal Type Ia SN
-2012cg, shown in the top panel of Figure~\ref{fig:SpecFit}, which has
-$\chi^2$ per degree of freedom $\nu$ equal to 42.1/87.  \change{If we
-fix the redshift at $z=1.3457$ then we find the best fit is from the
-normal Type Ia SN 2014J, with $\chi^2/\nu=51.8/87$.}
+match the observed SED of SN \tomas.  \change{With the redshift fixed
+at $z=1.3457$ we find the best fit is from the normal Type Ia SN
+2014J, with a $\chi^2$ per degree of freedom $\nu$ of
+$\chi^2/\nu=51.8/87$ shown in the top panel of
+Figure~\ref{fig:SpecFit}.  Allowing the redshift as an additional free
+parameter, we still find results that are consistent with the SNID
+fits and $<2\sigma$ from the host galaxy redshift: $z=1.31\pm0.02$ and
+a phase of $0\pm3$ rest-frame days. The best-fitting spectral template
+in this case is the normal Type Ia SN 2012cg at $z=1.31$ with
+$\chi^2/\nu=42.1/87$.}
 
@@
 we only allow each template SED to be scaled in flux coherently at all
-wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that when the \change{redshift is allowed as a free parameter} 
-the \tomas\ SED is best matched by a normal Type Ia SN (SN 2011fe) at
-redshift $z=1.31\pm0.02$.  \change{Fixing the redshift to 
-$z=1.3457$ of the host, we also find the best match is from SN 2011fe, with
-$\chi^2/\nu=133.7/91$. }
+wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that
+when the \change{redshift is allowed as a free parameter the \tomas\
+SED is best matched by a normal Type Ia SN (SN 2011fe) at redshift
+$z=1.31$ with $\chi^2/\nu=102.9/90$.  Fixing the redshift to the
+redshift $z=1.3457$ of the host, we also find the best match is from
+SN 2011fe, with $\chi^2/\nu=133.7/91$. }
 
@@
 found. Furthermore, a redshift $z\sim1$ is at odds with the host
-galaxy photo-z ($1.5\pm0.2$), and we will see in the following section
+galaxy redshift ($z=1.3457$), and we will see in the following section
 that the photometric data is also incompatible with a Type Ia SN at
@@
 The marginal posterior distribution in redshift for the Type Ia model
-is sharply peaked at $z=1.35\pm0.02$, which is fully consistent with
-the photo-$z$ of the presumed host galaxy ($z=1.5\pm0.2$), and
-$<2\sigma$ from the spectroscopic redshift of $z=1.31\pm0.01$ derived
-in Section~\ref{sec:SpecRedshift}.  The time of peak brightness is
-also tightly constrained at $t_{\rm pk}=56816.3\pm0.3$, which means
-the spectroscopic observations were collected within 2 rest-frame days
-of the epoch of peak brightness, consistent with our spectroscopic
-analysis.
+is sharply peaked at $z=1.35\pm0.02$, which \change{is fully
+consistent with the redshift of the presumed host galaxy ($z=1.3457$)
+as well as the redshift of $z=1.31\pm0.02$ derived from the SN
+spectrum in Section~\ref{sec:SpecRedshift}.  The time of peak
+brightness is also tightly constrained at $t_{\rm pk}=56816.3\pm0.3$,
+which means the HST grism observations were collected within 2
+rest-frame days of the epoch of peak brightness -- also consistent
+with our spectroscopic analysis.}
 
@@
 
-With the spectroscopic type and redshift securely defined as a normal
-Type Ia SN at $z=1.31$, we now turn to fitting the light curve with
+With the type and redshift securely defined as a normal
+Type Ia SN at $z=1.3457$, we now turn to fitting the light curve with
 Type Ia templates to measure the distance modulus.  Here we use two
@@
 (top row) and SALT2 (bottom row) fitters. The model redshifts are set to
-$z=1.33\pm0.02$, encompassing both redshift values as determined from
+$z=1.3457$ as determined from combined
 spectroscopic and photometric constraints.  Solid lines denote the
@@
 With both fitters we find light curve shape and color parameters that
-are fully consistent with a normal Type Ia SN, regardless of whether
-we adopt the spectroscopic redshift $z=1.31$ from
-Section~\ref{sec:SpecRedshift} or the photometric redshift $z=1.35$
-from Section~\ref{sec:PhotometricClassification}.  For SALT2, with the
-redshift range set to $1.33\pm0.02$, we find a light curve shape
-parameter of $x_1=0.164\pm0.199$ and a color parameter of
-$c=-0.115\pm0.025$, yielding a $\chi^2$ value of 48.4 for 36 degrees
+are fully consistent with a normal Type Ia SN.  For SALT2, with the
+\change{redshift fixed at $z=1.3457$, we find a light curve shape
+parameter of $x_1=0.135\pm0.199$ and a color parameter of
+$c=-0.127\pm0.025$, yielding a $\chi^2$ value of 45.0 for 36 degrees
 of freedom, $\nu$.  With the MLCS2k2 fitter the best-fit shape
-parameter is $\Delta=-0.033\pm0.083$ and the color term is
-$A_{\rm V}=0.014\pm0.037$, giving $\chi^2/\nu=23.9/36$.
+parameter is $\Delta=-0.082\pm0.070$ and the color term is
+$A_{\rm V}=0.011\pm0.025$, giving $\chi^2/\nu=22.8/36$.}
 
@@
 
-As in \P14, we derive a distance modulus\footnote{We use 'dm' to
+As in \citealt{Patel:2014}, we derive a distance modulus (dm)\footnote{We use 'dm' to
 indicate the distance modulus to avoid confusion, reserving the symbol
@@
 effects of gravitational lensing, so that we can later use it to
-derive a direct measurment of the magnification.  From the SALT2 fit
-we get
+derive a direct measurement of the magnification.
+\change{The MLCS2k2 fitter returns $\rm{dm}_{\rm MLCS2k2}$ directly, as it is defined as one of the free parameters in the model.
+To derive dm from} the SALT2 fit
+we use
 
@@
 to match the arbitrary normalization of the SALT2 fitter used
-by \citet{Guy:2010} and \citet{Sullivan:2011}.  This conversion allows
+by \citet{Guy:2010} and \citet{Sullivan:2011}.  \change{This conversion from SALT2 to SiFTO is necessary, as it} allows
 us to adopt values for the constants $M$, $\alpha$, and $\beta$
@@
 correction of 0.20 mag to the MLCS2k2 distances as
-in \P14.  This correction was derived by applying both
+in \citealt{Patel:2014}.  This correction was derived by applying both
 fitters to a sample of Type Ia SNe from the SDSS
@@
 fiducial cosmological model fit to the SN Ia Hubble diagram (distance
-modulus vs redshift).  Thus, $\sigma_{\rm int}$ is designed to
-account for any unknown sources of scatter in the Type Ia SN
-population, including unidentified errors in the data analysis as well
-as the natural scatter in intrinsic Type Ia SN luminosities.  The value of 
-$\sigma_{\rm int}$ may be expected to vary as a function of
-redshift and also from survey to survey.
+modulus vs redshift).  Thus, $\sigma_{\rm int}$ is designed to account
+for any unknown sources of scatter in the Type Ia SN population,
+including unidentified errors in the data analysis as well as the
+natural scatter in intrinsic Type Ia SN luminosities.  The value of
+$\sigma_{\rm int}$ may be expected to vary as a function of redshift
+and also from survey to survey.
 
@@
 Table~\ref{tab:MeasuredMagnification}, adopting the spectroscopic
-redshift ($z=1.31$).  In addition to modifying the distance modulus
+redshift ($z=1.3457$).  In addition to modifying the distance modulus
 uncertainty for SN \tomas, we also add $\sigma_{\rm int}=0.08$ mag in
 quadrature to the uncertainty for every SN in the control sample. Note
-however that the uncertainty on the control sample value at $z=1.31$
-is only 0.05 mag, smaller than the intrinsic dispersion because it
+however that the uncertainty on the control sample value at $z=1.3457$
+is only 0.06 mag, smaller than the intrinsic dispersion because it
 reflects only our measurement error on the mean distance modulus of
@@
 $10^{10.135}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
-{\it BPZ} SED fit to define rest-frame optical magnitudes.
+{\it BPZ} SED fit (Section~\ref{sec:DiscoveryAndFollowup}) to define rest-frame optical magnitudes.
 
@@
 understood, but may be related to the metallicity or age of the SN
-progenitor systems. In either case, it is reasonable to expect that
-the significance of this effect decreases with redshift, as metal-rich
-passive galaxies become much less common at $z>1$.  Indeed, when the
-size of the mass step correction is allowed to vary with redshift,
-there is no significant evidence that a non-zero mass step is required
-at $z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
+progenitor systems.  In either case, the significance of this effect
+should decrease with redshift, as metal-rich passive galaxies become
+much less common at $z>1$ \change{\citep[see
+e.g.][]{Rigault:2013,Childress:2014b}.}  Indeed, when the size of the
+mass step correction is allowed to vary with redshift, there is no
+significant evidence that a non-zero mass step is required at
+$z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
 absence of a clear physical model and the lack of empirical support
@@
 cosmological model \citep[e.g.][]{Nordin:2014}.  To that end, we
-follow \P14\ and define the magnification by comparing
+follow \citealt{Patel:2014} and define the magnification by comparing
 the measured distance modulus of SN \tomas\ against an average
@@
 the ``parametric'' family, and the six in green at the bottom are
-``free-form.''  Dashed lines mark the unweighted mean of each model
-family and shaded regions show the standard error of the mean.
+``free-form.''  The grey dashed line marks the unweighted mean for the
+set of all models, at $\mu=2.53$.
 \label{fig:lensingtest} }
@@
 
-Table~\ref{tab:PredictedMagnifications} lists the \change{11} models,
+Table~\ref{tab:PredictedMagnifications} lists the 14 models,
 giving for each one the predicted magnification and uncertainty for a
@@
 their quoted uncertainties), one would get a mean for the full sample
-of $\mu=2.51\pm0.34$.  This is separated from the observed SN
-magnification by $\delta\mu/\mu=27\%$, which is only a 1.2$\sigma$
-difference.
+of \change{$\mu=2.53\pm0.38$.  This is separated from the observed SN
+magnification by $\delta\mu/\mu=25\%$, which is just over a
+1$\sigma$ difference.}
 
@@
 Figure~\ref{fig:lensingtest} also separates the models based on the
-scope of input data constraints used.  Ten of the models rely only
-on strong-lensing constraints (plotted as circles), while the other
-four also use weak-lensing measurements (diamonds).  Ten of the
-models were constructed using only pre-HFF data (open symbols), and
-four others added new multiply-imaged systems and redshifts.
+scope of input data constraints used.  Ten of the models rely only on
+strong-lensing constraints (plotted as circles), while the other four
+also use weak-lensing measurements (diamonds).  Nine of the models
+were constructed using only pre-HFF data (open symbols), while five
+others added new multiply-imaged systems and redshifts.
 
@@
 estimates of the magnification.  Six of the tested models
-(CATS, GLAFIC, Zitrin-NFW, Bradac(v2), Merten, Diego) report a median
+(CATSv1, GLAFIC, Zitrin-NFW, Bradac(v2), Merten, Diego) report a median
 value that falls within the 1$\sigma$ uncertainty range of the
@@
 
-However, beyond this first-order agreement, there is a systematic bias
-apparent. All of the lens models return median magnifications
-that are {\it higher} than the observed value, and half of
-the models are discrepant by more than $1\sigma$.  It is important to
-emphasize that SN \tomas\ only samples a single sight-line through the
-cluster, so any conclusions to be drawn from this analysis are
-necesssarily limited.  Nevertheless, a systematic shift common to all
-models is surprising, given the wide range of modeling strategies,
-input data, and physical assumptions represented by this set of
-models.  In the following subsections we examine possible explanations
-for this small but apparently universal bias.
+However, beyond this first-order agreement, there is a small
+systematic bias apparent. All of the lens models \change{except one}
+return median magnifications that are {\it higher} than the observed
+value, and \change{six of the models are discrepant by more than $1.5\sigma$.}
+It is important to emphasize that SN \tomas\ only samples a single
+sight-line through the cluster, so any conclusions to be drawn from
+this analysis are necessarily limited.  Nevertheless, a systematic
+shift common to all models is surprising, given the wide range of
+modeling strategies, input data, and physical assumptions represented
+by this set of models.  In the following subsections we examine
+possible explanations for this small but \change{nearly} universal
+bias.
 
@@
 
-We tested this hypothesis using the CATS-SL(v2) model by allowing the mass
+We tested this hypothesis using the CATS(v2) model by allowing the mass
 of the nearby cluster member galaxy to vary as a free parameter in the
@@
 constraints and reduce the tension between the predicted and observed
-magnification.  However, for two of the most recent
-models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
+magnification.  However, for two of the most recent models (CATSv2,
+Lam; \citealt{Jauzac:2014c,Lam:2014}) that include new strong-lensing
 constraints, the predicted magnification is still significantly higher
 than the observed value.  Again the CATS model family provides a
-useful case study.  The CATS-SL(v2) model \citep[from][]{Jauzac:2014c}
+useful case study.  The CATS(v2) model \citep[from][]{Jauzac:2014c}
 shares the same lens modeling software (LensTool), and the same
-primary methodology as the earlier CATS models, though with
-two key differences:  (1) the CATS-SL(v2) model changes the location of a
+primary methodology as the earlier CATS models, though with two key
+differences: (1) the CATS(v2) model changes the location of a
 multiply-imaged system near the SN \tomas\ position; and (2) the model
 incorporates 33 new multiply imaged galaxies.  These improvements
-should in principle make the CATS-SL(v2) model magnification estimates
+should in principle make the CATS(v2) model magnification estimates
 more accurate, though we in fact see the opposite result: the
-CATS-SL(v2) model predicts a $\mu$ that is higher than the measured
-value by $4.1\sigma$, and higher than either of the previous
-two versions of the CATS models.
+CATS(v2) model predicts a $\mu$ that is higher than the measured
+value by $4.3\sigma$, and higher than either of the previous two
+versions of the CATS models.
 
@@
 question]{Lam:2014}.  Given the large discrepancy between the
-CATS-SL(v2) model and the SN measurement, one might question whether
+CATS(v2) model and the SN measurement, one might question whether
 this change in the position of image 3.3 is driving the increase in
 the predicted $\mu$ for SN \tomas. However, \citet{Jauzac:2014c} also
-examined a version of the CATS-SL(v2) model where this single source
+examined a version of the CATS(v2) model where this single source
 is left in the original position, and find that it does not
@@
 of the effect of introducing weak lensing constraints.  The initial
-CATS model uses only strong-lensing constraints, and gives
-$\mu=2.27^{+0.05}_{-0.04}$, slightly higher than the measured value.
-A second iteration of this model, labeled here as CATS-SL+WL, used the
+CATS(v1) model uses only strong-lensing constraints, and gives
+$\mu=2.29^{+0.05}_{-0.04}$, slightly higher than the measured value.
+A second iteration of this model, labeled here as CATS(v1sw), used the
 same strong-lensing features, but added in weak lensing constraints.
@@
 
-As a quantitative example, we have modified the Sharon(v2) model to
-include this cosmological parameter uncertainty,
-following \citep{Bayliss:2015}. At the position of SN \tomas, the
-68\%\ confidence range for the magnification at $z=1.31$ increases
-from [2.63,2.83] to [2.42,2.85], and the best-fit magnification value
-of $mu=2.73$ remains the same.  This moves the Sharon(v2) model from
-being discrepant at the $2.5\sigma$ level to a $1.75\sigma$ tension.
-Incorporating this cosmological parameter uncertainty in the other
-models would similarly reduce the tension between models and
-observation, but would not resolve the overall systematic shift.  Even
-a factor of 2.5 increase in the uncertainties (the most drastic change
-seen in the analysis of \citep{Bayliss:2015}) would still leave the
-most extreme outlier (CATS-SL(v2)) discrepant by $2.6\sigma$.
+\change{
+We have used the Sharon(v2) model to provide a quantitative example of
+how the magnification errors are affected by inclusion of this
+cosmological parameter uncertainty.  Following \citealt{Bayliss:2015},
+we propagate cosmological parameter variations into the magnification
+uncertainties, and find that the 68\%\ confidence range for the
+magnification at $z=1.3457$ increases from [2.63,2.83] to [2.42,2.85].
+The best-fit magnification value of $mu=2.74$ and the median value of
+$mu=2.59$ remain the same. For this model only,
+Table~\ref{tab:PredictedMagnifications} includes this cosmological
+uncertainty. In this case, the Sharon(v2) model moves from being discrepant at
+the $2.5\sigma$ level to a $1.7\sigma$ tension.  Incorporating this
+cosmological parameter uncertainty in the other models would similarly
+reduce the tension between models and observation, but would not
+resolve the overall systematic shift.  Even a factor of 2.5 increase
+in the uncertainties (the most drastic change seen in the analysis
+of \citep{Bayliss:2015}) would still leave the most extreme outlier
+(CATS(v2)) discrepant by $2.9\sigma$.  }
 
@@
 inferred from the projected separation between the SN and nearby
-galaxies.  In this case the redshift evidence comes from the SN
-itself, and we find a consistent redshift from both the SN spectrum
+galaxies.  In this case the redshift evidence \change{is strongly supported} with evidence from the SN
+itself: we find a consistent redshift from both the SN spectrum
 (Section~\ref{sec:SpecRedshift}) and the light curve
@@
 picture, so the evidence strongly disfavors any redshift that is
-significantly different from $z=1.3$.
-
-We have adopted the spectroscopic redshift of $z=1.31\pm0.01$ for the
-magnification comparison.  Spectroscopic SN redshifts are generally more
-precise and accurate than those derived from SN
-photometry \citep{Rodney:2010b,Kessler:2010,Sako:2011}.  However, in
-this case the spectrum is limited to the rest-frame near-UV
-wavelengths, where the available SN spectral template libraries are
-more limited than at optical wavelengths.  If we use the photometric
-redshift of $z=1.35\pm0.02$ instead, then the measured magnification
-is reduced.\footnote{By increasing the redshift, the SN is presumed to
-be at a greater distance, so to first order one would be expect it to
-appear slightly fainter (larger distance modulus). If the distance
-modulus inferred from the light curve fit remained constant, this
-would drive the inferred magnification to a higher value.  However,
-the light curve fitting is more strongly affected by the covariance
-between redshift, color, and light curve width.  In this case, these
-effects drive the distance modulus to a larger value at $z=1.35$,
-resulting in a smaller value of the observed magnification $\mu$.}
-From the SALT2 fitter we derive $\mu_{\rm SALT2}=1.80\pm0.30$ and from
-MLCS2k2 we get $\mu_{\rm MLCS2k2}=1.83\pm0.17$.  The lens models are
-also shifted, and they uniformly move in the opposite direction, to
-magnification values that are {\it larger} than at $z=1.31$, by
-$\sim1$\%.  Thus, shifting the SN to the photometric redshift of
-$z=1.35$ only serves to (slightly) exacerbate the tension between the
-observations and models.
+significantly different from $z=1.35$.
+
+We have adopted the \change{most precise redshift of $z=1.3457$ from
+the host galaxy as our baseline for the magnification comparison.  If
+instead we adopt the spectroscopic redshift from the SN itself
+($z=1.31$; Section~\ref{sec:SpecRedshift}) then we find no significant
+change in the inferred magnifications or in the suggestion of a small
+systematic bias.}
 
@@
 the blue end of the normal range of Type Ia SN colors.  With the SALT2
-fitter we measured a color parameter $c=-0.115\pm0.025$, and with
+fitter we measured a color parameter $c=-0.127\pm0.025$, and with
 MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
-V}=0.014\pm0.037$ magnitudes.  These colors are tightly constrained,
+V}=0.011\pm0.025$ magnitudes.  These colors are tightly constrained,
 as we are fitting to photometry that covers a rest-frame wavelength
@@
 this can have a measurable impact on precise cosmological constraints,
-it is far less than the 0.25 mag difference between the observed
+it is far less than the 0.23 mag difference between the observed
 magnification of \tomas\ and the mean of the model predictions.
@@
 2006bt. Dashed blue lines show the color curves for a normal Type Ia
-SN, derived from the SALT2 model with a color parameter $c=-0.12$, set
+SN, derived from the SALT2 model with a color parameter $c=-0.13$, set
 to match the best-fit color for SN \tomas.
@@
 Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
-classified SN Tomas as a normal Type Ia SN based on both the
+classified SN \tomas\ as a normal Type Ia SN based on both the
 spectroscopic and photometric evidence.  This rules out the
@@
 Although the near-IR shoulder is more prominent in the rest-frame {\it
-i} band, we can see in Figures~\ref{fig:LightCurveFits} that the F160W
+i} band, we can see in Figure~\ref{fig:LightCurveFits} that the F160W
 light curve may suggest a weak or delayed near-IR shoulder.  The
@@
 SN 2006bt prototype by at least 0.25 magnitudes in every color. The
-observed \tomas\ colors are fully consistent with the a normal, blue
+observed \tomas\ colors are fully consistent with a normal, blue
 Type Ia SN (the SALT2 model is shown).
@@
 light curve of SN \tomas\ are well matched by templates of a normal
-Type Ia SN at $z=1.31\pm0.01$.  Using the two most prevalent \SNIa\
+Type Ia SN at $z=1.3457$.  Using the two most prevalent \SNIa\
 light curve fitters, SALT2 and MLCS2k2, we get a consistent
@@
 have derived a consistent measured magnification of $\mu_{\rm
-SALT2}=1.88\pm0.35$.  $\mu_{\rm MLCS2k2}=2.00\pm0.28$, from the two
+SALT2}=1.99\pm0.38$.  $\mu_{\rm MLCS2k2}=2.03\pm0.29$, from the two
 light curve fitters.
 
+\change{
 Taking advantage of the availability of 14 well-constrained lens
-models for the Abell 2744 cluster, we have used SN \tomas\ to ask
-how accurately these lens models can predict the magnification along
-this line of sight.   We find that these models are consistent, and
-fairly accurate, collectively predicting $\mu=2.60\pm0.34$.  This is
+models for the Abell 2744 cluster, we have used SN \tomas\ to ask how
+accurately these lens models can predict the magnification along this
+line of sight.  We find that these models are consistent, and fairly
+accurate, collectively predicting $\mu=2.53\pm0.38$.  This is
 encouraging, and reinforces the quality and value of these public lens
-models for studying magnified background objects.   However, the fact
-that all models predict a larger magnification value than we observe
-is an indication that there is a small systematic bias inherent to
-this cluster or sight-line.
-
-We have speculated on the origin of this systematic bias,
+models for studying magnified background objects.  However, we note
+that all but one of the tested models provides a median magnification
+value that is larger than we observe.  This may be an indication that
+there is a small systematic bias inherent to this cluster or
+sight-line.
+}
+
+We have speculated on what could be the origin for such a systematic bias,
 evaluating seven possible causes:
@@
 At least for this particular sight-line, the free-form models perform
-better both in the sense that the mean and standard error for this
-subset ($2.34\pm0.27$) is closer to the measured value ($2.00\pm0.28$)
-than is the parametric set ($2.59 +- 0.36$).  These free-form models
-also deliver more realistic uncertainties (with the exception of the
+better in the sense that the mean and standard error for this subset
+($2.37\pm0.35$) is closer to the measured value ($2.03\pm0.29$) than
+is the parametric set ($2.59 +- 0.37$).  These free-form models also
+deliver more realistic uncertainties (with the exception of the
 Bradac(v2) model -- see \citet{Wang:2015} for further discussion of
-the changes made from v1 to v2 of that model).  This may indicate that
-the free-form approach in general is more successful in capturing the
-uncertainty from biases inherent to the mass modeling exercise, such
-as the mass sheet degeneracy and more complex ``approximate
-invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  It may also be
-the case that the greater flexibility of the free-form models makes
-them better suited for predicting magnifications of sources that fall
-outside the strong-lensing region -- such as SN \tomas.
+the changes made from v1 to v2 of that model). \change{The free-form
+model family also includes the only model that predicts a
+magnification lower than the observed value (Diego).}  This may
+indicate that the free-form approach in general is more successful in
+capturing the uncertainty from biases inherent to the mass modeling
+exercise, such as the mass sheet degeneracy and more complex
+``approximate invariances'' \citep{Liesenborgs:2012,Schneider:2014}.
+It may also be the case that the greater flexibility of the free-form
+models makes them better suited for predicting magnifications of
+sources that fall outside the strong-lensing region -- such as
+SN \tomas.
 
@@
 that a redshift error is the primary cause of the discrepancy, as the
-redshift evidence is derived principally from the SN itself and not
-from the host galaxy. A value of $z\sim1.3$ is well supported by both
-the spectroscopic and photometric SN data, and changing the redshift
-within the constraints of these complementary observations only serves
-to increase the tension between the observed and predicted
-magnifications.  We also find it implausible that there is sufficient
-dust in the cluster or elsewhere along the line of sight to account
-for the magnification discrepancy.  A dust-induced bias is also
-disfavored by the very blue color of SN \tomas.
+redshift evidence is well supported by multiple lines of evidence from
+both the SN and the presumed host galaxy. Changing the redshift within
+the constraints of these complementary observations does not resolve
+the tension. We also find it implausible that there is sufficient dust
+in the cluster or elsewhere along the line of sight to account for the
+magnification discrepancy.  A dust-induced bias is also disfavored by
+the very blue color of SN \tomas.
 
@@
 
-This single object behind a single cluster is not in and of itself a
-cause for alarm.  Previous analyses of lensed \SNIa\ found no
-significant discrepancy beween the observed \SNIa\ magnifications and
-the predictions from lens models
-(\citetalias{Patel:2014}; \citealt{Nordin:2014}), albeit with a much
-smaller set of lens models being tested.  The observed systematic bias
-for \tomas\ is small, and many of the lens models being evaluated are
-preliminary models that have not been updated to include all of the
-HFF data.  Future revisions of the lens models for Abell
-2744 could either incorporate the observed magnification
+We have evaluated here only a single object behind a single cluster,
+with a minor tension between the observed magnification and most
+predictions.  This is not in and of itself a cause for alarm.
+Previous analyses of lensed \SNIa\ found no significant discrepancy
+between the observed \SNIa\ magnifications and the predictions from
+lens models (\citetalias{Patel:2014}; \citealt{Nordin:2014}), albeit
+with a much smaller set of lens models being tested.  The observed
+systematic bias for \tomas\ is small, and many of the lens models
+being evaluated are preliminary models that have not been updated to
+include all of the HFF data.  Future revisions of the lens models for
+Abell 2744 could either incorporate the observed magnification
 of \tomas\ as a new model constraint, or can revisit this test to
@@
 
+This work utilizes gravitational lensing models produced by PIs
+Bradac, Ebeling, Merten \& Zitrin, Sharon, and Williams funded as part
+of the HST Frontier Fields program conducted by STScI. STScI is
+operated by the Association of Universities for Research in Astronomy,
+Inc. under NASA contract NAS 5-26555. The lens models were obtained
+from the Mikulski Archive for Space Telescopes (MAST).
+
 Financial support for this work was provided to SAR by NASA through grants

### 2015-04-17 snTomasCode/hubble_fig.py

@@ -1,4 +1,6 @@
-def plot_hubble_fig( fitter='both', showlcdm=False, datfilename='data/distances/z135/hubblefig.dat'):
+def plot_hubble_fig( fitter='both', showlcdm=False,
+                     zsn=1.31,
+                     datfilename='data/distances/z135/hubblefig.dat'):
     from pytools import plotsetup, colorpalette as cp
     from astropy.io import ascii
     import numpy as np
@@ -13,12 +15,21 @@ def plot_hubble_fig( fitter='both', showlcdm=False, datfilename='data/distances/
     dmint_mlcs=0.08 # intrinsic scatter in SNIa luminosities for MLCS2k2 (Jha:2007)
     dmint_salt=0.08 # intrinsic scatter in SNIa luminosities for SALT2 (Conley:2011)
 
-    zTomas = 1.3457#1.31#,
-    zerrTomas = 0.001#,0.01]
-    dmTomas_mlcs = 44.205#,44.06#,
-    dmerrTomas_mlcs = np.sqrt(0.0859**2 + dmint_mlcs**2)
-    dmTomas_salt = 44.177#44.09
-    dmerrTomas_salt = np.sqrt(0.163**2 + dmint_salt**2)
+    if (zsn-1.31)<0.01:
+        zTomas = 1.31
+        zerrTomas = 0.01
+        dmTomas_mlcs = 44.06
+        dmerrTomas_mlcs = np.sqrt(0.0859**2 + dmint_mlcs**2)
+        dmTomas_salt = 44.09
+        dmerrTomas_salt = np.sqrt(0.163**2 + dmint_salt**2)
+
+    elif (zsn-1.3457)<0.01:
+        zTomas = 1.3457
+        zerrTomas = 0.001
+        dmTomas_mlcs = 44.205
+        dmerrTomas_mlcs = np.sqrt(0.0859**2 + dmint_mlcs**2)
+        dmTomas_salt = 44.177
+        dmerrTomas_salt = np.sqrt(0.163**2 + dmint_salt**2)
 
     thisfile = sys.argv[0]
     if 'ipython' in thisfile :
@@ -71,7 +82,7 @@ def plot_hubble_fig( fitter='both', showlcdm=False, datfilename='data/distances/
 
     # dm_mlcs = slope * z - intercept
     def line( x, slope, intercept ):
-        return slope*(x-1.3457) + intercept
+        return slope*(x-zTomas) + intercept
 
     lineparam0 = np.array([1,45])
[…]

### 2015-04-17 snTomasCode/sn06bt_comparison_fig.py

@@ -23,7 +23,7 @@ def getdata():
 
     # simulate a normal SN Ia
     snIa = sncosmo.Model( 'salt2' )
-    snIa.set(c=-0.15)
+    snIa.set(c=-0.13)
     snIa.set(z=0.001)
     trest=[]
     mag = []
@@ -135,7 +135,7 @@ def colorfig( **plotargs ):
     pl.ylabel('B-r',rotation=-90, labelpad=10)
     ax4.set_ylim(-0.14,1.09)
     ax4.text(5, 0.8,'SN 2006bt',rotation=45, color='darkorange')
-    ax4.text(6.8, 0.37,'\\noindent normal Ia\\\\ $c=-0.12$',rotation=40, color='b', ha='left')
+    ax4.text(6.8, 0.37,'\\noindent normal Ia\\\\ $c=-0.13$',rotation=40, color='b', ha='left')
 
     fig.subplots_adjust(left=0.15,right=0.87,bottom=0.12,top=0.92,hspace=0,wspace=0)
     suplabel( 'x', 'Rest-frame time (days)', labelpad=8, ha='center', va='bottom')

### 2015-04-17 snTomasCode/specfig.py

@@ -8,10 +8,119 @@ def getchi2(templatedatfile, obsdatfile='SPECTRUM/snTomas_acs_g800l_1d.dat'):
     chi2 = np.sum( (fluxmod-flux)**2 / err**2 )
     return( chi2 )
 
+def isigclip( valarray, sigclip, igood=[], maxiter=10, thisiter=0 ) :
+    """ find the indices of valarray that
+    survive after a clipping all values more than
+    sigclip from the mean.  recursively iterative """
+    import numpy as np
+    if not type(valarray)==np.ndarray :
+        valarray = np.array( valarray )
+    if not len(igood) : igood = range(len(valarray))
+
+    Ngood = len(igood)
+    mnval = np.mean( valarray[igood] )
+    sigma = np.std( valarray[igood] )
+    igood = np.where( (np.abs(valarray-mnval)<(sigclip*sigma))  )[0]
+
+    # import pdb; pdb.set_trace()
+    if len(igood) == Ngood : return( igood )
+    if thisiter>=maxiter :
+        print("WARNING : Stopping after %i recursions"%maxiter)
+        return( igood )
+    thisiter+=1
+    igood = isigclip( valarray, sigclip, igood=igood, maxiter=maxiter, thisiter=thisiter )
+    return( igood )
+
+
+def binspecdat( wavelength, flux, fluxerr=[], binwidth=10, sigclip=0, sumerrs=False,
+                wstart=0, wend=0 ):
+    """  bin up the given wavelength and flux arrays
+    and return the binned values.
+    binwidth is in the wavelength units of the wavelength
+    array  (typically Angstroms)
+    """
+    import numpy as np
+
+    w,f = wavelength, flux
+    wbinned, fbinned = [], []
+    wbin,fbin,dfbin = np.array([]), np.array([]), np.array([])
+    dw, df = [], []
+    if wstart : istart = np.where( w>wstart )[0][0]
+    else : istart = 0
+    if wend : iend = np.where( w<wend )[0][-1]
+    else : iend = len(w)
+    w0 = w[istart]
+    for i in range(istart,iend):
+        fullbin = False
+        if wend and w[i]>wend : break
+        if w[i]>w0+binwidth :
+            # determine the mean value in this bin
+            w0 = w[i]
+            igoodval = []
+            if sigclip :
+                # use sigma clipping to reject outliers
[…]

### 2015-04-17 snTomas.tex
a few small corrections

@@
 
-The unlensed sample comprises 18 spectroscopically confirmed Type Ia
-SNe in the range $1.14\leq z \leq1.42$ from the GOODS and SCP
-surveys,\footnote{GOODS: Great Observatories Origins Deep Survey,
-PI:Giavalisco, HST-PID:9425,9583; SCP: Supernova Cosmology Project,
-PI:Perlmutter} which used the HST Advanced Camera for
-Surveys \citep{Riess:2006,Suzuki:2012}.  Using the SALT2 and MLCS2k2
+The unlensed sample comprises \change{22 spectroscopically confirmed Type Ia
+SNe in the range $1.14\leq z \leq1.55$ from three HST surveys: 11 from GOODS\footnote{GOODS: the Great Observatories Origins Deep Survey, PI:Giavalisco, HST-PID:9425,9583} \citep{Riess:2007}, 7 from SCP\footnote{SCP: the Supernova Cosmology Project, PI:Perlmutter} \citep{Suzuki:2012}, and 4 from CANDELS\footnote{CANDELS: the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey, PI:Faber \&\ Ferguson} \citep{Rodney:2012,Rodney:2014}.}  Using the SALT2 and MLCS2k2
 fitters as described above, we get distance modulus measures for every
@@
 \caption{ Measurement of the lensing magnification from comparison of
-the \tomas\ distance modulus to a sample of unlensed field SN.
+the \tomas\ distance modulus to a sample of unlensed field SN.  SNe
+from the GOODS program are plotted as squares, those from the SCP
+survey are shown as circles, and the CANDELS objects are triangles.
 The distance modulus for each SN is derived from light curve fits
-using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom panel).
+using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom
+panel).
 \label{fig:MagnificationMeasurement} }
@@
 Comparison of the observed lensing magnification to predictions from
-lens models. Solid vertical lines show the constraints from SN \tomas\
-derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
-MLCS2k2 (blue) fitters, with shaded regions marking the total
-uncertainty for each. Markers with horizontal error bars show the
-median magnification and 68\%\ confidence region from each of the 14
-lensing models.  Circles indicate models that use only strong-lensing
+lens models. The vertical blue line shows the constraints from
+SN \tomas\ derived in Section~\ref{sec:Magnification} using the
+MLCS2k2 fitter, with a shaded region marking the total
+uncertainty. Markers with horizontal error bars show the median
+magnification and 68\%\ confidence region from each of the 14 lensing
+models.  Circles indicate models that use only strong-lensing
 constraints, while diamonds denote those that also incorporate
@@
 
-We thank the Hubble Frontier Fields team at STScI
-for their substantial efforts to make the HFF program successful.  In
+We thank the Hubble Frontier Fields team at STScI for their
+substantial efforts to make the HFF program successful.  In
 particular, thanks are due to Matt Mountain for the allocation of
@@
 for curating the excellent and accessible lens model comparison tools.
-We also must thank the CLASH team, led by Marc Postman, for
-observations, catalogs, and high level science products that were of
-significant value for this analysis.
-
-This work utilizes gravitational lensing models produced by PIs
-Bradac, Ebeling, Merten \& Zitrin, Sharon, and Williams funded as part
-of the HST Frontier Fields program conducted by STScI. STScI is
-operated by the Association of Universities for Research in Astronomy,
-Inc. under NASA contract NAS 5-26555. The lens models were obtained
-from the Mikulski Archive for Space Telescopes (MAST).
+We also thank the CLASH team, led by Marc Postman, for observations,
+catalogs, and high level science products that were of significant
+value for this analysis.  Thanks to Jonatan Selsing for helpful
+comments on the manuscript.
+
+This work utilizes gravitational lensing models produced by modeling
+teams that were funded as part of the HST Frontier Fields program
+conducted by STScI. STScI is operated by the Association of
+Universities for Research in Astronomy, Inc. under NASA contract NAS
+5-26555. The lens models were obtained from the Mikulski Archive for
+Space Telescopes (MAST).
 

### 2015-04-17 authors.tex
incorporated AZ comments
cleaned up author ref macros and preamble, updated code   * adjusting figures to reflect the new redshift from the host galaxy
updates including spec fitting fig and text

@@
 \newcommand{\JHU}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 N. Charles St., Baltimore, MD 21218, USA}
-\newcommand{\elsewhere}{St. Elsewhere University.}
 \newcommand{\STScI}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
@@
 \newcommand{\CfA}{Harvard/Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA}
-\newcommand{\Minnesota}{Department of Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA}
+\newcommand{\Minnesota}{School of Physics and Astronomy, University of Minnesota, 116 Church Street SE, Minneapolis, MN 55455, USA}
 \newcommand{\NOAO}{National Optical Astronomical Observatory, Tucson, AZ 85719, USA}
@@
 \newcommand{\HongKong}{Department of Physics, The University of Hong Kong, Pokfulam Road, Hong Kong}
-\newcommand{\Oxford}{Department of Physics, University of Oxford, Clarendon Laboratory, Parks Road, Oxford, UK}
+\newcommand{\Oxford}{Department of Physics, Oxford University, Keble Road, Oxford OX1 3RH, UK}
 \newcommand{\CRAL}{CRAL, Observatoire de Lyon, Universit\'e Lyon 1, 9 Avenue Ch. Andr\'e, F-69561 Saint Genis Laval Cedex, France}
@@
 \newcommand{\affilref}[1]{%
-    \@ifundefined{c@#1}{%
-    	\newcounter{#1}%
-    	\setcounter{#1}{0}%
-    }{}%
-    \ifthenelse{\value{#1} > 0}{%
-      \ref{#1}%
-    }{%
+  \@ifundefined{c@#1}%
+    {\newcounter{#1}%
+     \setcounter{#1}{\theaffilct}%
      \refstepcounter{affilct}%
      \label{#1}%
+     }{}%
   \ref{#1}%
-    	\addtocounter{#1}{1}%
-    }%
  }
@@
 \makeatletter
-\newcommand{\affilreftxt}[2]{%
-    \@ifundefined{c@#1txt}{%
-    	\newcounter{#1txt}%
-    	\setcounter{#1txt}{0}%
-    }{}%
-    \ifthenelse{\value{#1txt} > 0}{%
-    }{%
-      \altaffiltext{\ref{#1}}{#2}%
-    	\addtocounter{#1txt}{1}%
-    }%
+\newcommand*\affilreftxt[2]{%
+  \@ifundefined{c@#1txt}
+    {\newcounter{#1txt}%
+     \setcounter{#1txt}{1}
+     \altaffiltext{\ref{#1}}{#2}
+     }{
+     }
   }
@@
 
-\author{Ryan Foley\altaffilmark{\affilref{IllinoisPhysics},\affilref{IllinoisAstro}}}
+\author{Ryan~J.~Foley\altaffilmark{\affilref{IllinoisPhysics},\affilref{IllinoisAstro}}}
 \affilreftxt{IllinoisPhysics}{\IllinoisPhysics}

### 2015-04-17 snTomas.tex
updates including spec fitting fig and text

@@
 actively star-forming galaxy at a redshift of
-$z=1.5\pm0.2$.  \change{This photo-z was subsequently supported by a
-spectroscopic redshift of $z=1.3457\pm0.0001$, based on emission lines
-consistent with \textcolor{red}{??? the [OII] $\lambda\lambda$ 3726-3729 \AA\ doublet.
-???}}  Another nearby bright galaxy to the East of the SN has a
-spectroscopic redshift of $z=1.742$.  This redshift was determined
-from a spectrum taken with the G141 grism of the HST WFC3-IR camera,
-collected as part of the Grism Lens Amplified Survey from Space
-(GLASS, PI:Treu, PID:13459, \citealt{Treu:2015}). As we will see in
-Sections~\ref{sec:Spectroscopy}
-and \ref{sec:PhotometricClassification}, the SN data are \change{consistent
-with $z=1.3457$,} meaning that the latter galaxy is a background object and
-therefore has no impact on the SN magnification.
+$z=1.5\pm0.2$.  \change{This photo-z was subsequently refined to a
+spectroscopic redshift of $z=1.3457\pm0.0001$, based on optical
+spectroscopy of the host (Mahler et al. in prep.) that shows two
+significant ($>10\sigma$) emission lines at 8740.2 and 8746.7
+Angstroms, consistent with the [OII] $\lambda\lambda$ 3726-3729 \AA\
+doublet.}
+
+The next nearest galaxy detected in HST imaging is \change{2.2\arcsec
+northeast of the SN position}. It has a redshift of $z=1.742$
+determined from a spectrum taken with the G141 grism of the HST
+WFC3-IR camera, collected as part of the Grism Lens Amplified Survey
+from Space (GLASS, PI:Treu, PID:13459, \citealt{Treu:2015}).  As we
+will see in Sections~\ref{sec:Spectroscopy}
+and \ref{sec:PhotometricClassification}, both the spectroscopic and
+photometric data from the SN itself are \change{consistent with the
+redshift of the fainter galaxy at $z=1.3457$, and
+incompatible with $z=1.742$ from this brighter galaxy.}  This means
+that the latter galaxy is a background object and therefore has no
+impact on the SN magnification.
 
@@
 arbitrary units, and the x axis marks wavelength in \AA\ with the
-observer-frame on the bottom and rest-frame on the top.
-The \tomas\ spectrum observed with the
-HST ACS G800L grism is shown in black, overlaid with model fits
-derived from a library of Type Ia templates that have extended
-rest-frame UV coverage.  {\it Top}: The best match is at $z=1.31$ with
-age=$+3$ days, from the normal Type Ia SN 2012cg template when using a
-smooth 3rd-order polynomial to warp the shape of the template
-pseudo-continuum.  When the templates are not warped, an acceptable
-fit can be found with a normal Type Ia at $z=1.31$ (middle) or at
-$z\sim1$ (bottom), although the latter is inconsistent with the host
-galaxy redshift prior and the light curve. No \CCSN\ templates can
-provide a statistically acceptable fit at any redshift, within the age
-constraints imposed by the light curve.}
+observer-frame on the bottom and rest-frame on the top.  The \tomas\
+spectrum observed with the HST ACS G800L grism is shown in black,
+overlaid with model fits derived from a library of Type Ia templates
+that have extended rest-frame UV coverage.  \changeG{The top two panels show
+the best matching templates when using a smooth 3rd-order polynomial
+to warp the shape of the template pseudo-continuum, with the redshift
+fixed at z=1.3457 and then allowed to float as a free parameter.  The
+lower three panels show matches found when the templates are not
+warped, both with and without fixing the redshift.  The bottom panel
+shows the best match in this set, although at $z=0.98$ it is
+inconsistent with the host galaxy redshift prior and the light curve.}
+}
 \end{center}
@@
 template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
-match the observed SED of SN \tomas.  \change{With the redshift fixed
-at $z=1.3457$ we find the best fit is from the normal Type Ia SN
-2014J, with a $\chi^2$ per degree of freedom $\nu$ of
-$\chi^2/\nu=51.8/87$ shown in the top panel of
+match the observed SED of SN \tomas.  \changeG{This approach will find
+templates that have similar abundances and photospheric
+velocities. With the redshift fixed at $z=1.3457$ we find the best fit
+is from the normal Type Ia SN 2014J, with a $\chi^2$ per degree of
+freedom $\nu$ of $\chi^2/\nu=121.8/89$ shown in the top panel of
 Figure~\ref{fig:SpecFit}.  Allowing the redshift as an additional free
@@
 in this case is the normal Type Ia SN 2012cg at $z=1.31$ with
-$\chi^2/\nu=42.1/87$.}
-
+$\chi^2/\nu=98.5/88$ (second panel of Figure~\ref{fig:SpecFit}).}
+
+\changeG{
 Next, we repeat the fitting, but without any warping of the templates
@@
 we only allow each template SED to be scaled in flux coherently at all
-wavelengths.  As shown in Figure~\ref{fig:SpecFit}, we again find that
-when the \change{redshift is allowed as a free parameter the \tomas\
-SED is best matched by a normal Type Ia SN (SN 2011fe) at redshift
-$z=1.31$ with $\chi^2/\nu=102.9/90$.  Fixing the redshift to the
-redshift $z=1.3457$ of the host, we also find the best match is from
-SN 2011fe, with $\chi^2/\nu=133.7/91$. }
-
-Without the continuum warping, an alternative
-fit also arises: the fast-declining (91bg-like) Type Ia SN 2011iv at
+wavelengths, so the fits are more sensitive to the overall color of
+the SED. Fixing the redshift to $z=1.3457$, we find the best match is
+from the normal Type Ia SN 2011fe, though the fit is quite poor, with
+$\chi^2/\nu=313.2/91$ (third panel of Figure~\ref{fig:SpecFit}).  When
+the redshift is allowed as a free parameter the \tomas\ SED is still
+matched best by a SN 2011fe template, now at redshift $z=1.31$ with
+$\chi^2/\nu=240.8/90$ (fourth panel of Figure~\ref{fig:SpecFit}).  }
+
+Without the continuum warping, an alternative fit also arises: the
+fast-declining (91bg-like) Type Ia SN 2011iv at
 $z=0.98\pm0.01$. Formally, this match provides a slightly better fit
-to the unwarped \tomas\ spectrum, although the fit is notably poor at
-$\sim8700$\AA\ where the most significant absorption feature is
-found. Furthermore, a redshift $z\sim1$ is at odds with the host
-galaxy redshift ($z=1.3457$), and we will see in the following section
-that the photometric data is also incompatible with a Type Ia SN at
-$z\sim1.0$.
+to the unwarped \tomas\ spectrum \changeG{($\chi^2/\nu=220.6/90$,
+bottom panel of Figure~\ref{fig:SpecFit}),} although the fit is
+notably poorer at $\sim8700$\AA\ where the most significant absorption
+feature is found. Furthermore, a redshift $z\sim1$ is at odds with the
+spectroscopic redshift of the nearest galaxy ($z=1.3457$), and we will
+see in the following section that the photometric data is also
+incompatible with a Type Ia SN at $z\sim1.0$.
 
@@
 rest-frame days from peak brightness, which is also consistent with
-the observed light curve.
+the observed light curve.  \changeG{Taken together with the host galaxy
+spectroscopic redshift, these fits suggest that SN \tomas\ is a normal
+Type Ia SN at $z=1.3457$ with an SED color close to SN 2011fe, but
+spectral absorption features similar to SN 2014J.}
 
@@
 Financial support for this work was provided to SAR by NASA through grants
-HST-HF-51312 and HST-GO-13386 from the Space Telescope
-Science Institute, which is operated by Associated Universities for
-Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+HST-HF-51312 and HST-GO-13386 from STScI, which is operated by Associated Universities for
+Research in Astronomy, Inc. (AURA), under NASA contract NAS 5-26555.
 
@@
 
+A.Z. acknowledges financial support from NASA through grant
+HST-HF-51334.01-A awarded by STScI and operated by AURA.
+
 {\it Facilities:} \facility{HST (WFC3)}

### 2015-04-17 snTomasCode/specfig.py

@@ -1,116 +1,20 @@
 
-def getchi2(templatedatfile, obsdatfile='SPECTRUM/snTomas_acs_g800l_1d.dat'):
+def getchi2(templatedatfile, obsdatfile='snTomas_acs_g800l_1d.dat'):
     import numpy as np
     from matplotlib import pyplot as pl, ticker
+    import os
+    import sys
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile:
+        thisfile = __file__
+    thisdir = os.path.dirname( thisfile )
+    obsdatfile = thisdir+'/data/spectrum/'+obsdatfile
 
     wave, flux, err, sens = np.loadtxt(obsdatfile, unpack=True)#, usecols=[0,1])
     wavemod,fluxmod= np.loadtxt(templatedatfile, unpack=True)
     chi2 = np.sum( (fluxmod-flux)**2 / err**2 )
     return( chi2 )
-
-def isigclip( valarray, sigclip, igood=[], maxiter=10, thisiter=0 ) :
-    """ find the indices of valarray that
-    survive after a clipping all values more than
-    sigclip from the mean.  recursively iterative """
-    import numpy as np
-    if not type(valarray)==np.ndarray :
-        valarray = np.array( valarray )
-    if not len(igood) : igood = range(len(valarray))
-
-    Ngood = len(igood)
-    mnval = np.mean( valarray[igood] )
-    sigma = np.std( valarray[igood] )
-    igood = np.where( (np.abs(valarray-mnval)<(sigclip*sigma))  )[0]
-
-    # import pdb; pdb.set_trace()
-    if len(igood) == Ngood : return( igood )
-    if thisiter>=maxiter :
-        print("WARNING : Stopping after %i recursions"%maxiter)
-        return( igood )
-    thisiter+=1
-    igood = isigclip( valarray, sigclip, igood=igood, maxiter=maxiter, thisiter=thisiter )
-    return( igood )
-
-
-def binspecdat( wavelength, flux, fluxerr=[], binwidth=10, sigclip=0, sumerrs=False,
-                wstart=0, wend=0 ):
-    """  bin up the given wavelength and flux arrays
-    and return the binned values.
-    binwidth is in the wavelength units of the wavelength
-    array  (typically Angstroms)
-    """
-    import numpy as np
-
-    w,f = wavelength, flux
-    wbinned, fbinned = [], []
-    wbin,fbin,dfbin = np.array([]), np.array([]), np.array([])
-    dw, df = [], []
[…]

### 2015-04-22 TABLE/magnifications.tex
incorporating minor comments on draft, post redshift change   * notably: updated references and minor rearrangement of section 5  and new text in 6.6

@@
 CATS(v1sw)   & \nodata  & 2.62  &   2.44$-$2.80 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
 GLAFIC       & 2.34     & 2.29  &   2.19$-$2.37 &   HFF\tablenotemark{d}; \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{g} \\

### 2015-04-22 snTomas.tex
incorporating minor comments on draft, post redshift change   * notably: updated references and minor rearrangement of section 5  and new text in 6.6

@@
 appearance.  Labeled ellipses mark the nearest galaxies and their
-redshift constraints: a photometric redshift for the most likely host
-galaxy is marked in blue, and the spectroscopic redshift for a
-background galaxy is given in yellow. The bottom panel is constructed
-from all HFF F814W imaging taken while the SN was detectable, and
-marks the SN location with an arrow.  (Left panel image credit: NASA,
-ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team (STScI))
-}
+\changeG{spectroscopic} redshift constraints, with the most likely host
+galaxy marked in blue, and a background galaxy in yellow. The bottom
+panel is constructed from all HFF F814W imaging taken while the SN was
+detectable, and marks the SN location with an arrow.  (Left panel
+image credit: NASA, ESA, and J. Lotz, M. Mountain, A. Koekemoer, and
+the HFF Team (STScI)) }
 \end{center}
@@
 velocities. With the redshift fixed at $z=1.3457$ we find the best fit
-is from the normal Type Ia SN 2014J, with a $\chi^2$ per degree of
-freedom $\nu$ of $\chi^2/\nu=121.8/89$ shown in the top panel of
-Figure~\ref{fig:SpecFit}.  Allowing the redshift as an additional free
-parameter, we still find results that are consistent with the SNID
-fits and $<2\sigma$ from the host galaxy redshift: $z=1.31\pm0.02$ and
-a phase of $0\pm3$ rest-frame days. The best-fitting spectral template
-in this case is the normal Type Ia SN 2012cg at $z=1.31$ with
-$\chi^2/\nu=98.5/88$ (second panel of Figure~\ref{fig:SpecFit}).}
+is a spectrum from the normal Type Ia SN 2014J \citep{Foley:2014},
+with a $\chi^2$ per degree of freedom $\nu$ of $\chi^2/\nu=121.8/89$
+shown in the top panel of Figure~\ref{fig:SpecFit}.  Allowing the
+redshift as an additional free parameter, we still find results that
+are consistent with the SNID fits and $<2\sigma$ from the host galaxy
+redshift: $z=1.31\pm0.02$ and a phase of $0\pm3$ rest-frame days. The
+best-fitting spectral template in this case is the normal Type Ia SN
+2012cg \citep{Amanullah:2015} at $z=1.31$ with $\chi^2/\nu=98.5/88$
+(second panel of Figure~\ref{fig:SpecFit}).}
 
@@
 the SED. Fixing the redshift to $z=1.3457$, we find the best match is
-from the normal Type Ia SN 2011fe, though the fit is quite poor, with
+from the normal Type Ia SN 2011fe \citep{Mazzali:2014}, though the fit is quite poor, with
 $\chi^2/\nu=313.2/91$ (third panel of Figure~\ref{fig:SpecFit}).  When
@@
 Without the continuum warping, an alternative fit also arises: the
-fast-declining (91bg-like) Type Ia SN 2011iv at
+fast-declining (91bg-like) Type Ia SN 2011iv \citep{Foley:2012b} at
 $z=0.98\pm0.01$. Formally, this match provides a slightly better fit
@@
 
-\section{Light Curve Fitting}
-\label{sec:LightCurveFitting}
-
-With the type and redshift securely defined as a normal
-Type Ia SN at $z=1.3457$, we now turn to fitting the light curve with
-Type Ia templates to measure the distance modulus.  Here we use two
-independent light curve fitters: the SALT2 model described
-above and the MLCS2k2 model \citep{Jha:2007}.
+\section{Distance Modulus and Magnification}
+\label{sec:DistanceAndMagnification}
+
+With the type and redshift securely defined as a normal Type Ia SN at
+$z=1.3457$, we now turn to fitting the light curve with Type Ia
+templates to measure the distance modulus \changeG{ and then derive
+the gravitational lensing magnification.  In this process, we would
+like to avoid introducing systematic uncertainties inherent to any
+assumed cosmological model \citep[e.g.][]{Nordin:2014}.  To that end,
+we follow \citealt{Patel:2014} and define the magnification by
+comparing the measured distance modulus of SN \tomas\ against an
+average distance modulus derived from a ``control sample'' of unlensed
+Type Ia SNe at similar redshift.  This allows us to make only the
+minimal assumption that the redshift-distance relationship for Type Ia
+SN is smooth and approximately linear over a small redshift span,
+which should be true for any plausible cosmological model.  
+}
 
@@
 
-With both fitters we find light curve shape and color parameters that
-are fully consistent with a normal Type Ia SN.  For SALT2, with the
+\subsection{Light Curve Fitting}
+\label{sec:LightCurveFitting}
+
+\changeG{
+As in \citealt{Patel:2014}, we derive a distance modulus for
+SN \tomas\ and all SNe in our control sample using two independent
+light curve fitters: the SALT2 model described above and the MLCS2k2
+model \citep{Jha:2007}.  }  With both fitters we find light curve
+shape and color parameters for \tomas\ that are fully consistent with
+a normal Type Ia SN.  For SALT2, with the
 \change{redshift fixed at $z=1.3457$, we find a light curve shape
@@
 
-\subsection{Distance Modulus}
-\label{sec:DistanceModulus}
-
-As in \citealt{Patel:2014}, we derive a distance modulus (dm)\footnote{We use 'dm' to
-indicate the distance modulus to avoid confusion, reserving the symbol
-$\mu$ to refer to the lensing magnification. This 'dm' is a standard
-distance modulus, defined as ${\rm dm}=5\log_{10}d_L+25$, where $d_L$
-is the luminosity distance in Mpc.} while ignoring the
-effects of gravitational lensing, so that we can later use it to
-derive a direct measurement of the magnification.
-\change{The MLCS2k2 fitter returns $\rm{dm}_{\rm MLCS2k2}$ directly, as it is defined as one of the free parameters in the model.
-To derive dm from} the SALT2 fit
-we use
+\changeG{
+ The MLCS2k2 fitter returns a distance
+modulus\footnote{We use 'dm' to indicate the distance modulus to avoid
+confusion, reserving the symbol $\mu$ to refer to the lensing
+magnification. This 'dm' is a standard distance modulus, defined as
+${\rm dm}=5\log_{10}d_L+25$, where $d_L$ is the luminosity distance in
+Mpc.}  $\rm{dm}_{\rm MLCS2k2}$ directly, as it is defined to be one of
+the free parameters in the model.} To derive dm from the SALT2 fit, we
+use
 
@@
 however that the uncertainty on the control sample value at $z=1.3457$
-is only 0.06 mag, smaller than the intrinsic dispersion because it
-reflects only our measurement error on the mean distance modulus of
-the population.  The distance moduli derived from the SALT2 and
-MLCS2k2 light curve fitters are fully consistent within the
-uncertainties.
-
-\subsection{Host Galaxy Mass Correction}
+is only 0.06 mag, smaller than the intrinsic dispersion \changeG{of
+any single SN} because it reflects our measurement error on the mean
+distance modulus of the population.  The distance moduli derived from
+the SALT2 and MLCS2k2 light curve fitters are fully consistent within
+the uncertainties.
+
+\subsubsection{Host Galaxy Mass Correction}
 \label{sec:HostGalaxyMassCorrection}
@@
 significant evidence that a non-zero mass step is required at
-$z>1$ \citep{Rigault:2013,Shafer:2014,Betoule:2014}.  Given the
+$z>1$ \citep{Suzuki:2012,Shafer:2014,Betoule:2014}.  Given the
 absence of a clear physical model and the lack of empirical support
@@
 
-\subsection{Magnification}
-\label{sec:Magnification}
-
-To measure the lensing magnification, we would like to avoid
-introducing systematic uncertainties inherent to any assumed
-cosmological model \citep[e.g.][]{Nordin:2014}.  To that end, we
-follow \citealt{Patel:2014} and define the magnification by comparing
-the measured distance modulus of SN \tomas\ against an average
-distance modulus derived from a ``control sample'' of unlensed Type Ia
-SN at similar redshift.  This allows us to make only the minimal
-assumption that the redshift-distance relationship for Type Ia SN is
-smooth and approximately linear over a small redshift span, which
-should be true for any plausible cosmological model.
+\subsection{Control Sample Comparison}
+\label{sec:ControlSampleComparison}
 
@@
 lens models. The vertical blue line shows the constraints from
-SN \tomas\ derived in Section~\ref{sec:Magnification} using the
+SN \tomas\ derived in Section~\ref{sec:DistanceAndMagnification} using the
 MLCS2k2 fitter, with a shaded region marking the total
@@
 alongside the observed magnification of SN \tomas, derived in
-Section~\ref{sec:Magnification}.  This comparison shows that these 14
+Section~\ref{sec:DistanceAndMagnification}.  This comparison shows that these 14
 models are largely consistent with each other. Naively treating each
@@
 changing the cosmological parameter within the range of current
-acceptable cosmologies \citep[e.g.][]{Hinshaw:2013,Planck:2015},
+acceptable cosmologies \citep[e.g.][]{Hinshaw:2013,Planck-Collaboration:2015},
 introduces a magnification uncertainty that is comparable in magnitude
@@
 
-\subsection{Foreground Dust}
+\subsection{Foreground Dust and SN Color}
 \label{sec:ForegroundDust}
@@
 magnification of \tomas\ and the mean of the model predictions.
+
+\changeG{
+Although the very blue color of SN \tomas\ is helpful to rule out dust
+as a possible explanation for the observed small systematic bias, it
+is possible that this very blue color is itself leading to a bias in
+the distance measurement.  \citet{Scolnic:2014b} measured a small bias
+in the SALT2 fitter for Type Ia SNe that have a color parameter
+derived from the light curve fit $c<-0.1$ (see, e.g., their Figure 10
+and Section 5.1). For \tomas\ we have measured $c=-0.13$, which would
+correspond to a bias of roughly $+0.05$ mag in the SALT2 distance
+measurement.  If we were to apply a $-0.05$ mag correction to the
+distance modulus from the SALT2 fit, then this would increase the
+inferred magnification to $\mu_{\rm SALT2}=2.08\pm0.36$.  This would
+still be consistent with the mild tension apparent from the MLCS2k2
+fit, though with a decrease in significance. 
+}
 
@@
 
-J.M.D acknowledges support of the consolider project CAD2010-00064 and
+J.M.D acknowledges support of the consolider project CSD2010-00064 and
 AYA2012-39475-C02-01 funded by the Ministerio de Economia y

### 2015-04-22 snTomasCode/hubble_fig.py

@@ -1,7 +1,7 @@
 def plot_hubble_fig( fitter='both', showlcdm=False,
-                     zsn=1.31,
+                     zsn=1.3457, presfig=False,
                      datfilename='data/distances/z135/hubblefig.dat'):
-    from pytools import plotsetup, colorpalette as cp
+    from pytools import plotsetup, colorpalette as cp, cosmo
     from astropy.io import ascii
     import numpy as np
     from scipy import optimize as scopt
@@ -10,7 +10,11 @@ def plot_hubble_fig( fitter='both', showlcdm=False,
     import os
     import sys
 
-    from pytools import cosmo
+    if presfig :
+        fig = plotsetup.presfig( )
+    else :
+        fig = plotsetup.halfpaperfig( )
+
 
     dmint_mlcs=0.08 # intrinsic scatter in SNIa luminosities for MLCS2k2 (Jha:2007)
     dmint_salt=0.08 # intrinsic scatter in SNIa luminosities for SALT2 (Conley:2011)
@@ -46,7 +50,6 @@ def plot_hubble_fig( fitter='both', showlcdm=False,
     iscp = np.where( hubbledat['survey']=='scp')
     igoods = np.where( hubbledat['survey']=='goods')
     icandels = np.where( hubbledat['survey']=='candels')
-    fig = plotsetup.halfpaperfig( )
     pl.clf()
     if fitter.lower()=='both':
         ax1 = fig.add_subplot(2,1,1)
@@ -63,14 +66,14 @@ def plot_hubble_fig( fitter='both', showlcdm=False,
         ax1.errorbar( z[iscp], dm_mlcs[iscp], dm_mlcs_err[iscp], ls=' ', marker='o', capsize=0, color=cp.lightgrey, ecolor=cp.darkgrey )
         ax1.errorbar( z[icandels], dm_mlcs[icandels], dm_mlcs_err[icandels], ls=' ', marker='^', capsize=0, color=cp.lightgrey, ecolor=cp.darkgrey )
         ax1.errorbar( zTomas, dmTomas_mlcs, dmerrTomas_mlcs, zerrTomas, marker='D',
-                      color=cp.teal, capsize=0, ls=' ')
+                      color=cp.lightblue, capsize=0, ls=' ')
 
     if fitter.lower()[:5] in ['both','salt'] :
[…]

### 2015-04-30 TABLE/magnifications.tex
included tension vs N fig, rearranging sec 6

--- 2015-04-17 TABLE/magnifications.tex
@@
-\begin{deluxetable*}{p{0.7in}cccp{1.4in}p{2.5in}}
-\tablecolumns{6}
+\clearpage
+\begin{turnpage}
+\begin{deluxetable*}{p{0.62in}rrrrcccp{1.3in}p{2.9in}}
+\tablecolumns{10}
 \tablecaption{Predicted magnifications for SN \tomas\ from lens models.\label{tab:PredictedMagnifications}}
-\tablehead{ \colhead{Model} & \colhead{Best\tablenotemark{a}} & \colhead{Median\tablenotemark{b}} & \colhead{68\% Conf. Range\tablenotemark{c}} & \colhead{References} & \colhead{Description}}
+\tablehead{ \colhead{Model} & \colhead{Sys\tablenotemark{a}} & \colhead{Im\tablenotemark{a}} & 
+            \colhead{Spec\tablenotemark{b}} & \colhead{Phot\tablenotemark{b}} & 
+            \colhead{Best\tablenotemark{c}} & \colhead{Median\tablenotemark{d}} & 
+            \colhead{68\% Conf. Range\tablenotemark{e}} & \colhead{References} & \colhead{Description}}
 \startdata
-Sharon(v1)   & 2.56     & 2.60  &   2.44$-$2.78 &   HFF\tablenotemark{d}  & LENSTOOL\tablenotemark{e} parametric, strong-lensing based model\\
-Sharon(v2)   & 2.74     & 2.59  &   2.42$-$2.85 &   HFF\tablenotemark{d}; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.
+Sharon(v1)     & 17 &  60 & 2 & 14 & 2.56     & 2.60  &   2.44$-$2.78 &   HFF\tablenotemark{f}  & LENSTOOL\tablenotemark{g} parametric, strong-lensing based model\\
+Sharon(v2)     & 17 &  60 & 2 & 14 & 2.74     & 2.59  &   2.42$-$2.85 &   HFF; \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model.
 Includes cosmological parameter variations in uncertainty estimates.\\
-CATS(v1)     & 2.28     & 2.29  &   2.25$-$2.34 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team implementation of LENSTOOL parametric strong-lensing based model.\\
-CATS(v1sw)   & \nodata  & 2.62  &   2.44$-$2.80 &   HFF\tablenotemark{d}; \citealt{Richard:2014} &  CATS\tablenotemark{f} team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)     & \nodata  & 3.42  &   3.27$-$3.58 &   HFF\tablenotemark{d}; \citealt{Jauzac:2014} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
-GLAFIC       & 2.34     & 2.29  &   2.19$-$2.37 &   HFF\tablenotemark{d}; \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{g} \\
-Zitrin-NFW   & 2.09     & 2.29  &   2.07$-$2.52 &   HFF\tablenotemark{d}; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{h} profiles for galaxies and NFW\tablenotemark{i} profiles for dark matter halos.\\
-Zitrin-LTM   & 2.67     & 2.99  &   2.61$-$3.77 &   HFF\tablenotemark{d}; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac(v1)   & 3.19     & 2.48  &   2.31$-$2.66 &   HFF\tablenotemark{d}; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{j} : Free-form, strong+weak-lensing based model.
+CATS(v1)       & 50 & 151 & 4 & 0  & 2.28     & 2.29  &   2.25$-$2.34 &   HFF; \citealt{Richard:2014} &  CATS\tablenotemark{h} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS(v1sw)     & 24 &  67 & 3 & 12 & \nodata  & 2.62  &   2.44$-$2.80 &   HFF; \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
+CATS(v2)       & 17 &  60 & 2 & 14 & \nodata  & 3.42  &   3.27$-$3.58 &   HFF; \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+GLAFIC         & 15 &  47 & 3 & 11 & 2.34     & 2.29  &   2.19$-$2.37 &   HFF; \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{i} \\
+Zitrin-NFW     & 10 &  44 & 2 & 0  & 2.09     & 2.29  &   2.07$-$2.52 &   HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{j} profiles for galaxies and NFW\tablenotemark{k} profiles for dark matter halos.\\
+Zitrin-LTM     & 10 &  44 & 2 & 0  & 2.67     & 2.99  &   2.61$-$3.77 &   HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
+Bradac(v1)     & 16 &  56 & 2 & 14 & 3.19     & 2.48  &   2.31$-$2.66 &   HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{l} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
-Bradac(v2)   & 2.23     & 2.26  &   2.30$-$2.23 &   \citealt{Wang:2015} & Updated version of the {\tt SWUnited}\tablenotemark{j} model with new strong-lensing constraints from HFF imaging.
+Bradac(v2)     & 10 &  40 & 2 & 8  & 2.23     & 2.26  &   2.30$-$2.23 &   \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Williams     & 2.70     & 2.81  &   1.65$-$5.54 &   HFF\tablenotemark{d} & {\tt GRALE}\tablenotemark{k} : Free-form strong-lensing model using a genetic algorithm.  \\
-Merten       & 2.33     & 2.24  &   2.04$-$2.92 &   HFF\tablenotemark{d}; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{l} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam          & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{m} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Diego\tablenotemark{n}  & \nodata  & 1.80  &   1.44$-$2.16 & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{m} model, using a different set of strong-lensing constraints and redshifts.
+Williams       & 16 &  56 & 2 & 14 & 2.70     & 2.81  &   1.65$-$5.54 &   HFF & {\tt GRALE}\tablenotemark{m} : Free-form strong-lensing model using a genetic algorithm.  \\
+Merten         & 25 &  72 & 7 & 18 & 2.33     & 2.24  &   2.04$-$2.92 &   HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{n} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Lam(v1)        & 21 &  65 & 4 & 17 & \nodata  & 2.79  &   2.42$-$3.16 &   \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{o} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Lam(v2)        & 10 &  32 & 5 & 5  & 1.86     & 1.91  &   1.54$-$2.28 &   \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{p} models for galaxy mass.\\
+Diego$^{\rm q}$ & 15 &  48 & 4 & 11 & \nodata  & 1.80  &   1.44$-$2.16 & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.
 \enddata
-\tablenotetext{a}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
-\tablenotetext{b}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
-\tablenotetext{c}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
-\tablenotetext{d}{Lens models with the reference code ``HFF'' were produced as part of the 
+\tablenotetext{a}{Number of multiply imaged systems used as strong-lensing constraints.}
+\tablenotetext{b}{Number of multiply imaged systems with spectroscopic redshifts.}
+\tablenotetext{c}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
+\tablenotetext{d}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
+\tablenotetext{e}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
+\tablenotetext{f}{Lens models with the reference code ``HFF'' were produced as part of the 
 Hubble Frontier Fields lens modeling
@@
 }
-\tablenotetext{e}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
-\tablenotetext{f}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
-\tablenotetext{g}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{h}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
-\tablenotetext{i}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
-\tablenotetext{j}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
-\tablenotetext{k}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
-\tablenotetext{l}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{m}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
-\tablenotetext{n}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
+\tablenotetext{g}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
+\tablenotetext{h}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
+\tablenotetext{i}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{j}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
+\tablenotetext{k}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
+\tablenotetext{l}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
+\tablenotetext{m}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
+\tablenotetext{n}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
+\tablenotetext{o}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
+\tablenotetext{p}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
+\tablenotetext{q}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
 No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.
@@
 \end{deluxetable*}
+\end{turnpage}
+\clearpage
+\global\pdfpageattr\expandafter{\the\pdfpageattr/Rotate 90}

### 2015-04-30 TABLE/magnifications2.tex
included tension vs N fig, rearranging sec 6

\begin{deluxetable*}{p{0.62in}rrrrp{1.4in}p{2.5in}}
\tablecolumns{7}
\tablecaption{\changeR{Tested lens models for Abell 2744.\label{tab:LensModels}}}
\tablehead{ \colhead{Model} & \colhead{N$_{\rm sys}$\tablenotemark{a}} & \colhead{N$_{\rm im}$\tablenotemark{b}} & 
            \colhead{N$_{\rm spec}$\tablenotemark{c}} & \colhead{N$_{\rm phot}$\tablenotemark{d}} & 
            \colhead{References} & \colhead{Description}}
\startdata
Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF\tablenotemark{e}  & LENSTOOL\tablenotemark{f} parametric, strong-lensing based model\\
Sharon(v2)     & 17 &  60 & 2 & 14 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
CATS(v1)       & 50 & 151 & 4 & 0  &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
CATS(v1sw)     & 24 &  67 & 3 & 12 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
CATS(v2)       & 17 &  60 & 2 & 14 &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
GLAFIC         & 15 &  47 & 3 & 11 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{i} profiles for galaxies and NFW\tablenotemark{j} profiles for dark matter halos.\\
Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{k} : Free-form, strong+weak-lensing based model. Errors from bootstrap resampling only weak-lensing constraints.\\
Bradac(v2)     & 10 &  40 & 2 & 8  &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging. Errors from bootstrap resampling only strong-lensing constraints.\\
Williams       & 16 &  56 & 2 & 14 &  HFF & {\tt GRALE}\tablenotemark{l} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten         & 25 &  72 & 7 & 18 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{m} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{n} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{o} models for galaxy mass.\\
Diego$^{\rm p}$ & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.
\enddata
\tablenotetext{a}{Number of multiply imaged systems used as strong-lensing constraints.}
\tablenotetext{b}{Total number of multiple images used.}
\tablenotetext{c}{Number of multiply imaged systems with spectroscopic redshifts.}
\tablenotetext{d}{Number of multiply imaged systems with photometric redshifts.}
\tablenotetext{e}{Lens models with the reference code ``HFF'' were produced as part of the 
Hubble Frontier Fields lens modeling
program, using arcs identified in HST archival imaging from
\citealt{Merten:2011}, spectroscopic redshifts from
\citealt{Richard:2014}, and ground-based imaging from
\citealt{Cypriano:2004,Okabe:2008,Okabe:2010a,Okabe:2010b}. Details on
the model construction and an interactive model magnification web interface 
are available at
\url{http://archive.stsci.edu/prepds/frontier/lensmodels/} 
}
\tablenotetext{f}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
\tablenotetext{g}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
\tablenotetext{h}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{i}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{j}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{k}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
\tablenotetext{l}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
\tablenotetext{m}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
\tablenotetext{n}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
\tablenotetext{o}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
\tablenotetext{p}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.
}
\end{deluxetable*}

\begin{deluxetable}{p{0.62in}ccc}
\tablecolumns{4}
\tablecaption{\changeR{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}}
\tablehead{ \colhead{Model\tablenotemark{a}} & 
            \colhead{Best\tablenotemark{b}} & \colhead{Median\tablenotemark{c}} & 
            \colhead{68\% Conf. Range\tablenotemark{d}}}
\startdata
Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\
Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\
Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28 \\
Diego$^{\rm *}$ &  \nodata  & 1.80  &   1.44$-$2.16 \\
\enddata
\tablenotetext{a}{Models marked by an asterisk were not part of the blind test, as they include modifications made after the measured magnification of the SN was known.}  
\tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{c}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
\tablenotetext{d}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
\end{deluxetable}

### 2015-04-30 snTomas.tex
included tension vs N fig, rearranging sec 6

@@
 measurement of the magnification against predicted magnifications
-from 14 lens models, representing a broad range of
-methodologies and incorporating a variety of strong- and weak-lensing
-constraints.  The models are collectively fairly accurate: 6 of the
-models deliver median magnifications that are consistent with the
-measured $\mu$ to within the 1$\sigma$ uncertainties.  However, the
-models are systematically biased to higher values: \change{all but
-one} of the tested models yield a median magnification higher than the
-observed $\mu$, and \change{6 of the models are $\geq1.5\sigma$}
-above the measured magnification.  We evaluate possible causes for
-this mild bias, considering both modeling errors and
-misinterpretation of the SN data. Although we find no single
-explanation that can resolve this, we \change{ highlight several ways
-that lens models can deliver more realistic uncertainties, such as
-incorporating errors from assumed cosmological parameters and allowing
-greater flexibility in the form of the cluster mass distribution.  A
-more robust evaluation of systematic biases could be achieved with
-further cooperative lens model comparisons using a larger sample of
-lensed Type Ia SNe and cluster lensing simulations.}
+from \changeR{15 lens models developed by 8 independent groups},
+representing a broad range of methodologies and incorporating a
+variety of strong- and weak-lensing constraints.  The models are
+collectively fairly accurate: 8 of the models deliver median
+magnifications that are consistent with the measured $\mu$ to within
+the 1$\sigma$ uncertainties.  \changeR{However, the models exhibit a
+subtle systematic bias: all of the models that disagree with the SN by
+more than $1\sigma$ are {\it higher} than the measured value}
+and \change{6 of these models are $\geq1.5\sigma$} above the measured
+magnification.  We evaluate possible causes for this mild
+bias, \changeR{and reject explanations that invoke modeling errors or
+misinterpretation of the SN data. We conclude that -- at least for
+this single line of sight -- the most accurate models are those with
+(1) stringent quality cuts for strong-lensing constraints and (2)
+relatively flexible model design}. \change{A more robust evaluation of
+systematic biases could be achieved with further cooperative lens
+model comparisons using a larger sample of lensed Type Ia SNe as well
+as cluster lensing simulations.}
 \end{abstract}
 
-\keywords{ supernovae: general, supernovae: individual: HFF14Tom, galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, gravitational lensing: strong, gravitational lensing: weak  }
+\keywords{ supernovae: general, supernovae: individual: HFF14Tom, 
+galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, 
+gravitational lensing: strong, gravitational lensing: weak  }
 
@@
 using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom
-panel).
+panel).  \changeR{Grey lines with shading show a linear fit to the
+unlensed control sample is shown, anchored at the redshift of
+SN \tomas, with fit parameters given at the top.  The derived
+magnification is reported at the bottom of each panel.}
 \label{fig:MagnificationMeasurement} }
@@
 collection of all imaging and spectroscopic data available at the
-time.  In response to this opportunity, five teams generated eight
+time.  In response to this opportunity, five teams generated seven
 models for Abell 2744.  These models necessarily relied on
@@
 magnification estimates and uncertainties from each model for any
-given redshift and position.  In this work we also consider three
-additional models that were created later, taking advantage of new
+given redshift and position.  In this work we also consider 8
+additional models that were created later.  \changeR{Some of these are
+updates of the original models produced in response to the lens
+modeling call,  and some of them include new
 multiply-imaged galaxies discovered in the HFF imaging as well as new
-redshifts for lensed background galaxies.
-
-\input{TABLE/magnifications}
+redshifts for lensed background galaxies.  Magnifications derived from
+several of these later models are also available on the interactive
+web tool hosted by STScI.  The full list of models and details on
+their construction are given in Table~\ref{tab:LensModels}.}
+
+\input{TABLE/magnifications2}
 
@@
 uncertainty. Markers with horizontal error bars show the median
-magnification and 68\%\ confidence region from each of the 14 lensing
+magnification and 68\%\ confidence region from each of the 15 lensing
 models.  Circles indicate models that use only strong-lensing
@@
 additional input constraints, including new multiply imaged systems
-and redshifts.  The eight models shown in black at the top are from
+and redshifts.  Points with magenta outline indicate ``unblind''
+models, which were generated after the magnification of the SN was
+known. The eight models shown in black at the top are from
 the ``parametric'' family, and the six in green at the bottom are
 ``free-form.''  The grey dashed line marks the unweighted mean for the
-set of all models, at $\mu=2.53$.
+set of all models, at $\mu=2.5$.
 \label{fig:lensingtest} }
@@
 
-Table~\ref{tab:PredictedMagnifications} lists the 14 models,
-giving for each one the predicted magnification and uncertainty for a
-source at \change{$z=1.3457$} and at the position of \tomas.  These models
-represent a broad sampling of the techniques and assumptions that can
-be applied to the modeling of mass distributions in galaxy clusters. A
-rigorous comparison of these disparate lens modeling techniques is
-beyond the scope of this work. Table~\ref{tab:PredictedMagnifications}
-includes a brief description of each model, but for a complete
-discussion of the methodology the reader is referred to the listed
-references.
+\changeR{
+Table~\ref{tab:PredictedMagnifications} gives each model's predicted}
+magnification and uncertainty for a source at \change{$z=1.3457$} and
+at the position of \tomas.  These models represent a broad sampling of
+the techniques and assumptions that can be applied to the modeling of
+mass distributions in galaxy clusters. A rigorous comparison of these
+disparate lens modeling techniques is beyond the scope of this
+work. Table~\ref{tab:PredictedMagnifications} includes a brief
+description of each model, but for a complete discussion of the
+methodology the reader is referred to the listed references.
 
@@
 their quoted uncertainties), one would get a mean for the full sample
-of \change{$\mu=2.53\pm0.38$.  This is separated from the observed SN
-magnification by $\delta\mu/\mu=25\%$, which is just over a
+of \change{$\mu=2.5\pm0.4$.  This is separated from the observed SN
+magnification by $\delta\mu/\mu=23\%$, which is approximately a
 1$\sigma$ difference.}
@@
 ``simply-parameterized'' would be more accurate, though we adopt the
-more common usage here.}  models on top and six {\it free-form} models
+more common usage here.}  models on top and seven {\it free-form} models
 on the bottom.  Broadly speaking, the parametric models use
@@
 size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
-the Williams model (using GRALE), which has the largest, and possibly the
-most realistic uncertainties is able to account for mass sheet
-degeneracy by introducing a free parameter in the reconstruction that
-represents an arbitrarily scaled mass sheet, with normalization to
-be chosen by the genetic algorithm.  More complex degeneracies are
-also accounted for in this model through the use of basis
+the Williams model (using GRALE), which has the largest uncertainties
+is able to account for mass sheet degeneracy by introducing a free
+parameter in the reconstruction that represents an arbitrarily scaled
+mass sheet, with normalization to be chosen by the genetic algorithm.
+More complex degeneracies are also accounted for in this model through
+the use of basis
 functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
@@
 also use weak-lensing measurements (diamonds).  Nine of the models
-were constructed using only pre-HFF data (open symbols), while five
-others added new multiply-imaged systems and redshifts.
+were constructed using only pre-HFF data (open symbols), while six
+others added new multiply-imaged systems and redshifts (filled symbols).
+For twelve of these models the SN magnification qualifies as a true
+``blind test'', as they were completed before the SN \tomas\
+magnification measurement was known.  The remaining three models
+(Bradac-v2, Lam-v2, and Diego) are technically not blind, although
+none of these modelers used the SN magnification as a constraint, and
+the modelers did not have access to the final SN magnification value
+when constructing their model.
 
@@
 lens models overall are delivering consistent and fairly accurate
-estimates of the magnification.  Six of the tested models
-(CATSv1, GLAFIC, Zitrin-NFW, Bradac(v2), Merten, Diego) report a median
-value that falls within the 1$\sigma$ uncertainty range of the
-measured magnification, and two of the free-form models (Williams,
-Diego) report uncertainties that overlap the central $\mu$ as measured
-from both of the SN light curve fitters.  Furthermore, the scatter
-amongst models provides a reasonable estimate of the magnification
-uncertainty.
+estimates of the magnification.  Seven of the tested models (CATS(v1),
+GLAFIC, Zitrin-NFW, Merten, Bradac(v2), Lam(v2), Diego) report a
+median value that falls within the 1$\sigma$ uncertainty range of the
+measured magnification, and three of the free-form models (Williams,
+Lam(v2), Diego) report uncertainties that overlap the central $\mu$ as
+measured from both of the SN light curve fitters.  Furthermore, the
+scatter amongst models provides a reasonable estimate of the
+magnification uncertainty.
 
@@
 of \citetalias{Patel:2014} and \citet{Nordin:2014}.  The fact that the
-model predictions are collectively within $2\sigma$ of the observed
+model predictions are collectively within $1\sigma$ of the observed
 magnification is especially encouraging for these Abell 2744
 models. This is a merging cluster with a complex mass distribution,
-and most of the models we are evaluating are preliminary products,
+and many of the models we are evaluating are preliminary products,
 generated quickly and without access to the rich data from the
@@
 However, beyond this first-order agreement, there is a small
-systematic bias apparent. All of the lens models \change{except one}
+systematic bias apparent. All but two of the lens models
 return median magnifications that are {\it higher} than the observed
@@
 It is important to emphasize that SN \tomas\ only samples a single
-sight-line through the cluster, so any conclusions to be drawn from
-this analysis are necessarily limited.  Nevertheless, a systematic
-shift common to all models is surprising, given the wide range of
+line of sight through the cluster, and this bias to higher
+magnifications is minor.  Nevertheless, a systematic
+shift of this nature is surprising, given the wide range of
 modeling strategies, input data, and physical assumptions represented
@@
 bias.
+
+\subsection{Possible Errors in Supernova Interpretation}
+\label{sec:SupernovaErrors}
+
+\changeR{Before examining the lens models or the cluster, let us first
+consider whether we might have misinterpreted the data on the SN
+itself.}
+
+\subsubsection{Redshift Error}
+\label{sec:RedshiftError}
+
+If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
+were incorrect, then one would derive a different value for the
+magnification, both from the SN measurement and the lens model
+predictions.  Conceivably, this could resolve the tension between the
+measurement and the models.  It is often the case in SN surveys that
+redshifts are assigned based on a host galaxy association, typically
+inferred from the projected separation between the SN and nearby
+galaxies.  In this case the redshift \change{is strongly supported} by
+evidence from the SN
+itself: we find a consistent redshift from both the SN spectrum
+(Section~\ref{sec:SpecRedshift}) and the light curve
+Section~\ref{sec:PhotometricClassification}, which are both within the
+$1\sigma$ range of the photometric redshift for the nearest detected
+galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
+picture, so the evidence strongly disfavors any redshift that is
+significantly different from $z=1.35$.
+
+We have adopted the \change{most precise redshift of $z=1.3457$ from
+the host galaxy as our baseline for the magnification comparison.  If
+instead we adopt the spectroscopic redshift from the SN itself
+($z=1.31$; Section~\ref{sec:SpecRedshift}) then we find no significant
+change in the inferred magnifications or in the suggestion of a small
+systematic bias.}
+
+\subsubsection{Foreground Dust and SN Color}
+\label{sec:ForegroundDust}
+
+All SN sight-lines must intersect some amount of foreground dust from
+the immediate circumstellar environment, the host galaxy, and the
+intergalactic medium (IGM). In the case of SN \tomas\ one might posit
+some dust extinction from the intra-cluster medium (ICM) of Abell
+2744, although measurements of rich clusters suggest that the ICM has
+only a negligible dust
+content \citep{Maoz:1995,Stickel:2002,Bai:2007}.  When fitting
+the \tomas\ light curve we account for dust by including corrections
+that modify the inferred luminosity distance based on the SN color.
+If after applying these dust corrections we are still {\it
+underestimating} the effect of dust along this sight-line, then the SN
+would appear more dim, the inferred distance modulus would be higher,
+and the measured magnification would be reduced -- consistent with the
+discrepancy we observe.
+
+In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
+the blue end of the normal range of Type Ia SN colors.  With the SALT2
+fitter we measured a color parameter $c=-0.127\pm0.025$, and with
+MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
+V}=0.011\pm0.025$ magnitudes.  These colors are tightly constrained,
+as we are fitting to photometry that covers a rest-frame wavelength
+range from $\sim3500-7000$\AA\ and extends to $\sim$30 days past
+maximum brightness.  This leaves little room for the luminosity
+measurement to be biased by dust, as the dimming of \tomas\ would also
+necessarily be accompanied by some degree of reddening.
+
+Nevertheless, one might suppose that a bias could be introduced if we
+have adopted incorrect values for the color correction parameter
+$\beta$ or extinction law $R_V$ in the SALT2 and MLCS2k2 fits,
+respectively.  The appropriate value to use for this color correction
+and how it affects inferences about the intrinsic scatter in Type Ia
+SN luminosities is a complex question that is beyond the scope of this
+work \citep[see
+e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
+However, we can already rule this out as a solution for the
+magnification discrepancy.  Our error on the \tomas\ distance modulus
+already includes an uncertainty in the extinction law and a related
+error to account for the intrinsic luminosity scatter. These are well
+vetted parameters, based on observations of $\sim500$ SNe extending
+to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason
+to propose that SN \tomas\ is uniquely affected by a peculiar type of
+dust.  Thus, any change in the color correction applied to SN \tomas\
+would require the same adjustment to be applied to the unlensed SNe at
+similar redshift that make up our comparison sample, largely negating
+the effect on the inferred magnification.
+
+The traditional color corrections as formalized in SN light curve
+fitters are designed to account for a dust component that lies in the
+rest frame of the SN.  The inferred luminosity of a SN can also be
+affected by the presence of foreground dust with a different redshift
+and possibly a different reddening law \citep{Menard:2010b}.  However,
+the magnitude of such a bias is insufficient to account for the
+observed discrepancy, \citet{Menard:2010a} estimate the opacity of the
+universe as $\langle A_{V}\rangle\sim0.03$ mag up to $z=0.5$.  While
+this can have a measurable impact on precise cosmological constraints,
+it is far less than the 0.23 mag difference between the observed
+magnification of \tomas\ and the mean of the model predictions.
+
+\changeG{
+Although the very blue color of SN \tomas\ is helpful to rule out dust
+as a possible explanation for the observed small systematic bias, it
+is possible that this very blue color is itself leading to a bias in
+the distance measurement.  \citet{Scolnic:2014b} measured a small bias
+in the SALT2 fitter for Type Ia SNe that have a color parameter
+derived from the light curve fit $c<-0.1$ (see, e.g., their Figure 10
+and Section 5.1). For \tomas\ we have measured $c=-0.13$, which would
+correspond to a bias of roughly $+0.05$ mag in the SALT2 distance
+measurement.  If we were to apply a $-0.05$ mag correction to the
+distance modulus from the SALT2 fit, then this would increase the
+inferred magnification to $\mu_{\rm SALT2}=2.08\pm0.36$.  This would
+still be consistent with the mild tension apparent from the MLCS2k2
+fit, though with a decrease in significance. 
+}
+
+\subsubsection{Misclassification}
+\label{sec:Misclassification}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{FIG/snTomas_sn06bt_colorcurves}
+\caption{ 
+Comparing \tomas\ observations to the color curves of SN 2006bt and a
+normal Type Ia SN model. Grey points show the observed colors of
+SN \tomas, k-corrected to rest-frame UBVr bands. Solid orange lines
+show the observed color curves for the peculiar Type Ia SN
+2006bt. Dashed blue lines show the color curves for a normal Type Ia
+SN, derived from the SALT2 model with a color parameter $c=-0.13$, set
+to match the best-fit color for SN \tomas.
+\label{fig:colorcomparison} }
+\end{center}
+\end{figure}
+
+Is it possible that \tomas\ is an example of a peculiar stellar
+explosion that does not follow the relationship between light curve
+shape and luminosity observed in normal Type Ia SNe?  In
+Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
+classified SN \tomas\ as a normal Type Ia SN based on both the
+spectroscopic and photometric evidence.  This rules out the
+possibility that \tomas\ belongs to a different class of normal SN
+explosions (Type Ib, Ic, or II). In
+Section \ref{sec:LightCurveFitting} we fit the \tomas\ light curve to
+determine a luminosity distance and found that the light curve shape
+and color are consistent with a Type Ia SN of average light curve
+width, with minimal dust extinction.  This excludes the possibility
+that \tomas\ is one of the sub-class of faint and fast-declining Type
+Ia SNe like SN 1991bg.
+
+One remaining possibility is that \tomas\ could be part of a rare
+sub-category of peculiar Type Ia SNe that masquerade as their normal
+cousins, epitomized by the prototype SN 2006bt \citep{Foley:2010}.
+These objects appear to have a normal Type Ia light curve shape,
+except for the absence of a secondary maximum or ``shoulder'' in
+near-IR bands.  The reddest filter available for the \tomas\ light
+curve is F160W, which has an effective rest-frame wavelength of
+6623\AA\ at $z=1.31$, making it close to the rest-frame {\it r} band.
+Although the near-IR shoulder is more prominent in the rest-frame {\it
+i} band, we can see in Figure~\ref{fig:LightCurveFits} that the F160W
+light curve may suggest a weak or delayed near-IR shoulder.  The
+second-to-last observation in F160W is $\sim1\sigma$ lower than
+predicted by the best-fit SALT2 and MLCS2k2 models. This is tenuous
+evidence, but it would be consistent with a 2006bt-like light curve.
+
+In this case, however, the color of SN \tomas\ can rule out a
+classification as a 2006bt-like object.  All members of this peculiar
+sub-class exhibit very red colors across all optical and near-IR
+bands, consistent with a very cool photosphere \citep{Foley:2010}.
+Figure~\ref{fig:colorcomparison} shows that \tomas\ is bluer than the
+SN 2006bt prototype by at least 0.25 magnitudes in every color. The
+observed \tomas\ colors are fully consistent with a normal, blue
+Type Ia SN (the SALT2 model is shown).
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=\textwidth]{FIG/tension}
+\caption{ \label{fig:Nspecz}
+\changeR{
+The model tension as a function of strong-lensing constraints. The y
+axis in both panels marks the number of standard deviations in
+discrepancy between the measured SN magnification and the prediction
+from each lens model. The left panel plots this tension against the
+total number of multiply imaged systems used, and the right panel
+plots the fraction of
+multiply-imaged systems that have a spectroscopic redshift
+constraint.  Marker shapes and colors are the same as in
+Figure~\ref{fig:LensingTest}.}
+}
+\end{center}
+\end{figure*}
+
+\subsection{Possible Error in Lens Model Construction}
+\label{sec:LensModelErrors}
+
+\changeR{Having now ruled out misinterpetations of the SN
+data, we are left to seek an explanation for the small systematic bias
+by scrutinizing the lens models.  TODO: note that 
+the most successful models are those that use a
+stringent criteria for strong lensing constraints, which results in a
+larger fraction that have spectroscopic redshifts. 
+}
 
@@
 (CATS(v2)) discrepant by $2.9\sigma$.  }
-
-\subsection{Redshift Error}
-\label{sec:RedshiftError}
-
-If the redshift of the SN derived in Section~\ref{sec:Spectroscopy}
-were incorrect, then one would derive a different value for the
-magnification, both from the SN measurement and the lens model
-predictions.  Conceivably, this could resolve the tension between the
-measurement and the models.  It is often the case in SN surveys that
-redshifts are assigned based on a host galaxy association, typically
-inferred from the projected separation between the SN and nearby
-galaxies.  In this case the redshift evidence \change{is strongly supported} with evidence from the SN
-itself: we find a consistent redshift from both the SN spectrum
-(Section~\ref{sec:SpecRedshift}) and the light curve
-Section~\ref{sec:PhotometricClassification}, which are both within the
-$1\sigma$ range of the photometric redshift for the nearest detected
-galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
-picture, so the evidence strongly disfavors any redshift that is
-significantly different from $z=1.35$.
-
-We have adopted the \change{most precise redshift of $z=1.3457$ from
-the host galaxy as our baseline for the magnification comparison.  If
-instead we adopt the spectroscopic redshift from the SN itself
-($z=1.31$; Section~\ref{sec:SpecRedshift}) then we find no significant
-change in the inferred magnifications or in the suggestion of a small
-systematic bias.}
-
-\subsection{Foreground Dust and SN Color}
-\label{sec:ForegroundDust}
-
-All SN sight-lines must intersect some amount of foreground dust from
-the immediate circumstellar environment, the host galaxy, and the
-intergalactic medium (IGM). In the case of SN \tomas\ one might posit
-some dust extinction from the intra-cluster medium (ICM) of Abell
-2744, although measurements of rich clusters suggest that the ICM has
-only a negligible dust
-content \citep{Maoz:1995,Stickel:2002,Bai:2007}.  When fitting
-the \tomas\ light curve we account for dust by including corrections
-that modify the inferred luminosity distance based on the SN color.
-If after applying these dust corrections we are still {\it
-underestimating} the effect of dust along this sight-line, then the SN
-would appear more dim, the inferred distance modulus would be higher,
-and the measured magnification would be reduced -- consistent with the
-discrepancy we observe.
-
-In Section~\ref{sec:LightCurveFitting} we found that SN \tomas\ is on
-the blue end of the normal range of Type Ia SN colors.  With the SALT2
-fitter we measured a color parameter $c=-0.127\pm0.025$, and with
-MLCS2k2 we found the host galaxy dust extinction to be $A_{\rm
-V}=0.011\pm0.025$ magnitudes.  These colors are tightly constrained,
-as we are fitting to photometry that covers a rest-frame wavelength
-range from $\sim3500-7000$\AA\ and extends to $\sim$30 days past
-maximum brightness.  This leaves little room for the luminosity
-measurement to be biased by dust, as the dimming of \tomas\ would also
-necessarily be accompanied by some degree of reddening.
-
-Nevertheless, one might suppose that a bias could be introduced if we
-have adopted incorrect values for the color correction parameter
-$\beta$ or extinction law $R_V$ in the SALT2 and MLCS2k2 fits,
-respectively.  The appropriate value to use for this color correction
-and how it affects inferences about the intrinsic scatter in Type Ia
-SN luminosities is a complex question that is beyond the scope of this
-work \citep[see
-e.g.][]{Marriner:2011,Chotard:2011,Kessler:2013,Scolnic:2014a}.
-However, we can already rule this out as a solution for the
-magnification discrepancy.  Our error on the \tomas\ distance modulus
-already includes an uncertainty in the extinction law and a related
-error to account for the intrinsic luminosity scatter. These are well
-vetted parameters, based on observations of $\sim500$ SNe extending
-to $z\sim1.5$ \citep{Sullivan:2011}.  Furthermore, there is no reason
-to propose that SN \tomas\ is uniquely affected by a peculiar type of
-dust.  Thus, any change in the color correction applied to SN \tomas\
-would require the same adjustment to be applied to the unlensed SNe at
-similar redshift that make up our comparison sample, largely negating
-the effect on the inferred magnification.
-
-The traditional color corrections as formalized in SN light curve
-fitters are designed to account for a dust component that lies in the
-rest frame of the SN.  The inferred luminosity of a SN can also be
-affected by the presence of foreground dust with a different redshift
-and possibly a different reddening law \citep{Menard:2010b}.  However,
-the magnitude of such a bias is insufficient to account for the
-observed discrepancy, \citet{Menard:2010a} estimate the opacity of the
-universe as $\langle A_{V}\rangle\sim0.03$ mag up to $z=0.5$.  While
-this can have a measurable impact on precise cosmological constraints,
-it is far less than the 0.23 mag difference between the observed
-magnification of \tomas\ and the mean of the model predictions.
-
-\changeG{
-Although the very blue color of SN \tomas\ is helpful to rule out dust
-as a possible explanation for the observed small systematic bias, it
-is possible that this very blue color is itself leading to a bias in
-the distance measurement.  \citet{Scolnic:2014b} measured a small bias
-in the SALT2 fitter for Type Ia SNe that have a color parameter
-derived from the light curve fit $c<-0.1$ (see, e.g., their Figure 10
-and Section 5.1). For \tomas\ we have measured $c=-0.13$, which would
-correspond to a bias of roughly $+0.05$ mag in the SALT2 distance
-measurement.  If we were to apply a $-0.05$ mag correction to the
-distance modulus from the SALT2 fit, then this would increase the
-inferred magnification to $\mu_{\rm SALT2}=2.08\pm0.36$.  This would
-still be consistent with the mild tension apparent from the MLCS2k2
-fit, though with a decrease in significance. 
-}
-
-\subsection{Misclassification}
-\label{sec:Misclassification}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{FIG/snTomas_sn06bt_colorcurves}
-\caption{ 
-Comparing \tomas\ observations to the color curves of SN 2006bt and a
-normal Type Ia SN model. Grey points show the observed colors of
-SN \tomas, k-corrected to rest-frame UBVr bands. Solid orange lines
-show the observed color curves for the peculiar Type Ia SN
-2006bt. Dashed blue lines show the color curves for a normal Type Ia
-SN, derived from the SALT2 model with a color parameter $c=-0.13$, set
-to match the best-fit color for SN \tomas.
-\label{fig:colorcomparison} }
-\end{center}
-\end{figure}
-
-Is it possible that \tomas\ is an example of a peculiar stellar
-explosion that does not follow the relationship between light curve
-shape and luminosity observed in normal Type Ia SNe?  In
-Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
-classified SN \tomas\ as a normal Type Ia SN based on both the
-spectroscopic and photometric evidence.  This rules out the
-possibility that \tomas\ belongs to a different class of normal SN
-explosions (Type Ib, Ic, or II). In
-Section \ref{sec:LightCurveFitting} we fit the \tomas\ light curve to
-determine a luminosity distance and found that the light curve shape
-and color are consistent with a Type Ia SN of average light curve
-width, with minimal dust extinction.  This excludes the possibility
-that \tomas\ is one of the sub-class of faint and fast-declining Type
-Ia SNe like SN 1991bg.
-
-One remaining possibility is that \tomas\ could be part of a rare
-sub-category of peculiar Type Ia SNe that masquerade as their normal
-cousins, epitomized by the prototype SN 2006bt \citep{Foley:2010}.
-These objects appear to have a normal Type Ia light curve shape,
-except for the absence of a secondary maximum or ``shoulder'' in
-near-IR bands.  The reddest filter available for the \tomas\ light
-curve is F160W, which has an effective rest-frame wavelength of
-6623\AA\ at $z=1.31$, making it close to the rest-frame {\it r} band.
-Although the near-IR shoulder is more prominent in the rest-frame {\it
-i} band, we can see in Figure~\ref{fig:LightCurveFits} that the F160W
-light curve may suggest a weak or delayed near-IR shoulder.  The
-second-to-last observation in F160W is $\sim1\sigma$ lower than
-predicted by the best-fit SALT2 and MLCS2k2 models. This is tenuous
-evidence, but it would be consistent with a 2006bt-like light curve.
-
-In this case, however, the color of SN \tomas\ can rule out a
-classification as a 2006bt-like object.  All members of this peculiar
-sub-class exhibit very red colors across all optical and near-IR
-bands, consistent with a very cool photosphere \citep{Foley:2010}.
-Figure~\ref{fig:colorcomparison} shows that \tomas\ is bluer than the
-SN 2006bt prototype by at least 0.25 magnitudes in every color. The
-observed \tomas\ colors are fully consistent with a normal, blue
-Type Ia SN (the SALT2 model is shown).
 
@@
 
+%\input{TABLE/magnifications}
 \end{document}

### 2015-04-30 snTomasCode/lensing_test_fig.py

@@ -3,7 +3,8 @@
 # The lensing comparison figure
 import numpy as np
 
-def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
+def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
+                      labelvalues=False ):
     from matplotlib import pyplot as pl
     from matplotlib.patches import FancyArrowPatch
     from pytools import plotsetup, colorpalette as cp
@@ -17,13 +18,11 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
     muSNsalterr = 0.38
 
     if presfig :
-        fig = plotsetup.presfig( figsize=[12,8])
-        labelvalues=True
+        fig = plotsetup.presfig( figsize=[8,12])
         pl.clf()
         ax1 = pl.axes( [0.01,0.14,0.67,0.83] )
         ms=15
     else :
-        labelvalues=False
         fig = plotsetup.fullpaperfig( figsize=[4,5])
         ms=8
         pl.clf()
@@ -57,6 +56,12 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
             marker='D'
         else:
             marker='o'
+        if row['postSN']:
+            mec='magenta'
+            mew=ms/7.
+        else :
+            mec=color
+            mew=ms/8.
 
         #ax1.plot( best, y, marker='x', ms=ms, color=color,
         #          zorder=100, label='_nolegend_' )
@@ -64,13 +69,14 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False ):
             # make an arrow for the really long williams error
             errplus = 3.6-med
             ax1.errorbar( med, y, yerr=None, xerr=[[0],[errplus]],
-                          marker=None, capsize=0.6*ms, color=color,
-                          xlolims=[True], zorder=10, label='_nolegend_' )
+                          marker=None, capsize=0.6*ms, color=color, mec=mec,
+                          ms=ms, mew=mew, xlolims=[True], zorder=10,
+                          label='_nolegend_' )
         ax1.errorbar( med, y, yerr=None,
[…]

### 2015-04-30 TABLE/magnifications2.tex
finished (another) overhaul of the discussion section   * now includes a discussion of Cosmic Weak Lensing   * highlights the quality vs quantity strong lensing argument   * reorganizes the discussion to evaluate SN problems first, then lens models

@@
 GLAFIC         & 15 &  47 & 3 & 11 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
-Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{i} profiles for galaxies and NFW\tablenotemark{j} profiles for dark matter halos.\\
+Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD profiles for galaxies and NFW profiles for dark matter halos.\\
 Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{k} : Free-form, strong+weak-lensing based model.
+Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{i} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
@@
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Williams       & 16 &  56 & 2 & 14 &  HFF & {\tt GRALE}\tablenotemark{l} : Free-form strong-lensing model using a genetic algorithm.  \\
-Merten         & 25 &  72 & 7 & 18 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{m} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{n} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{o} models for galaxy mass.\\
-Diego$^{\rm p}$ & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.
+Williams       & 16 &  56 & 2 & 14 &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
+Merten         & 25 &  72 & 7 & 18 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.\\
+Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.
 \enddata
@@
 \tablenotetext{h}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{i}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
-\tablenotetext{j}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
-\tablenotetext{k}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
-\tablenotetext{l}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
-\tablenotetext{m}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{n}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
-\tablenotetext{o}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
-\tablenotetext{p}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
+\tablenotetext{i}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
+\tablenotetext{j}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
+\tablenotetext{k}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
+\tablenotetext{l}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
+\tablenotetext{m}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
+\tablenotetext{n}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
 No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.

### 2015-04-30 snTomas.tex
finished (another) overhaul of the discussion section   * now includes a discussion of Cosmic Weak Lensing   * highlights the quality vs quantity strong lensing argument   * reorganizes the discussion to evaluate SN problems first, then lens models

@@
 misinterpretation of the SN data. We conclude that -- at least for
-this single line of sight -- the most accurate models are those with
-(1) stringent quality cuts for strong-lensing constraints and (2)
-relatively flexible model design}. \change{A more robust evaluation of
-systematic biases could be achieved with further cooperative lens
-model comparisons using a larger sample of lensed Type Ia SNe as well
-as cluster lensing simulations.}
+this cluster and this line of sight -- the most accurate models are
+those that employ stringent quality cuts for strong-lensing
+constraints.} \change{A more robust evaluation of systematic biases
+could be achieved with further cooperative lens model comparisons
+using a larger sample of lensed Type Ia SNe as well as cluster lensing
+simulations.}
 \end{abstract}
@@
 set of all models, at $\mu=2.5$.
-\label{fig:lensingtest} }
+\label{fig:LensingTest} }
 \end{center}
@@
 
-\changeR{
-Table~\ref{tab:PredictedMagnifications} gives each model's predicted}
+Table~\ref{tab:PredictedMagnifications} gives each model's predicted
 magnification and uncertainty for a source at \change{$z=1.3457$} and
@@
 the techniques and assumptions that can be applied to the modeling of
-mass distributions in galaxy clusters. A rigorous comparison of these
+mass distributions in galaxy clusters.  The first eight models in this
+table are so-called {\it parametric}\footnote{Although this
+nomenclature is becoming standard in the literature, it is somewhat
+misleading, as the pixels or grid cells in free-form models are
+effectively parameters as well. Perhaps ``simply-parameterized'' would
+be more accurate, though we adopt the more common usage here.}
+models, and the bottom seven are {\it free-form} models.  Broadly
+speaking, the parametric models use parameterized density
+distributions to describe the arrangement of mass within the cluster,
+typically associating massive dark matter halos with the positions of
+bright cluster member galaxies. Therefore, parametric models rely (to
+varying degrees) on the assumption that the cluster's dark matter can
+be described by analytic forms such as NFW halos \citep{Navarro:1997},
+or pseudo isothermal elliptical mass
+distributions \citep[PIEMD][]{Kassiola:1993}.  Free-form models divide
+the cluster into a grid, generally using a multi-scale grid to get
+better sampling in denser regions. Each grid cell is assigned a mass
+or a potential, and then the mass values are iteratively refined to
+match the observed lensing constraints. In some cases an adaptive grid
+is used so that the grid spacing itself can also be modified as the
+model is iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.  
+A more rigorous comparison of these
 disparate lens modeling techniques is beyond the scope of this
-work. Table~\ref{tab:PredictedMagnifications} includes a brief
-description of each model, but for a complete discussion of the
-methodology the reader is referred to the listed references.
-
-In Figure~\ref{fig:lensingtest} the model predictions are plotted
+work.  For a complete discussion of each model's
+methodology, the reader is directed to the listed references.
+
+In Figure~\ref{fig:LensingTest} the model predictions are plotted
 alongside the observed magnification of SN \tomas, derived in
-Section~\ref{sec:DistanceAndMagnification}.  This comparison shows that these 14
-models are largely consistent with each other. Naively treating each
-model as an independent prediction for the magnification (and ignoring
-their quoted uncertainties), one would get a mean for the full sample
-of \change{$\mu=2.5\pm0.4$.  This is separated from the observed SN
-magnification by $\delta\mu/\mu=23\%$, which is approximately a
-1$\sigma$ difference.}
-
-The models shown in Figure~\ref{fig:lensingtest} are separated along
-the $y$ direction into two broad classes, with eight so-called {\it
-parametric}\footnote{Although this nomenclature is becoming standard
-in the literature, it is somewhat misleading, as the pixels or grid
-cells in free-form models are effectively parameters as well. Perhaps
-``simply-parameterized'' would be more accurate, though we adopt the
-more common usage here.}  models on top and seven {\it free-form} models
-on the bottom.  Broadly speaking, the parametric models use
-parameterized density distributions to describe the arrangement of
-mass within the cluster, typically associating massive dark matter
-halos with the positions of bright cluster member galaxies. Therefore,
-parametric models rely (to varying degrees) on the assumption that the
-cluster's dark matter can be described by analytic forms such as NFW
-halos \citep{Navarro:1997}, or pseudo isothermal elliptical mass
-distributions \citep{Kassiola:1993}.  Free-form models divide the
-cluster into a grid, generally using a
-multi-scale grid to get better sampling in denser regions. Each grid cell
-is assigned a mass or a potential, and then the mass values are
-iteratively refined to match the observed lensing
-constraints. In some cases an adaptive grid is used so
-that the grid spacing itself can also be modified as the model is
-iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.
+Section~\ref{sec:DistanceAndMagnification}.  To first order, this
+comparison shows that these 15 models are largely consistent with each
+other and with the observed magnification of SN \tomas. Naively
+treating each model as an independent prediction for the magnification
+(and ignoring their quoted uncertainties), one would get a mean for
+the full sample of \change{$\mu=2.5\pm0.4$.  This is separated from
+the observed SN magnification by $\delta\mu/\mu=23\%$, which is
+approximately a 1$\sigma$ difference.}
 
@@
 space more fully than parametric methods.  This is reflected in the
-size of the error-bars in Figure~\ref{fig:lensingtest}.  For example,
-the Williams model (using GRALE), which has the largest uncertainties
-is able to account for mass sheet degeneracy by introducing a free
-parameter in the reconstruction that represents an arbitrarily scaled
-mass sheet, with normalization to be chosen by the genetic algorithm.
-More complex degeneracies are also accounted for in this model through
-the use of basis
+size of the error-bars in Figure~\ref{fig:LensingTest}.  For example,
+the Williams model (using GRALE) has the largest uncertainties, in
+part because it accounts for mass sheet degeneracy by introducing a
+free parameter in the reconstruction that represents an arbitrarily
+scaled mass sheet, with normalization to be chosen by the genetic
+algorithm.  More complex degeneracies are also accounted for in this
+model through the use of basis
 functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
 
-Figure~\ref{fig:lensingtest} also separates the models based on the
+Figure~\ref{fig:LensingTest} also separates the models based on the
 scope of input data constraints used.  Ten of the models rely only on
@@
 possible explanations for this small but \change{nearly} universal
-bias.
-
-\subsection{Possible Errors in Supernova Interpretation}
-\label{sec:SupernovaErrors}
-
-\changeR{Before examining the lens models or the cluster, let us first
-consider whether we might have misinterpreted the data on the SN
-itself.}
+bias.  \changeR{We first consider whether a misinterpretation of the data on the SN
+itself can account for the observed systematic bias, and then 
+ examine the lens models.}
+
+\subsection{Possible Errors in Supernova Analysis}
+\label{sec:SupernovaError}
 
@@
 
+\subsection{Possible Errors in Lens Modeling}
+\label{sec:LensModelComparison}
+
+\changeR{
+Having now ruled out misinterpetations of the SN data, we are left to
+seek an explanation for the mild tension by scrutinizing the lens
+models.  Here we evaluate four possible sources for a systematic bias to
+appear in the lens models.
+}
+
+\subsubsection{Cosmic Weak Lensing}
+\changeR{ 
+In addition to the dominant gravitational lensing from the foreground
+cluster, a distant source like SN \tomas\ will also be subject to the
+cumulative weak lensing effects due to uncorrelated large scale
+structure along the line of sight, sometimes called ``Cosmic Weak
+Lensing'' \citep[CWL;][]{Wong:2011,Host:2012,Bayliss:2014,McCully:2014,DAloisio:2014}.
+This CWL effect is most important for very high redshift sources
+($z>5$), which have a much longer path length over which to encounter
+large scale structure and for highly magnified sources very near to
+the cluster lensing critical curve (because CWL can perturb the
+position of the critical curve).  For SN \tomas\ at the modest
+redshift of $z=1.35$ and far from the critical curve, CWL should
+increase the scatter in the lensing magnification at a level much less
+than 10\% \citep{DAloisio:2014}.  The CWL effect is therefore unable
+to account for the observed discrepancy of $\sim23$\% by
+itself.
+}
+
+\subsubsection{Nearby Cluster Member}
+\changeR{
+A component of the Abell 2744 lens that is particularly relevant to SN \tomas\ is the cluster member
+galaxy that lies just 5\farcs8 north of the SN position (see
+Figure~\ref{fig:DiscoveryImage}).  If the mass-to-light ratio or the
+profile of the dark matter halo for this galaxy were significantly
+different from other cluster member galaxies, then its
+proximity to the SN sight-line might drive a bias in the magnification.
+We tested this hypothesis using the CATS(v2) model by allowing the mass
+of the nearby cluster member galaxy to vary as a free parameter in the
+model. We found that the change in the SN \tomas\ magnification
+prediction was less than $\Delta\mu=0.1$.  This additional dispersion
+is already included in the uncertainties quoted for that model in
+Table~\ref{tab:PredictedMagnifications} and
+Figure~\ref{fig:LensingTest}.  Furthermore, an erroneous M/L
+value for the nearby cluster member galaxy could not explain the
+systematic shift of all lens models, because some do not incorporate
+cluster member galaxies into their constraints at all (the free-form
+Bradac, Williams and Merten models).
+}
+
+\subsubsection{Cosmological Parameter Uncertainty}
+\changeR{
+Most lens models make a
+fixed assumption for the values of cosmological parameters in a
+standard \LCDM\ cosmology (typically: \Om=0.3,\OL=0.7,\Ho=70 km
+s$^{-1}$ Mpc$^{-1}$). This can introduce a systematic magnification
+error that is comparable in magnitude to that of the statistical
+uncertainties \citep{Zitrin:2014b,Bayliss:2015}.  
+Incorporating this
+cosmological parameter uncertainty would increase the model magnification errors typically by 1-10\%. 
+This would reduce the tension between models and observation, but would not
+resolve the overall systematic shift.  Even a factor of 2.5 increase
+in the uncertainties (the most drastic change seen in the analysis
+of \citet{Bayliss:2015}) would still leave the most extreme outlier
+(CATS(v2)) discrepant by $2.9\sigma$. 
+}
+
+\subsubsection{Misidentification of a multiple image}
+
+\changeR{
+\citet{Jauzac:2014c} proposed a correction
+for the location of image 3.3, the third component of a triply-imaged
+galaxy \citep{Merten:2011} at $z=3.98\pm0.02$ \citep{Johnson:2014}.
+This possibly specious multiple image is only $\sim$10\arcsec\ from
+the SN \tomas\ position, meaning a change in its location could have a
+large impact on the predicted magnification for
+SN \tomas\ \citep[see][for a quantitative discussion of this
+effect]{Johnson:2014}.  However, \citet{Jauzac:2014c} also evaluated a
+version of the CATS(v2) model in which this single source is left in
+the original position and found that the location of image 3.3 does
+not significantly affect the predicted magnifications.  Furthermore,
+dividing our 15 models into those using the original location vs those
+that adopt the new position, we find that both groups include models
+that are within 1$\sigma$ of the observed $\mu$ as well as
+significantly discrepant points.
+}
+
+\subsection{Quantity and Quality of Lensing Constraints}
+\label{sec:LensModelComparison}
+
+\changeR{
+None of the possibilities described above can completely account for
+the mild tension between the observed and predicted magnifications.
+However, in lieu of a physical explanation, we can simply take a
+pragmatic approach and seek to identify any shared characteristics of
+the most accurate models.  In this way SN \tomas\ may serve as a guide
+for optimizing future lens models for magnification predictions.  }
+
 \begin{figure*}
@@
 
-\subsection{Possible Error in Lens Model Construction}
-\label{sec:LensModelErrors}
-
-\changeR{Having now ruled out misinterpetations of the SN
-data, we are left to seek an explanation for the small systematic bias
-by scrutinizing the lens models.  TODO: note that 
-the most successful models are those that use a
-stringent criteria for strong lensing constraints, which results in a
-larger fraction that have spectroscopic redshifts. 
+\changeR{
+As can be seen in Table~\ref{tab:LensModels} and
+Figure~\ref{fig:LensingTest}, among the 7 models that yield
+magnifications discrepant by more than 1$\sigma$ we find a variety of
+methodologies (both parametric and free-form) and a mix of lensing
+constraints (both strong-lensing only and strong+weak).  The left
+panel of Figure~\ref{fig:Nspecz} shows that this subset of 7 also
+includes a wide range in the number of multiply-imaged galaxies used
+as strong-lensing constraints (from $\sim$10 to 50).  Given that the
+discrepancy persists across all of these categories, none of them can
+provide a satisfactory explanation for the small observed bias.
 }
 
-\subsection{Nearby Cluster Member Galaxy}
-\label{sec:NearbyClusterMemberGalaxy}
-
-The line of sight to SN \tomas\ is 5\farcs8 from a bright cluster
-member galaxy, due North of the SN position (see
-Figure~\ref{fig:DiscoveryImage}).  If the mass-to-light ratio (M/L)
-for this galaxy were significantly different from the M/L for other
-cluster member galaxies, then its proximity to the SN sight-line could
-introduce a bias in the magnification.  This bias might be
-particularly acute for models that hew more closely to a
-simple ``light traces mass'' assumption, such as the Sharon, CATS,
-GLAFIC and Zitrin-LTM models.
-
-We tested this hypothesis using the CATS(v2) model by allowing the mass
-of the nearby cluster member galaxy to vary as a free parameter in the
-model. We found that the change in the SN \tomas\ magnification
-prediction was less than $\Delta\mu=0.1$.  This additional dispersion
-is already included in the uncertainties quoted for that model in
-Table~\ref{tab:PredictedMagnifications} and
-Figure~\ref{fig:lensingtest}.  Furthermore, an erroneous M/L
-value for the nearby cluster member galaxy could not explain the
-systematic shift of all lens models, because some do not incorporate
-cluster member galaxies into their constraints at all (the free-form
-Bradac, Williams and Merten models).
-
-\subsection{Sparse Strong Lensing Constraints}
-\label{sec:SparseStrongLensingConstraints}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{FIG/system3.png}
-\caption{ 
-The disputed component of the multiply-imaged galaxy System 3. The
-original position, as given in \citet{Merten:2011} is marked with a
-dashed magenta circle labeled 3.3. The solid magenta circle
-labeled \33p\ shows the revised location as proposed
-in \citet{Jauzac:2014c}.  Both positions are $\sim$10\arcsec\ from the
-SN location.  The inset panel shows the other two components of this
-multiply-imaged system, 3.1 and 3.2 (on the same scale as the main
-panel), which are located north-east of the cluster center, and have a
-secure spectroscopic redshift of $z=3.98\pm0.02$ \citep{Johnson:2014}.
-\label{fig:system3} }
-\end{center}
-\end{figure}
-
-At the outset of the HFF survey, only 33 multiply-imaged galaxies
-behind Abell 2744 were known.  One might expect that the addition of
-new lensing constraints from the HFF data would improve the model
-constraints and reduce the tension between the predicted and observed
-magnification.  However, for two of the most recent models (CATSv2,
-Lam; \citealt{Jauzac:2014c,Lam:2014}) that include new strong-lensing
-constraints, the predicted magnification is still significantly higher
-than the observed value.  Again the CATS model family provides a
-useful case study.  The CATS(v2) model \citep[from][]{Jauzac:2014c}
-shares the same lens modeling software (LensTool), and the same
-primary methodology as the earlier CATS models, though with two key
-differences: (1) the CATS(v2) model changes the location of a
-multiply-imaged system near the SN \tomas\ position; and (2) the model
-incorporates 33 new multiply imaged galaxies.  These improvements
-should in principle make the CATS(v2) model magnification estimates
-more accurate, though we in fact see the opposite result: the
-CATS(v2) model predicts a $\mu$ that is higher than the measured
-value by $4.3\sigma$, and higher than either of the previous two
-versions of the CATS models.
-
-The change in location proposed by \citet{Jauzac:2014c} is for image
-3.3, the third component of a triply-imaged
-galaxy \citep{Merten:2011}, shown in Figure~\ref{fig:system3}.  Images
-3.1 and 3.2 of this system have a secure spectroscopic redshift of
-$z=3.98\pm0.02$ \citep{Johnson:2014}. \citet{Jauzac:2014c} found that
-reassigning this multiple image to a source roughly 8\arcsec\ to the
-south results in a tighter model reconstruction for the locations of
-other multiply-imaged systems in the vicinity \citep[though][argue
-against the reassignment based on the colors of the two sources in
-question]{Lam:2014}.  Given the large discrepancy between the
-CATS(v2) model and the SN measurement, one might question whether
-this change in the position of image 3.3 is driving the increase in
-the predicted $\mu$ for SN \tomas. However, \citet{Jauzac:2014c} also
-examined a version of the CATS(v2) model where this single source
-is left in the original position, and find that it does not
-significantly affect the predicted magnification.
-
-Furthermore, the shift to higher magnifications is not unique to the
-SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
-mass model of Abell 2744 results in a systematic increase in the
-magnification values across the cluster field. Examining a sample of
-$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
-magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
-models.  Although the single sight-line to SN \tomas\ can
-only provide a very limited test of the model,
-the $4.1\sigma$ discrepancy is at least a strong suggestion
-that even with a large number of high-quality strong-lensing
-constraints it is still possible to generate magnification
-maps that are susceptible to systematic biases.
-
-\subsection{Mass Profile Extrapolation}
-\label{sec:MassProfileExtrapolation}
-
-Eight of the mass models evaluated here are constrained only using
-strong-lensing features such as multiply-imaged background galaxies
-and highly magnified arcs.  There are now $\sim$150 known lensed
-images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
-located several arcseconds outside the core region of the cluster
-where these multiply-imaged galaxies are found.  Therefore these eight
-``strong-lensing only'' models must necessarily rely on extrapolations
-to provide a prediction for the SN \tomas\ magnification.  Let us
-suppose that the true cluster density profile for Abell 2744 happens
-to have a sharp drop right at the edge of this core strong-lensing
-region. In that case these eight models might well overestimate the
-mass interior to the \tomas\ position, and thus systematically
-overestimate the magnification.
-
-The other three models in our comparison set also use the strong
-lensing constraints from the core region, but additionally utilize
-weak lensing measurements to provide additional constraints on the
-mass distribution farther from the cluster core.  The signal from weak
-lensing relies on a large sample of background galaxies, so this
-constraint operates principally at separations more than 1\arcmin\
-from the cluster core.  At a projected separation of $\sim40\arcsec$,
-SN \tomas\ falls in between the strong- and weak-lensing regimes, and
-one would expect that models incorporating both of those constraints
-would be less susceptible to the possible systematic bias of
-a sharply steepening mass profile.  The lowest magnification estimate
-in our sample (from the Merten model) is among this sub-sample.
-However, we find that collectively these three strong+weak models
-(shown as diamonds in Figure~\ref{fig:lensingtest}) exhibit the same
-propensity to overestimate the magnification along this line of sight.
-Thus, a sudden change in the mass profile outside the strong lensing
-region is not a likely explanation for this small systematic bias.
-
-With two versions of the CATS model, we also have a more direct test
-of the effect of introducing weak lensing constraints.  The initial
-CATS(v1) model uses only strong-lensing constraints, and gives
-$\mu=2.29^{+0.05}_{-0.04}$, slightly higher than the measured value.
-A second iteration of this model, labeled here as CATS(v1sw), used the
-same strong-lensing features, but added in weak lensing constraints.
-The revised magnification of $\mu=2.62\pm0.18$ is further from the
-measured value, which serves to reinforce the conclusion that adding
-weak lensing constraints cannot, by itself, resolve this bias.
-
-\subsection{Cosmological Uncertainty}
-
-All of the models presented here use a fixed assumption for the
-parameters of a standard \LCDM\ cosmology (typically: \Om=0.3,\OL=0.7,\Ho=70 km
-s$^{-1}$ Mpc$^{-1}$).  The parameter values selected for this fiducial
-cosmology do have an impact on the inferred magnifications, and
-variation of these parameters must be accounted for when using cluster
-mass models for cosmological tests \citep{Zitrin:2014b}. 
-\citep{Bayliss:2015} demonstrated that
-changing the cosmological parameter within the range of current
-acceptable cosmologies \citep[e.g.][]{Hinshaw:2013,Planck-Collaboration:2015},
-introduces a magnification uncertainty that is comparable in magnitude
-to that of the statistical uncertainties.  This leads to the
-conclusion that the lens modeling uncertainties presented here are
-underestimated, and should be significantly increased.
-
-\change{
-We have used the Sharon(v2) model to provide a quantitative example of
-how the magnification errors are affected by inclusion of this
-cosmological parameter uncertainty.  Following \citealt{Bayliss:2015},
-we propagate cosmological parameter variations into the magnification
-uncertainties, and find that the 68\%\ confidence range for the
-magnification at $z=1.3457$ increases from [2.63,2.83] to [2.42,2.85].
-The best-fit magnification value of $mu=2.74$ and the median value of
-$mu=2.59$ remain the same. For this model only,
-Table~\ref{tab:PredictedMagnifications} includes this cosmological
-uncertainty. In this case, the Sharon(v2) model moves from being discrepant at
-the $2.5\sigma$ level to a $1.7\sigma$ tension.  Incorporating this
-cosmological parameter uncertainty in the other models would similarly
-reduce the tension between models and observation, but would not
-resolve the overall systematic shift.  Even a factor of 2.5 increase
-in the uncertainties (the most drastic change seen in the analysis
-of \citep{Bayliss:2015}) would still leave the most extreme outlier
-(CATS(v2)) discrepant by $2.9\sigma$.  }
+\changeR{
+However, the right panel of Figure~\ref{fig:Nspecz} shows that 3 of
+the most successful lens models (Bradac(v2), Lam(v2), Diego) do share
+a common quality: they all use a set of multiply-imaged galaxies for
+which a large fraction have spectroscopic redshifts.  In practice,
+this means that the strong-lensing constraints in these models are
+defined more stringently than other models. Some other models may use
+a larger set of strong-lensing features, but the dearth of
+spectroscopic constraints means that it is more likely that some of
+those multiply-imaged galaxies are assigned with incorrect redshifts.
+}
+
+\changeR{
+This comparison suggests that to get accurate magnifications, lens
+models should employ a strict vetting of the strong-lensing
+constraints.  Multiply-imaged systems should ideally have
+spectroscopic redshifts, or at least very well constrained photometric
+redshifts.  The {\it quantity} of strong-lensing constraints is not as
+important as their {\it quality}.
+}
 
@@
 \change{
-Taking advantage of the availability of 14 well-constrained lens
+Taking advantage of the availability of 15 well-constrained lens
 models for the Abell 2744 cluster, we have used SN \tomas\ to ask how
@@
 line of sight.  We find that these models are consistent, and fairly
-accurate, collectively predicting $\mu=2.53\pm0.38$.  This is
-encouraging, and reinforces the quality and value of these public lens
-models for studying magnified background objects.  However, we note
-that all but one of the tested models provides a median magnification
-value that is larger than we observe.  This may be an indication that
-there is a small systematic bias inherent to this cluster or
-sight-line.
-}
+accurate, collectively predicting $\mu=2.5\pm0.4$, within 1$\sigma$ of
+the measured value.  This is encouraging, and reinforces the quality
+and value of these public lens models for studying magnified
+background objects.  However, we note that all but two of the tested
+models provide a median magnification prediction that is larger than
+the measurement from the SN, and all the models with significant
+discrepancy are too high.  This may be an indication that there is a
+small systematic bias at work.  }
 
 We have speculated on what could be the origin for such a systematic bias,
-evaluating seven possible causes:
+first considering and rejecting three possible explanations that presume an error in the
+interpretation of the available SN data.
 
 \begin{enumerate}
-\item The close proximity of a cluster member galaxy is leading to a
-biased magnification, because that galaxy's M/L is atypical.
-\item The models are limited by a scarcity of strong lensing constraints
-\item Model uncertainties are underestimated, by not accounting for 
-       uncertainties in cosmological parameters.
-\item The cluster mass profile exhibits a sudden change outside of the core
-strong-lensing region, where we lack multiply-imaged background
-sources to constrain it.
-\item The redshift assigned to SN \tomas\ is in error.
-\item SN \tomas\ is dimmed by foreground dust.
-\item SN \tomas\ is not a normal Type Ia SN.
-\end{enumerate}
-
-\noindent The first four of these take on the discrepancy from 
-the lens modeling side, but none are completely satisfactory. For each
-of these scenarios, we would expect that certain subsets of the
-available lens models would be less sensitive to the proposed
-systematic bias.  However, the small discrepancy between the predicted
-and observed lensing magnification is persistent when we bifurcate the
-sample of lens models according to methodology (parametric
-vs. free-form), number of strong-lensing constraints (pre- vs
-post-HFF), and scope of lensing constraints (strong-lensing only
-vs. strong+weak). Thus, comparison of the available models does not
-provide any definitive explanation for this magnification tension.
-
-At least for this particular sight-line, the free-form models perform
-better in the sense that the mean and standard error for this subset
-($2.37\pm0.35$) is closer to the measured value ($2.03\pm0.29$) than
-is the parametric set ($2.59 +- 0.37$).  These free-form models also
-deliver more realistic uncertainties (with the exception of the
-Bradac(v2) model -- see \citet{Wang:2015} for further discussion of
-the changes made from v1 to v2 of that model). \change{The free-form
-model family also includes the only model that predicts a
-magnification lower than the observed value (Diego).}  This may
-indicate that the free-form approach in general is more successful in
-capturing the uncertainty from biases inherent to the mass modeling
-exercise, such as the mass sheet degeneracy and more complex
-``approximate invariances'' \citep{Liesenborgs:2012,Schneider:2014}.
-It may also be the case that the greater flexibility of the free-form
-models makes them better suited for predicting magnifications of
-sources that fall outside the strong-lensing region -- such as
-SN \tomas.
-
-The last three possible explanations presume an error in the
-interpretation of the available SN data.  We reject the possibility
-that a redshift error is the primary cause of the discrepancy, as the
-redshift evidence is well supported by multiple lines of evidence from
-both the SN and the presumed host galaxy. Changing the redshift within
-the constraints of these complementary observations does not resolve
-the tension. We also find it implausible that there is sufficient dust
-in the cluster or elsewhere along the line of sight to account for the
-magnification discrepancy.  A dust-induced bias is also disfavored by
-the very blue color of SN \tomas.
-
-Finally, we have considered whether the SN could be
-mis-classified. Once again the combination of spectroscopic and
+\item Redshift: We reject the possibility that a redshift error is the primary cause
+of the discrepancy, as the redshift evidence is well supported by
+multiple lines of evidence from both the SN and the presumed host
+galaxy. Changing the redshift within the constraints of these
+complementary observations does not resolve the tension. 
+\item Dust: We find
+it implausible that there is sufficient dust in the cluster or
+elsewhere along the line of sight to account for the magnification
+discrepancy.  A dust-induced bias is also disfavored by the very blue
+color of SN \tomas. SN \tomas\ is dimmed by foreground dust.
+\item Misclassification: The combination of spectroscopic and
 photometric evidence strongly supports our classification of
@@
 reject this alternative. 
+\end{enumerate}
+
+\noindent
+
+\changeR{
+Turning to the lens models, we have considered 4 ways in which a bias
+might be introduced into the lens models:
+}
+
+\begin{enumerate}
+\item Cosmic weak lensing 
+\item Peculiar mass for a nearby cluster member
+\item Cosmological parameter uncertainty
+\item Misidentification of a multiple image
+\end{enumerate}
+
+\noindent
+\changeR{
+Although each of these could plausibly introduce a small systematic
+bias, we find that none are likely to be significant enough
+to completely resolve the tension between models and observations.
+}
+
+\changeR{
+Finally, we have examined whether there is a simple prescription for
+the kind of strong lensing constraints that are most likely to deliver
+an accurate magnification prediction for this sight-line. 
+ We find
+that the number of multiply imaged systems used is not in itself
+predictive of model accuracy.  Rather, it is the fraction of multiply
+imaged systems that have spectroscopic redshifts that is most
+correlated with model accuracy.  A reasonable interpretation 
+-- at least for this cluster and this particular set of models -- is
+that the spectroscopic redshift fraction serves as an effective proxy
+for the ``quality'' of the strong lensing constraints. This quality of
+the input data appears to be a key ingredient for deriving accurate
+magnifications outside the strong-lensing regime.  }
 
 We have evaluated here only a single object behind a single cluster,
-with a minor tension between the observed magnification and most
+with a minor tension between the observed magnification and the model
 predictions.  This is not in and of itself a cause for alarm.
@@
 with a much smaller set of lens models being tested.  The observed
-systematic bias for \tomas\ is small, and many of the lens models
-being evaluated are preliminary models that have not been updated to
-include all of the HFF data.  Future revisions of the lens models for
-Abell 2744 could either incorporate the observed magnification
-of \tomas\ as a new model constraint, or can revisit this test to
-evaluate whether the bias persists.
+systematic bias for \tomas\ is small, and many of the lens models that
+deviate from the measured magnification are preliminary models that
+have not been updated to include all of the HFF data.  Future
+revisions of the lens models for Abell 2744 could either incorporate
+the observed magnification of \tomas\ as a new model constraint, or
+can revisit this test to evaluate whether the bias persists.
 
 A promising avenue for exploring the origins of systematic biases in
-cluster lens models is through the use of simulated data.  One can
+cluster lens models is through the use of simulated lensing data.  One can
 start with very deep high-resolution multi-band imaging on an unlensed
@@
 Grogin and Patricia Royle for accommodations in strategy and
-implementation to make the FrontierSN program possible; and to Dan Coe
-for curating the excellent and accessible lens model comparison tools.
-We also thank the CLASH team, led by Marc Postman, for observations,
-catalogs, and high level science products that were of significant
-value for this analysis.  Thanks to Jonatan Selsing for helpful
-comments on the manuscript.
+implementation to make the FrontierSN program possible; to Anton
+Koekemoer for HFF data processing support; and to Dan Coe for curating the
+excellent and accessible lens model comparison tools.  We also thank
+the CLASH team, led by Marc Postman, for observations, catalogs, and
+high level science products that were of significant value for this
+analysis.  Thanks to Jonatan Selsing for helpful comments on the
+manuscript.
 

### 2015-04-30 TABLE/magnifications2.tex
fixed the numbers for CATS(v2) in the table

@@
 Sharon(v2)     & 17 &  60 & 2 & 14 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
-CATS(v1)       & 50 & 151 & 4 & 0  &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
 CATS(v1sw)     & 24 &  67 & 3 & 12 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)       & 17 &  60 & 2 & 14 &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
 GLAFIC         & 15 &  47 & 3 & 11 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\

### 2015-05-01 authors.tex
incorporating minor comments on draft, post redshift change   * notably: updated references and minor rearrangement of section 5  and new text in 6.6
added AR
added and re-sorted authors, text modifications   * tweaks to discussion of free-form models and simulations

@@
 \newcommand{\HongKong}{Department of Physics, The University of Hong Kong, Pokfulam Road, Hong Kong}
-\newcommand{\Oxford}{Department of Physics, Oxford University, Keble Road, Oxford OX1 3RH, UK}
+\newcommand{\Oxford}{Department of Physics, University of Oxford, Keble Road, Oxford OX1 3RH, UK}
 \newcommand{\CRAL}{CRAL, Observatoire de Lyon, Universit\'e Lyon 1, 9 Avenue Ch. Andr\'e, F-69561 Saint Genis Laval Cedex, France}
@@
 \newcommand{\IllinoisPhysics}{ Department of Physics, University of Illinois at Urbana-Champaign, 1110 W.\ Green Street, Urbana, IL 61801, USA }
+\newcommand{\INAF}{INAF, Osservatorio Astronomico di Bologna, via Ranzani 1, I-40127 Bologna, Italy}
+\newcommand{\JPL}{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Pasadena, CA 91109, USA}
+\newcommand{\INFN}{INFN, Sezione di Bologna, Viale Berti Pichat 6/2, I-40127 Bologna, Italy}
 
@@
 
-\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
-\affilreftxt{Durham}{\Durham}
-\affilreftxt{KwaZulu}{\KwaZulu}
-
 \author{Gabriel Brammer\altaffilmark{\affilref{STScI}}}
@@
 
-\author{Marusa Bradac\altaffilmark{\affilref{UCDavis}}}
+\author{Maru\v{s}a Brada\v{c}\altaffilmark{\affilref{UCDavis}}}
 \affilreftxt{UCDavis}{\UCDavis}
 
-\author{Jose~Maria~Diego\altaffilmark{\affilref{Cantabria}}}
+\author{Jose~M.~Diego\altaffilmark{\affilref{Cantabria}}}
 \affilreftxt{Cantabria}{\Cantabria}
-
-\author{Jens Hjorth\altaffilmark{\affilref{DARK}}}
-\affilreftxt{DARK}{\DARK}
 
@@
 
+\author{Jens Hjorth\altaffilmark{\affilref{DARK}}}
+\affilreftxt{DARK}{\DARK}
+
 \author{Austin Hoag\altaffilmark{\affilref{UCDavis}}}
 \affilreftxt{UCDavis}{\UCDavis}
+
+\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
+\affilreftxt{Durham}{\Durham}
+\affilreftxt{KwaZulu}{\KwaZulu}
 
@@
 
+\author{Curtis McCully\altaffilmark{\affilref{LCOGT},\affilref{UCSB}}}
+\affilreftxt{LCOGT}{\LCOGT}
+\affilreftxt{UCSB}{\UCSB}
+
 \author{Elinor Medezinski\altaffilmark{\affilref{JHU},\affilref{Hebrew}}}
@@
 \affilreftxt{Hebrew}{\Hebrew}
+
+\author{Massimo Meneghetti\altaffilmark{\affilref{INAF},\affilref{JPL},\affilref{INFN}}}
+\affilreftxt{INAF}{\INAF}
+\affilreftxt{JPL}{\JPL}
+\affilreftxt{INFN}{\INFN}
 
@@
 \affilreftxt{CRAL}{\CRAL}
+
+\author{Adam Riess\altaffilmark{\affilref{JHU},\affilref{STScI}}}
+\affilreftxt{JHU}{\JHU}
+\affilreftxt{STScI}{\STScI}
 
@@
 
-\author{Liliya Williams\altaffilmark{\affilref{Minnesota}}}
+\author{Liliya~L.~R.~Williams\altaffilmark{\affilref{Minnesota}}}
 \affilreftxt{Minnesota}{\Minnesota}

### 2015-05-01 snTomas.tex
added and re-sorted authors, text modifications   * tweaks to discussion of free-form models and simulations

@@
 with resolutions of $\sim$100
-pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
+pc \citep[e.g.][]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
 
@@
 space more fully than parametric methods.  This is reflected in the
-size of the error-bars in Figure~\ref{fig:LensingTest}.  For example,
-the Williams model (using GRALE) has the largest uncertainties, in
-part because it accounts for mass sheet degeneracy by introducing a
-free parameter in the reconstruction that represents an arbitrarily
-scaled mass sheet, with normalization to be chosen by the genetic
-algorithm.  More complex degeneracies are also accounted for in this
-model through the use of basis
-functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}
+size of the error-bars in Figure~\ref{fig:LensingTest}.  The Williams
+model (using GRALE) has the largest uncertainties, \changeR{with a
+68\% confidence range that encompasses the median magnification values
+returned by all other models.  This is possibly the most complete
+uncertainty estimate as it includes many systematic error sources
+that are not incorporated into most other models. For example, this
+implementation of GRALE} accounts for mass sheet degeneracy by
+introducing a free parameter in the reconstruction that represents an
+arbitrarily scaled mass sheet, with normalization to be chosen by the
+genetic algorithm.  More complex degeneracies are also accounted for
+in this model through the use of basis
+functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}.
 
@@
 A promising avenue for exploring the origins of systematic biases in
-cluster lens models is through the use of simulated lensing data.  One can
-start with very deep high-resolution multi-band imaging on an unlensed
-field that has a fairly complete spectroscopic redshift catalog, such
-as the Hubble Ultra Deep Field.  Then a simulated galaxy cluster is
-placed in the field, and the background galaxies are distorted into
-arcs and multiple images using a well-defined lensing prescription.
-The artificially lensed images can then be distributed to lens
-modeling teams who attempt to reconstruct the (known) mass profile of
-the simulated cluster.  This exercise has recently been pursued with a
-set of synthetic clusters similar to those observed in the HFF program
-(Meneghetti et al. in prep).  Preliminary analysis of this simulation
-comparison suggests that magnifications tend to be
+cluster lens models is through the use of simulated lensing data.  One
+can start with very deep high-resolution multi-band imaging on an
+unlensed field that has a fairly complete spectroscopic redshift
+catalog, such as the Hubble Ultra Deep Field.  Then a simulated galaxy
+cluster is placed in the field, and the background galaxies are
+distorted into arcs and multiple images using a well-defined lensing
+prescription.  The artificially lensed images can then be distributed
+to lens modeling teams who attempt to reconstruct the (known) mass
+profile of the simulated cluster.  This exercise has recently been
+pursued with a set of synthetic clusters similar to those observed in
+the HFF program (Meneghetti et al. in prep).  Preliminary analysis of
+this simulation comparison suggests that magnifications tend to be
 overestimated for sources that lie outside the strong-lensing region
-along the minor axis direction of an elongated cluster.  Our analysis
-of SN \tomas\ here indicates that such simulation efforts will be an
-important step for moving toward precision science with cluster-lensed
-sources.
+along the minor axis direction of \changeR{simulated clusters that are
+very elongated, similar to Abell 2744. This finding would be
+consistent with a recent lens model comparison on 25 real clusters
+from the CLASH program \citep{Zitrin:2015}.} Our analysis of
+SN \tomas\ here indicates that such simulation efforts \changeR{and
+head-to-head lens model comparisons} will be an important step for
+moving toward precision science with cluster-lensed sources.
 
@@
 
-Financial support for this work was provided to SAR by NASA through grants
-HST-HF-51312 and HST-GO-13386 from STScI, which is operated by Associated Universities for
-Research in Astronomy, Inc. (AURA), under NASA contract NAS 5-26555.
-
-AM acknowledge the financial support of the Brazilian funding agency
-FAPESP (Post-doc fellowship - process number 2014/11806-9)
-
-Support for this research at Rutgers University was provided in part
-by NSF CAREER award AST-0847157 to SWJ.  The Dark Cosmology Centre is
-supported by the Danish National Research Foundation.
-
-J.M.D acknowledges support of the consolider project CSD2010-00064 and
-AYA2012-39475-C02-01 funded by the Ministerio de Economia y
-Competitividad.
-
-J.M. contributed to this research from the Jet Propulsion Laboratory,
-California Institute of Technology, under a contract with NASA and
-acknowledges support from NASA Grants HST-GO-13343.05-A and
-HST-GO-13386.13-A. The research leading to these results has received
-funding from the People Programme (Marie Curie Actions) of the European
-Union's Seventh Framework Programme (FP7/2007-­2013) under REA grant
-agreement number 627288.
-
-A.Z. acknowledges financial support from NASA through grant
-HST-HF-51334.01-A awarded by STScI and operated by AURA.
+Financial support for this work was provided to S.A.R. by NASA through
+grants HST-HF-51312 and HST-GO-13386 from STScI, which is operated by
+Associated Universities for Research in Astronomy, Inc. (AURA), under
+NASA contract NAS 5-26555. A.M. acknowledge the financial support of
+the Brazilian funding agency FAPESP (Post-doc fellowship - process
+number 2014/11806-9). Support for this research at Rutgers University
+was provided in part by NSF CAREER award AST-0847157 to SWJ.  The Dark
+Cosmology Centre is supported by the Danish National Research
+Foundation. J.M.D acknowledges support of the consolider project
+CSD2010-00064 and AYA2012-39475-C02-01 funded by the Ministerio de
+Economia y Competitividad. J.M. contributed to this research from the
+Jet Propulsion Laboratory, California Institute of Technology, under a
+contract with NASA and acknowledges support from NASA Grants
+HST-GO-13343.05-A and HST-GO-13386.13-A. The research leading to these
+results has received funding from the People Programme (Marie Curie
+Actions) of the European Union's Seventh Framework Programme
+(FP7/2007-­2013) under REA grant agreement number
+627288. A.Z. acknowledges financial support from NASA through grant
+HST-HF-51334.01-A awarded by STScI and operated by AURA. LLRW
+acknowledges the support of the Minnesota Supercomputing Institute.
 

### 2015-05-01 snTomas.tex
added a legend to Fig 8

@@
 
-\keywords{ supernovae: general, supernovae: individual: HFF14Tom, 
-galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, 
-gravitational lensing: strong, gravitational lensing: weak  }
+%\keywords{ supernovae: general, supernovae: individual: HFF14Tom, 
+%galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, 
+%gravitational lensing: strong, gravitational lensing: weak  }
 
@@
 of the SNID template library, which includes template SEDs covering
-all Type Ia and Core Collapse sub-classes, and has recently been
+all Type Ia and core collapse sub-classes, and has recently been
 updated with corrections and improvements to the Type Ib/c
@@
 $\chi^2/\nu=240.8/90$ (fourth panel of Figure~\ref{fig:SpecFit}).  }
+\changeR{SN 2011fe had effectively no dust reddening \citep[e.g.][]{Nugent:2011,Li:2011c}, so the fact that SN 2011fe provides the best un-warped template match is further evidence that SN \tomas\ suffers from very little dust extinction.}
 
@@
 discrepancy.  A dust-induced bias is also disfavored by the very blue
-color of SN \tomas. SN \tomas\ is dimmed by foreground dust.
+color of SN \tomas.
 \item Misclassification: The combination of spectroscopic and

### 2015-05-01 snTomasCode/lensing_test_fig.py

@@ -157,7 +157,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
     pl.draw()
 
 
-def mkTensionFig(presfig=False):
+def mkTensionFig(presfig=False, showlegend=True):
     from matplotlib import ticker,pyplot as pl, rcParams
     from pytools import plotsetup
     from astropy.io import ascii
@@ -226,7 +226,23 @@ def mkTensionFig(presfig=False):
     ax1.xaxis.set_minor_locator( ticker.MultipleLocator( 2 ) )
     ax2.xaxis.set_major_locator( ticker.MultipleLocator( 0.2 ) )
     ax2.xaxis.set_minor_locator( ticker.MultipleLocator( 0.05 ) )
-    pl.setp(ax2.get_yticklabels(), visible=False)
+    ax2.yaxis.set_ticks_position('right')
+    # pl.setp(ax2.get_yticklabels(), visible=False)
 
+    if showlegend:
+        axleg = pl.axes([0.75,0.68,0.18,0.22], frameon=True )
+        SLpre    = axleg.plot(0,2,marker='o',mfc='w',mec='0.5',ls=' ',ms=ms,label='strong')
+        SLWLpre  = axleg.plot(0,1,marker='D',mfc='w',mec='0.5',ls=' ',ms=ms,label='str+wk')
+        SLpost   = axleg.plot(1,2,marker='o',mfc='k',mec='0.5',ls=' ',ms=ms,label='strong')
+        SLWLpost = axleg.plot(1,1,marker='D',mfc='k',mec='0.5',ls=' ',ms=ms,label='str+wk')
+        unblind  = axleg.plot(0.5,0,marker='s',mfc='w',mec='magenta',ls=' ',ms=ms,label='unblind')
+        axleg.text( -0.5, 2.5, 'pre/post-HFF', ha='left',va='bottom' )
+        axleg.text( 1.5, 2.0, 'strong', va='center' )
+        axleg.text( 1.5, 1.0, 'str+wk', va='center' )
+        axleg.text( 1.5, 0.0, 'unblind', va='center' )
+        axleg.set_xlim(-0.8,3.8)
+        axleg.set_ylim(-0.6,3.7)
+        axleg.xaxis.set_ticks([])
+        axleg.yaxis.set_ticks([])
     pl.draw()
 

### 2015-05-01 snTomas.tex
really minor tweaks to text. Added some caveats on unblind models

@@
 magnification.  We evaluate possible causes for this mild
-bias, \changeR{and reject explanations that invoke modeling errors or
-misinterpretation of the SN data. We conclude that -- at least for
-this cluster and this line of sight -- the most accurate models are
-those that employ stringent quality cuts for strong-lensing
-constraints.} \change{A more robust evaluation of systematic biases
+bias, \changeR{and reject explanations that
+invoke} \changeP{misinterpretation of the SN data or errors in the
+definition of the lens models}. \changeR{We conclude that -- at least for this
+cluster and this line of sight -- the most accurate models are those
+that employ stringent quality cuts for strong-lensing
+constraints.} \change{ A more robust evaluation of systematic biases
 could be achieved with further cooperative lens model comparisons
@@
 the most successful lens models (Bradac(v2), Lam(v2), Diego) do share
-a common quality: they all use a set of multiply-imaged galaxies for
+a common characteristic: they all use a set of multiply-imaged galaxies for
 which a large fraction have spectroscopic redshifts. In practice,
 this means that the strong-lensing constraints in these models are
-defined more stringently than other models. Some other models may use
+defined more stringently. Other models use
 a larger set of strong-lensing features, but the dearth of
@@
 spectroscopic redshifts, or at least very well constrained photometric
-redshifts.  The {\it quantity} of strong-lensing constraints is not as
-important as their {\it quality}.
-}
+redshifts.}
+\changeP{The {\it quality} of strong-lensing constraints is perhaps just as
+important as the {\it quantity}.}
+
+\changeP{
+It is relevant to note that the three models highlighted for their
+accuracy here (Bradac(v2), Lam(v2), Diego) also happen to be the three
+models that are not truly ``blind,'' in that the modelers were aware
+of preliminary analysis of the SN magnification.  However, none of
+these models used the SN magnification as an input constraint, none
+were tuned to match the SN magnification, and the modelers did not
+have a final measurement of the SN magnification at the time their
+models were generated.}
 
@@
 light curve of SN \tomas\ are well matched by templates of a normal
-Type Ia SN at $z=1.3457$.  Using the two most prevalent \SNIa\
-light curve fitters, SALT2 and MLCS2k2, we get a consistent
-measurement of the distance modulus
-(Table~\ref{tab:MeasuredMagnification}).  Using a
+Type Ia SN at $z=1.3457$.  Using the two most prevalent \SNIa\ light
+curve fitters, SALT2 and MLCS2k2, we get a consistent measurement of
+the distance modulus (Table~\ref{tab:MeasuredMagnification}).  Using a
 cosmology-independent comparison against a sample of unlensed \SNeIa\

### 2015-05-01 snTomasCode/lensing_test_fig.py

@@ -203,6 +203,9 @@ def mkTensionFig(presfig=False, showlegend=True):
             mec=color
             mew=ms/8.
         specfrac = row['nzSpec']/float(row['nSys'])
+
+        nim = row['nIm']/float(row['nSys'])
+
         nsys = row['nSys']
         tension = (med-muSNmlcs)/np.sqrt(errminus**2+muSNmlcserr**2)
 

### 2015-05-04 TABLE/magnifications2.tex
fixed shuffled values in Table 4

@@
 \startdata
+CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS(v1sw)     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
+CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
 Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF\tablenotemark{e}  & LENSTOOL\tablenotemark{f} parametric, strong-lensing based model\\
-Sharon(v2)     & 17 &  60 & 2 & 14 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
-CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
-CATS(v1sw)     & 24 &  67 & 3 & 12 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
-GLAFIC         & 15 &  47 & 3 & 11 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
+Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
 Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD profiles for galaxies and NFW profiles for dark matter halos.\\
 Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
+Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Williams       & 10 &  40 & 2 & 8  &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
 Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{i} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
-Bradac(v2)     & 10 &  40 & 2 & 8  &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Williams       & 16 &  56 & 2 & 14 &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
-Merten         & 25 &  72 & 7 & 18 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
 Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\

### 2015-05-04 snTomas.tex
fixed shuffled values in Table 4

@@
 pursued with a set of synthetic clusters similar to those observed in
-the HFF program (Meneghetti et al. in prep).  Preliminary analysis of
-this simulation comparison suggests that magnifications tend to be
-overestimated for sources that lie outside the strong-lensing region
-along the minor axis direction of \changeR{simulated clusters that are
-very elongated, similar to Abell 2744. This finding would be
+the HFF program (Meneghetti et al. in prep), \changeP{using techniques
+similar to \citet{Meneghetti:2010,Meneghetti:2014}}.  Preliminary
+analysis of this simulation comparison suggests that
+magnifications \change{can} be systematically overestimated for
+sources that lie outside the strong-lensing region along the minor
+axis direction of \changeR{ simulated clusters that are very
+elongated, similar to Abell 2744.}  \changeP{This indicates that some
+lens models significantly underestimate the ellipticity of the mass
+distribution on large scales for those simulated clusters, which is
 consistent with a recent lens model comparison on 25 real clusters

### 2015-05-15 snTomas.tex
removed old changetext markings. tweak to cosmological parameter uncertainty section

--- 2015-05-01 snTomas.tex
@@
 SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
-\change{$z=1.3457\pm0.0001$} behind the galaxy cluster Abell 2744 ($z=0.308$). This
+$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
 SN has a projected separation from the cluster core of
@@
 extinction.  In a cosmology-independent analysis, we find that \tomas\
-is \change{$0.77\pm0.15$} magnitudes brighter than unlensed Type Ia
+is $0.77\pm0.15$ magnitudes brighter than unlensed Type Ia
 SNe at similar redshift, implying a lensing magnification
-of \change{$\mu_{\rm obs}=2.03\pm0.29$}.  We compare this direct
+of $\mu_{\rm obs}=2.03\pm0.29$. We compare this direct
 measurement of the magnification against predicted magnifications
-from \changeR{15 lens models developed by 8 independent groups},
+from 15 lens models developed by 8 independent groups,
 representing a broad range of methodologies and incorporating a
@@
 magnifications that are consistent with the measured $\mu$ to within
-the 1$\sigma$ uncertainties.  \changeR{However, the models exhibit a
+the 1$\sigma$ uncertainties.  However, the models exhibit a
 subtle systematic bias: all of the models that disagree with the SN by
-more than $1\sigma$ are {\it higher} than the measured value}
-and \change{6 of these models are $\geq1.5\sigma$} above the measured
+more than $1\sigma$ are {\it higher} than the measured value
+and 6 of these models are $\geq1.5\sigma$ above the measured
 magnification.  We evaluate possible causes for this mild
-bias, \changeR{and reject explanations that invoke modeling errors or
-misinterpretation of the SN data. We conclude that -- at least for
-this cluster and this line of sight -- the most accurate models are
-those that employ stringent quality cuts for strong-lensing
-constraints.} \change{A more robust evaluation of systematic biases
+bias, and reject explanations that
+invoke misinterpretation of the SN data or errors in the
+definition of the lens models. We conclude that -- at least for this
+cluster and this line of sight -- the most accurate models are those
+that employ stringent quality cuts for strong-lensing
+constraints. A more robust evaluation of systematic biases
 could be achieved with further cooperative lens model comparisons
 using a larger sample of lensed Type Ia SNe as well as cluster lensing
-simulations.}
+simulations.
 \end{abstract}
@@
 object (called ``SN Refsdal'') within 5 years, delivering a precise
-test of lens model predictions \citep{Oguri:2015,Sharon:2015}.
+test of lens model predictions \citep{Oguri:2015,Sharon:2015,Diego:2015}.
 Although detections of such objects are currently very
@@
 appearance.  Labeled ellipses mark the nearest galaxies and their
-\changeG{spectroscopic} redshift constraints, with the most likely host
+spectroscopic redshift constraints, with the most likely host
 galaxy marked in blue, and a background galaxy in yellow. The bottom
@@
 actively star-forming galaxy at a redshift of
-$z=1.5\pm0.2$.  \change{This photo-z was subsequently refined to a
+$z=1.5\pm0.2$.  This photo-z was subsequently refined to a
 spectroscopic redshift of $z=1.3457\pm0.0001$, based on optical
@@
 Angstroms, consistent with the [OII] $\lambda\lambda$ 3726-3729 \AA\
-doublet.}
-
-The next nearest galaxy detected in HST imaging is \change{2.2\arcsec
-northeast of the SN position}. It has a redshift of $z=1.742$
+doublet.
+
+The next nearest galaxy detected in HST imaging is 2.2\arcsec
+northeast of the SN position. It has a redshift of $z=1.742$
 determined from a spectrum taken with the G141 grism of the HST
@@
 and \ref{sec:PhotometricClassification}, both the spectroscopic and
-photometric data from the SN itself are \change{consistent with the
+photometric data from the SN itself are consistent with the
 redshift of the fainter galaxy at $z=1.3457$, and
-incompatible with $z=1.742$ from this brighter galaxy.}  This means
+incompatible with $z=1.742$ from this brighter galaxy.  This means
 that the latter galaxy is a background object and therefore has no
@@
 overlaid with model fits derived from a library of Type Ia templates
-that have extended rest-frame UV coverage.  \changeG{The top two panels show
+that have extended rest-frame UV coverage.  The top two panels show
 the best matching templates when using a smooth 3rd-order polynomial
@@
 shows the best match in this set, although at $z=0.98$ it is
-inconsistent with the host galaxy redshift prior and the light curve.}
+inconsistent with the host galaxy redshift prior and the light curve.
 }
@@
 template spectrum by dividing out a 3$^{\rm rd}$-order polynomial to
-match the observed SED of SN \tomas.  \changeG{This approach will find
+match the observed SED of SN \tomas.  This approach will find
 templates that have similar abundances and photospheric
@@
 2012cg \citep{Amanullah:2015} at $z=1.31$ with $\chi^2/\nu=98.5/88$
-(second panel of Figure~\ref{fig:SpecFit}).}
-
-\changeG{
+(second panel of Figure~\ref{fig:SpecFit}).
+
 Next, we repeat the fitting, but without any warping of the templates
@@
 matched best by a SN 2011fe template, now at redshift $z=1.31$ with
-$\chi^2/\nu=240.8/90$ (fourth panel of Figure~\ref{fig:SpecFit}).  }
-\changeR{SN 2011fe had effectively no dust reddening \citep[e.g.][]{Nugent:2011,Li:2011c}, so the fact that SN 2011fe provides the best un-warped template match is further evidence that SN \tomas\ suffers from very little dust extinction.}
+$\chi^2/\nu=240.8/90$ (fourth panel of Figure~\ref{fig:SpecFit}).  
+SN 2011fe had effectively no dust reddening \citep[e.g.][]{Nugent:2011,Li:2011c}, so the fact that SN 2011fe provides the best un-warped template match is further evidence that SN \tomas\ suffers from very little dust extinction.
 
@@
 $z=0.98\pm0.01$. Formally, this match provides a slightly better fit
-to the unwarped \tomas\ spectrum \changeG{($\chi^2/\nu=220.6/90$,
-bottom panel of Figure~\ref{fig:SpecFit}),} although the fit is
+to the unwarped \tomas\ spectrum ($\chi^2/\nu=220.6/90$,
+bottom panel of Figure~\ref{fig:SpecFit}), although the fit is
 notably poorer at $\sim8700$\AA\ where the most significant absorption
@@
 rest-frame days from peak brightness, which is also consistent with
-the observed light curve.  \changeG{Taken together with the host galaxy
+the observed light curve.  Taken together with the host galaxy
 spectroscopic redshift, these fits suggest that SN \tomas\ is a normal
 Type Ia SN at $z=1.3457$ with an SED color close to SN 2011fe, but
-spectral absorption features similar to SN 2014J.}
+spectral absorption features similar to SN 2014J.
 
@@
 The marginal posterior distribution in redshift for the Type Ia model
-is sharply peaked at $z=1.35\pm0.02$, which \change{is fully
+is sharply peaked at $z=1.35\pm0.02$, which is fully
 consistent with the redshift of the presumed host galaxy ($z=1.3457$)
@@
 rest-frame days of the epoch of peak brightness -- also consistent
-with our spectroscopic analysis.}
+with our spectroscopic analysis.
 
@@
 $z=1.3457$, we now turn to fitting the light curve with Type Ia
-templates to measure the distance modulus \changeG{ and then derive
+templates to measure the distance modulus  and then derive
 the gravitational lensing magnification.  In this process, we would
@@
 which should be true for any plausible cosmological model.
-}
 
@@
 
-\changeG{
 As in \citealt{Patel:2014}, we derive a distance modulus for
@@
 light curve fitters: the SALT2 model described above and the MLCS2k2
-model \citep{Jha:2007}.  }  With both fitters we find light curve
+model \citep{Jha:2007}.    With both fitters we find light curve
 shape and color parameters for \tomas\ that are fully consistent with
 a normal Type Ia SN.  For SALT2, with the
-\change{redshift fixed at $z=1.3457$, we find a light curve shape
+redshift fixed at $z=1.3457$, we find a light curve shape
 parameter of $x_1=0.135\pm0.199$ and a color parameter of
@@
 parameter is $\Delta=-0.082\pm0.070$ and the color term is
-$A_{\rm V}=0.011\pm0.025$, giving $\chi^2/\nu=22.8/36$.}
-
-\changeG{
+$A_{\rm V}=0.011\pm0.025$, giving $\chi^2/\nu=22.8/36$.
+
  The MLCS2k2 fitter returns a distance
@@
 Mpc.}  $\rm{dm}_{\rm MLCS2k2}$ directly, as it is defined to be one of
-the free parameters in the model.} To derive dm from the SALT2 fit, we
+the free parameters in the model. To derive dm from the SALT2 fit, we
 use
@@
 to match the arbitrary normalization of the SALT2 fitter used
-by \citet{Guy:2010} and \citet{Sullivan:2011}.  \change{This conversion from SALT2 to SiFTO is necessary, as it} allows
+by \citet{Guy:2010} and \citet{Sullivan:2011}. This conversion from SALT2 to SiFTO is necessary, as it allows
 us to adopt values for the constants $M$, $\alpha$, and $\beta$
@@
 however that the uncertainty on the control sample value at $z=1.3457$
-is only 0.06 mag, smaller than the intrinsic dispersion \changeG{of
-any single SN} because it reflects our measurement error on the mean
+is only 0.06 mag, smaller than the intrinsic dispersion of
+any single SN because it reflects our measurement error on the mean
 distance modulus of the population.  The distance moduli derived from
@@
 should decrease with redshift, as metal-rich passive galaxies become
-much less common at $z>1$ \change{\citep[see
-e.g.][]{Rigault:2013,Childress:2014b}.}  Indeed, when the size of the
+much less common at $z>1$ \citep[see
+e.g.][]{Rigault:2013,Childress:2014b}.  Indeed, when the size of the
 mass step correction is allowed to vary with redshift, there is no
@@
 
-The unlensed sample comprises \change{22 spectroscopically confirmed Type Ia
-SNe in the range $1.14\leq z \leq1.55$ from three HST surveys: 11 from GOODS\footnote{GOODS: the Great Observatories Origins Deep Survey, PI:Giavalisco, HST-PID:9425,9583} \citep{Riess:2007}, 7 from SCP\footnote{SCP: the Supernova Cosmology Project, PI:Perlmutter} \citep{Suzuki:2012}, and 4 from CANDELS\footnote{CANDELS: the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey, PI:Faber \&\ Ferguson} \citep{Rodney:2012,Rodney:2014}.}  Using the SALT2 and MLCS2k2
+The unlensed sample comprises 22 spectroscopically confirmed Type Ia
+SNe in the range $1.14\leq z \leq1.55$ from three HST surveys: 11 from GOODS\footnote{GOODS: the Great Observatories Origins Deep Survey, PI:Giavalisco, HST-PID:9425,9583} \citep{Riess:2007}, 7 from SCP\footnote{SCP: the Supernova Cosmology Project, PI:Perlmutter} \citep{Suzuki:2012}, and 4 from CANDELS\footnote{CANDELS: the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey, PI:Faber \&\ Ferguson} \citep{Rodney:2012,Rodney:2014}.
+Using the SALT2 and MLCS2k2
 fitters as described above, we get distance modulus measures for every
@@
 using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom
-panel).  \changeR{Grey lines with shading show a linear fit to the
+panel).  Grey lines with shading show a linear fit to the
 unlensed control sample is shown, anchored at the redshift of
 SN \tomas, with fit parameters given at the top.  The derived
-magnification is reported at the bottom of each panel.}
+magnification is reported at the bottom of each panel.
 \label{fig:MagnificationMeasurement} }
@@
 given redshift and position.  In this work we also consider 8
-additional models that were created later.  \changeR{Some of these are
+additional models that were created later.  Some of these are
 updates of the original models produced in response to the lens
@@
 web tool hosted by STScI.  The full list of models and details on
-their construction are given in Table~\ref{tab:LensModels}.}
+their construction are given in Table~\ref{tab:LensModels}.
 
@@
 Table~\ref{tab:PredictedMagnifications} gives each model's predicted
-magnification and uncertainty for a source at \change{$z=1.3457$} and
+magnification and uncertainty for a source at $z=1.3457$ and
 at the position of \tomas.  These models represent a broad sampling of
@@
 (and ignoring their quoted uncertainties), one would get a mean for
-the full sample of \change{$\mu=2.5\pm0.4$.  This is separated from
+the full sample of $\mu=2.5\pm0.4$.  This is separated from
 the observed SN magnification by $\delta\mu/\mu=23\%$, which is
-approximately a 1$\sigma$ difference.}
+approximately a 1$\sigma$ difference.
 
@@
 size of the error-bars in Figure~\ref{fig:LensingTest}.  The Williams
-model (using GRALE) has the largest uncertainties, \changeR{with a
+model (using GRALE) has the largest uncertainties, with a
 68\% confidence range that encompasses the median magnification values
@@
 that are not incorporated into most other models. For example, this
-implementation of GRALE} accounts for mass sheet degeneracy by
+implementation of GRALE accounts for mass sheet degeneracy by
 introducing a free parameter in the reconstruction that represents an
@@
 return median magnifications that are {\it higher} than the observed
-value, and \change{six of the models are discrepant by more than $1.5\sigma$.}
+value, and six of the models are discrepant by more than $1.5\sigma$.
 It is important to emphasize that SN \tomas\ only samples a single
@@
 by this set of models.  In the following subsections we examine
-possible explanations for this small but \change{nearly} universal
-bias.  \changeR{We first consider whether a misinterpretation of the data on the SN
+possible explanations for this small but nearly universal
+bias.  We first consider whether a misinterpretation of the data on the SN
 itself can account for the observed systematic bias, and then 
- examine the lens models.}
+ examine the lens models.
 
@@
 inferred from the projected separation between the SN and nearby
-galaxies.  In this case the redshift \change{is strongly supported} by
+galaxies.  In this case the redshift is strongly supported by
 evidence from the SN
@@
 
-We have adopted the \change{most precise redshift of $z=1.3457$ from
+We have adopted the most precise redshift of $z=1.3457$ from
 the host galaxy as our baseline for the magnification comparison.  If
@@
 change in the inferred magnifications or in the suggestion of a small
-systematic bias.}
+systematic bias.
 
@@
 
-\changeG{
 Although the very blue color of SN \tomas\ is helpful to rule out dust
@@
 fit, though with a decrease in significance.
-}
 
@@
 
-\changeR{
 Having now ruled out misinterpetations of the SN data, we are left to
@@
 appear in the lens models.
-}
 
 \subsubsection{Cosmic Weak Lensing}
-\changeR{ 
 In addition to the dominant gravitational lensing from the foreground
@@
 itself.
-}
 
 \subsubsection{Nearby Cluster Member}
-\changeR{
 A component of the Abell 2744 lens that is particularly relevant to SN \tomas\ is the cluster member
@@
 Bradac, Williams and Merten models).
-}
 
 \subsubsection{Cosmological Parameter Uncertainty}
-\changeR{
 Most lens models make a
@@
 Incorporating this
-cosmological parameter uncertainty would increase the model magnification errors typically by 1-10\%. 
-This would reduce the tension between models and observation, but would not
-resolve the overall systematic shift.  Even a factor of 2.5 increase
-in the uncertainties (the most drastic change seen in the analysis
-of \citet{Bayliss:2015}) would still leave the most extreme outlier
-(CATS(v2)) discrepant by $2.9\sigma$. 
-}
+cosmological parameter uncertainty would increase the model magnification 
+errors, and therefore reduce the tension between models and observation, but would not
+resolve the overall systematic shift.
+\change{\citet{Bayliss:2015} find that for Abell 2744 the additional cosmological uncertainty for magnifications $\mu\approx2$ is $<10\%$ which would still leave 6 models discrepant by at least 1.5$\sigma$.}
 
@@
 
-\changeR{
 \citet{Jauzac:2014c} proposed a correction
@@
 significantly discrepant points.
-}
 
@@
 
-\changeR{
 None of the possibilities described above can completely account for
@@
 the most accurate models.  In this way SN \tomas\ may serve as a guide
-for optimizing future lens models for magnification predictions.  }
+for optimizing future lens models for magnification predictions.
 
@@
 \caption{ \label{fig:Nspecz}
-\changeR{
 The model tension as a function of strong-lensing constraints. The y
@@
 Figure~\ref{fig:LensingTest}.}
-}
 \end{center}
@@
 
-\changeR{
 As can be seen in Table~\ref{tab:LensModels} and
@@
 provide a satisfactory explanation for the small observed bias.
-}
-
-\changeR{
+
 However, the right panel of Figure~\ref{fig:Nspecz} shows that 3 of
 the most successful lens models (Bradac(v2), Lam(v2), Diego) do share
-a common quality: they all use a set of multiply-imaged galaxies for
+a common characteristic: they all use a set of multiply-imaged galaxies for
 which a large fraction have spectroscopic redshifts. In practice,
 this means that the strong-lensing constraints in these models are
-defined more stringently than other models. Some other models may use
+defined more stringently. Other models use
 a larger set of strong-lensing features, but the dearth of
@@
 those multiply-imaged galaxies are assigned with incorrect redshifts.
-}
-
-\changeR{
+
 This comparison suggests that to get accurate magnifications, lens
@@
 spectroscopic redshifts, or at least very well constrained photometric
-redshifts.  The {\it quantity} of strong-lensing constraints is not as
-important as their {\it quality}.
-}
+redshifts.
+The {\it quality} of strong-lensing constraints is perhaps just as
+important as the {\it quantity}.
+
+It is relevant to note that the three models highlighted for their
+accuracy here (Bradac(v2), Lam(v2), Diego) also happen to be the three
+models that are not truly ``blind,'' in that the modelers were aware
+of preliminary analysis of the SN magnification.  However, none of
+these models used the SN magnification as an input constraint, none
+were tuned to match the SN magnification, and the modelers did not
+have a final measurement of the SN magnification at the time their
+models were generated.
 
@@
 
-\change{
 Taking advantage of the availability of 15 well-constrained lens
@@
 discrepancy are too high.  This may be an indication that there is a
-small systematic bias at work.  }
+small systematic bias at work.
 
@@
 
-\changeR{
 Turning to the lens models, we have considered 4 ways in which a bias
 might be introduced into the lens models:
-}
 
@@
 \noindent
-\changeR{
 Although each of these could plausibly introduce a small systematic
@@
 to completely resolve the tension between models and observations.
-}
-
-\changeR{
+
 Finally, we have examined whether there is a simple prescription for
@@
 the input data appears to be a key ingredient for deriving accurate
-magnifications outside the strong-lensing regime.  }
+magnifications outside the strong-lensing regime.
 
@@
 pursued with a set of synthetic clusters similar to those observed in
-the HFF program (Meneghetti et al. in prep).  Preliminary analysis of
-this simulation comparison suggests that magnifications tend to be
-overestimated for sources that lie outside the strong-lensing region
-along the minor axis direction of \changeR{simulated clusters that are
-very elongated, similar to Abell 2744. This finding would be
+the HFF program (Meneghetti et al. in prep), using techniques
+similar to \citet{Meneghetti:2010,Meneghetti:2014}.  Preliminary
+analysis of this simulation comparison suggests that
+magnifications can be systematically overestimated for
+sources that lie outside the strong-lensing region along the minor
+axis direction of simulated clusters that are very
+elongated, similar to Abell 2744.  This indicates that some
+lens models significantly underestimate the ellipticity of the mass
+distribution on large scales for those simulated clusters, which is
 consistent with a recent lens model comparison on 25 real clusters
-from the CLASH program \citep{Zitrin:2015}.} Our analysis of
-SN \tomas\ here indicates that such simulation efforts \changeR{and
-head-to-head lens model comparisons} will be an important step for
+from the CLASH program \citep{Zitrin:2015}. Our analysis of
+SN \tomas\ here indicates that such simulation efforts and
+head-to-head lens model comparisons will be an important step for
 moving toward precision science with cluster-lensed sources.

### 2015-05-16 snTomas.tex
Updated abstract to be <250 words

@@
 \begin{abstract}
-SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
-$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
-SN has a projected separation from the cluster core of
-$\sim$40\arcsec, closer to the critical lensing line than any previous
-cluster-lensed Type Ia SN.  As such, it provides a valuable
-opportunity to confront gravitational lens models of galaxy clusters
+\change{Reduced to $<250$ words.}\\
+SN \tomas\ is a Type Ia Supernova (SN) discovered at
+$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744
+($z=0.308$). This SN 
+%has a projected separation from the cluster core
+%of $\sim$40\arcsec, 
+is closer to the critical lensing line than any
+previous cluster-lensed Type Ia SN, 
+%As such, it provides 
+providing a valuable
+opportunity to test galaxy cluster lens models
 with the direct measurement of an absolute magnification at the edge
-of the strong-lensing region.  We derive a tightly constrained measure
-of the peak apparent magnitude, corrected for light curve shape and
-extinction.  In a cosmology-independent analysis, we find that \tomas\
-is $0.77\pm0.15$ magnitudes brighter than unlensed Type Ia
-SNe at similar redshift, implying a lensing magnification
-of $\mu_{\rm obs}=2.03\pm0.29$. We compare this direct
-measurement of the magnification against predicted magnifications
-from 15 lens models developed by 8 independent groups,
-representing a broad range of methodologies and incorporating a
-variety of strong- and weak-lensing constraints.  The models are
-collectively fairly accurate: 8 of the models deliver median
-magnifications that are consistent with the measured $\mu$ to within
-the 1$\sigma$ uncertainties.  However, the models exhibit a
-subtle systematic bias: all of the models that disagree with the SN by
-more than $1\sigma$ are {\it higher} than the measured value
-and 6 of these models are $\geq1.5\sigma$ above the measured
-magnification.  We evaluate possible causes for this mild
-bias, and reject explanations that
-invoke misinterpretation of the SN data or errors in the
-definition of the lens models. We conclude that -- at least for this
-cluster and this line of sight -- the most accurate models are those
-that employ stringent quality cuts for strong-lensing
-constraints. A more robust evaluation of systematic biases
-could be achieved with further cooperative lens model comparisons
-using a larger sample of lensed Type Ia SNe as well as cluster lensing
-simulations.
+of the strong-lensing region.  
+%We derive a tightly constrained measure
+%of the peak apparent magnitude, corrected for light curve shape and
+%extinction.  
+In a cosmology-independent analysis, we find that \tomas\ is
+$0.77\pm0.15$ magnitudes brighter than unlensed Type Ia SNe at similar
+redshift, implying a lensing magnification of 
+$\mu_{\rm obs}=2.03\pm0.29$. 
+\change{In future lens models of Abell 2744 this could
+provide valuable leverage for breaking degeneracies that positional
+constraints cannot disentangle.}  We compare the measured $\mu$
+against predicted magnifications from 15 lens models, \change{ of
+which 13 were generated before the SN magnification was known,
+qualifying as a pure ``blind test.''}  The models are collectively
+fairly accurate: \change{6 of the blind models and both of the post-SN
+models} deliver median magnifications that are consistent with the
+measured $\mu$ to within 1$\sigma$.  However, there is a subtle
+systematic bias: all of the models that disagree with the SN $\mu$ 
+%by more than $1\sigma$ 
+are {\it higher} than the measured value and 6 of these
+are $\geq1.5\sigma$ above the measured magnification.  We
+evaluate possible causes for this mild bias,
+%and reject explanations
+%that invoke misinterpretation of the SN data or errors in the
+%definition of the lens models. We 
+and conclude that
+% -- at least for this
+%cluster and this line of sight -- 
+the most accurate models are those that employ stringent quality cuts
+for strong-lensing constraints. 
+% A more robust evaluation
+%\change{Further examination} of systematic biases 
+%could be achieved 
+%\change{could be pursued with more}
+%lens model comparisons using lensed
+%Type Ia SNe, as well as cluster lensing simulations.
 \end{abstract}

### 2015-05-16 TABLE/magnifications2.tex
more tweaks to discussion section. Updated some figs

@@
 \tablecolumns{7}
-\tablecaption{\changeR{Tested lens models for Abell 2744.\label{tab:LensModels}}}
+\tablecaption{Tested lens models for Abell 2744.\label{tab:LensModels}}
 \tablehead{ \colhead{Model} & \colhead{N$_{\rm sys}$\tablenotemark{a}} & \colhead{N$_{\rm im}$\tablenotemark{b}} & 
@@
 \startdata
+Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{i} : Free-form, strong+weak-lensing based model.
+Errors from bootstrap resampling only weak-lensing constraints.\\
 CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
 CATS(v1sw)     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
-GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
+Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
 Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF\tablenotemark{e}  & LENSTOOL\tablenotemark{f} parametric, strong-lensing based model\\
 Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
+Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
 Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD profiles for galaxies and NFW profiles for dark matter halos.\\
-Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
-Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
 Williams       & 10 &  40 & 2 & 8  &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
-Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{i} : Free-form, strong+weak-lensing based model.
-Errors from bootstrap resampling only weak-lensing constraints.\\
+\cutinhead{Post-HFF models : include data from the HFF program}\\
+CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.\\
+GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
+Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+\cutinhead{Unblind models : generated after the SN magnification was known}\\
 Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.\\
-Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.
 \enddata
@@
 \tablecolumns{4}
-\tablecaption{\changeR{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}}
+\tablecaption{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}
 \tablehead{ \colhead{Model\tablenotemark{a}} & 
@@
 \startdata
+Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
+CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
+CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
+Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
 Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
 Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
-CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
-CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
+Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
+Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
+Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\[0.1em]
+\tableline\\[-0.5em]
 CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
+Diego           &  \nodata  & 1.80  &   1.44$-$2.16 \\
 GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
-Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
-Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
-Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
+Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\[0.5em]
 Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
-Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\
-Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
-Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\
-Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28 \\
-Diego$^{\rm *}$ &  \nodata  & 1.80  &   1.44$-$2.16 \\
+Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28
 \enddata
-\tablenotetext{a}{Models marked by an asterisk were not part of the blind test, as they include modifications made after the measured magnification of the SN was known.}  
+\tablenotetext{a}{Models above the line are from the pre-HFF set, and those below incorporate HFF data.
+The final two, marked by an asterisk, were not part of the blind test as they include modifications made after the measured magnification of the SN was known.}
 \tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  

### 2015-05-16 snTomas.tex
more tweaks to discussion section. Updated some figs

@@
 would be {\it strongly lensed} SNe that are resolved into multiple
-images \citep{Holz:2001,Oguri:2003}.  Transients that are lensed into
+images\ \citep{Holz:2001,Oguri:2003}.  Transients that are lensed into
 multiple images can also become cosmological tools, as the measurement
@@
 cosmological parameters \citep{Linder:2011}.  We have recently
-observed the first example of a multiply-imaged
-SN \citep{Kelly:2015}, and expect to detect the reappearance of this
-object (called ``SN Refsdal'') within 5 years, delivering a precise
-test of lens model predictions \citep{Oguri:2015,Sharon:2015,Diego:2015}.
-Although detections of such objects are currently very
-unlikely \citep{Li:2012}, they will become much more common in the
-next decade \citep{Coe:2009,Dobke:2009}, and may be developed into an
-important new cosmological tool.
+observed the first example of a multiply-imaged SN \citep{Kelly:2015},
+and expect to detect the reappearance of this object (called ``SN
+Refsdal'') \change{within the next
+year} \citep{Oguri:2015,Sharon:2015,Diego:2015}, delivering a precise
+test of lens model predictions.  Although detections of such objects
+are currently very unlikely \citep{Li:2012}, they will become much
+more common in the next decade \citep{Coe:2009,Dobke:2009}, and may be
+developed into an important new cosmological tool.
 
@@
 gravitational lenses is in addressing the problem of the
-mass-sheet degeneracy \citep{Falco:1985,Bradac:2004}.  This
+mass-sheet degeneracy \citep{Falco:1985,Schneider:1995}.  This
 degeneracy arises because one can introduce into a lens model an
@@
 produce exactly the same values for all positional and shear
-constraints from strong and weak lensing.  When lensed background
+constraints from strong and weak lensing \citep{Seitz:1997}.  When lensed background
 sources are available across a wide range of redshifts (as is the case
@@
 possible to account for the simplest form of a single mass sheet
-within that redshift range.  However, there are more complex versions
+within that redshift range \citep{Bradac:2004}.  However, there are more complex versions
 of positional constraint
@@
 HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
-The HFF program is a 3-year director's discretionary initiative that
+The HFF program is a 3-year Director's discretionary initiative that
 is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
@@
 at $z\approx1.35$.  At this redshift, the absorption at $\sim$8700\AA\
-corresponds to the blended \ion{Ca}{2} H\&K features.
-This \ion{Ca}{2} absorption is commonly seen in Type Ia SN spectra
+corresponds to the blended \ion{Ca}{2} H\&K \change{and \ion{Si}{2} $\lambda$3858} features.
+\change{Generally referred to as the Ca H\&K feature, this} absorption is commonly seen in Type Ia SN spectra
 near maximum light, although it is also prominent in the spectra of
@@
 -- although this information was not used by {\tt SNID} for the
-template matching.  As we will see in Section~\ref{sec:PhotometricClassification},
-this spectral classification of SN \tomas\ is reinforced by the
-photometric information, which also supports classification as a Type
-Ia SN at $z\approx1.35$.
+template matching.  As we will see in
+Section~\ref{sec:PhotometricClassification}, this spectral
+classification of SN \tomas\ is reinforced by the photometric
+information, which also supports classification as a Type Ia SN at
+$z\approx1.35$.
 
@@
 with a $\chi^2$ per degree of freedom $\nu$ of $\chi^2/\nu=121.8/89$
-shown in the top panel of Figure~\ref{fig:SpecFit}.  Allowing the
-redshift as an additional free parameter, we still find results that
-are consistent with the SNID fits and $<2\sigma$ from the host galaxy
+shown in the top panel of Figure~\ref{fig:SpecFit}. \change{The excess
+variance in this fit may be attributed to the intrinsic variation of
+Type Ia SN spectra, which is more prominent at UV
+wavelengths \citep[e.g.][]{Foley:2008b,Wang:2012} and is not fully
+represented in the available template library.}  Allowing the redshift
+as an additional free parameter, we still find results that are
+consistent with the SNID fits and $<2\sigma$ from the host galaxy
 redshift: $z=1.31\pm0.02$ and a phase of $0\pm3$ rest-frame days. The
@@
 $z=1.3457$, we now turn to fitting the light curve with Type Ia
-templates to measure the distance modulus  and then derive
-the gravitational lensing magnification.  In this process, we would
-like to avoid introducing systematic uncertainties inherent to any
-assumed cosmological model \citep[e.g.][]{Nordin:2014}.  To that end,
-we follow \citealt{Patel:2014} and define the magnification by
-comparing the measured distance modulus of SN \tomas\ against an
-average distance modulus derived from a ``control sample'' of unlensed
-Type Ia SNe at similar redshift.  This allows us to make only the
-minimal assumption that the redshift-distance relationship for Type Ia
-SN is smooth and approximately linear over a small redshift span,
-which should be true for any plausible cosmological model.
+templates to measure the distance
+modulus \change{(\S\ref{sec:LightCurveFitting})} and then derive the
+gravitational lensing
+magnification \change{(\S\ref{sec:ControlSampleComparison})}.  In this
+process, we would like to avoid introducing systematic uncertainties
+inherent to any assumed cosmological model.  To that end, \change{in
+section \ref{sec:ControlSampleComparison}} we
+follow \citealt{Patel:2014} and define the magnification by comparing
+the measured distance modulus of SN \tomas\ against an average
+distance modulus derived from a ``control sample'' of unlensed Type Ia
+SNe at similar redshift. This allows us to make only the minimal
+assumption that the redshift-distance relationship for Type Ia SN is
+smooth and approximately linear over a small redshift span, which
+should be true for any plausible cosmological model.
 
@@
 The unlensed sample comprises 22 spectroscopically confirmed Type Ia
-SNe in the range $1.14\leq z \leq1.55$ from three HST surveys: 11 from GOODS\footnote{GOODS: the Great Observatories Origins Deep Survey, PI:Giavalisco, HST-PID:9425,9583} \citep{Riess:2007}, 7 from SCP\footnote{SCP: the Supernova Cosmology Project, PI:Perlmutter} \citep{Suzuki:2012}, and 4 from CANDELS\footnote{CANDELS: the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey, PI:Faber \&\ Ferguson} \citep{Rodney:2012,Rodney:2014}.
+SNe in the range $1.1<z<1.6$ from three HST surveys: 11 from the GOODS Higher-$z$ SN search\footnote{GOODS: the Great Observatories Origins Deep Survey, PI:Giavalisco, HST-PID:9425,9583} \citep{Strolger:2004,Riess:2007}, 7 from SCP\footnote{SCP: the Supernova Cosmology Project, PI:Perlmutter} \citep{Suzuki:2012}, and 4 from CANDELS\footnote{CANDELS: the Cosmic Assembly Near-infrared Deep Extragalactic Legacy Survey, PI:Faber \&\ Ferguson} \citep{Rodney:2012,Rodney:2014}.
 Using the SALT2 and MLCS2k2
@@
 
-\section{Discussion}
+%\section{Discussion}
+%\label{sec:Discussion}
+
+\section{Comparison to Model Predictions}
 \label{sec:Discussion}
-
-%\subsection{Comparison to Model Predictions}
-%\label{sec:ComparisonToModelPredictions}
+\label{sec:ComparisonToModelPredictions}
 
@@
 lens models. The vertical blue line shows the constraints from
-SN \tomas\ derived in Section~\ref{sec:DistanceAndMagnification} using the
-MLCS2k2 fitter, with a shaded region marking the total
+SN \tomas\ derived in Section~\ref{sec:DistanceAndMagnification} using
+the MLCS2k2 fitter, with a shaded region marking the total
 uncertainty. Markers with horizontal error bars show the median
@@
 constraints, while diamonds denote those that also incorporate
-weak-lensing measurements.  Models shown with open markers were
-constructed using only data available before the start of the Frontier
-Fields observations.  Filled markers indicate models that use
-additional input constraints, including new multiply imaged systems
-and redshifts.  Points with magenta outline indicate ``unblind''
-models, which were generated after the magnification of the SN was
-known. The eight models shown in black at the top are from
-the ``parametric'' family, and the six in green at the bottom are
-``free-form.''  The grey dashed line marks the unweighted mean for the
-set of all models, at $\mu=2.5$.
-\label{fig:LensingTest} }
+weak-lensing measurements.  \change{Models using a ``free-form''
+approach are shown as open markers, while those in the ``parametric''
+family are given filled markers.  The top half, with points in black, shows the nine
+models that were constructed using only data available before the
+start of the Frontier Fields observations. A black dashed line marks the
+unweighted mean for these models, at $\mu=2.6$.
+The lower six models in
+green used additional input constraints, including new multiply imaged
+systems and redshifts.  The final two points, with square orange
+outlines, are the ``unblind'' models that were generated after the
+magnification of the SN was known.  
+The green dashed line marks the
+unweighted mean for these six models, at $\mu=2.3$.
+\label{fig:LensingTest} }}
 \end{center}
@@
 Table~\ref{tab:PredictedMagnifications} gives each model's predicted
-magnification and uncertainty for a source at $z=1.3457$ and
-at the position of \tomas.  These models represent a broad sampling of
-the techniques and assumptions that can be applied to the modeling of
-mass distributions in galaxy clusters.  The first eight models in this
-table are so-called {\it parametric}\footnote{Although this
+magnification and uncertainty for a source at $z=1.3457$ and at the
+position of \tomas.  These models represent a broad sampling of the
+techniques and assumptions that can be applied to the modeling of mass
+distributions in galaxy clusters. 
+\change{We discuss some of the modeling choices here, but
+a more rigorous comparison of these disparate lens modeling techniques
+is beyond the scope of this work. For a complete discussion of each
+model's methodology the reader is directed to the listed references.}
+
+ Eight of these are so-called {\it parametric}\footnote{Although this
 nomenclature is becoming standard in the literature, it is somewhat
@@
 be more accurate, though we adopt the more common usage here.}
-models, and the bottom seven are {\it free-form} models.  Broadly
+models, and the remining seven are {\it free-form} models.  Broadly
 speaking, the parametric models use parameterized density
@@
 or pseudo isothermal elliptical mass
-distributions \citep[PIEMD][]{Kassiola:1993}.  Free-form models divide
+distributions \citep[PIEMD][]{Kassiola:1993}.
+
+Free-form models divide
 the cluster into a grid, generally using a multi-scale grid to get
@@
 model is iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.  
-A more rigorous comparison of these
-disparate lens modeling techniques is beyond the scope of this
-work.  For a complete discussion of each model's
-methodology, the reader is directed to the listed references.
-
-In Figure~\ref{fig:LensingTest} the model predictions are plotted
-alongside the observed magnification of SN \tomas, derived in
-Section~\ref{sec:DistanceAndMagnification}.  To first order, this
-comparison shows that these 15 models are largely consistent with each
-other and with the observed magnification of SN \tomas. Naively
-treating each model as an independent prediction for the magnification
-(and ignoring their quoted uncertainties), one would get a mean for
-the full sample of $\mu=2.5\pm0.4$.  This is separated from
-the observed SN magnification by $\delta\mu/\mu=23\%$, which is
-approximately a 1$\sigma$ difference.
-
-In general, free-form methods tend to explore the model parameter
-space more fully than parametric methods.  This is reflected in the
-size of the error-bars in Figure~\ref{fig:LensingTest}.  The Williams
+\change{
+In general, free-form methods tend to be more flexible than parametric methods,   
+as reflected by the
+size of the error-bars in Figure~\ref{fig:LensingTest}.
+For example, the Williams
 model (using GRALE) has the largest uncertainties, with a
 68\% confidence range that encompasses the median magnification values
-returned by all other models.  This is possibly the most complete
-uncertainty estimate as it includes many systematic error sources
-that are not incorporated into most other models. For example, this
+returned by all other models.  This is due in part to the 
+ inclusion of many systematic error sources. For example, this
 implementation of GRALE accounts for mass sheet degeneracy by
 introducing a free parameter in the reconstruction that represents an
-arbitrarily scaled mass sheet, with normalization to be chosen by the
-genetic algorithm.  More complex degeneracies are also accounted for
+arbitrarily scaled mass sheet. More complex degeneracies are also accounted for
 in this model through the use of basis
 functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}. 
+}
 
@@
 
-In spite of the great variety in input data and methodology, these
-lens models overall are delivering consistent and fairly accurate
-estimates of the magnification.  Seven of the tested models (CATS(v1),
-GLAFIC, Zitrin-NFW, Merten, Bradac(v2), Lam(v2), Diego) report a
-median value that falls within the 1$\sigma$ uncertainty range of the
-measured magnification, and three of the free-form models (Williams,
-Lam(v2), Diego) report uncertainties that overlap the central $\mu$ as
-measured from both of the SN light curve fitters.  Furthermore, the
-scatter amongst models provides a reasonable estimate of the
-magnification uncertainty.
+In Figure~\ref{fig:LensingTest} the model predictions are plotted
+alongside the observed magnification of SN \tomas, derived in
+Section~\ref{sec:DistanceAndMagnification}.  To first order, this
+comparison shows that these 15 models are largely consistent with each
+other and with the observed magnification of SN \tomas. \change{If we
+take the first set of 9 pre-HFF models and naively treat each as an
+independent prediction for the magnification (they are not all
+independent) and if we ignore their quoted uncertainties, we would get
+an unweighted mean for the pre-HFF sample of $\mu_{\rm
+pre}=2.6\pm0.4$.  This is separated from the observed SN magnification
+by $\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$
+difference. The addition of deeper imaging and new spectroscopic
+constraints from the HFF program and affiliated efforts should be
+expected to improve the lens models, and in fact we see that it does:
+the mean for the post-HFF sample is $\mu_{\rm post}=2.3\pm0.6$, fully
+consistent with the observed SN magnification.}
 
 This is largely in agreement with the results
-of \citetalias{Patel:2014} and \citet{Nordin:2014}.  The fact that the
-model predictions are collectively within $1\sigma$ of the observed
-magnification is especially encouraging for these Abell 2744
-models. This is a merging cluster with a complex mass distribution,
-and many of the models we are evaluating are preliminary products,
-generated quickly and without access to the rich data from the
-Frontier Fields program.
+of \citetalias{Patel:2014} and \citet{Nordin:2014}, \change{where
+model predictions were found to be in reasonably good agreement with a
+set of 3 lensed SNe from the CLASH program.  The general agreement
+between the model predictions and the SN measurement} is especially
+encouraging for these Abell 2744 models. This is a merging cluster
+with a complex mass distribution, and \change{the SN is located
+outside of the strong-lensing region where the models are most tightly
+constrained.}
+
+%In spite of the great variety in input data and methodology, these
+%lens models overall are delivering consistent and fairly accurate
+%estimates of the magnification.  Seven of the tested models (CATS(v1),
+%GLAFIC, Merten, Zitrin-NFW, Bradac(v2), Diego, Lam(v2)) report a
+%median value that falls within the 1$\sigma$ uncertainty range of the
+%measured magnification, and three of the models (Williams,
+%Diego, Lam(v2)) report uncertainties that overlap the central $\mu$ as
+%measured from both of the SN light curve fitters.
 
 However, beyond this first-order agreement, there is a small
-systematic bias apparent. All but two of the lens models
-return median magnifications that are {\it higher} than the observed
-value, and six of the models are discrepant by more than $1.5\sigma$.
-It is important to emphasize that SN \tomas\ only samples a single
-line of sight through the cluster, and this bias to higher
-magnifications is minor.  Nevertheless, a systematic
-shift of this nature is surprising, given the wide range of
-modeling strategies, input data, and physical assumptions represented
-by this set of models.  In the following subsections we examine
-possible explanations for this small but nearly universal
-bias.  We first consider whether a misinterpretation of the data on the SN
-itself can account for the observed systematic bias, and then 
- examine the lens models.
+systematic bias apparent. All but two of the lens models return median
+magnifications that are {\it higher} than the observed value, and six
+of the models are discrepant by more than $1.5\sigma$. \change{These
+six discrepant models are all biased to higher magnifications. They
+are found in both the pre-HFF and post-HFF models, in the parametric
+and free-form families, and among the strong-lensing-only and the
+strong+weak subsets.}  It is important to emphasize that SN \tomas\
+only samples a single line of sight through the cluster, and this bias
+to higher magnifications is minor.  Nevertheless, a systematic shift
+of this nature is surprising, given the wide range of modeling
+strategies, input data, and physical assumptions represented by this
+set of models.  In the following subsections we examine possible
+explanations for this small but nearly universal bias.  We first
+consider whether a misinterpretation of the data on the SN itself can
+account for the observed systematic bias, and then examine the lens
+models.
 
@@
 
-\subsection{Possible Errors in Lens Modeling}
-\label{sec:LensModelComparison}
-
-Having now ruled out misinterpetations of the SN data, we are left to
-seek an explanation for the mild tension by scrutinizing the lens
-models.  Here we evaluate four possible sources for a systematic bias to
-appear in the lens models.
+\subsection{Possible Errors in Lens Model Inputs}
+\label{sec:LensModelInputs}
+
+Having \change{found no evidence for} misinterpetations of the SN
+data, we are left to seek an explanation for the mild tension by
+scrutinizing the lens models.  Here we evaluate four
+possible \change{ways in which the input data or assumptions of these
+lens models could lead to a systematic bias in the magnification.}
 
@@
 \subsubsection{Misidentification of a multiple image}
-
 \citet{Jauzac:2014c} proposed a correction
@@
 
-\subsection{Quantity and Quality of Lensing Constraints}
-\label{sec:LensModelComparison}
-
-None of the possibilities described above can completely account for
-the mild tension between the observed and predicted magnifications.
-However, in lieu of a physical explanation, we can simply take a
-pragmatic approach and seek to identify any shared characteristics of
-the most accurate models.  In this way SN \tomas\ may serve as a guide
-for optimizing future lens models for magnification predictions.
+\change{
+\subsection{Best Practices for Magnification Prediction}
+\label{sec:BestPractices}
+}
+
+\change{
+None of the possible errors in lens model inputs described above can
+completely account for the mild tension between the observed and
+predicted magnifications.  However, we do have several models that
+agree with the measured SN magnification.  In this section we take a
+simple pragmatic approach and seek to identify any shared
+characteristics of the most accurate models.  In this way SN \tomas\
+may serve as a guide toward optimizing future lens models for
+magnification predictions.  }
 
@@
 
-As can be seen in Table~\ref{tab:LensModels} and
-Figure~\ref{fig:LensingTest}, among the 7 models that yield
-magnifications discrepant by more than 1$\sigma$ we find a variety of
-methodologies (both parametric and free-form) and a mix of lensing
-constraints (both strong-lensing only and strong+weak).  The left
-panel of Figure~\ref{fig:Nspecz} shows that this subset of 7 also
-includes a wide range in the number of multiply-imaged galaxies used
-as strong-lensing constraints (from $\sim$10 to 50).  Given that the
-discrepancy persists across all of these categories, none of them can
-provide a satisfactory explanation for the small observed bias.
-
-However, the right panel of Figure~\ref{fig:Nspecz} shows that 3 of
-the most successful lens models (Bradac(v2), Lam(v2), Diego) do share
-a common characteristic: they all use a set of multiply-imaged galaxies for
-which a large fraction have spectroscopic redshifts. In practice,
-this means that the strong-lensing constraints in these models are
-defined more stringently. Other models use
-a larger set of strong-lensing features, but the dearth of
-spectroscopic constraints means that it is more likely that some of
-those multiply-imaged galaxies are assigned with incorrect redshifts.
+\change{
+\subsubsection{Quantity and Quality of Strong Lensing Constraints}
+\label{sec:QuantityAndQuality}
+}
+
+\change{
+Increasing the number of multiply imaged galaxies used as
+strong-lensing constraints should in principle lead to improvements in
+the accuracy and precision of magnification predictions.  We have
+already seen some suggestion of this from
+Figure~\ref{fig:LensingTest}, which shows that the post-HFF models are
+collectively better than the pre-HFF models at predicting the
+SN \tomas\ magnification.  
+The left panel of Figure~\ref{fig:Nspecz} isolates this variable by
+plotting the tension between each model prediction and the measured SN
+magnification against the number of multiply-imaged galaxies used as
+strong-lensing constraints. There is no clear correlation here, and in
+fact the most significant outlier (CATS(v2)) is actually the one using
+the most multiply-imaged systems.  
+}
+
+\change{
+In the right panel of
+Figure~\ref{fig:Nspecz} we examine an alternative explanation by plotting 
+the model tension against the fraction of strong-lensing constraints that have a spectroscopic redshift. 
+Here we see a suggestion of a trend, and find that two of the most successful lens
+models (Bradac(v2) and Lam(v2)) do share a common characteristic: they
+both use a set of multiply-imaged galaxies for which a large fraction
+have spectroscopic redshifts. In practice, this means that the
+strong-lensing constraints in these models are defined more
+stringently. Other models use a larger set of strong-lensing features,
+but the dearth of spectroscopic constraints means that it is more
+likely that some of those multiply-imaged galaxies are assigned with
+incorrect redshifts.
+}
 
@@
 
-It is relevant to note that the three models highlighted for their
-accuracy here (Bradac(v2), Lam(v2), Diego) also happen to be the three
+It is relevant to note that the two models highlighted for their
+accuracy here (Bradac(v2) and Lam(v2)) also happen to be the two
 models that are not truly ``blind,'' in that the modelers were aware
-of preliminary analysis of the SN magnification.  However, none of
-these models used the SN magnification as an input constraint, none
-were tuned to match the SN magnification, and the modelers did not
+of preliminary analysis of the SN magnification.  However, neither of
+these models used the SN magnification as an input constraint, neither
+were consciously tuned to match the SN magnification, and the modelers did not
 have a final measurement of the SN magnification at the time their
 models were generated.
+
+%\subsubsection{Source Plane Minimization}
+%
+%A third model that stands out for delivering both an accurate and fairly precise estimate of the magnification 
+%
+%A general tendency towards high model magnification can result when
+%lens models are minimized in the source plane (rather than the image
+%plane).  As the overall magnification of a given model
+%increases, differences in angle between the delensed
+%images of the same source become smaller, corresponding to an overly shallow lensing mass profile. In
+%the limit of only a small number of multiple images that cover a
+%limited range of source redshift, this results in a tendency to force all
+%sources toward the same location in the source plane, thereby
+%maximizing the magnification.
+%
+%Minimizing in the image plane avoids this well known bias but is much
+%more difficult (Broadhurst etal 2005 ApJ 621,53, Zitrin etal 2009,
+%MNRAS 396,1985) as model generated images must be searched for in the
+%image plane near the corresponding observed images.  
+%
+%Alternatively, one may guard against this bias using a modified source plane minimization that is
+%constrained not to generate overly small re-lensed sources  (Sendra etal 2012,MNRAS 437,2642,Diego etal
+%2014).
+%
+%For models that incorporate HFF
+%data, this bias should be reduced, as many
+%multiply images spread over a wide redshift range will lessen the bias
+%towards high magnification. 
+%
+%
+%
+%\subsubsection{Model Flexibility}
+%
+%Let us first define a successful magnification prediction as one whose
+%quoted uncertainties overlap the measured $\mu=2.03$ from the SN.
+%There are three models that meet this criteria: Williams, Diego, and
+%Lam(v2). All of these are free-form models
 

### 2015-05-16 snTomasCode/lensing_test_fig.py

@@ -45,8 +45,10 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
     y = ytop
     for row in lensingdat:
         y-=1
-        color = row['parametric'] and 'k' or 'g'
-        mfc = row['postFF'] and color or 'w'
+        # color = row['parametric'] and 'k' or 'g'
+        #mfc = row['postFF'] and color or 'w'
+        color = row['postFF'] and 'g' or 'k'
+        mfc = row['parametric'] and color or 'w'
         model = row['model']
         best = row['best']
         med = row['med']
@@ -56,12 +58,8 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
             marker='D'
         else:
             marker='o'
-        if row['postSN']:
-            mec='magenta'
-            mew=ms/7.
-        else :
-            mec=color
-            mew=ms/8.
+        mec=color
+        mew=ms/8.
 
         #ax1.plot( best, y, marker='x', ms=ms, color=color,
         #          zorder=100, label='_nolegend_' )
@@ -77,6 +75,11 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
                       marker=marker, mfc=mfc, mec=mec, mew=mew, ms=ms,
                       capsize=1, color=color, zorder=10,
                       label='_nolegend_' )
+        if row['postSN']:
+            ax1.plot( med, y, marker='s', mfc='w', mec='darkorange',
+                      mew=ms/7, ms=1.3*ms, zorder=-10,
+                      label='_nolegend_' )
+
         print( "%s discrepancy = %.2f sigma"%(model,(med-muSNmlcs)/np.sqrt(errminus**2+muSNmlcserr**2)))
         if labelvalues:
             label = '%s: $%.2f^{%+.2f}_{%+.2f}$'%( model, med, errplus, errminus )
@@ -89,10 +92,12 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
 
         ax1.text( xlabel, float(y)/ytop, label, ha=ha, va='center',
                   color=color, transform=ax1.transAxes)
[…]

### 2015-05-17 TABLE/magnifications2.tex
incorporated many comments from many people

@@
 \startdata
-Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{i} : Free-form, strong+weak-lensing based model.
+Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF\tablenotemark{e}; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{f} : Free-form, strong+weak-lensing based model.
 Errors from bootstrap resampling only weak-lensing constraints.\\
-CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL parametric strong-lensing based model.\\
+CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL\tablenotemark{h} parametric strong-lensing based model.\\
 CATS(v1sw)     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF\tablenotemark{e}  & LENSTOOL\tablenotemark{f} parametric, strong-lensing based model\\
+Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{i} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF;  & LENSTOOL parametric, strong-lensing based model\\
 Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
@@
 CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
-Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.\\
-GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\
-Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+Diego\tablenotemark{k} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{m} \\
+Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.\\
 \cutinhead{Unblind models : generated after the SN magnification was known}\\
-Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging.
+Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging and GLASS spectra.
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.
 \enddata
@@
 }
-\tablenotetext{f}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
+\tablenotetext{f}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
 \tablenotetext{g}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
-\tablenotetext{h}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{i}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
+\tablenotetext{h}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
+\tablenotetext{i}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
 \tablenotetext{j}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
-\tablenotetext{k}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{l}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
-\tablenotetext{m}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
-\tablenotetext{n}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
+\tablenotetext{k}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
 No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.
 }
+\tablenotetext{l}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
+\tablenotetext{m}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{n}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
+
 \end{deluxetable*}

### 2015-05-17 authors.tex
incorporated many comments from many people

@@
 \newcommand{\UCDavis}{University of California Davis, 1 Shields Avenue, Davis, CA 95616}
-\newcommand{\UCLA}{University of California, Los Angeles, CA 90095}
+\newcommand{\UCLA}{Department of Physics and Astronomy, University of California, Los Angeles, CA 90095}
+\newcommand{\Packard}{Packard Fellow}
 \newcommand{\CalTech}{California Institute of Technology, 1200 East California Boulevard, Pasadena, CA 91125}
@@
 \newcommand{\INFN}{INFN, Sezione di Bologna, Viale Berti Pichat 6/2, I-40127 Bologna, Italy}
+\newcommand{\EHU}{Fisika Teorikoa, Zientzia eta Teknologia Fakultatea, Euskal Herriko Unibertsitatea UPV/EHU}
+\newcommand{\Basque}{IKERBASQUE, Basque Foundation for Science, Alameda Urquijo, 36-5 48008 Bilbao, Spain}
 
@@
 
+\author{Tom Broadhurst\altaffilmark{\affilref{EHU},\affilref{Basque}}}
+\affilreftxt{EHU}{\EHU}
+\affilreftxt{Basque}{\Basque}
+
 \author{Jose~M.~Diego\altaffilmark{\affilref{Cantabria}}}
@@
 
-\author{Saurabh Jha\altaffilmark{\affilref{Rutgers}}}
+\author{Saurabh W.~Jha\altaffilmark{\affilref{Rutgers}}}
 \affilreftxt{Rutgers}{\Rutgers}
@@
 
-\author{Tommaso Treu\altaffilmark{\affilref{UCLA}}}
+\author{Tommaso Treu\altaffilmark{\affilref{UCLA},\affilref{Packard}}}
 \affilreftxt{UCLA}{\UCLA}
+\affilreftxt{Packard}{\Packard}
 

### 2015-05-17 snTomas.tex
incorporated many comments from many people

@@
 
-\title{Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744}
+\title{Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by the Galaxy Cluster Abell 2744}
 
@@
 $\mu_{\rm obs}=2.03\pm0.29$. 
-\change{In future lens models of Abell 2744 this could
-provide valuable leverage for breaking degeneracies that positional
+\change{In future lens models of Abell 2744, this could
+provide some leverage for breaking degeneracies that positional
 constraints cannot disentangle.}  We compare the measured $\mu$
@@
 %definition of the lens models. We 
-and conclude that
+and find that
 % -- at least for this
@@
 the most accurate models are those that employ stringent quality cuts
-for strong-lensing constraints. 
+\change{and use a large fraction of spectroscopically measured 
+redshifts of multiple images.}
 % A more robust evaluation
@@
 with resolutions of $\sim$100
-pc \citep[e.g.][]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
+pc \citep[e.g.][]{Stark:2008,Jones:2010,Yuan:2011,Wuyts:2014,Livermore:2015}.
 
@@
 for the study of $z>1.5$ supernovae
-(SNe) \citep[e.g.]{Kovner:1988,Kolatt:1998,Sullivan:2000,Saini:2000,Gunnarsson:2003,Goobar:2009,Postman:2012},
+(SNe) \citep[e.g.][]{Kovner:1988,Kolatt:1998,Sullivan:2000,Saini:2000,Gunnarsson:2003,Goobar:2009,Postman:2012},
 which are still extremely difficult to characterize in unlensed
-fields \citep[e.g.]{Riess:2001,Riess:2007,Suzuki:2012,Rodney:2012,Rubin:2013,Jones:2013}.
+fields \citep[e.g.][]{Riess:2001,Riess:2007,Suzuki:2012,Rodney:2012,Rubin:2013,Jones:2013}.
 
@@
 cosmological parameters \citep{Linder:2011}.  We have recently
-observed the first example of a multiply-imaged SN \citep{Kelly:2015},
-and expect to detect the reappearance of this object (called ``SN
+observed the first example of a multiply-imaged SN \citep{Kelly:2015}.
+We expect to detect the reappearance of this object (called ``SN
 Refsdal'') \change{within the next
@@
 more common in the next decade \citep{Coe:2009,Dobke:2009}, and may be
-developed into an important new cosmological tool.
+developed into an important new cosmological
+tool \citep{Oguri:2010,Linder:2011}.
 
@@
 put cluster mass models to the test with the much more common category
-of lensed Type Ia SNe.  
+of Type Ia SNe that are magnified but not multiply-imaged.  
 \citet[][hereafter P14]{Patel:2014} and \citet{Nordin:2014} presented
@@
 ``middle distance'' from the cluster core, where both strong- and
-weak-lensing constraints are unavailable.
+weak-lensing constraints are unavailable. \change{Moreover, given
+enough time, multiple background SNe Ia could be measured behind the
+same cluster, each providing a new magnification constraint.}
 
@@
 for the Abell 2744 cluster discussed here), it should in principle be
-possible to account for the simplest form of a single mass sheet
-within that redshift range \citep{Bradac:2004}.  However, there are more complex versions
+possible to break this degeneracy \citep{Seitz:1997,Bradac:2004}.  However, there are more complex versions
 of positional constraint
@@
 degeneracies do not extend to the {\it absolute} magnification of a
-background source's flux and size.  Therefore, an absolute measurement
+background source's flux and size.
+\change{In the case of the simple mass sheet degeneracy described above, the magnification scales as $\mu\propto(1-\lambda)^{-2}$ \citep[see e.g.][]{Bartelmann:2010}.} Therefore, an absolute measurement
 of magnification from a standard candle or a standard ruler
@@
 In Section~\ref{sec:DiscoveryAndFollowup} we present the discovery and
-follow-up observations of SN \tomas\ at $z=1.3457$, discovered behind the
-galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
+follow-up observations of SN \tomas\ at $z=1.3457$, discovered behind
+the galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
 and \ref{sec:PhotometricClassification} describe the spectroscopy and
 photometry of this SN, leading to a classification of the object as a
-normal Type Ia SN.  In Section~\ref{sec:LightCurveFitting} we make a
-direct measurement of the magnification of this source due to
-gravitational lensing, and compare to predictions from lens models.
-Finally, Section~\ref{sec:Discussion} discusses the tension between
-our magnification measurement and the lens models, with implications
-for the systematic error budget in magnification estimates for other
-high-$z$ lensed sources.
+normal Type Ia SN.  In Section~\ref{sec:DistanceAndMagnification} we
+make a direct measurement of the magnification of this source due to
+gravitational lensing.  Section~\ref{sec:Discussion} discusses the
+tension between our magnification measurement and the lens models,
+and our conclusions are summarized in Section~\ref{sec:SummaryAndConclusions}.
+with implications for the systematic error budget in magnification
+estimates for other high-$z$ lensed sources.
 
@@
 with the Advanced Camera for Surveys (ACS) in the F606W and F814W
-bands (V and i), collected on UT 2014 May 15 as part of the Hubble
+bands (V and I), collected on UT 2014 May 15 as part of the Hubble
 Frontier Fields (HFF) survey (PI:J.Lotz,
@@
 determined from a spectrum taken with the G141 grism of the HST
-WFC3-IR camera, collected as part of the Grism Lens Amplified Survey
-from Space (GLASS, PI:Treu, PID:13459, \citealt{Treu:2015}).  As we
+WFC3-IR camera, collected as part of the Grism Lens-Amplified Survey
+from Space (GLASS, PI:Treu, PID:13459, \citealt{Treu:2015,Schmidt:2014}).  As we
 will see in Sections~\ref{sec:Spectroscopy}
@@
 A spectrum of SN \tomas\ was collected with the ACS G800L grism on
-2014 June 4 and 7, when the SN was very near to its peak brightness.
-The observations -- listed at the bottom of Table~\ref{tab:Photometry}
--- used 5 HST orbits from the FrontierSN program for a total
+2014 June 4 and 7, when the SN was \change{within 3 observer-frame
+days of the observed peak brightness in the F814W band.}  The
+observations -- listed at the bottom of Table~\ref{tab:Photometry} --
+used 5 HST orbits from the FrontierSN program for a total
 spectroscopic exposure time of $\sim$10 ksec.  The grism data were
@@
 pipeline \citep{Brammer:2012}, which was developed for the 3D-HST
-program (PI:Van Dokkum; PID:12177, 12328) and also used by the Grism
-Lens Amplified Survey from Space (GLASS; PI:Treu; PID:13459).
+program (PI:Van Dokkum; PID:12177, 12328) and also used by the GLASS
+team.
 
@@
 
-Using {\tt SNID} we can find an acceptable \CCSN\ match only
-when we remove all age and redshift constraints. In this case the best
-non-Ia match is the Type Ic SN 1997ef, which delivers {\it rlap}$=6.8$
-at $z=0.51$ and age=47.3 rest-frame days past peak.  This is not as
-good a fit as the best Type Ia models, is at odds with the host galaxy
-redshift prior, and is strongly disfavored by the shape and colors of
-the SN light curve (see Section~\ref{sec:PhotometricClassification}).
+Using {\tt SNID} we can find an acceptable \CCSN\ match only when we
+remove all age and redshift constraints. In this case the best non-Ia
+match is the Type Ic SN 1997ef, which delivers {\it rlap}$=6.8$ at
+$z=0.51$ and age=47.3 rest-frame days past peak (71 observer-frame
+days).  This is not as good a fit as the best Type Ia models, is at
+odds with the host galaxy redshift prior, and is strongly disfavored
+by the shape and colors of the SN light curve (see
+Section~\ref{sec:PhotometricClassification}).
 
@@
 wavelengths, so the fits are more sensitive to the overall color of
-the SED. Fixing the redshift to $z=1.3457$, we find the best match is
+the SED.\footnote{Note that gravitational lensing does not affect the color of background sources at all, so the expected lensing magnification of \tomas\ does not affect this analysis.}  Fixing the redshift to $z=1.3457$, we find the best match is
 from the normal Type Ia SN 2011fe \citep{Mazzali:2014}, though the fit is quite poor, with
@@
 SN \tomas\ host galaxy mass, which we have measured to be
-$10^{10.135}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
+$10^{10.1}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
 {\it BPZ} SED fit (Section~\ref{sec:DiscoveryAndFollowup}) to define rest-frame optical magnitudes.
@@
 \input{TABLE/magnifications2}
+
+Table~\ref{tab:PredictedMagnifications} gives each model's predicted
+magnification and uncertainty for a source at $z=1.3457$ and at the
+position of \tomas.  
+\changeG{For thirteen of these models the SN magnification qualifies as a true
+``blind test'', as they were completed before the SN \tomas\
+magnification measurement was known.  The final two models (Bradac-v2
+and Lam-v2) are technically not blind, although none of these modelers
+used the SN magnification as a constraint, and the modelers did not
+have access to the final SN magnification value when constructing
+their model.}
+
+These models represent a broad sampling of the
+techniques and assumptions that can be applied to the modeling of mass
+distributions in galaxy clusters. 
+\change{We discuss some of the modeling choices here, but
+a more rigorous comparison of these disparate lens modeling techniques
+is beyond the scope of this work. For a complete discussion of each
+model's methodology the reader is directed to the listed references.}
+Eight of these are so-called {\it parametric}\footnote{Although this
+nomenclature is becoming standard in the literature, it is somewhat
+misleading, as the pixels or grid cells in free-form models are
+effectively parameters as well. Perhaps ``simply-parameterized'' would
+be more accurate, though we adopt the more common usage here.}
+models, and the remining seven are {\it free-form} models.  
+Broadly speaking, the parametric models use parameterized density
+distributions to describe the arrangement of mass within the cluster.
+%typically associating massive dark matter halos with the positions of
+%bright cluster member galaxies. 
+Therefore, parametric models rely (to
+varying degrees) on the assumption that the cluster's dark matter can
+be described by analytic forms such as NFW halos \citep{Navarro:1997},
+or pseudo isothermal elliptical mass
+distributions \citep[PIEMD][]{Kassiola:1993}.
+
+The seven free-form models divide the cluster field into a grid,
+generally using a multi-scale grid to get better sampling in regions with a higher density of information. Each grid cell is assigned a mass or a potential, and then
+the mass values are iteratively refined to match the observed lensing
+constraints. In some cases an adaptive grid is used so that the grid
+spacing itself can also be modified as the model is
+iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009,Bradac:2009}.
+\change{ In general, free-form methods tend to be more flexible than 
+parametric methods, as they are not guided (or restricted) by
+assumptions about the mass distribution of dark matter halos. }
+
+%\change{
+% Table~\ref{tab:PredictedMagnifications} also shows that the quoted
+% errors from these models vary widely.  At one extreme is the
+% Bradac(v2) model, with quoted magnification uncertainties of
+% $\pm$0.04, not accounting for systematic errors.  At the other
+% extreme is the Williams model, which has the largest uncertainties,
+% with a 68\% confidence range that encompasses the median
+% magnification values returned by all other models.  This is due in
+% part to the intentional exploration of many systematic error sources
+% such as the mass sheet degeneracy and more complex
+% degeneracies \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}.
+% }
 
@@
 
-Table~\ref{tab:PredictedMagnifications} gives each model's predicted
-magnification and uncertainty for a source at $z=1.3457$ and at the
-position of \tomas.  These models represent a broad sampling of the
-techniques and assumptions that can be applied to the modeling of mass
-distributions in galaxy clusters. 
-\change{We discuss some of the modeling choices here, but
-a more rigorous comparison of these disparate lens modeling techniques
-is beyond the scope of this work. For a complete discussion of each
-model's methodology the reader is directed to the listed references.}
-
- Eight of these are so-called {\it parametric}\footnote{Although this
-nomenclature is becoming standard in the literature, it is somewhat
-misleading, as the pixels or grid cells in free-form models are
-effectively parameters as well. Perhaps ``simply-parameterized'' would
-be more accurate, though we adopt the more common usage here.}
-models, and the remining seven are {\it free-form} models.  Broadly
-speaking, the parametric models use parameterized density
-distributions to describe the arrangement of mass within the cluster,
-typically associating massive dark matter halos with the positions of
-bright cluster member galaxies. Therefore, parametric models rely (to
-varying degrees) on the assumption that the cluster's dark matter can
-be described by analytic forms such as NFW halos \citep{Navarro:1997},
-or pseudo isothermal elliptical mass
-distributions \citep[PIEMD][]{Kassiola:1993}.
-
-Free-form models divide
-the cluster into a grid, generally using a multi-scale grid to get
-better sampling in denser regions. Each grid cell is assigned a mass
-or a potential, and then the mass values are iteratively refined to
-match the observed lensing constraints. In some cases an adaptive grid
-is used so that the grid spacing itself can also be modified as the
-model is iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.  
-\change{
-In general, free-form methods tend to be more flexible than parametric methods,   
-as reflected by the
-size of the error-bars in Figure~\ref{fig:LensingTest}.
-For example, the Williams
-model (using GRALE) has the largest uncertainties, with a
-68\% confidence range that encompasses the median magnification values
-returned by all other models.  This is due in part to the 
- inclusion of many systematic error sources. For example, this
-implementation of GRALE accounts for mass sheet degeneracy by
-introducing a free parameter in the reconstruction that represents an
-arbitrarily scaled mass sheet. More complex degeneracies are also accounted for
-in this model through the use of basis
-functions \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}. 
-}
-
-Figure~\ref{fig:LensingTest} also separates the models based on the
-scope of input data constraints used.  Ten of the models rely only on
-strong-lensing constraints (plotted as circles), while the other four
-also use weak-lensing measurements (diamonds).  Nine of the models
-were constructed using only pre-HFF data (open symbols), while six
-others added new multiply-imaged systems and redshifts (filled symbols).
-For twelve of these models the SN magnification qualifies as a true
-``blind test'', as they were completed before the SN \tomas\
-magnification measurement was known.  The remaining three models
-(Bradac-v2, Lam-v2, and Diego) are technically not blind, although
-none of these modelers used the SN magnification as a constraint, and
-the modelers did not have access to the final SN magnification value
-when constructing their model.
-
 In Figure~\ref{fig:LensingTest} the model predictions are plotted
@@
 constraints from the HFF program and affiliated efforts should be
-expected to improve the lens models, and in fact we see that it does:
-the mean for the post-HFF sample is $\mu_{\rm post}=2.3\pm0.6$, fully
-consistent with the observed SN magnification.}
+expected to improve the lens models, and in
+Figure~\ref{fig:LensingTest} we see that it does: the mean for the
+post-HFF sample is $\mu_{\rm post}=2.3\pm0.6$, fully consistent with
+the observed SN magnification.}
+
+%Figure~\ref{fig:LensingTest} also separates the models based on the
+%scope of input data constraints used.  Ten of the models rely only on
+%strong-lensing constraints (plotted as circles), while the other four
+%also use weak-lensing measurements (diamonds).
 
@@
 (Section~\ref{sec:SpecRedshift}) and the light curve
-Section~\ref{sec:PhotometricClassification}, which are both within the
-$1\sigma$ range of the photometric redshift for the nearest detected
-galaxy: $z=1.5\pm0.2$. This appears to be a solid and self-consistent
+Section~\ref{sec:PhotometricClassification}, which are both within
+$1\sigma$ of the spectroscopic redshift for the nearest detected
+galaxy: $z=1.3457$. This appears to be a solid and self-consistent
 picture, so the evidence strongly disfavors any redshift that is
@@
 that modify the inferred luminosity distance based on the SN color.
-If after applying these dust corrections we are still {\it
+If after applying these dust corrections we were still {\it
 underestimating} the effect of dust along this sight-line, then the SN
-would appear more dim, the inferred distance modulus would be higher,
-and the measured magnification would be reduced -- consistent with the
-discrepancy we observe.
+\change{would appear dimmer than it really is, the inferred distance modulus would be higher,
+and the measured magnification would be biased to an artifically low
+value. Thus, an underestimation of dust would be in the right
+direction to match discrepancy we observe.}
 
@@
 inferred magnification to $\mu_{\rm SALT2}=2.08\pm0.36$.  This would
-still be consistent with the mild tension apparent from the MLCS2k2
-fit, though with a decrease in significance.
+\change{slightly reduce the tension between the SALT2 measurement and the model predictions, though it would not be enough to completely alleviate it.}
 
@@
 
-\subsection{Possible Errors in Lens Model Inputs}
-\label{sec:LensModelInputs}
+\subsection{Possible Errors in Lens Modeling}
+\label{sec:LensModelErrors}
 
@@
 structure along the line of sight, sometimes called ``Cosmic Weak
-Lensing'' \citep[CWL;][]{Wong:2011,Host:2012,Bayliss:2014,McCully:2014,DAloisio:2014}.
+Lensing'' \citep[CWL;][]{Wong:2011,Host:2012,Collett:2013,Greene:2013,Bayliss:2014,McCully:2014,DAloisio:2014}.
 This CWL effect is most important for very high redshift sources
@@
 \change{
-\subsection{Best Practices for Magnification Prediction}
-\label{sec:BestPractices}
+\subsubsection{Source Plane Minimization}
+\label{sec:SourcePlaneMinimization}
+}
+
+\change{
+A general tendency towards high model magnification can result when
+lens models are minimized in the source plane (rather than the image
+plane).  For a given model, modifying the surface mass density to have
+a shallower profile (declining less quickly with radius) will lead to
+an increase in the predicted magnifications across the field.  As the
+magnification applies to both flux and area, the shallower profile
+also leads to a smaller source plane area, which necessarily brings
+delensed images of the same source closer together in the source
+plane.  Thus, any models that are optimized in the source plane will
+have a tendency toward shallower mass profiles and larger
+magnifications, which force all sources toward the same location in
+the source plane.  }
+
+\change{  There are several strategies for mitigating this well known bias.
+Optimizing a model in the image plane can  avoid this bias entirely \citep{Broadhurst:2005,Zitrin:2009a}. Alternatively, one may guard against it by using
+a modified source plane minimization that is constrained not to
+generate overly small re-lensed sources \citep{Sendra:2014,Diego:2014}.
+Finally, the effect of this bias should be reduced when one uses many strong
+lensing constraints over a wide range of redshifts. }
+
+\change{ Of the 15 models examined here, both of the Zitrin models 
+follow the first strategy, using image-plane optimization.  The
+Zitrin-LTM model delivers a significantly discrepant magnification,
+while the Zitrin-NFW latter is within 1$\sigma$ of the SN
+magnification.  The Diego model uses the second strategy of restricted
+source-plane minimization, and reports a magnification very close to
+the measured value.  The CATS(v2) model is the most extreme example of
+the final strategy, as it incorporates more multiply-imaged sources
+over a wider redshift range than any other model. However, this model
+is also the most discrepant, with a predicted $\mu$ that is $>4\sigma$
+from the SN magnification.  Thus, the results from this simplistic
+model comparison are mixed.  We therefore cannot conclude that source
+plane minimization alone is the root cause of the observed systematic
+bias. }
+
+%\change{
+%\subsection{Best Practices for Magnification Prediction}
+%\label{sec:BestPractices}
+%}
+
+\change{
+\subsection{Quantity and Quality of Strong Lensing Constraints}
+\label{sec:QuantityAndQuality}
 }
@@
 simple pragmatic approach and seek to identify any shared
-characteristics of the most accurate models.  In this way SN \tomas\
-may serve as a guide toward optimizing future lens models for
-magnification predictions.  }
+characteristics of the models that are most accurate for this
+particular sight-line.  In this way SN \tomas\ may serve as a guide
+toward optimizing future lens models for magnification predictions,
+particularly in regions where strong-lensing constratins may be
+scarce.}
 
@@
 \change{
-\subsubsection{Quantity and Quality of Strong Lensing Constraints}
-\label{sec:QuantityAndQuality}
-}
-
-\change{
 Increasing the number of multiply imaged galaxies used as
@@
 \change{
-In the right panel of
-Figure~\ref{fig:Nspecz} we examine an alternative explanation by plotting 
-the model tension against the fraction of strong-lensing constraints that have a spectroscopic redshift. 
-Here we see a suggestion of a trend, and find that two of the most successful lens
-models (Bradac(v2) and Lam(v2)) do share a common characteristic: they
-both use a set of multiply-imaged galaxies for which a large fraction
-have spectroscopic redshifts. In practice, this means that the
-strong-lensing constraints in these models are defined more
-stringently. Other models use a larger set of strong-lensing features,
-but the dearth of spectroscopic constraints means that it is more
-likely that some of those multiply-imaged galaxies are assigned with
-incorrect redshifts.
-}
-
-This comparison suggests that to get accurate magnifications, lens
-models should employ a strict vetting of the strong-lensing
-constraints.  Multiply-imaged systems should ideally have
-spectroscopic redshifts, or at least very well constrained photometric
-redshifts.
-The {\it quality} of strong-lensing constraints is perhaps just as
-important as the {\it quantity}.
+In the right panel of Figure~\ref{fig:Nspecz} we examine an
+alternative explanation by plotting the model tension against the
+fraction of strong-lensing constraints that have a spectroscopic
+redshift. Here we see evidence for a correlation between model
+accuracy and the fraction of multiply-imaged galaxies with
+spectroscopic redshifts.  The apparent correlation is anchored on one
+end by the low spectroscopic fraction and high tension for the
+CATS(v2) model. At the other end we find two of the most accurate lens
+models (Bradac(v2) and Lam(v2)), which both have a high spec-$z$
+fraction and low tension.}
+
+\change{
+Of course this is not direct causation.  Consider the limit of just a
+single multiply-imaged galaxy constraint: the spec-$z$ fraction could
+be 1.0 but the model would be wildly unconstrained.  Rather, the
+spec-$z$ fraction here serves as a stand-in for how stringently the
+strong-lensing constraints are defined in these models.  Erroneous
+redshifts assigned to multiply-imaged systems lacking a spec-$z$ are especially
+problematic for relatively low redshift background systems. At lower
+redshifts, the model-derived deflection angle and magnification show a
+more rapid variation with the redshift of the background galaxy than
+for similarly positioned high redshift background galaxies}
+
+The SN \tomas\ comparison therefore suggests that to get accurate
+magnifications, lens models should employ a strict vetting of the
+strong-lensing constraints.  Multiply-imaged systems should ideally
+have spectroscopic redshifts, or at least very well constrained
+photometric redshifts.  The {\it quality} of strong-lensing
+constraints is perhaps just as important as the {\it quantity}.
 
@@
 %
-%A general tendency towards high model magnification can result when
-%lens models are minimized in the source plane (rather than the image
-%plane).  As the overall magnification of a given model
-%increases, differences in angle between the delensed
-%images of the same source become smaller, corresponding to an overly shallow lensing mass profile. In
-%the limit of only a small number of multiple images that cover a
-%limited range of source redshift, this results in a tendency to force all
-%sources toward the same location in the source plane, thereby
-%maximizing the magnification.
-%
-%Minimizing in the image plane avoids this well known bias but is much
-%more difficult (Broadhurst etal 2005 ApJ 621,53, Zitrin etal 2009,
-%MNRAS 396,1985) as model generated images must be searched for in the
-%image plane near the corresponding observed images.  
-%
-%Alternatively, one may guard against this bias using a modified source plane minimization that is
-%constrained not to generate overly small re-lensed sources  (Sendra etal 2012,MNRAS 437,2642,Diego etal
-%2014).
-%
-%For models that incorporate HFF
-%data, this bias should be reduced, as many
-%multiply images spread over a wide redshift range will lessen the bias
-%towards high magnification. 
 %
@@
 discrepancy are too high.  This may be an indication that there is a
-small systematic bias at work.
-
-We have speculated on what could be the origin for such a systematic bias,
-first considering and rejecting three possible explanations that presume an error in the
-interpretation of the available SN data.
+small systematic bias at work, at least in some of the models.
+
+We have speculated on what could be the origin for such a systematic
+bias, first considering and rejecting three possible explanations that
+presume an error in the interpretation of the available SN data.
 
@@
 \item Misidentification of a multiple image
+\item Source plane minimization
 \end{enumerate}
@@
 Although each of these could plausibly introduce a small systematic
-bias, we find that none are likely to be significant enough
-to completely resolve the tension between models and observations.
+bias, we find that none are likely to be significant enough \change{(or
+universal enough)} to completely resolve the tension between models and
+observations.
 
@@
 sources that lie outside the strong-lensing region along the minor
-axis direction of simulated clusters that are very
+axis direction of a simulated cluster that is very
 elongated, similar to Abell 2744.  This indicates that some
 lens models significantly underestimate the ellipticity of the mass
-distribution on large scales for those simulated clusters, which is
+distribution on large scales for that simulated cluster, which is
 consistent with a recent lens model comparison on 25 real clusters
@@
 627288. A.Z. acknowledges financial support from NASA through grant
-HST-HF-51334.01-A awarded by STScI and operated by AURA. LLRW
+HST-HF-51334.01-A awarded by STScI and operated by AURA. 
+TT acknowledges support by the Packard Foundation in the form of Packard Research Fellowship. GLASS is funded by NASA through HST grant GO-13459. LLRW
 acknowledges the support of the Minnesota Supercomputing Institute.

### 2015-05-17 snTomas.tex
Adjustments to the host galaxy section

@@
 \begin{abstract}
-\change{Reduced to $<250$ words.}\\
+\changenote{Reduced to $<250$ words.}\\
 SN \tomas\ is a Type Ia Supernova (SN) discovered at
@@
 One of the key values in observing standard candles behind
-gravitational lenses is in addressing the problem of the
-mass-sheet degeneracy \citep{Falco:1985,Schneider:1995}.  This
-degeneracy arises because one can introduce into a lens model an
-unassociated sheet of uniform mass in front of or behind the
-lens, without disturbing the primary observable quantities.  For
-example, take a lens model with a given surface mass density $\kappa$,
-and then transform the surface mass density to
-$\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any arbitrary value
-$\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$ models will
-produce exactly the same values for all positional and shear
-constraints from strong and weak lensing \citep{Seitz:1997}.  When lensed background
-sources are available across a wide range of redshifts (as is the case
-for the Abell 2744 cluster discussed here), it should in principle be
-possible to break this degeneracy \citep{Seitz:1997,Bradac:2004}.  However, there are more complex versions
-of positional constraint
-degeneracies \citep{Schneider:2014,Liesenborgs:2012}.  Such
+gravitational lenses is in addressing the problem of the mass-sheet
+degeneracy \citep{Falco:1985,Schneider:1995}.  This degeneracy arises
+because one can introduce into a lens model an unassociated sheet of
+uniform mass in front of or behind the lens, without disturbing the
+primary observable quantities.  For example, take a lens model with a
+given surface mass density $\kappa$, and then transform the surface
+mass density to $\kappa^{\prime}=(1-\lambda)\kappa+\lambda$ for any
+arbitrary value $\lambda$.  Both the $\kappa$ and $\kappa^{\prime}$
+models will produce exactly the same values for all positional and
+shear constraints from strong and weak lensing \citep{Seitz:1997}.
+When lensed background sources are available across a wide range of
+redshifts (as is the case for the Abell 2744 cluster discussed here),
+it should in principle be possible to break this
+degeneracy \citep{Seitz:1997,Bradac:2004}.  However, there are more
+complex versions of positional constraint
+degeneracies \citep{Liesenborgs:2012,Schneider:2014}.  Such
 degeneracies do not extend to the {\it absolute} magnification of a
-background source's flux and size.
-\change{In the case of the simple mass sheet degeneracy described above, the magnification scales as $\mu\propto(1-\lambda)^{-2}$ \citep[see e.g.][]{Bartelmann:2010}.} Therefore, an absolute measurement
-of magnification from a standard candle or a standard ruler
-\citep{Sonnenfeld:2011}  can break these fundamental degeneracies
-\citep{Holz:2001}.
+background source's flux and size. \change{In the case of the simple
+mass sheet degeneracy described above, the magnification scales as
+$\mu\propto(1-\lambda)^{-2}$ \citep[see e.g.][]{Bartelmann:2010}.}
+Therefore, one can break these fundamental degeneracies with an
+absolute measurement of magnification from a standard
+candle \citep{Holz:2001} or a standard ruler \citep{Sonnenfeld:2011}.
 
@@
 follow-up observations of SN \tomas\ at $z=1.3457$, discovered behind
-the galaxy cluster Abell 2744.  Sections~\ref{sec:Spectroscopy}
+the galaxy cluster Abell 2744.  Section~\ref{sec:HostGalaxy} examines
+the SN host galaxy.  Sections~\ref{sec:Spectroscopy}
 and \ref{sec:PhotometricClassification} describe the spectroscopy and
@@
 gravitational lensing.  Section~\ref{sec:Discussion} discusses the
-tension between our magnification measurement and the lens models,
-and our conclusions are summarized in Section~\ref{sec:SummaryAndConclusions}.
-with implications for the systematic error budget in magnification
-estimates for other high-$z$ lensed sources.
+tension between our magnification measurement and the lens models. Our
+conclusions are summarized in Section~\ref{sec:SummaryAndConclusions},
+along with a discussion of future prospects.
 
@@
 
-The most probable host galaxy for SN \tomas\ is a faint and diffuse
-galaxy immediately to the south-east of the SN location.  With
-photometry of the host galaxy collected from the template images, we
-fit the spectral energy distribution (SED) using the {\it BPZ} code --
-a Bayesian photometric redshift estimator \citep{Benitez:2000}. 
-%The best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
-From the {\it BPZ} analysis, we found the host to be most likely an
-actively star-forming galaxy at a redshift of
-$z=1.5\pm0.2$.  This photo-z was subsequently refined to a
-spectroscopic redshift of $z=1.3457\pm0.0001$, based on optical
-spectroscopy of the host (Mahler et al. in prep.) that shows two
-significant ($>10\sigma$) emission lines at 8740.2 and 8746.7
-Angstroms, consistent with the [OII] $\lambda\lambda$ 3726-3729 \AA\
-doublet.
-
-The next nearest galaxy detected in HST imaging is 2.2\arcsec
-northeast of the SN position. It has a redshift of $z=1.742$
-determined from a spectrum taken with the G141 grism of the HST
-WFC3-IR camera, collected as part of the Grism Lens-Amplified Survey
-from Space (GLASS, PI:Treu, PID:13459, \citealt{Treu:2015,Schmidt:2014}).  As we
-will see in Sections~\ref{sec:Spectroscopy}
-and \ref{sec:PhotometricClassification}, both the spectroscopic and
-photometric data from the SN itself are consistent with the
-redshift of the fainter galaxy at $z=1.3457$, and
-incompatible with $z=1.742$ from this brighter galaxy.  This means
-that the latter galaxy is a background object and therefore has no
-impact on the SN magnification.
-
 Upon discovery, HST target-of-opportunity observations were triggered
@@
 imaging data.
+
+\section{Host Galaxy}
+\label{sec:HostGalaxy}
+
+The most probable host galaxy for SN \tomas\ is a faint and diffuse
+galaxy immediately to the south-east of the SN location.  With
+photometry of the host galaxy collected from the template images, we
+fit the spectral energy distribution (SED) using the {\it BPZ} code --
+a Bayesian photometric redshift estimator \citep{Benitez:2000}. 
+%The best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
+From the {\it BPZ} analysis, we found the host to be most likely an
+actively star-forming galaxy at a redshift of
+$z=1.5\pm0.2$.  This photo-z was subsequently refined to a
+spectroscopic redshift of $z=1.3457\pm0.0001$, based on optical
+spectroscopy of the host (Mahler et al. in prep.) that shows two
+significant ($>10\sigma$) emission lines at 8740.2 and 8746.7
+Angstroms, consistent with the [OII] $\lambda\lambda$ 3726-3729 \AA\
+doublet.
+
+The next nearest galaxy detected in HST imaging is 2.2\arcsec
+northeast of the SN position. It has a redshift of $z=1.742$
+determined from a spectrum taken with the G141 grism of the HST
+WFC3-IR camera, collected as part of the Grism Lens-Amplified Survey
+from Space (GLASS, PI:Treu, PID:13459, \citealt{Treu:2015,Schmidt:2014}).  As we
+will see in Sections~\ref{sec:Spectroscopy}
+and \ref{sec:PhotometricClassification}, both the spectroscopic and
+photometric data from the SN itself are consistent with the
+redshift of the fainter galaxy at $z=1.3457$, and
+incompatible with $z=1.742$ from this brighter galaxy.  This means
+that the latter galaxy is a background object and therefore has no
+impact on the SN magnification.
+
+\change{
+The galaxy identified as the host is not close enough to the cluster
+core to {\it necessarily} be multiply-imaged, but it is still possible
+that the host galaxy is one of the outer images of a multiple image
+system.  In such a case, and given the position of the SN host, one
+would expect that another image of the galaxy would be present at a
+similar brightness, and would therefore be detectable in HST
+imaging. To date, no plausible candidate for a counter-image has been
+identified.}
+
+\change{To measure the stellar mass of the host galaxy
+we use Eq. 8 of \citet{Taylor:2011}, which relates the rest-frame
+(g-i) color and i-band luminosity to the total stellar mass. To derive
+these values, we fixed the redshift at $z=1.3457$ and repeated the SED
+fitting using BPZ. From the best-fit SED we extracted rest-frame
+optical magnitudes, and corrected them for lensing using a
+magnification factor of $\mu=2.0$ -- a value that we will derive from
+the SN itself in Section~\ref{sec:DistanceAndMagnification}.  From
+this we determine the host galaxy mass to be $10^{10.1}$ \Msun. }
 
@@
 $10^{10}$\Msun, although this is somewhat arbitrary \citep[see
-e.g.][]{Betoule:2014}.  This happens to be very close to the
-SN \tomas\ host galaxy mass, which we have measured to be
-$10^{10.1}$ \Msun\ based on Eq. 7 of \citet{Taylor:2011}, using the
-{\it BPZ} SED fit (Section~\ref{sec:DiscoveryAndFollowup}) to define rest-frame optical magnitudes.
+e.g.][]{Betoule:2014}.
 
@@
 or the control sample.
+
+\change{
+If we were to apply the correction to this sample, then the SN \tomas\
+distance modulus would not be adjusted, because its host galaxy mass
+(Section~\ref{sec:HostGalaxy}) is below 10$^{10}$ \Msun. Note that
+there is some circularity here, as we used the SN magnification in
+deriving the host galaxy mass, and now use the host mass to inform the
+magnification.  However, changing the magnification value to $mu=2.5$
+does not move the \tomas\ host mass above the mass step threshold, so
+the circularity is not relevant in this case. Applying the
+mass step correction across the entire control sample would lead to a
+small adjustment of the inferred SN \tomas\ magnification, but it is $<5\%$
+and therefore could not relieve the observed tension.}
 
@@
 The seven free-form models divide the cluster field into a grid,
-generally using a multi-scale grid to get better sampling in regions with a higher density of information. Each grid cell is assigned a mass or a potential, and then
+generally using a multi-scale grid to get better sampling in regions
+with a higher density of information (e.g. density of multiple
+images). Each grid cell is assigned a mass or a potential, and then
 the mass values are iteratively refined to match the observed lensing
@@
 iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009,Bradac:2009}.
-\change{ In general, free-form methods tend to be more flexible than 
-parametric methods, as they are not guided (or restricted) by
-assumptions about the mass distribution of dark matter halos. }
+
+\change{
+As usual, there is a tradeoff between a model's flexibility, the
+strength of the model assumptions, and the resulting uncertainties. In
+a probabilistic framework, the posterior distribution function of the
+desired quantities depends on all the priors, including model
+assumptions like parametrization.  In general, free-form methods tend
+to be more flexibile than simply parameterized models, and thus tend
+to result in larger error bars.  In brief, if the free form methods
+are too flexible, then they will result in overestimated error
+bars. Conversely, if the simply parameterized models are too
+inflexible, they will result in underestimated error bars.
+}
 
@@
 
+In
+addition, some sources of uncertainty are taken into account only by a
+subset of models. For example, the Willams model (using GRALE;
+Liesenborgs et al. 2006, 2007; Mohammed et al. 2014) accounts for mass
+sheet degeneracy by introducing a free parameter in the reconstruction
+that represents an arbitrarily scaled mass sheet. The flexibility of
+the Williams model and the inclusion of this source of uncertainty
+contribute to its relatively large uncertainties compared to the other
+models.
+
 \subsubsection{Nearby Cluster Member}

### 2015-05-18 TABLE/magnifications2.tex
added latest CATSv2 models, using Wang'15 spec-z and MI lists

@@
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.\\
+CATS(v2.1)     & 50 & 151 & 7 & 18  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for the Bradac(v2) model.\\
+CATS(v2.2)     & 25 &  72 & 7 & 18  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for the Bradac(v2) model.
 \enddata
@@
 \tablenotetext{n}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
-
 \end{deluxetable*}
@@
 Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
-Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28
+Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28\\
+CATS(v2.1)$^{\rm *}$ & \nodata & 3.06  &   2.90$-$3.22 \\
+CATS(v2.2)$^{\rm *}$ & \nodata & 3.07  &   2.92$-$3.24 \\
 \enddata

### 2015-05-18 snTomas.tex
tiny tweaks
added latest CATSv2 models, using Wang'15 spec-z and MI lists

@@
 constraints cannot disentangle.}  We compare the measured $\mu$
-against predicted magnifications from 15 lens models, \change{ of
+against predicted magnifications from 17 lens models, \change{ of
 which 13 were generated before the SN magnification was known,
 qualifying as a pure ``blind test.''}  The models are collectively
-fairly accurate: \change{6 of the blind models and both of the post-SN
-models} deliver median magnifications that are consistent with the
-measured $\mu$ to within 1$\sigma$.  However, there is a subtle
-systematic bias: all of the models that disagree with the SN $\mu$ 
+fairly accurate: 8 of the models deliver median magnifications that
+are consistent with the measured $\mu$ to within 1$\sigma$.  However,
+there is a subtle systematic bias: all of the models that disagree
+with the SN $\mu$
 %by more than $1\sigma$ 
@@
 ``blind test'', as they were completed before the SN \tomas\
-magnification measurement was known.  The final two models (Bradac-v2
-and Lam-v2) are technically not blind, although none of these modelers
-used the SN magnification as a constraint, and the modelers did not
-have access to the final SN magnification value when constructing
-their model.}
+magnification measurement was known.  The final four models
+(Bradac-v2, Lam-v2, CATSv2.1 and 2.2) are technically not blind,
+although none of these modelers used the SN magnification as a
+constraint, and the modelers did not have access to the final SN
+magnification value when constructing their model.}
 
@@
 uncertainty. Markers with horizontal error bars show the median
-magnification and 68\%\ confidence region from each of the 15 lensing
+magnification and 68\%\ confidence region from each of the 17 lensing
 models.  Circles indicate models that use only strong-lensing
@@
 Section~\ref{sec:DistanceAndMagnification}.  To first order, this
-comparison shows that these 15 models are largely consistent with each
-other and with the observed magnification of SN \tomas. \change{If we
-take the first set of 9 pre-HFF models and naively treat each as an
-independent prediction for the magnification (they are not all
-independent) and if we ignore their quoted uncertainties, we would get
-an unweighted mean for the pre-HFF sample of $\mu_{\rm
-pre}=2.6\pm0.4$.  This is separated from the observed SN magnification
-by $\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$
-difference. The addition of deeper imaging and new spectroscopic
-constraints from the HFF program and affiliated efforts should be
-expected to improve the lens models, and in
-Figure~\ref{fig:LensingTest} we see that it does: the mean for the
-post-HFF sample is $\mu_{\rm post}=2.3\pm0.6$, fully consistent with
-the observed SN magnification.}
-
-%Figure~\ref{fig:LensingTest} also separates the models based on the
-%scope of input data constraints used.  Ten of the models rely only on
-%strong-lensing constraints (plotted as circles), while the other four
-%also use weak-lensing measurements (diamonds).
-
-This is largely in agreement with the results
-of \citetalias{Patel:2014} and \citet{Nordin:2014}, \change{where
+comparison shows that these 17 models are largely consistent with each
+other and with the observed magnification of SN \tomas. \change{ The
+``naive mean'' of the full set of models is $\mu_{\rm pre}=2.6\pm0.4$.
+This is an unweighted mean (i.e. we ignore all quoted uncertainties)
+derived by naively treating each as an independent
+prediction for the magnification (this is clearly incorrect, as
+several models are represented multiple times as different versions).
+The naive mean is separated from the observed SN magnification by
+$\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$ difference.}
+
+\change{
+This is approximately consistent with the results
+of \citetalias{Patel:2014} and \citet{Nordin:2014}, where
 model predictions were found to be in reasonably good agreement with a
 set of 3 lensed SNe from the CLASH program.  The general agreement
-between the model predictions and the SN measurement} is especially
+between the model predictions and the SN measurement is especially
 encouraging for these Abell 2744 models. This is a merging cluster
-with a complex mass distribution, and \change{the SN is located
+with a complex mass distribution, and the SN is located
 outside of the strong-lensing region where the models are most tightly
@@
 not significantly affect the predicted magnifications.  Furthermore,
-dividing our 15 models into those using the original location vs those
+dividing our 17 models into those using the original location vs those
 that adopt the new position, we find that both groups include models
@@
 
-\change{ Of the 15 models examined here, both of the Zitrin models 
+\change{ Of the 17 models examined here, both of the Zitrin models 
 follow the first strategy, using image-plane optimization.  The
@@
 constraint.  Marker shapes and colors are the same as in
-Figure~\ref{fig:LensingTest}.}
+Figure~\ref{fig:LensingTest}.
+\change{In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the quantity and quality of strong lensing constraints changed substantially from one model version to the next.}
+} 
 \end{center}
@@
 \change{
-Increasing the number of multiply imaged galaxies used as
-strong-lensing constraints should in principle lead to improvements in
-the accuracy and precision of magnification predictions.  We have
-already seen some suggestion of this from
-Figure~\ref{fig:LensingTest}, which shows that the post-HFF models are
-collectively better than the pre-HFF models at predicting the
-SN \tomas\ magnification.  
-The left panel of Figure~\ref{fig:Nspecz} isolates this variable by
-plotting the tension between each model prediction and the measured SN
-magnification against the number of multiply-imaged galaxies used as
-strong-lensing constraints. There is no clear correlation here, and in
-fact the most significant outlier (CATS(v2)) is actually the one using
-the most multiply-imaged systems.  
+The addition of deeper imaging and new spectroscopic constraints from
+the HFF program and affiliated efforts might be expected to improve
+the accuracy of magnification predictions. However, in
+Figure~\ref{fig:LensingTest} we saw no evidence for a universal
+improvement in model accuracy when moving from the pre- to the
+post-HFF models.  In Figure~\ref{fig:Nspecz} we attempt to refine this
+hypothesis by isolating the quantity and quality of strong lensing constraints. 
 }
+
+\change{
+The left panel plots the tension between each model prediction and the
+measured SN magnification against the number of multiply-imaged
+galaxies used as strong-lensing constraints. The Bradac, Lam and
+CATSv2 model series are highlighted here with connecting lines, as
+three examples where the number of systems used has changed
+substantially from one version to the next, but the model construction
+has remained fundamentally unchanged.
+There is no clear correlation here, and in
+fact for both the Lam and CATSv2 model series, we see the tension
+actually {\it increases} for a larger number of strong-lensing constraints.}
 
@@
 fraction of strong-lensing constraints that have a spectroscopic
-redshift. Here we see evidence for a correlation between model
-accuracy and the fraction of multiply-imaged galaxies with
-spectroscopic redshifts.  The apparent correlation is anchored on one
-end by the low spectroscopic fraction and high tension for the
-CATS(v2) model. At the other end we find two of the most accurate lens
-models (Bradac(v2) and Lam(v2)), which both have a high spec-$z$
-fraction and low tension.}
+redshift. Here we see that all three of the testable model series
+(Bradac,Lam,CATSv2) become {\it more} accurate as the spec-z fraction
+increases.\footnote{Of course this apparent correlation does not imply
+any direct causation. Consider the limit of just a single
+multiply-imaged galaxy constraint: the spec-$z$ fraction could be 1.0
+but the model would be wildly unconstrained.}  The spec-$z$ fraction
+here serves as a crude stand-in for measuring how
+stringently the strong-lensing constraints are selected in these
+models.
+}
 
 \change{
-Of course this is not direct causation.  Consider the limit of just a
-single multiply-imaged galaxy constraint: the spec-$z$ fraction could
-be 1.0 but the model would be wildly unconstrained.  Rather, the
-spec-$z$ fraction here serves as a stand-in for how stringently the
-strong-lensing constraints are defined in these models.  Erroneous
-redshifts assigned to multiply-imaged systems lacking a spec-$z$ are especially
-problematic for relatively low redshift background systems. At lower
-redshifts, the model-derived deflection angle and magnification show a
-more rapid variation with the redshift of the background galaxy than
-for similarly positioned high redshift background galaxies}
-
-The SN \tomas\ comparison therefore suggests that to get accurate
-magnifications, lens models should employ a strict vetting of the
-strong-lensing constraints.  Multiply-imaged systems should ideally
-have spectroscopic redshifts, or at least very well constrained
-photometric redshifts.  The {\it quality} of strong-lensing
-constraints is perhaps just as important as the {\it quantity}.
-
-It is relevant to note that the two models highlighted for their
-accuracy here (Bradac(v2) and Lam(v2)) also happen to be the two
-models that are not truly ``blind,'' in that the modelers were aware
-of preliminary analysis of the SN magnification.  However, neither of
-these models used the SN magnification as an input constraint, neither
-were consciously tuned to match the SN magnification, and the modelers did not
-have a final measurement of the SN magnification at the time their
-models were generated.
+The SN \tomas\ comparison therefore supports the notion that the {\it
+quality} of strong-lensing constraints is just as important as the
+{\it quantity}.  To get accurate magnifications, lens models should
+employ a strict vetting of the multiply-imaged systems.  Each system
+used should ideally have a spectroscopic redshift, or at least a very
+well constrained photometric redshift.  The primary value in this
+strict vetting is to avoid erroneous redshifts being assigned to
+multiply-imaged systems that are unconstrained in redshift space.
+Such redshift errors are especially problematic for relatively low-$z$
+background systems: at lower redshifts the model-derived deflection
+angle and magnification show a more rapid variation with the redshift
+of the background galaxy than for similarly positioned high redshift
+galaxies.}
+
+It is relevant to note that the three model series highlighted here
+(Bradac, CATSv2 and Lam) also happen to be the three models that are
+not truly ``blind,'' in that the modelers were aware of preliminary
+analysis of the SN magnification when constructing the latest version.
+However, none of these models used the SN magnification as an input
+constraint, and none were consciously tuned to match the SN
+magnification. In fact, for the Bradac(v2) and Lam(v2) cases, the
+modelers did not have access to a final measurement of the SN
+magnification at the time their models were generated.
 
@@
 
-Taking advantage of the availability of 15 well-constrained lens
+Taking advantage of the availability of 17 well-constrained lens
 models for the Abell 2744 cluster, we have used SN \tomas\ to ask how
@@
 
-Turning to the lens models, we have considered 4 ways in which a bias
+Turning to the lens models, we have considered 5 ways in which a bias
 might be introduced into the lens models:
@@
 \item Misidentification of a multiple image
-\item Source plane minimization
+\item \change{Source plane minimization}
 \end{enumerate}

### 2015-05-18 snTomasCode/lensing_test_fig.py

@@ -3,7 +3,7 @@
 # The lensing comparison figure
 import numpy as np
 
-def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
+def mkLensingTestFig( show2snfits=False, showlegend=True, presfig=False,
                       labelvalues=False ):
     from matplotlib import pyplot as pl
     from matplotlib.patches import FancyArrowPatch
@@ -23,7 +23,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
         ax1 = pl.axes( [0.01,0.14,0.67,0.83] )
         ms=15
     else :
-        fig = plotsetup.fullpaperfig( figsize=[4,5])
+        fig = plotsetup.fullpaperfig( figsize=[4,6])
         ms=8
         pl.clf()
         if showlegend:
@@ -124,8 +124,8 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
             ['MLCS2k2','SALT2','Pre-HFF','Post-HFF'] ):
         if not show2snfits :
             if fitter=='SALT2': continue
-        ax1.axvline( muSN, ls=ls, color=textcolor, lw=2, ymin=ymin, ymax=ymax )
         if not ls=='--':
+            ax1.axvline( muSN, ls=ls, color=textcolor, lw=2, ymin=ymin, ymax=ymax )
             ax1.axvspan( muSN-muSNerr, muSN+muSNerr, ymin=ymin, ymax=ymax,
                          color=color, alpha=0.3,zorder=-100 )
         #ax1.text( muSN-0.03,  ymax*ytop+0.05, fitter, color=textcolor,
@@ -134,7 +134,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
     ax1.text( 1.75, 2*ytop/3, 'SN HFF14tom', rotation=90,
               ha='right', va='center', color=cp.darkblue )
 
-    # ax1.axvline( np.mean(lensingdat['med']), ls='--', color='0.5', lw=1 )
+    ax1.axvline( np.mean(lensingdat['med']), ls='--', color='0.5', lw=1 )
     print( "All models : mu=%.2f +- %.2f"%(np.mean(lensingdat['med']),np.std(lensingdat['med'])))
 
     if showlegend:
@@ -168,7 +168,7 @@ def mkLensingTestFig( show2snfits=False, showlegend=False, presfig=False,
     pl.draw()
 
 
[…]

### 2015-05-18 snTomas.tex
red text waiting for clarification of host galaxy mass from AM

@@
 the SN itself in Section~\ref{sec:DistanceAndMagnification}.  From
-this we determine the host galaxy mass to be $10^{10.1}$ \Msun. }
+this we determine the host galaxy mass to be 
+\changeR{$10^{9}$ \Msun.} }
 
@@
 distance modulus would not be adjusted, because its host galaxy mass
-(Section~\ref{sec:HostGalaxy}) is below 10$^{10}$ \Msun. Note that
+(Section~\ref{sec:HostGalaxy}) is \changeR{below} 10$^{10}$ \Msun. Note that
 there is some circularity here, as we used the SN magnification in
@@
 magnification.  However, changing the magnification value to $mu=2.5$
-does not move the \tomas\ host mass above the mass step threshold, so
+\changeR{does not move the \tomas\ host mass above the mass} step threshold, so
 the circularity is not relevant in this case. Applying the

### 2015-05-19 TABLE/magnifications2.tex
tweak to abstract; updated CATSv2.1,2.2 numbers; tweak to quality/quantity discussion

--- 2015-05-17 TABLE/magnifications2.tex
@@
 Errors from bootstrap resampling only strong-lensing constraints.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.\\
+CATS(v2.1)     & 55 & 154 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for the Bradac(v2) model.\\
+CATS(v2.2)     & 25 &  72 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for the Bradac(v2) model.
 \enddata
@@
 Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
-Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28
+Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28\\
+CATS(v2.1)$^{\rm *}$ & \nodata & 3.06  &   2.92$-$3.19 \\
+CATS(v2.2)$^{\rm *}$ & \nodata & 3.07  &   2.94$-$3.20 \\
 \enddata

### 2015-05-19 snTomas.tex
tweak to abstract; updated CATSv2.1,2.2 numbers; tweak to quality/quantity discussion

@@
 %definition of the lens models. We 
-and find that
+and \changeR{find that model accuracy can be improved to some extent
+by using multiply-imaged systems vetted with stringent quality cuts
+and requiring a large fraction with spectroscopic redshifts.}
 % -- at least for this
 %cluster and this line of sight -- 
-the most accurate models are those that employ stringent quality cuts
-\change{and use a large fraction of spectroscopically measured 
-redshifts of multiple images.}
 % A more robust evaluation
@@
 Figure~\ref{fig:LensingTest}.
-\change{In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the quantity and quality of strong lensing constraints changed substantially from one model version to the next.}
+\change{In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the number of strong lensing constraints and the fraction with spectroscopic redshifts changed substantially from one model version to the next.}
 } 
@@
 quality} of strong-lensing constraints is just as important as the
-{\it quantity}.  To get accurate magnifications, lens models should
-employ a strict vetting of the multiply-imaged systems.  Each system
-used should ideally have a spectroscopic redshift, or at least a very
-well constrained photometric redshift.  The primary value in this
-strict vetting is to avoid erroneous redshifts being assigned to
+{\it quantity}} \changeR{ -- at least for computing magnifications of sources outside the strong-lensing region.
+Once a sufficient number of robust multiply-imaged systems have been included (perhaps $\sim$10) most models will be dominated by systematic uncertainties such as those described in Section~\ref{sec:LensModelErrors}.
+To improve the accuracy of magnification predictions with a large number of strong-lensing constraints, one }
+\change{
+should employ a strict vetting of the multiply-imaged systems.  Each
+system used should ideally have a spectroscopic redshift, or at least
+a very well constrained photometric redshift.  The primary value in
+this strict vetting is to avoid erroneous redshifts being assigned to
 multiply-imaged systems that are unconstrained in redshift space.

### 2015-05-19 snTomasCode/lensing_test_fig.py

@@ -239,7 +239,7 @@ def mkTensionFig(presfig=False, showlegend=True, showlines=True):
     ax1.set_xlabel('\# multiply imaged systems')
     ax2.set_xlabel('Fraction with spec-z')
     ax1.set_ylim(-0.9,5.1)
-    ax1.set_xlim(1,55)
+    ax1.set_xlim(1,58)
     ax2.set_xlim(0.01,0.65)
     ax1.yaxis.set_major_locator( ticker.MultipleLocator( 1 ) )
     ax1.yaxis.set_minor_locator( ticker.MultipleLocator( 0.25 ) )
@@ -280,7 +280,7 @@ def mkTensionFig(presfig=False, showlegend=True, showlines=True):
             ax1.plot( nsys, tension, ls='-', marker=' ', color='0.5' )
             ax2.plot( specfrac, tension, ls='-', marker=' ', color='0.5' )
         ax1.text(48,4.1,'CATS(v2)',color='0.5',fontsize='small',ha='right',va='bottom')
-        ax1.text(50,2.8,'2.1',color='0.5',fontsize='small',ha='center',va='top')
+        ax1.text(55,2.8,'2.1',color='0.5',fontsize='small',ha='center',va='top')
         ax1.text(25,2.8,'2.2',color='0.5',fontsize='small',ha='center',va='top')
         ax1.text(27,0.6,'v2',color='0.5',fontsize='small',ha='left',va='bottom')
         ax1.text(14,1.2,'Bradac(v1)',color='0.5',fontsize='small',ha='right',va='bottom')

### 2015-05-19 snTomas.tex
trivial tweak to abstract
small changes in abstract and host mass section

@@
 %by more than $1\sigma$ 
-are {\it higher} than the measured value and 6 of these
+are {\it higher} than the measured value and \changeR{8} of these
 are $\geq1.5\sigma$ above the measured magnification.  We
@@
 by using multiply-imaged systems vetted with stringent quality cuts
-and requiring a large fraction with spectroscopic redshifts.}
+and requiring that a large fraction have spectroscopic redshifts.}
 % -- at least for this
@@
 this we determine the host galaxy mass to be 
-\changeR{$10^{9}$ \Msun.} }
+\changeR{$10^{9.8}$ \Msun.} }
 
@@
 purely empirical ``mass step'' correction is generally set around
-$10^{10}$\Msun, although this is somewhat arbitrary \citep[see
-e.g.][]{Betoule:2014}.
+$10^{10}$\Msun.  \changeR{Although this threshold value} is somewhat arbitrary \citep[see
+e.g.][]{Betoule:2014}, \changeR{it happens to be very close to the
+-SN \tomas\ host galaxy mass of $10^{9.8}$\Msun (Section~\ref{sec:HostGalaxy}).}
 
@@
 
-\change{
-If we were to apply the correction to this sample, then the SN \tomas\
-distance modulus would not be adjusted, because its host galaxy mass
-(Section~\ref{sec:HostGalaxy}) is \changeR{below} 10$^{10}$ \Msun. Note that
-there is some circularity here, as we used the SN magnification in
-deriving the host galaxy mass, and now use the host mass to inform the
-magnification.  However, changing the magnification value to $mu=2.5$
-\changeR{does not move the \tomas\ host mass above the mass} step threshold, so
-the circularity is not relevant in this case. Applying the
-mass step correction across the entire control sample would lead to a
-small adjustment of the inferred SN \tomas\ magnification, but it is $<5\%$
-and therefore could not relieve the observed tension.}
+\changeR{
+If we were to apply the correction to this sample using the standard
+approach, then the SN \tomas\ distance modulus would not be adjusted,
+because its host galaxy mass (Section~\ref{sec:HostGalaxy}) is just
+below 10$^{10}$ \Msun. Note that there is some circularity here, as we
+used the SN magnification in deriving the host galaxy mass, and now
+use the host mass to inform the magnification.  However, regardless of
+whether the \tomas\ host mass falls above the mass threshold or below,
+this correction is not substantial enough to account for the observed
+magnification tension.  The appropriate correction to be applied to
+a SN above the mass threshold in this redshift range would be $<$0.04
+mag \citep{Rigault:2013,Childress:2014b}, which results in a change to
+the inferred magnification of \tomas\ that is much less than the
+observed discrepancy of $\sim$0.24 mag.}
 

### 2015-05-19 snTomas.tex
trivial abstract tweak

@@
 by using multiply-imaged systems vetted with stringent quality cuts
-and requiring that a large fraction have spectroscopic redshifts.}
+and requiring that a large fraction of those systems have
+spectroscopic redshifts.}
 % -- at least for this

### 2015-05-20 snTomas.tex
modified source plane min. and specz frac discussion

@@
 \change{  There are several strategies for mitigating this well known bias.
-Optimizing a model in the image plane can  avoid this bias entirely \citep{Broadhurst:2005,Zitrin:2009a}. Alternatively, one may guard against it by using
-a modified source plane minimization that is constrained not to
-generate overly small re-lensed sources \citep{Sendra:2014,Diego:2014}.
-Finally, the effect of this bias should be reduced when one uses many strong
-lensing constraints over a wide range of redshifts. }
-
-\change{ Of the 17 models examined here, both of the Zitrin models 
-follow the first strategy, using image-plane optimization.  The
-Zitrin-LTM model delivers a significantly discrepant magnification,
-while the Zitrin-NFW latter is within 1$\sigma$ of the SN
-magnification.  The Diego model uses the second strategy of restricted
-source-plane minimization, and reports a magnification very close to
-the measured value.  The CATS(v2) model is the most extreme example of
-the final strategy, as it incorporates more multiply-imaged sources
-over a wider redshift range than any other model. However, this model
-is also the most discrepant, with a predicted $\mu$ that is $>4\sigma$
-from the SN magnification.  Thus, the results from this simplistic
-model comparison are mixed.  We therefore cannot conclude that source
-plane minimization alone is the root cause of the observed systematic
-bias. }
+Optimizing a model in the image plane can avoid this bias
+entirely \citep{Broadhurst:2005,Zitrin:2009a}.} \changeR{The
+Sharon(v2), Zitrin-LTM, Zitrin-NFW, and CATS(v2-2.2) models all use
+image plane minimization.}  \change{Alternatively, one may guard against this
+bias by using a modified source plane minimization that is constrained
+not to generate overly small re-lensed
+sources \citep{Sendra:2014,Diego:2014}.} \changeR{In our test set, this
+second strategy is employed by the Diego model.}  \change{Finally, the
+effect of this bias should be reduced when one uses many strong
+lensing constraints over a wide range of redshifts.} \changeR{The
+CATS(v2) and CATS(v2.1) models have the largest number of
+strong-lensing constraints, using 50 and 55 multiply-imaged systems,
+respectively.}
+
+\changeR{ Although many of the tested models utilize these 
+strategies to avoid a source plane minimization bias,
+Table~\ref{tab:PredictedMagnifications} and
+Figure~\ref{fig:LensingTest} show that these models do not uniformly
+deliver more accurate magnification predictions.  The most direct test
+of this is in the Sharon and CATS model series.  In both cases the v1
+model used the faster source plane minimization approach, but the v2
+model was constructed with the more costly image plane minimization.
+Neither of those models show a significant improvement in model
+accuracy from v1 to v2.  T his provides a strong indication that the
+observed tension between models and the SN observation cannot be
+entirely attributed to a bias arising from source plane minimization.}
 
@@
 fraction of strong-lensing constraints that have a spectroscopic
-redshift. Here we see that all three of the testable model series
-(Bradac,Lam,CATSv2) become {\it more} accurate as the spec-z fraction
-increases.\footnote{Of course this apparent correlation does not imply
-any direct causation. Consider the limit of just a single
-multiply-imaged galaxy constraint: the spec-$z$ fraction could be 1.0
-but the model would be wildly unconstrained.}  The spec-$z$ fraction
-here serves as a crude stand-in for measuring how
-stringently the strong-lensing constraints are selected in these
-models.  
-}
+redshift. 
+For the SN \tomas\ magnification prediction, we see that all three of
+the testable model series (Bradac,Lam,CATSv2) become {\it more}
+accurate as the spec-z fraction increases.\footnote{Of course this
+apparent correlation does not imply any direct causation. Consider the
+limit of just a single multiply-imaged galaxy constraint: the spec-$z$
+fraction could be 1.0 but the model would be wildly unconstrained.}
+The spec-$z$ fraction here serves as a crude stand-in for measuring
+how stringently the strong-lensing constraints are selected in these
+models.  }
 
@@
 of the background galaxy than for similarly positioned high redshift
-galaxies.}
+galaxies.}  \changeR{This conclusion should be unsurprising, as for
+example, \citet{Bayliss:2015} have shown that cosmological
+uncertainties are smaller for models that use a large fraction of
+strong-lensing constraints with spectroscopic redshifts,
+and \citet{Johnson:2014} have shown a case study where adding
+spectroscopic redshift information changes the inferred magnification
+by $\sim$10\%.}
 

### 2015-05-21 snTomas.tex
updated with comments from D.Coe; substantial rewrite of abstract

@@
 
-\title{Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by the Galaxy Cluster Abell 2744}
+\title{Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the \changeR{Frontier Fields} Galaxy Cluster Abell 2744}
 
@@
 \begin{abstract}
-\changenote{Reduced to $<250$ words.}\\
+\changeG{
 SN \tomas\ is a Type Ia Supernova (SN) discovered at
-$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744
-($z=0.308$). This SN 
-%has a projected separation from the cluster core
-%of $\sim$40\arcsec, 
-is closer to the critical lensing line than any
-previous cluster-lensed Type Ia SN, 
-%As such, it provides 
-providing a valuable
-opportunity to test galaxy cluster lens models
-with the direct measurement of an absolute magnification at the edge
-of the strong-lensing region.  
-%We derive a tightly constrained measure
-%of the peak apparent magnitude, corrected for light curve shape and
-%extinction.  
+$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744 ($z=0.308$).
 In a cosmology-independent analysis, we find that \tomas\ is
 $0.77\pm0.15$ magnitudes brighter than unlensed Type Ia SNe at similar
-redshift, implying a lensing magnification of 
-$\mu_{\rm obs}=2.03\pm0.29$. 
-\change{In future lens models of Abell 2744, this could
-provide some leverage for breaking degeneracies that positional
-constraints cannot disentangle.}  We compare the measured $\mu$
-against predicted magnifications from 17 lens models, \change{ of
-which 13 were generated before the SN magnification was known,
-qualifying as a pure ``blind test.''}  The models are collectively
-fairly accurate: 8 of the models deliver median magnifications that
-are consistent with the measured $\mu$ to within 1$\sigma$.  However,
-there is a subtle systematic bias: all of the models that disagree
-with the SN $\mu$
-%by more than $1\sigma$ 
-are {\it higher} than the measured value and \changeR{8} of these
-are $\geq1.5\sigma$ above the measured magnification.  We
-evaluate possible causes for this mild bias,
-%and reject explanations
-%that invoke misinterpretation of the SN data or errors in the
-%definition of the lens models. We 
-and \changeR{find that model accuracy can be improved to some extent
-by using multiply-imaged systems vetted with stringent quality cuts
-and requiring that a large fraction of those systems have
-spectroscopic redshifts.}
-% -- at least for this
-%cluster and this line of sight -- 
-% A more robust evaluation
-%\change{Further examination} of systematic biases 
-%could be achieved 
-%\change{could be pursued with more}
-%lens model comparisons using lensed
-%Type Ia SNe, as well as cluster lensing simulations.
+redshift, implying a lensing magnification of $\mu_{\rm
+obs}=2.03\pm0.29$.  This observed magnification provides a rare
+opportunity for a direct empirical test of galaxy cluster lens models.
+Here we test 17 lens models, 13 of which were generated before the SN
+magnification was known, qualifying as pure ``blind tests''.  The
+models are collectively fairly accurate: 8 of the models deliver
+median magnifications that are consistent with the measured $\mu$ to
+within 1$\sigma$.  However, there is a subtle systematic bias: the
+significant disagreements all involve models {\it overpredicting} the
+magnification. We evaluate possible causes for this mild bias, and
+find no single physical or methodological explanation to account for
+it.  We do find that model accuracy can be improved to some extent
+with stringent quality cuts on multiply-imaged systems, such as
+requiring that a large fraction have spectroscopic redshifts.  In
+addition to testing model accuracies as we have done here, Type Ia SN
+magnifications could also be used as inputs for future lens models of
+Abell 2744 and other clusters, providing valuable constraints in
+regions where traditional strong- and weak-lensing information is
+unavailable.}
 \end{abstract}
 
-%\keywords{ supernovae: general, supernovae: individual: HFF14Tom, 
-%galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, 
-%gravitational lensing: strong, gravitational lensing: weak  }
+\keywords{ supernovae: general, supernovae: individual: HFF14Tom, 
+galaxies: clusters: general, galaxies: clusters: individual: Abell 2744, 
+gravitational lensing: strong, gravitational lensing: weak  }
 
@@
 \change{We discuss some of the modeling choices here, but
-a more rigorous comparison of these disparate lens modeling techniques
+a more rigorous comparison of these diverse lens modeling techniques
 is beyond the scope of this work. For a complete discussion of each
@@
 delensed images of the same source closer together in the source
-plane.  Thus, any models that are optimized in the source plane will
-have a tendency toward shallower mass profiles and larger
+plane.  \changeR{Thus, models that are optimized in the source plane may
+have a tendency} toward shallower mass profiles and larger
 magnifications, which force all sources toward the same location in
@@
 bias by using a modified source plane minimization that is constrained
-not to generate overly small re-lensed
+not to generate overly small de-lensed
 sources \citep{Sendra:2014,Diego:2014}.} \changeR{In our test set, this
@@
 
-A promising avenue for exploring the origins of systematic biases in
+\changeR{
+The general problem of combining predictions from many independent
+models has a rich history in the astronomical and statistical
+literature \citep[e.g.,][]{Press:1997,Hoeting:1999,Liddle:2009}.
+In a recent example, \citet{Dahlen:2013} examined the photometric
+redshifts from multiple galaxy SED fitting codes using the same input
+data.  They found that the photo-z accuracy and precision can be
+substantially improved by combining the outputs using a sum of
+probability distributions, a hierarchical Bayesian method, or even a
+technique as simple as taking the straight median from all available
+models.  It may be that lensing magnifications are similar, in that
+they can in general be improved through a simple combination of lens
+model predictions.  Such model averaging will not, however, resolve a
+{\it systematic} bias that is shared by many models.}
+
+A promising avenue for exploring the origins of such systematic biases in
 cluster lens models is through the use of simulated lensing data.  One
@@
 distribution on large scales for that simulated cluster, which is
-consistent with a recent lens model comparison on 25 real clusters
+consistent with a recent lens model comparison using 25 real clusters
 from the CLASH program \citep{Zitrin:2015}. Our analysis of
@@
 
-Increasing the sample of SNe behind clusters like those in
-the HFF program -- with rich lensing constraints and deep imaging -- 
-would allow this test to be repeated and refined.  With 10 or 100 such
-objects, it would be possible to see whether the SN \tomas\ $\mu$
-discrepancy is simply an outlier, or an indication of a more
+Increasing the sample of SNe behind clusters like those in the HFF
+program -- with rich lensing constraints and deep imaging -- would
+allow the test described here to be repeated and refined.  With 10 or
+100 such objects, it would be possible to see whether the SN \tomas\
+$\mu$ discrepancy is simply an outlier, or an indication of a more
 pernicious systematic error.  Any cluster that has been vetted by

### 2015-05-22 snTomas.tex
final comments and author additions before submission

@@
 reported in the final column of Table~\ref{tab:MeasuredMagnification}.
+\changeR{
+Although we have chosen to use a cosmology-independent approach to
+determine the magnifications, we note that these results are fully
+consistent with the values that would be determined by comparing the
+observed SN \tomas\ distance modulus against the predicted value from
+a flat \LCDM\ cosmology. Adopting the cosmological parameters used
+in \citetalias{Patel:2014} and derived in \citet{Sullivan:2011}
+(\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
+$dm_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
+Substituting alternative cosmological
+parameters \citep[e.g.,][]{Betoule:2014,Planck:2015} would not
+significantly change the inferred magnification or affect our
+conclusions.
+}
 
@@
 using the MLCS2k2 fitter (top panel) and the SALT2 fitter (bottom
-panel).  Grey lines with shading show a linear fit to the
-unlensed control sample is shown, anchored at the redshift of
-SN \tomas, with fit parameters given at the top.  The derived
-magnification is reported at the bottom of each panel.
+panel).  Grey lines with shading show a linear fit to the unlensed
+control sample is shown, anchored at the redshift of SN \tomas, with
+fit parameters given at the top.  The derived magnification is
+reported at the bottom of each panel.
 \label{fig:MagnificationMeasurement} }

### 2015-05-22 snTomas.tex
final tweaks during arXiv submission

@@
 \begin{abstract}
-\changeG{
+{
 SN \tomas\ is a Type Ia Supernova (SN) discovered at
@@
 implementation to make the FrontierSN program possible; to Anton
-Koekemoer for HFF data processing support; and to Dan Coe for curating the
-excellent and accessible lens model comparison tools.  We also thank
+Koekemoer for HFF data processing support.  We also thank
 the CLASH team, led by Marc Postman, for observations, catalogs, and
@@
 {\it Facilities:} \facility{HST (WFC3)}
-\smallskip
+\pagebreak
 

### 2015-08-10 APJ.submitted/lensmodels.tex
Updated with response to referee. Ready for resubmission

--- 2015-05-19 TABLE/magnifications2.tex
@@
 \startdata
-Bradac(v1)     & 16 &  56 & 2 & 14 &  HFF\tablenotemark{e}; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{f} : Free-form, strong+weak-lensing based model.
-Errors from bootstrap resampling only weak-lensing constraints.\\
-CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{g} team implementation of LENSTOOL\tablenotemark{h} parametric strong-lensing based model.\\
-CATS(v1sw)     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
-Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{i} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
-Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF;  & LENSTOOL parametric, strong-lensing based model\\
-Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
+Bradac(v1)\tablenotemark{e}     & 16 &  56 & 2 & 14 &  HFF\tablenotemark{f}; \citealt{Bradac:2009} & {\tt SWUnited}\tablenotemark{g} : Free-form, strong+weak-lensing based model.Errors from bootstrap resampling only weak-lensing constraints.\\
+CATS(v1)       & 17 &  60 & 2 & 14 &  HFF; \citealt{Richard:2014} &  CATS\tablenotemark{h} team implementation of LENSTOOL\tablenotemark{i} parametric strong-lensing based model.\\
+CATS(v1.1)\tablenotemark{j}     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
+Merten\tablenotemark{e}         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
+Sharon(v1)     & 17 &  60 & 2 & 14 &  HFF;  & LENSTOOL parametric strong-lensing based model\\
+Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
 Zitrin-LTM     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2009a} & Parametric strong-lensing model, adopts the Light-Traces-Mass assumption for both the luminous and dark matter.\\
 Zitrin-NFW     & 10 &  44 & 2 & 0  &  HFF; \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD profiles for galaxies and NFW profiles for dark matter halos.\\
-Williams       & 10 &  40 & 2 & 8  &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
+Williams       & 10 &  40 & 2 & 8  &  HFF & {\tt GRALE}\tablenotemark{l} : Free-form strong-lensing model using a genetic algorithm.  \\
 \cutinhead{Post-HFF models : include data from the HFF program}\\
 CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
-Diego\tablenotemark{k} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & {\tt WSLAP+}\tablenotemark{l} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
-GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{m} \\
+Diego\tablenotemark{m} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & {\tt WSLAP+}\tablenotemark{n} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
+GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{o} \\
 Lam(v1)        & 21 &  65 & 4 & 17 &  \citealt{Lam:2014} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.\\
 \cutinhead{Unblind models : generated after the SN magnification was known}\\
-Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging and GLASS spectra.
-Errors from bootstrap resampling only strong-lensing constraints.\\
-Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.\\
-CATS(v2.1)     & 55 & 154 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for the Bradac(v2) model.\\
-CATS(v2.2)     & 25 &  72 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for the Bradac(v2) model.
+Bradac(v2)\tablenotemark{e}     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging and GLASS spectra.
+Errors derived via bootstrap resampling only strong-lensing constraints.\\
+Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{p} models for galaxy mass.\\
+CATS(v2.1)     & 55 & 154 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for Bradac(v2).\\
+CATS(v2.2)     & 25 &  72 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for Bradac(v2).
 \enddata
@@
 \tablenotetext{d}{Number of multiply imaged systems with photometric redshifts.}
-\tablenotetext{e}{Lens models with the reference code ``HFF'' were produced as part of the 
+\tablenotetext{e}{\change{Uses weak lensing constraints from HST- and ground-based imaging, as described in \citet{Merten:2011}.}} 
+\tablenotetext{f}{Lens models with the reference code ``HFF'' were produced as part of the 
 Hubble Frontier Fields lens modeling
@@
 }
-\tablenotetext{f}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
-\tablenotetext{g}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
-\tablenotetext{h}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
-\tablenotetext{i}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
-\tablenotetext{j}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
-\tablenotetext{k}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
+\tablenotetext{g}{{\tt SWunited} : Strong and Weak lensing United; \citealt{Bradac:2005}}
+\tablenotetext{h}{{\tt CATS} : Clusters As TelescopeS lens modeling team. PI's: J.-P. Kneib \&\ P. Natarajan}
+\tablenotetext{i}{{\tt LENSTOOL} : \citealt{Jullo:2007}; \url{http://projects.lam.fr/repos/lenstool/wiki}}
+\tablenotetext{j}{\change{Uses weak lensing constraints from HST imaging, as described in \citet{Richard:2014}}}
+\tablenotetext{k}{{\tt SaWLENS} : \citealt{Merten:2009}; Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
+\tablenotetext{l}{{\tt GRALE} : GRAvitational LEnsing; \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}}
+\tablenotetext{m}{Abell 2744 model available at \url{http://www.ifca.unican.es/users/jdiego/LensExplorer}. 
 No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.
 }
-\tablenotetext{l}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
-\tablenotetext{m}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
-\tablenotetext{n}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
+\tablenotetext{n}{{\tt WSLAP+} : \citealt{Sendra:2014}; Weak and Strong Lensing Analysis Package plus member galaxies (Note: no weak-lensing constraints used for Abell 2744)}
+\tablenotetext{o}{{\tt GLAFIC} : \citealt{Oguri:2010}; \url{http://www.slac.stanford.edu/~oguri/glafic/}}
+\tablenotetext{p}{{\tt GALFIT} : Two-dimensional galaxy fitting algorithm \citep{Peng:2002}}
 \end{deluxetable*}
@@
 CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
-CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
+\change{CATS(v1.1)}      & \nodata  & 2.62  &   2.44$-$2.80 \\
 Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
@@
 \tablenotetext{a}{Models above the line are from the pre-HFF set, and those below incorporate HFF data.
-The final two, marked by an asterisk, were not part of the blind test as they include modifications made after the measured magnification of the SN was known.}
+The final \change{four, marked with asterisks, were not formally} part of the blind test as they include modifications made after the measured magnification of the SN was known.}
 \tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  

### 2015-08-10 APJ.submitted/snTomas.tex
Updated with response to referee. Ready for resubmission

--- 2015-05-22 snTomas.tex
@@
 
-\title{Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the \changeR{Frontier Fields} Galaxy Cluster Abell 2744}
+\title{Illuminating a Dark Lens : A Type Ia Supernova Magnified by \\ the Frontier Fields Galaxy Cluster Abell 2744}
 
@@
 We expect to detect the reappearance of this object (called ``SN
-Refsdal'') \change{within the next
-year} \citep{Oguri:2015,Sharon:2015,Diego:2015}, delivering a precise
+Refsdal'') within the next
+year \citep{Oguri:2015,Sharon:2015,Diego:2015}, delivering a precise
 test of lens model predictions.  Although detections of such objects
@@
 ``middle distance'' from the cluster core, where both strong- and
-weak-lensing constraints are unavailable. \change{Moreover, given
+weak-lensing constraints are unavailable. Moreover, given
 enough time, multiple background SNe Ia could be measured behind the
-same cluster, each providing a new magnification constraint.}
+same cluster, each providing a new magnification constraint.
 
@@
 degeneracies do not extend to the {\it absolute} magnification of a
-background source's flux and size. \change{In the case of the simple
+background source's flux and size. In the case of the simple
 mass sheet degeneracy described above, the magnification scales as
-$\mu\propto(1-\lambda)^{-2}$ \citep[see e.g.][]{Bartelmann:2010}.}
+$\mu\propto(1-\lambda)^{-2}$ \citep[see e.g.][]{Bartelmann:2010}.
 Therefore, one can break these fundamental degeneracies with an
@@
 \begin{center}
-%\includegraphics[width=\textwidth]{FIG/discovery_image}
-\includegraphics[width=\textwidth]{FIG/discovery_image_lowres}
+%\includegraphics[width=\textwidth]{discovery_image}
+\includegraphics[width=\textwidth]{discovery_image_lowres}
 \caption{  \label{fig:DiscoveryImage} 
@@
 
-\input{TABLE/positions}
-
-\input{TABLE/photometry}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=\columnwidth]{FIG/host_sed_fit}
-%\caption{  \label{fig:HostSED}
-%Best-fit SED template match for the most probable \tomas\ host
-%galaxy. Using the {\it BPZ} code to match the observed SED, we find
-%the nearest galaxy to the SN position is a late type galaxy with a
-%photometric redshift of $z=1.5\pm0.2$.}
-%\end{center}
-%\end{figure}
+\input{positions}
+
+\input{photometry}
 
@@
 a Bayesian photometric redshift estimator \citep{Benitez:2000}. 
-%The best-fit SED template match is shown in Figure~\ref{fig:HostSED}.
 From the {\it BPZ} analysis, we found the host to be most likely an
@@
 
-\change{
 The galaxy identified as the host is not close enough to the cluster
@@
 imaging. To date, no plausible candidate for a counter-image has been
-identified.}
-
-\change{To measure the stellar mass of the host galaxy
+identified.
+
+To measure the stellar mass of the host galaxy
 we use Eq. 8 of \citet{Taylor:2011}, which relates the rest-frame
@@
 the SN itself in Section~\ref{sec:DistanceAndMagnification}.  From
-this we determine the host galaxy mass to be 
-\changeR{$10^{9.8}$ \Msun.} }
+this we determine the host galaxy mass to be $10^{9.8}$ \Msun.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/specfit}
+\includegraphics[width=\columnwidth]{specfit}
 \caption{  \label{fig:SpecFit}
@@
 A spectrum of SN \tomas\ was collected with the ACS G800L grism on
-2014 June 4 and 7, when the SN was \change{within 3 observer-frame
-days of the observed peak brightness in the F814W band.}  The
+2014 June 4 and 7, when the SN was within 3 observer-frame
+days of the observed peak brightness in the F814W band.  The
 observations -- listed at the bottom of Table~\ref{tab:Photometry} --
@@
 feature at $\sim$8700\AA.
-%However, the signal to noise ratio (S/N)
-%for the host galaxy spectrum was too weak to yield any additional
-%constraints on the host type or redshift.
 
@@
 at $z\approx1.35$.  At this redshift, the absorption at $\sim$8700\AA\
-corresponds to the blended \ion{Ca}{2} H\&K \change{and \ion{Si}{2} $\lambda$3858} features.
-\change{Generally referred to as the Ca H\&K feature, this} absorption is commonly seen in Type Ia SN spectra
+corresponds to the blended \ion{Ca}{2} H\&K and \ion{Si}{2} $\lambda$3858 features.  Generally referred to as the Ca H\&K feature, this absorption is commonly seen in Type Ia SN spectra
 near maximum light, although it is also prominent in the spectra of
@@
 with a $\chi^2$ per degree of freedom $\nu$ of $\chi^2/\nu=121.8/89$
-shown in the top panel of Figure~\ref{fig:SpecFit}. \change{The excess
+shown in the top panel of Figure~\ref{fig:SpecFit}. The excess
 variance in this fit may be attributed to the intrinsic variation of
@@
 wavelengths \citep[e.g.][]{Foley:2008b,Wang:2012} and is not fully
-represented in the available template library.}  Allowing the redshift
+represented in the available template library.  Allowing the redshift
 as an additional free parameter, we still find results that are
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/snTomas_lightcurve_classification}
+\includegraphics[width=\columnwidth]{snTomas_lightcurve_classification}
 \caption{ 
@@
 dash-dot line). The Type Ia model is by far the best match, and the
-only one that is consistent with both the photo-$z$ of the probable
-host galaxy and the spectroscopic redshift from the SN spectrum.  The
-date of the HST spectral observations is marked with a thin grey
-vertical line.
+only one that is consistent with both the \change{spectroscopic
+redshift} of the probable host galaxy and the spectroscopic redshift
+from the SN spectrum.  The date of the HST spectral observations is
+marked with a thin grey vertical line.
 \label{fig:photoclass} }
@@
 using traditional Bayesian model selection \citep[as
-in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015a}.  In this
+in][]{Jones:2013,Rodney:2014,Graur:2014,Rodney:2015b}.  In this
 analysis we represent normal Type Ia SNe with the SALT2
@@
 ($t_{\rm pk}$), amplitude, and redshift ($z$). Due to the expected
-impact of gravitational lensing magnification, we do not include any
-prior on the intrinsic luminosity for any SN sub-class.  We also do
-not assign a prior for the SN redshift. This allows our photometric
+impact of gravitational lensing magnification, we \change{use a flat
+prior for the intrinsic luminosity of all SN sub-classes.  We also
+apply a flat prior for the SN redshift, which} allows our photometric
 analysis to provide an independent check on the host galaxy photo-$z$
-and spectroscopic redshift (Sections~\ref{sec:DiscoveryAndFollowup}
+and spectroscopic redshift (Sections~\change{\ref{sec:HostGalaxy}}
 and \ref{sec:SpecRedshift}).
@@
 templates to measure the distance
-modulus \change{(\S\ref{sec:LightCurveFitting})} and then derive the
+modulus (\S\ref{sec:LightCurveFitting}) and then derive the
 gravitational lensing
-magnification \change{(\S\ref{sec:ControlSampleComparison})}.  In this
+magnification (\S\ref{sec:ControlSampleComparison}).  In this
 process, we would like to avoid introducing systematic uncertainties
-inherent to any assumed cosmological model.  To that end, \change{in
-section \ref{sec:ControlSampleComparison}} we
-follow \citealt{Patel:2014} and define the magnification by comparing
+inherent to any assumed cosmological model.  To that end, in
+section \ref{sec:ControlSampleComparison} we
+follow \P14\ and define the magnification by comparing
 the measured distance modulus of SN \tomas\ against an average
@@
 \begin{center}
-\includegraphics[width=\textwidth]{FIG/snTomas_lightcurve_fit_fluxAB25}
+\includegraphics[width=\textwidth]{snTomas_lightcurve_fit_fluxAB25}
 \caption{ Type Ia light curve fits to SN \tomas\ using the MLCS2k2
@@
 
-As in \citealt{Patel:2014}, we derive a distance modulus for
+As in \P14, we derive a distance modulus for
 SN \tomas\ and all SNe in our control sample using two independent
@@
 
-\input{TABLE/dist_mag}
+\input{dist_mag}
 
@@
 correction of 0.20 mag to the MLCS2k2 distances as
-in \citealt{Patel:2014}.  This correction was derived by applying both
+in \P14.  This correction was derived by applying both
 fitters to a sample of Type Ia SNe from the SDSS
@@
 purely empirical ``mass step'' correction is generally set around
-$10^{10}$\Msun.  \changeR{Although this threshold value} is somewhat arbitrary \citep[see
-e.g.][]{Betoule:2014}, \changeR{it happens to be very close to the
--SN \tomas\ host galaxy mass of $10^{9.8}$\Msun (Section~\ref{sec:HostGalaxy}).}
+$10^{10}$\Msun.  Although this threshold value is somewhat arbitrary \citep[see
+e.g.][]{Betoule:2014}, it happens to be very close to the
+-SN \tomas\ host galaxy mass of $10^{9.8}$\Msun (Section~\ref{sec:HostGalaxy}).
 
@@
 
-\changeR{
 If we were to apply the correction to this sample using the standard
@@
 the inferred magnification of \tomas\ that is much less than the
-observed discrepancy of $\sim$0.24 mag.}
+observed discrepancy of $\sim$0.24 mag.
 
@@
 reported in the final column of Table~\ref{tab:MeasuredMagnification}.
-\changeR{
 Although we have chosen to use a cosmology-independent approach to
@@
 a flat \LCDM\ cosmology. Adopting the cosmological parameters used
-in \citetalias{Patel:2014} and derived in \citet{Sullivan:2011}
+in \P14\ and derived in \citet{Sullivan:2011}
 (\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
@@
 conclusions.
-}
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/snTomas_hubble_diagram}
+\includegraphics[width=\columnwidth]{snTomas_hubble_diagram}
 \caption{ Measurement of the lensing magnification from comparison of
@@
 \end{figure}
-
-%\section{Discussion}
-%\label{sec:Discussion}
 
@@
 
-\input{TABLE/magnifications2}
+\input{lensmodels}
 
@@
 position of \tomas.  
-\changeG{For thirteen of these models the SN magnification qualifies as a true
+For thirteen of these models the SN magnification qualifies as a true
 ``blind test'', as they were completed before the SN \tomas\
@@
 constraint, and the modelers did not have access to the final SN
-magnification value when constructing their model.}
+magnification value when constructing their model.
 
@@
 distributions in galaxy clusters. 
-\change{We discuss some of the modeling choices here, but
+We discuss \change{two primary modeling choices here}, but
 a more rigorous comparison of these diverse lens modeling techniques
 is beyond the scope of this work. For a complete discussion of each
-model's methodology the reader is directed to the listed references.}
-Eight of these are so-called {\it parametric}\footnote{Although this
+model's methodology the reader is directed to the listed references.
+
+\smallskip
+{\it (1) Parametric vs. Free-form:}
+\change{Ten of these models} are so-called {\it parametric}\footnote{Although this
 nomenclature is becoming standard in the literature, it is somewhat
@@
 be more accurate, though we adopt the more common usage here.}
-models, and the remining seven are {\it free-form} models.  
+models, and the remaining seven are {\it free-form} models.  
 Broadly speaking, the parametric models use parameterized density
 distributions to describe the arrangement of mass within the cluster.
-%typically associating massive dark matter halos with the positions of
-%bright cluster member galaxies. 
 Therefore, parametric models rely (to
@@
 
-\change{
 As usual, there is a tradeoff between a model's flexibility, the
@@
 inflexible, they will result in underestimated error bars.
-}
-
-%\change{
-% Table~\ref{tab:PredictedMagnifications} also shows that the quoted
-% errors from these models vary widely.  At one extreme is the
-% Bradac(v2) model, with quoted magnification uncertainties of
-% $\pm$0.04, not accounting for systematic errors.  At the other
-% extreme is the Williams model, which has the largest uncertainties,
-% with a 68\% confidence range that encompasses the median
-% magnification values returned by all other models.  This is due in
-% part to the intentional exploration of many systematic error sources
-% such as the mass sheet degeneracy and more complex
-% degeneracies \citep{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014}.
-% }
+
+\smallskip
+\change{{\it (2) Strong vs. Strong+Weak':}}
+\change{Thirteen of the mass models evaluated here are constrained only using
+strong-lensing features such as multiply-imaged background galaxies
+and highly magnified arcs.  There are now $\sim$150 known lensed
+images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
+located several arcseconds outside the core region of the cluster
+where these multiply-imaged galaxies are found.  Therefore these
+``strong-lensing only'' models must necessarily rely on extrapolations
+to provide a prediction for the SN \tomas\ magnification.}
+
+\change{The other four models in our comparison set also use the strong
+lensing constraints from the core region, but additionaly use
+weak lensing measurements to provide additional constraints on the
+mass distribution farther from the cluster core.  Notes on the
+derivation of these weak-lensing constraints are given in the final
+column of Table~\ref{tab:LensModels}.  The signal from weak lensing
+relies on a large sample of background galaxies, so this constraint
+operates principally at separations more than 1\arcmin\ from the
+cluster core.  At a projected separation of $\sim40\arcsec$,
+SN \tomas\ falls in between the strong- and weak-lensing regimes. }
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
+\includegraphics[width=\columnwidth]{snTomas_magnifications}
 \caption{ 
@@
 constraints, while diamonds denote those that also incorporate
-weak-lensing measurements.  \change{Models using a ``free-form''
+weak-lensing measurements.  Models using a ``free-form''
 approach are shown as open markers, while those in the ``parametric''
@@
 models that were constructed using only data available before the
-start of the Frontier Fields observations. A black dashed line marks the
-unweighted mean for these models, at $\mu=2.6$.
-The lower six models in
+start of the Frontier Fields observations. 
+The lower \change{eight} models in
 green used additional input constraints, including new multiply imaged
-systems and redshifts.  The final two points, with square orange
+systems and redshifts.  The final four points, with square orange
 outlines, are the ``unblind'' models that were generated after the
 magnification of the SN was known.  
-The green dashed line marks the
-unweighted mean for these six models, at $\mu=2.3$.
-\label{fig:LensingTest} }}
+\change{The black dashed line marks the
+unweighted mean for all 17 models, at $\mu=2.6$.}
+\label{fig:LensingTest} }
 \end{center}
@@
 
+\medskip
 In Figure~\ref{fig:LensingTest} the model predictions are plotted
@@
 comparison shows that these 17 models are largely consistent with each
-other and with the observed magnification of SN \tomas. \change{ The
+other and with the observed magnification of SN \tomas. The
 ``naive mean'' of the full set of models is $\mu_{\rm pre}=2.6\pm0.4$.
@@
 The naive mean is separated from the observed SN magnification by
-$\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$ difference.}
-
-\change{
+$\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$ difference.
+
 This is approximately consistent with the results
-of \citetalias{Patel:2014} and \citet{Nordin:2014}, where
+of \P14\ and \citet{Nordin:2014}, where
 model predictions were found to be in reasonably good agreement with a
@@
 outside of the strong-lensing region where the models are most tightly
-constrained.}
-
-%In spite of the great variety in input data and methodology, these
-%lens models overall are delivering consistent and fairly accurate
-%estimates of the magnification.  Seven of the tested models (CATS(v1),
-%GLAFIC, Merten, Zitrin-NFW, Bradac(v2), Diego, Lam(v2)) report a
-%median value that falls within the 1$\sigma$ uncertainty range of the
-%measured magnification, and three of the models (Williams,
-%Diego, Lam(v2)) report uncertainties that overlap the central $\mu$ as
-%measured from both of the SN light curve fitters.
+constrained.
 
@@
 magnifications that are {\it higher} than the observed value, and six
-of the models are discrepant by more than $1.5\sigma$. \change{These
+of the models are discrepant by more than $1.5\sigma$. These
 six discrepant models are all biased to higher magnifications. They
@@
 and free-form families, and among the strong-lensing-only and the
-strong+weak subsets.}  It is important to emphasize that SN \tomas\
+strong+weak subsets.  It is important to emphasize that SN \tomas\
 only samples a single line of sight through the cluster, and this bias
@@
 underestimating} the effect of dust along this sight-line, then the SN
-\change{would appear dimmer than it really is, the inferred distance modulus would be higher,
+would appear dimmer than it really is, the inferred distance modulus would be higher,
 and the measured magnification would be biased to an artifically low
 value. Thus, an underestimation of dust would be in the right
-direction to match discrepancy we observe.}
+direction to match discrepancy we observe.
 
@@
 inferred magnification to $\mu_{\rm SALT2}=2.08\pm0.36$.  This would
-\change{slightly reduce the tension between the SALT2 measurement and the model predictions, though it would not be enough to completely alleviate it.}
+slightly reduce the tension between the SALT2 measurement and the model predictions, though it would not be enough to completely alleviate it.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{FIG/snTomas_sn06bt_colorcurves}
+\includegraphics[width=\columnwidth]{snTomas_sn06bt_colorcurves}
 \caption{ 
@@
 
-Having \change{found no evidence for} misinterpetations of the SN
+Having found no evidence for misinterpetations of the SN
 data, we are left to seek an explanation for the mild tension by
 scrutinizing the lens models.  Here we evaluate four
-possible \change{ways in which the input data or assumptions of these
-lens models could lead to a systematic bias in the magnification.}
-
-\subsubsection{Cosmic Weak Lensing}
+possible ways in which the input data or assumptions of these
+lens models could lead to a systematic bias in the magnification.
+
+\change{\subsubsection{Unconstrained Mass Model Extrapolation}}
+
+\change{As noted above, the position 
+of SN \tomas\ just beyond the edge of the strong-lensing region means
+that all models relying only on strong-lensing constraints must
+extrapolate the mass profile in order to make a prediction for
+the \tomas\ magnification.  Let us suppose that the true cluster
+density profile for Abell 2744 happens to have a sharp drop right at
+the edge of this core strong-lensing region. In that case these {\it
+strong-lensing only} models might well overestimate the mass interior
+to the \tomas\ position, and thus systematically overestimate the
+magnification.}
+
+\change{ One would expect that models incorporating weak-lensing
+constraints would be less susceptible to such bias from a sharply
+steepening mass profile.  However, we find that collectively the four
+strong+weak lensing models (shown as diamonds in
+Figure~\ref{fig:LensingTest}) exhibit the same propensity to
+overestimate the magnification along this line of sight.  Thus, an
+error in extrapolating the mass profile outside the strong lensing
+region is not a likely explanation for the observed small systematic
+bias.}
+
+\change{With two versions of the CATS(v1) model, we also have a 
+more direct test of the effect of introducing weak lensing
+constraints.  The initial CATS(v1) model uses only strong-lensing
+constraints, and gives $\mu=2.29^{+0.05}_{-0.04}$, slightly higher
+than the measured value.  A second iteration of this model, labeled
+here as CATS(v1.1), used the same strong-lensing features, but added
+in weak lensing constraints.  The revised magnification of
+$\mu=2.62\pm0.18$ is further from the measured value, which serves to
+reinforce the conclusion that adding weak lensing constraints cannot,
+by itself, resolve this bias.}
+
+\change{\subsubsection{Line of Sight Structure}}
 In addition to the dominant gravitational lensing from the foreground
@@
 cumulative weak lensing effects due to uncorrelated large scale
-structure along the line of sight, sometimes called ``Cosmic Weak
-Lensing'' \citep[CWL;][]{Wong:2011,Host:2012,Collett:2013,Greene:2013,Bayliss:2014,McCully:2014,DAloisio:2014}.
-This CWL effect is most important for very high redshift sources
+structure (LSS) along the line of sight, sometimes called ``Cosmic Weak
+Lensing'' \citep{Wong:2011,Host:2012,Collett:2013,Greene:2013,Bayliss:2014,McCully:2014,DAloisio:2014}.
+This \change{LSS} effect is most important for very high redshift sources
 ($z>5$), which have a much longer path length over which to encounter
 large scale structure and for highly magnified sources very near to
-the cluster lensing critical curve (because CWL can perturb the
+the cluster lensing critical curve (because \change{LSS} can perturb the
 position of the critical curve).  For SN \tomas\ at the modest
-redshift of $z=1.35$ and far from the critical curve, CWL should
+redshift of $z=1.35$ and far from the critical curve, \change{LSS} should
 increase the scatter in the lensing magnification at a level much less
-than 10\% \citep{DAloisio:2014}.  The CWL effect is therefore unable
+than 10\% \citep{DAloisio:2014}.  The \change{LSS} effect is therefore unable
 to account for the observed discrepancy of $\sim23$\% by
@@
 resolve the overall systematic shift.
-\change{\citet{Bayliss:2015} find that for Abell 2744 the additional cosmological uncertainty for magnifications $\mu\approx2$ is $<10\%$ which would still leave 6 models discrepant by at least 1.5$\sigma$.}
+\citet{Bayliss:2015} find that for Abell 2744 the additional cosmological uncertainty for magnifications $\mu\approx2$ is $<10\%$ which would still leave 6 models discrepant by at least 1.5$\sigma$.
 
@@
 
-\change{
 \subsubsection{Source Plane Minimization}
 \label{sec:SourcePlaneMinimization}
-}
-
-\change{
+
 A general tendency towards high model magnification can result when
@@
 delensed images of the same source closer together in the source
-plane.  \changeR{Thus, models that are optimized in the source plane may
-have a tendency} toward shallower mass profiles and larger
+plane.  Thus, models that are \change{naively} optimized in the source
+plane will have a tendency toward shallower mass profiles and larger
 magnifications, which force all sources toward the same location in
-the source plane.  }
-
-\change{  There are several strategies for mitigating this well known bias.
+the source plane 
+\change{\citep[see, e.g.,][]{Kochanek:1991a,Kochanek:2006,Jee:2007,Ponente:2011}.}
+
+There are several strategies for mitigating this well known bias.
 Optimizing a model in the image plane can avoid this bias
-entirely \citep{Broadhurst:2005,Zitrin:2009a}.} \changeR{The
+entirely \citep{Broadhurst:2005,Zitrin:2009a}. The
 Sharon(v2), Zitrin-LTM, Zitrin-NFW, and CATS(v2-2.2) models all use
-image plane minimization.}  \change{Alternatively, one may guard against this
+image plane minimization.  Alternatively, one may guard against this
 bias by using a modified source plane minimization that is constrained
 not to generate overly small de-lensed
-sources \citep{Sendra:2014,Diego:2014}.} \changeR{In our test set, this
-second strategy is employed by the Diego model.}  \change{Finally, the
+sources \citep{Sendra:2014,Diego:2014}. In our test set, this
+second strategy is employed by the Diego model. 
+\change{ Similarly, the Williams model uses source plane optimization 
+in the GRALE algorithm, but avoids bias by maximizing the {\it
+fractional} overlap of extended sources plane images.}  Finally, the
 effect of this bias should be reduced when one uses many strong
-lensing constraints over a wide range of redshifts.} \changeR{The
-CATS(v2) and CATS(v2.1) models have the largest number of
-strong-lensing constraints, using 50 and 55 multiply-imaged systems,
-respectively.}
-
-\changeR{ Although many of the tested models utilize these 
-strategies to avoid a source plane minimization bias,
+lensing constraints over a wide range of redshifts. The CATS(v2) and
+CATS(v2.1) models have the largest number of strong-lensing
+constraints, using 50 and 55 multiply-imaged systems, respectively.
+
+Although many of the tested models utilize these 
+strategies to prevent a source plane minimization bias,
 Table~\ref{tab:PredictedMagnifications} and
@@
 deliver more accurate magnification predictions.  The most direct test
-of this is in the Sharon and CATS model series.  In both cases the v1
-model used the faster source plane minimization approach, but the v2
-model was constructed with the more costly image plane minimization.
-Neither of those models show a significant improvement in model
-accuracy from v1 to v2.  T his provides a strong indication that the
-observed tension between models and the SN observation cannot be
-entirely attributed to a bias arising from source plane minimization.}
-
-%\change{
-%\subsection{Best Practices for Magnification Prediction}
-%\label{sec:BestPractices}
-%}
-
-\change{
+of this is in the Sharon and CATS model series.  
+\change{Both of these model series use the LENSTOOL 
+software \citep{Kneib:1996,Jullo:2007,Jullo:2009,Kneib:2011a}, which
+allows a choice of how the minimization is done.  For both the Sharon
+and CATS model sets,} the v1 model used the faster source plane
+minimization approach, but the v2 model was constructed with the more
+costly image plane minimization.  Neither of those models show a
+significant improvement in model accuracy from v1 to v2.  This
+provides a strong indication that the observed tension between models
+and the SN observation cannot be entirely attributed to a bias arising
+from source plane minimization.
+
 \subsection{Quantity and Quality of Strong Lensing Constraints}
 \label{sec:QuantityAndQuality}
-}
-
-\change{
+
 None of the possible errors in lens model inputs described above can
@@
 particularly in regions where strong-lensing constratins may be
-scarce.}
+scarce.
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{FIG/tension}
+\includegraphics[width=\textwidth]{tension}
 \caption{ \label{fig:Nspecz}
@@
 discrepancy between the measured SN magnification and the prediction
-from each lens model. The left panel plots this tension against the
+from each lens model\change{: $(\mu_{\rm model}-\mu_{\rm SN})/(\sigma_{\rm model}^2 + \sigma_{\rm SN}^2)^{1/2}$.}  The left panel plots this tension against the
 total number of multiply imaged systems used, and the right panel
@@
 Figure~\ref{fig:LensingTest}.
-\change{In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the number of strong lensing constraints and the fraction with spectroscopic redshifts changed substantially from one model version to the next.}
-} 
+In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the number of strong lensing constraints and the fraction with spectroscopic redshifts changed substantially from one model version to the next.}
 \end{center}
@@
 
-\change{
 The addition of deeper imaging and new spectroscopic constraints from
@@
 hypothesis by isolating the quantity and quality of strong lensing constraints.
-}
-
-\change{
+
 The left panel plots the tension between each model prediction and the
@@
 fact for both the Lam and CATSv2 model series, we see the tension
-actually {\it increases} for a larger number of strong-lensing constraints.}
-
-\change{
+actually {\it increases} for a larger number of strong-lensing constraints.
+
 In the right panel of Figure~\ref{fig:Nspecz} we examine an
@@
 how stringently the strong-lensing constraints are selected in these
-models.  }
-
-\change{
+models.
+
 The SN \tomas\ comparison therefore supports the notion that the {\it
 quality} of strong-lensing constraints is just as important as the
-{\it quantity}} \changeR{ -- at least for computing magnifications of sources outside the strong-lensing region.
-Once a sufficient number of robust multiply-imaged systems have been included (perhaps $\sim$10) most models will be dominated by systematic uncertainties such as those described in Section~\ref{sec:LensModelErrors}.
-To improve the accuracy of magnification predictions with a large number of strong-lensing constraints, one }
-\change{
-should employ a strict vetting of the multiply-imaged systems.  Each
-system used should ideally have a spectroscopic redshift, or at least
-a very well constrained photometric redshift.  The primary value in
-this strict vetting is to avoid erroneous redshifts being assigned to
-multiply-imaged systems that are unconstrained in redshift space.
-Such redshift errors are especially problematic for relatively low-$z$
-background systems: at lower redshifts the model-derived deflection
-angle and magnification show a more rapid variation with the redshift
-of the background galaxy than for similarly positioned high redshift
-galaxies.}  \changeR{This conclusion should be unsurprising, as for
-example, \citet{Bayliss:2015} have shown that cosmological
-uncertainties are smaller for models that use a large fraction of
-strong-lensing constraints with spectroscopic redshifts,
-and \citet{Johnson:2014} have shown a case study where adding
-spectroscopic redshift information changes the inferred magnification
-by $\sim$10\%.}
+{\it quantity} -- at least for computing magnifications of sources
+outside the strong-lensing region. Once a sufficient number of robust
+multiply-imaged systems have been included (perhaps $\sim$10) most
+models will be dominated by systematic uncertainties such as those
+described in Section~\ref{sec:LensModelErrors}.  To improve the
+accuracy of magnification predictions with a large number of
+strong-lensing constraints, one should employ a strict vetting of the
+multiply-imaged systems.  Each system used should ideally have a
+spectroscopic redshift, or at least a very well constrained
+photometric redshift.  The primary value in this strict vetting is to
+avoid erroneous redshifts being assigned to multiply-imaged systems
+that are unconstrained in redshift space.  Such redshift errors are
+especially problematic for relatively low-$z$ background systems: at
+lower redshifts the model-derived deflection angle and magnification
+show a more rapid variation with the redshift of the background galaxy
+than for similarly positioned high redshift galaxies. This conclusion
+should be unsurprising, as for example, \citet{Bayliss:2015} have
+shown that cosmological uncertainties are smaller for models that use
+a large fraction of strong-lensing constraints with spectroscopic
+redshifts, and \citet{Johnson:2014} have shown a case study where
+adding spectroscopic redshift information changes the inferred
+magnification by $\sim$10\%.
 
@@
 magnification at the time their models were generated.
-
-%\subsubsection{Source Plane Minimization}
-%
-%A third model that stands out for delivering both an accurate and fairly precise estimate of the magnification 
-%
-%
-%
-%
-%\subsubsection{Model Flexibility}
-%
-%Let us first define a successful magnification prediction as one whose
-%quoted uncertainties overlap the measured $\mu=2.03$ from the SN.
-%There are three models that meet this criteria: Williams, Diego, and
-%Lam(v2). All of these are free-form models
 
@@
 
-Turning to the lens models, we have considered 5 ways in which a bias
+Turning to the lens models, we have considered 6 ways in which a bias
 might be introduced into the lens models:
@@
 \begin{enumerate}
-\item Cosmic weak lensing 
+\item \change{Mass profile extrapolation errors}
+\item \change{Large scale structure along the line of sight}
 \item Peculiar mass for a nearby cluster member
@@
 \item Misidentification of a multiple image
-\item \change{Source plane minimization}
+\item Source plane minimization
 \end{enumerate}
@@
 Although each of these could plausibly introduce a small systematic
-bias, we find that none are likely to be significant enough \change{(or
-universal enough)} to completely resolve the tension between models and
+bias, we find that none are likely to be significant enough (or
+universal enough) to completely resolve the tension between models and
 observations.
@@
 the kind of strong lensing constraints that are most likely to deliver
-an accurate magnification prediction for this sight-line. 
- We find
+an accurate magnification prediction for this sight-line.  We find
 that the number of multiply imaged systems used is not in itself
@@
 imaged systems that have spectroscopic redshifts that is most
-correlated with model accuracy.  A reasonable interpretation 
--- at least for this cluster and this particular set of models -- is
-that the spectroscopic redshift fraction serves as an effective proxy
-for the ``quality'' of the strong lensing constraints. This quality of
-the input data appears to be a key ingredient for deriving accurate
+correlated with model accuracy.  A reasonable interpretation -- at
+least for this cluster and this particular set of models -- is that
+the spectroscopic redshift fraction serves as an effective proxy for
+the ``quality'' of the strong lensing constraints. This quality of the
+input data appears to be a key ingredient for deriving accurate
 magnifications outside the strong-lensing regime.
@@
 
-\changeR{
 The general problem of combining predictions from many independent
@@
 model predictions.  Such model averaging will not, however, resolve a
-{\it systematic} bias that is shared by many models.}
+{\it systematic} bias that is shared by many models.
 
@@
 
-\bibliographystyle{apj}
-\bibliography{bibdesk}
-
-%\input{TABLE/magnifications}
+\input{snTomas.bbl}
+
+%\bibliographystyle{apj}
+%\bibliography{bibdesk}
+
 \end{document}

### 2015-08-10 APJ.submitted/snTomas.tex
Small corrections noted by SWJ

@@
 (\Ho=71.6, \Om=0.27, \OL=0.73) would give a predicted distance modulus
-$dm_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
+${\rm dm}_{\Lambda CDM}=44.90$ and a measured magnification $\mu=1.9$.
 Substituting alternative cosmological
@@
 \smallskip
-\change{{\it (2) Strong vs. Strong+Weak':}}
+\change{{\it (2) Strong vs. Strong+Weak:}}
 \change{Thirteen of the mass models evaluated here are constrained only using
@@
 This work is dedicated to our colleague and friend Tomas Dahlen, for
-whom this supernova has been named in memorium. He is dearly missed.
+whom this supernova has been named in memoriam. He is dearly missed.
 

### 2015-08-10 APJ.submitted/lensmodels.tex
small formatting correction in Table 5 via JH

@@
 CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
-\change{CATS(v1.1)}      & \nodata  & 2.62  &   2.44$-$2.80 \\
+CATS(v1.1)      & \nodata  & 2.62  &   2.44$-$2.80 \\
 Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\

### 2015-08-11 APJ.submitted/snTomas.tex
Added a paragraph on flexion

@@
 
-\change{ One would expect that models incorporating weak-lensing
+\change{ One might expect that models incorporating weak-lensing
 constraints would be less susceptible to such bias from a sharply
@@
 Figure~\ref{fig:LensingTest}) exhibit the same propensity to
-overestimate the magnification along this line of sight.  Thus, an
-error in extrapolating the mass profile outside the strong lensing
-region is not a likely explanation for the observed small systematic
-bias.}
+overestimate the magnification along this line of sight.  This
+comparison therefore provides no evidence to support the extrapolation
+error hypothesis. }
 
@@
 
+\change{Given the intermediate location of this SN, caught between the
+strong-lensing and weak-lensing regimes, an even more useful tool than
+weak lensing would be the {\it flexion}
+signal \citep{Goldberg:2002,Goldberg:2005,Irwin:2006,Goldberg:2007}.
+Flexion is a second-order lensing effect that distorts the shapes of
+background galaxies that are not lensed strongly enough to be warped
+into arcs or filaments.  A flexion measurement near the SN \tomas\
+sight line would be more sensitive to local gradients and substructure
+in the cluster mass profile.  However, no such flexion constraints are
+yet available.}
+
 \change{\subsubsection{Line of Sight Structure}}
@@
 cumulative weak lensing effects due to uncorrelated large scale
-structure (LSS) along the line of sight, sometimes called ``Cosmic Weak
+structure (LSS) along the line of sight, sometimes called ``Cosmic
+Weak
 Lensing'' \citep{Wong:2011,Host:2012,Collett:2013,Greene:2013,Bayliss:2014,McCully:2014,DAloisio:2014}.
-This \change{LSS} effect is most important for very high redshift sources
-($z>5$), which have a much longer path length over which to encounter
-large scale structure and for highly magnified sources very near to
-the cluster lensing critical curve (because \change{LSS} can perturb the
-position of the critical curve).  For SN \tomas\ at the modest
-redshift of $z=1.35$ and far from the critical curve, \change{LSS} should
-increase the scatter in the lensing magnification at a level much less
-than 10\% \citep{DAloisio:2014}.  The \change{LSS} effect is therefore unable
-to account for the observed discrepancy of $\sim23$\% by
-itself.
-
-In
-addition, some sources of uncertainty are taken into account only by a
+This \change{LSS} effect is most important for very high redshift
+sources ($z>5$), which have a much longer path length over which to
+encounter large scale structure and for highly magnified sources very
+near to the cluster lensing critical curve (because \change{LSS} can
+perturb the position of the critical curve).  For SN \tomas\ at the
+modest redshift of $z=1.35$ and far from the critical
+curve, \change{LSS} should increase the scatter in the lensing
+magnification at a level much less than 10\% \citep{DAloisio:2014}.
+The \change{LSS} effect is therefore unable to account for the
+observed discrepancy of $\sim23$\% by itself.
+
+In addition, some sources of uncertainty are taken into account only by a
 subset of models. For example, the Willams model (using GRALE;
@@
 between the observed \SNIa\ magnifications and the predictions from
-lens models (\citetalias{Patel:2014}; \citealt{Nordin:2014}), albeit
+lens models (\P14; \citealt{Nordin:2014}), albeit
 with a much smaller set of lens models being tested.  The observed
@@
 {\it systematic} bias that is shared by many models.
+
+\subsection{Future Work}
 

### 2015-08-11 APJ.submitted/snTomas.tex
Modified source plane minimization discussion

@@
 and highly magnified arcs.  There are now $\sim$150 known lensed
-images behind Abell 2744 \citep{Jauzac:2014c}, but SN \tomas\ is
+images behind Abell 2744 \citep{Jauzac:2015b}, but SN \tomas\ is
 located several arcseconds outside the core region of the cluster
@@
 \subsubsection{Misidentification of a multiple image}
-\citet{Jauzac:2014c} proposed a correction
+\citet{Jauzac:2015b} proposed a correction
 for the location of image 3.3, the third component of a triply-imaged
@@
 SN \tomas\ \citep[see][for a quantitative discussion of this
-effect]{Johnson:2014}.  However, \citet{Jauzac:2014c} also evaluated a
+effect]{Johnson:2014}.  However, \citet{Jauzac:2015b} also evaluated a
 version of the CATS(v2) model in which this single source is left in
@@
 Optimizing a model in the image plane can avoid this bias
-entirely \citep{Broadhurst:2005,Zitrin:2009a}. The
-Sharon(v2), Zitrin-LTM, Zitrin-NFW, and CATS(v2-2.2) models all use
-image plane minimization.  Alternatively, one may guard against this
-bias by using a modified source plane minimization that is constrained
-not to generate overly small de-lensed
-sources \citep{Sendra:2014,Diego:2014}. In our test set, this
-second strategy is employed by the Diego model. 
-\change{ Similarly, the Williams model uses source plane optimization 
-in the GRALE algorithm, but avoids bias by maximizing the {\it
-fractional} overlap of extended sources plane images.}  Finally, the
-effect of this bias should be reduced when one uses many strong
-lensing constraints over a wide range of redshifts. The CATS(v2) and
-CATS(v2.1) models have the largest number of strong-lensing
-constraints, using 50 and 55 multiply-imaged systems, respectively.
-
-Although many of the tested models utilize these 
+entirely \citep{Broadhurst:2005,Zitrin:2009a}. The Sharon(v2),
+Zitrin-LTM, Zitrin-NFW, and CATS(v1,v2-2.2) models all use image plane
+minimization.  Alternatively, one may guard against this bias by using
+a modified source plane minimization that is constrained not to
+generate overly small de-lensed
+sources \citep{Sendra:2014,Diego:2014}. In our test set, a version of
+this second strategy is employed by the \change{GLAFIC, Williams, and
+Diego} models.  \change{For example, the Williams model uses source
+plane optimization in the GRALE algorithm, but avoids bias by
+maximizing the {\it fractional} overlap of extended source plane
+images.}  Finally, the effect of this bias should be reduced when one
+uses many strong lensing constraints over a wide range of
+redshifts. The CATS(v2) and CATS(v2.1) models have the largest number
+of strong-lensing constraints, using 50 and 55 multiply-imaged
+systems, respectively.
+
+Although most of the tested models utilize one of these 
 strategies to prevent a source plane minimization bias,
@@
 software \citep{Kneib:1996,Jullo:2007,Jullo:2009,Kneib:2011a}, which
-allows a choice of how the minimization is done.  For both the Sharon
-and CATS model sets,} the v1 model used the faster source plane
-minimization approach, but the v2 model was constructed with the more
-costly image plane minimization.  Neither of those models show a
-significant improvement in model accuracy from v1 to v2.  This
-provides a strong indication that the observed tension between models
-and the SN observation cannot be entirely attributed to a bias arising
-from source plane minimization.
+allows a choice of how the minimization is done.  For the Sharon
+series, the v1 model used the faster source plane minimization
+approach, but the v2 model was constructed with the more accurate
+image plane minimization.  The CATS v1, 2, 2.1, and 2.2 models all
+used image plane optimization, while the v1.1 employed source plane
+optimization (and also added in weak lensing constraints).  In neither
+of these model series do we see a uniform improvement in accuracy when
+optimization is done in the image plane.  This test strongly suggests
+that the observed tension between the lens models and the SN
+observation cannot be entirely attributed to a bias arising from
+source plane minimization.}
 
@@
 
-\input{snTomas.bbl}
-
-%\bibliographystyle{apj}
-%\bibliography{bibdesk}
+%\input{snTomas.bbl}
+
+\bibliographystyle{apj}
+\bibliography{bibdesk}
 

### 2016-04-07 APJ.accepted/response.txt
updated files for accepted version

2015.08.10 
Author's Response to Referee Report

Dear Editors, 
 The referee provided a very positive and helpful report with only minor changes required.  Below, we provide the referee's comments (REF) and our responses (SR).   The re-submitted manuscript highlights all additions or changes with blue text.  Thank you for your attention to this paper, and please let us know if anything else is needed.

Sincerely,
Steve Rodney and co-authors

REF:   This paper reports the discovery of a type Ia supernova behind one of the HFF clusters, and uses its measured magnification to test cluster mass models. The discovery is definitely important, and this indeed provides quite a rare opportunity to do a blind test of many mass models constructed by different groups. The analysis is conducted very carefully to get convincing results, and the results are also presented very well. This paper clearly deserves publication in ApJ. I only have a few minor comments which I think are straightforward to address.

-----------------

REF:   1. HFF14Tom is located outside the strong lensing region, so naive expectation is that adding weak lensing constraints more or less reduces the potential bias in predicting its magnification. I'm sure the authors are aware of this, as they use different symbols for methods combining strong and weak lensing in e.g., Figure 6, but there is virtually no discussion about the role of weak lensing in the text. The SN region can at least be probed well by HST weak lensing. Even ground based weak lensing can get reasonable constraints on enclosed mass within 1 arcmin radius or so if the SN is high. On the other hand, looking at Figure 6 it is not clear if methods using weak lensing are better than strong lensing only methods. In particular CATS v1.1 is worse than CATS v1, which looks a bit strange given that their difference come from weak lensing constraints. Anyways, I think it's worth adding a paragraph or two to discuss effects of weak lensing constraints. I'm interested in the authors' opinion about this.   Also please describe (e.g., in Table 4) which weak lensing data each method used.

SR: A discussion of strong vs strong+weak lensing has been added to section 7 when first introducing the models.  Additionally, a new subsection (7.2.1) discusses how weak lensing could possibly avoid a particular extrapolation bias, but we conclude that there is no evidence for such a bias in this case.   Also, Table 4 has been updated with new table notes indicating the weak lensing data used.

-----------------

REF:  2. Sec. 7.2.5: Are there any good references for the discussion in the first paragraph? I see the point that the source plane minimization prefers high magnification solutions, but this is the case only when distances in the source plane (I mean the distances between average source position and source positions computed from individual image positions) are naively minimized. In fact one can convert these distances to corresponding image plane distances using magnifications (or more rigorously the Jacobian matrix), and once these corrections are applied this bias can easily be avoided. I know several methods (such as LENSTOOL, GLAFIC, ...) already implement this, although some details look different between different codes. It may be worth studying further which models are possibly affected by this source plane minimization bias.

SR:  We have updated this section (now 7.2.6) with some additional references, and clarifying text.   The Kochanek 1991 and Kochanek 2006 references provide a more general discussion of the issues of source plane vs image plane minimization.  Jee et al 2007 and Ponente & Diego 2011 include sections dealing more specifically with the bias toward high magnification.

-----------------

REF:  3. Figure 8 is nice, but it's a bit unclear what the y-axis means. It takes negative values, so it should be something like (\mu_model-\mu_SN)/\sigma, but \sigma here includes only the measurement error on the magnification from HFF14Tom, or does it also include model errors listed in Table 5? If so those errors are quadratically added?

SR:  Yes.  The referee is precisely correct on all counts.  This has been added in the figure caption.

-----------------

REF:  4. Sec. 5: ``we do not include any prior on...' Do you mean by flat prior?

SR:  Yes.  The text has been updated.

-----------------

REF:  5. Sec. 5: ``... the host galaxy photo-z and spectroscopic redshift (Section 2 and 4.2)'. I believe it is Section 3 not Section 2. In the caption of Figure 3 ``consistent with both the photo-z of the probable...' it should be spectroscopic redshift rather than photo-z.

SR: These corrections have been made.    We have also made a few other small corrections in the text that were not noted by the referee.  These are also highlighted in blue text in the revised manuscript.

### 2016-04-07 APJ.accepted/authors.tex
updated files for accepted version

--- 2015-05-17 authors.tex
@@
 % --------------------------------------------------
+\newcommand{\USC}{Department of Physics and Astronomy, University of South Carolina, 712 Main St., Columbia, SC 29208, USA}
 \newcommand{\HubbleFellow}{Hubble Fellow}
@@
 \newcommand{\Chicago}{Department of Physics, The University of Chicago, Chicago, IL 60637, USA}
+\newcommand{\Kavli}{Kavli Institute for Cosmological Physics, University of Chicago, 5640 South Ellis Avenue Chicago, IL 60637}
 \newcommand{\Berkeley}{Department of Astronomy, University of California, Berkeley, CA 94720-3411, USA}
@@
 \newcommand{\Packard}{Packard Fellow}
-\newcommand{\CalTech}{California Institute of Technology, 1200 East California Boulevard, Pasadena, CA 91125}
+\newcommand{\CalTech}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, MC 249-17, Pasadena, CA 91125, USA}
 \newcommand{\Durham}{Institute for Computational Cosmology, Durham University, South Road, Durham DH1 3LE, UK}
@@
 
-\author{Steven~A.~Rodney\altaffilmark{\affilref{JHU},\affilref{HubbleFellow}}}
+\author{Steven~A.~Rodney\altaffilmark{\affilref{USC},\affilref{JHU},\affilref{HubbleFellow}}}
+\affilreftxt{USC}{\USC}
 \affilreftxt{JHU}{\JHU}
 \affilreftxt{HubbleFellow}{\HubbleFellow}
+\email{srodney@sc.edu}
 
@@
 
-\author{Daniel~Scolnic\altaffilmark{\affilref{Chicago}}}
-\affilreftxt{Chicago}{\Chicago}
+\author{Daniel~Scolnic\altaffilmark{\affilref{Kavli}}}
+\affilreftxt{Kavli}{\Kavli}
 
@@
 
+\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
+\affilreftxt{Durham}{\Durham}
+\affilreftxt{KwaZulu}{\KwaZulu}
+
 \author{Maru\v{s}a Brada\v{c}\altaffilmark{\affilref{UCDavis}}}
@@
 \affilreftxt{Basque}{\Basque}
+
+\author{Dan Coe\altaffilmark{\affilref{STScI}}}
+\affilreftxt{STScI}{\STScI}
 
@@
 
-\author{Mathilde Jauzac\altaffilmark{\affilref{Durham},\affilref{KwaZulu}}}
-\affilreftxt{Durham}{\Durham}
-\affilreftxt{KwaZulu}{\KwaZulu}
-
 \author{Saurabh W.~Jha\altaffilmark{\affilref{Rutgers}}}
 \affilreftxt{Rutgers}{\Rutgers}
+
+\author{Traci L.~Johnson\altaffilmark{\affilref{Michigan}}}
+\affilreftxt{Michigan}{\Michigan}
 
@@
 
+\author{Xin Wang\altaffilmark{\affilref{UCSB}}}
+\affilreftxt{UCSB}{\UCSB}
+
 \author{Liliya~L.~R.~Williams\altaffilmark{\affilref{Minnesota}}}

### 2016-04-07 APJ.accepted/lensmodels.tex
updated files for accepted version

--- 2015-08-10 APJ.submitted/lensmodels.tex
@@
 \cutinhead{Post-HFF models : include data from the HFF program}\\
-CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
+CATS(v2)       & 50 & 151 & 4 & 1  &  \citealt{Jauzac:2015b} & Updated version of the CATSv1 model, adds 33 new multiply-imaged galaxies, for a total of 159 individual lensed images.\\
 Diego\tablenotemark{m} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & {\tt WSLAP+}\tablenotemark{n} : Free-form strong-lensing model using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
@@
 Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{p} models for galaxy mass.\\
-CATS(v2.1)     & 55 & 154 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for Bradac(v2).\\
-CATS(v2.2)     & 25 &  72 & 8 & 1  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for Bradac(v2).
+CATS(v2.1)     & 55 & 154 & 8 & 1  &  \citealt{Jauzac:2015b} & Updated version of the CATSv2 model, adopting the spec-z constraints used for Bradac(v2).\\
+CATS(v2.2)     & 25 &  72 & 8 & 1  &  \citealt{Jauzac:2015b} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for Bradac(v2).
 \enddata

### 2016-04-07 APJ.accepted/snTomas.tex
updated files for accepted version

--- 2015-08-11 APJ.submitted/snTomas.tex
@@
 %  PREAMBLE: sets up compiler modes, loads packages, defines macros, etc
+%  Steve Rodney, 2012
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{preamble}
+%%%%%%%%%%%%%%%%%%%%
+% COMPILER MODES
+%%%%%%%%%%%%%%%%%%%%
+
+%% Set default compiler modes 
+%% (these will be overridden by the -options.tex  file below, if it exists)
+
+% Changetext mode : highlight modified text in bold blue font
+\newif{\ifchangetext}
+%\changetexttrue
+\changetextfalse
+
+\documentclass[iop]{emulateapj}
+\citestyle{aa}
+
+%%%%%%%%%%%%%%%%%%%%
+% PACKAGES INCLUDED
+%%%%%%%%%%%%%%%%%%%%
+\usepackage{ifthen}
+\usepackage{natbib}   % reference citations and bibliography
+\usepackage{amsmath}  % extended math symbols
+\usepackage{hyperref}      % url text formatting
+\usepackage[usenames,dvipsnames]{xcolor}  % colored text
+%\usepackage{pdflscape}
+
+%\usepackage{amssymb}  % extended symbols lib
+%\usepackage{verbatim} % verbatim text formatting
+%\usepackage{enumerate}% enumerated lists
+%\usepackage{url}      % url text formatting
+%\usepackage{multirow}  % muti-row table cells
+%\usepackage{amsmath}  % extended equations lib (split)
+%\usepackage{mathrsfs} % extended math fonts (mathscr)
+%\usepackage{paralist} % inline enumeration (for Table ref lists)
+%\usepackage{authblk}
+%\usepackage{appendix}
+%\usepackage{array}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% changetext  mode settings
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ifchangetext
+  % Changed text is highlighted in bold, blue font 
+  \newcommand{\change}[1]{{ \textcolor{blue}{#1}}}
+  \newcommand{\changenote}[1]{{ \textcolor{blue}{#1}}}
+  \newcommand{\changeB}[1]{{ \textcolor{blue}{#1}}}
+  \newcommand{\changeG}[1]{{ \textcolor{ForestGreen}{#1}}}
+  \newcommand{\changeR}[1]{{ \textcolor{red}{#1}}}
+  \newcommand{\changeP}[1]{{ \textcolor{DarkOrchid}{#1}}}
+\else
+  % Changed text is indistinguishable
+  \newcommand{\change}[1]{#1}
+  \newcommand{\changeB}[1]{#1}
+  \newcommand{\changeG}[1]{#1}
+  \newcommand{\changeR}[1]{#1}
+  \newcommand{\changeP}[1]{#1}
+  \newcommand{\changenote}[1]{}
+\fi
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% PDF mode settings : Auto-select eps or pdf figures 
+% based  on the compiler used (i.e. latex vs pdflatex)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AUTHOR-DEFINED MACROS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Paper aliases 
+\defcitealias{Patel:2014}{P14}
+\def\P14{\citetalias{Patel:2014}}
+
+\def\tomas{HFF14Tom}
+
+% Cosmology:
+\def\Om{\ensuremath{\Omega_{\rm m}}}
+\def\Ot{\ensuremath{\Omega_{\rm tot}}}
+\def\Ob{\ensuremath{\Omega_{\rm b}}}
+\def\OL{\ensuremath{\Omega_{\Lambda}}}
+\def\Ok{\ensuremath{\Omega_{\rm k}}}
+\def\om{\ensuremath{\omega_{\rm m}}}
+\def\ob{\ensuremath{\omega_{\rm b}}}
+\def\wo{\ensuremath{w_0}}
+\def\wa{\ensuremath{w_{\rm a}}}
+\def\lcdm{$\Lambda$CDM}
+\def\LCDM{$\Lambda$CDM}
+\def\wcdm{$w$CDM}
+\def\Ho{\ensuremath{H_0}}
+\def\DA{\ensuremath{D_A}}
+\def\DL{\ensuremath{D_L}}
+
+% Astronomy:
+\def\arcsec{\ensuremath{^{\prime\prime}}} 
+\def\kms{\ensuremath{{\rm km s}^{-1}}}
+\def\hgpcq{\mbox{$h^{-3}$Gpc$^3$}}
+\def\hmpcq{\mbox{$h^{-3}$Mpc$^3$}}
+\def\perhmpcq{\mbox{$h^{3}$Mpc$^{-3}$}}
+\def\hmpc{\mbox{$h^{-1}$Mpc}}
+\def\hmpci{\mbox{$h$\,Mpc$^{-1}$}}
+\def\mpc{\mbox{Mpc}}
+\def\mpci{\mbox{Mpc$^{-1}$}}
+\def\mpcq{\mbox{Mpc$^{-3}$}}
+\def\Msun{\mbox{M$_{\odot}$}}
+\def\Av{\mbox{$A_V$}}
+\def\Rv{\mbox{$R_V$}}
+
+% Supernovae : 
+\newcommand{\CCSN}{core collapse SN}
+\newcommand{\CCSNe}{core collapse SNe}
+\newcommand{\SNIa}{Type Ia SN}
+\newcommand{\SNeIa}{Type Ia SNe}
+\newcommand{\SNRz}{SNR($z$)}
+\def\Mch{\mbox{M$_{\rm Ch}$}}
+\def\Ni{\ensuremath{^{56}\mbox{Ni}}}
+\newcommand{\dmfifteen}{\ensuremath{\Delta\mbox{m}_{15}}}
+\newcommand{\deltamfifteen}{\ensuremath{\Delta\mbox{m}_{15}}}
+
+% Missions:
+\def\HST{{\it HST}}
+\def\Hubble{{\it Hubble}}
+\def\Hubbles{{\it Hubble's}}
+\def\Spitzer{{\it Spitzer}}
+\def\Chandra{{\it Chandra}}
+\def\Herschel{{\it Herschel}}
+\def\XMM{{\it XMM}}
 
@@
 weak-lensing constraints are unavailable. Moreover, given
-enough time, multiple background SNe Ia could be measured behind the
+enough time, multiple background \SNeIa\ could be measured behind the
 same cluster, each providing a new magnification constraint.
@@
 \begin{center}
-%\includegraphics[width=\textwidth]{discovery_image}
-\includegraphics[width=\textwidth]{discovery_image_lowres}
+%\includegraphics[width=\textwidth]{discovery_image_lowres}
+\includegraphics[width=\textwidth]{discovery_image_medres}
+%\includegraphics[width=\textwidth]{discovery_image_highres}
 \caption{  \label{fig:DiscoveryImage} 
@@
 near maximum light, although it is also prominent in the spectra of
-Type Ib and Ic core collapse SNe (\CCSNe).  The red color of
+Type Ib and Ic \CCSNe.  The red color of
 the \tomas\ SED is qualitatively consistent with a redshift of $z>1$

### 2016-04-07 snTomasCode/lensing_test_fig.py

@@ -298,3 +298,185 @@ def mkTensionFig(presfig=False, showlegend=True, showlines=True):
 
     pl.draw()
 
+
+
+def mkLensingTestFig_simplified( show2snfits=False, showlegend=False,
+                                 presfig=False, labelvalues=False ):
+    from matplotlib import pyplot as pl
+    from matplotlib.patches import FancyArrowPatch
+    from pytools import plotsetup, colorpalette as cp
+    from astropy.io import ascii
+    import os
+    import sys
+
+    muSNmlcs = 2.03
+    muSNmlcserr = 0.29
+    muSNsalt = 1.99
+    muSNsalterr = 0.38
+
+    if presfig :
+        fig = plotsetup.presfig( figsize=[8,12])
+        pl.clf()
+        ax1 = pl.axes( [0.01,0.14,0.67,0.83] )
+        ms=15
+    else :
+        fig = plotsetup.fullpaperfig( figsize=[4,4])
+        ms=8
+        pl.clf()
+        if showlegend:
+            ax1 = pl.axes( [0.01,0.14,0.68,0.84] )
+        else:
+            ax1 = pl.axes( [0.03,0.14,0.92,0.80] )
+
+    thisfile = sys.argv[0]
+    if 'ipython' in thisfile :
+        thisfile = __file__
+    thisdir = os.path.dirname( os.path.abspath(thisfile))
+
+    lensdatfile = os.path.join(thisdir,'data/lensing/lensing_medians_simplified.dat')
+    lensingdat = ascii.read( lensdatfile, format='commented_header',
+                             header_start=-1, data_start=0 )
+
+    ytop=len(lensingdat['med'])+1
+    y = ytop
+
+    for row in lensingdat:
+        y-=1
+        # color = row['parametric'] and 'k' or 'g'
+        #mfc = row['postFF'] and color or 'w'
+        color = 'k' # row['postFF'] and 'g' or 'k'
+        mfc = row['parametric'] and color or 'w'
+        model = row['model']
+        best = row['best']
+        med = row['med']
+        errplus = row['med+']-med
+        errminus = row['med-']-med
+        mec=color
+        mew=ms/8.
+
+        disc = (med-muSNmlcs)/np.sqrt(errminus**2+muSNmlcserr**2)
+
+        if disc<1:
+            mfc='forestgreen'
+            marker='D'
[…]

### 2016-04-07 snTomasCode/lensing_test_fig.py
cleaned up the new function for making a simplified figure showing the SNTomas lensing test

@@ -300,10 +300,16 @@ def mkTensionFig(presfig=False, showlegend=True, showlines=True):
 
 
 
-def mkLensingTestFig_simplified( show2snfits=False, showlegend=False,
-                                 presfig=False, labelvalues=False ):
+def mkLensingTestFig_simplified():
+    """ Make a simplified version of the lensing test figure,
+    for use in proposals, presentations and the like
+    :param show2snfits:
+    :param showlegend:
+    :param presfig:
+    :param labelvalues:
+    :return:
+    """
     from matplotlib import pyplot as pl
-    from matplotlib.patches import FancyArrowPatch
     from pytools import plotsetup, colorpalette as cp
     from astropy.io import ascii
     import os
@@ -314,19 +320,10 @@ def mkLensingTestFig_simplified( show2snfits=False, showlegend=False,
     muSNsalt = 1.99
     muSNsalterr = 0.38
 
-    if presfig :
-        fig = plotsetup.presfig( figsize=[8,12])
-        pl.clf()
-        ax1 = pl.axes( [0.01,0.14,0.67,0.83] )
-        ms=15
-    else :
-        fig = plotsetup.fullpaperfig( figsize=[4,4])
-        ms=8
-        pl.clf()
-        if showlegend:
-            ax1 = pl.axes( [0.01,0.14,0.68,0.84] )
-        else:
-            ax1 = pl.axes( [0.03,0.14,0.92,0.80] )
+    fig = plotsetup.fullpaperfig( figsize=[4,4])
+    ms=8
+    pl.clf()
+    ax1 = pl.axes( [0.03,0.14,0.92,0.80] )
 
     thisfile = sys.argv[0]
     if 'ipython' in thisfile :
@@ -342,20 +339,14 @@ def mkLensingTestFig_simplified( show2snfits=False, showlegend=False,
 
     for row in lensingdat:
         y-=1
-        # color = row['parametric'] and 'k' or 'g'
-        #mfc = row['postFF'] and color or 'w'
-        color = 'k' # row['postFF'] and 'g' or 'k'
-        mfc = row['parametric'] and color or 'w'
         model = row['model']
-        best = row['best']
         med = row['med']
         errplus = row['med+']-med
         errminus = row['med-']-med
-        mec=color
+        mec='k'
[…]
